### 2016-08-12 manuscript.tex
Creating IJCAS paper. Have to modify all the subcaption commands to use an obsolete package (subfigure) since their template is old and useless.

\documentclass[fleqn]{IJCAS}  % Comment this line out if you need a4paper
\usepackage{ijcas_packages}

% NEED TO CHANGE ALL SUBFIGURES TO USE THE OBSOLETE SUBFIGURE PACKAGE

http://tug.ctan.org/obsolete/macros/latex/contrib/subfigure/subfigure.pdf
http://tex.stackexchange.com/questions/313249/confict-between-the-subfigure-and-customized-captionside-by-side-subfigures

\newcommand{\squeezeup}{\vspace{-2.5mm}}

\newcommand{\EditTL}[1]{{\color{red}\protect #1}}
%\renewcommand{\EditTL}[1]{{\protect #1}}

%%%% Editorial Information
%% Authors do not have to modify this section.
\journalvolumn{VV}
\journalnumber{N}
\journalyear{YYYY}
\setarticlestartpagenumber{1}
%%%% End of Editorial Information

\newtheorem{definition}{Definition}
\newtheorem{lem}{Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{cor}{Corollary}
\newtheorem{remark}{Remark}

\begin{document}
\title{\LARGE \bf
Geometric Adaptive Control of Attitude Dynamics on \(\SO\)\\ with State Inequality Constraints}

\author{Shankar Kulumani, Christopher Poole, and Taeyoung Lee}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
This paper presents a new geometric adaptive control system with state inequality constraints for the attitude dynamics of a rigid body. 
The control system is designed such that the desired attitude is asymptotically stabilized, while the controlled attitude trajectory avoids undesired regions defined by an inequality constraint. 
In addition, we develop an adaptive update law that enables attitude stabilization in the presence of unknown disturbances. 
The attitude dynamics and the proposed control systems are developed on the special orthogonal group such that singularities and ambiguities of other attitude parameterizations, such as Euler angles and quaternions are completely avoided. 
The effectiveness of the proposed control system is demonstrated through numerical simulations and experimental results.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{keywords}
attitude control, asymptotic stability, special orthogonal group, constraint
%At least four key words or phrases in alphabetical order, separated by commas.
\end{keywords}

\maketitle % \maketitle command must come here after ABSTRACT and KEYWORDS environments

\makeAuthorInformation{
Manuscript received January 20, 2015; revised February 10,2015; accepted March 10, 2015. Recommended by Associate Editor Soon-Shin Lee under the direction of Editor Milton John.
Shankar Kulumani, Christopher Poole, Taeyoung Lee, Mechanical and Aerospace Engineering, George Washington University, Washington DC 20052 {\tt \{skulumani,poolec,tylee\}@gwu.edu}

This research has been supported in part by NSF under the grants CMMI-1243000, CMMI-1335008, and CNS-1337722.
* Corresponding author.\vskip 0.5pc
}

\runningtitle{1}{Gil-Dong Hong, Adam Smith, and Ikuro Mizumoto}{Manuscript Template for the International Journal of Control, Automation, and Systems: ICROS {\&} KIEE}

\begin{multicols}{2}
\section{Introduction}\label{sec:intro}

Rigid body attitude control is an important problem for aerospace vehicles, ground and underwater vehicles, as well as robotic systems~\cite{hughes2004,wertz1978}.
One distinctive feature of the attitude dynamics of rigid bodies is that it evolves on a nonlinear manifold.
The three-dimensional special orthogonal group, or \( \SO \), is the set of \( 3 \times 3 \) orthogonal matrices whose determinant is one.
This configuration space is non-Euclidean and yields unique stability properties which are not observable on a linear space.
For example, it is impossible to achieve global attitude stabilization using continuous time-invariant feedback~\cite{bhat2000}.

% topological obstruction - smooth control system can only achieve almost global asymptotic stability

% discuss issues with parameterizations

Attitude control is typically studied using a variety of attitude parameterizations, such as Euler angles or quaternions~\cite{shuster1993}.
All attitude parameterizations fail to represent the nonlinear configuration space both globally and uniquely~\cite{chaturvedi2011a}.
For example, minimal attitude representations, such as Euler angle sequences or modified Rodriguez parameters, suffer from singularities.
These attitude representations are not suitable for large angular slews.
%In order to avoid singularities, the designer must carefully switch the chosen Euler angle sequence based on the operating region.
%Another option is to artificially limit the operating region of the rigid body.
%This ensures the system operates in a region free from singularities but limits the performance capabilities and ability to perform arbitrarily large angular maneuvers.
Quaternions do not have singularities but they double cover the special orthogonal group.
As a result, any physical attitude is represented by a pair of antipodal quaternions on the three-sphere.
%An immediate implication of this ambiguity is that closed-loop stability properties derived using quaternions may not hold for the physical rigid body evolving on the special orthogonal group.
During implementation, the designer must carefully resolve this non-unique representation in quaternion based attitude control systems to avoid undesirable unwinding behavior~\cite{bhat2000}.
%, where the rigid body starts close to the desired attitude, yet the system unnecessarily rotates through a large angle even while the initial error is small.

% introduce concept of state inequality constraints and how it creates a nonconvex region 
% mention applicability of this for spacecraft maneuvers, spherical air bearing testing, hardware limitations
Many physical rigid body systems must perform large angular slews in the presence of state constraints.
For example, autonomous spacecraft or aerial systems are typically equipped with sensitive optical payloads, such as infrared or interferometric sensors.
These systems require retargeting while avoiding direct exposure to sunlight or other bright objects.
%Determining a satisfactory attitude control maneuver in the presence of state constraints is a challenging task.
The removal of constrained regions from the rotational configuration space results in a \textit{nonconvex} region.
The attitude control problem in the absence of constraints has been extensively studied~\cite{bullo2004,MayTeePaCC11,LEEITAC15}.
However, the attitude control problem in the presence of constraints has received much less attention.

% discuss how previous papers (mcinnes and lee/meshabi) have short comings
Several approaches have been developed to treat the attitude control problem in the presence of constraints.
A conceptually straightforward approach is used in~\cite{hablani1999} to determine feasible attitude trajectories prior to implementation.
The algorithm determines an intermediate point such that an unconstrained maneuver can be calculated for each subsegment.
Typically, an optimal or easily implementable on-board control scheme for attitude maneuvers is applied to maneuver the vehicle along these segments.
In this manner it is possible to accomplish constraint avoidance by linking several intermediary unconstrained maneuvers.
While this method is conceptually simple, it is difficult to generalize for an arbitrary number of constraints.
In addition, this approach is only applicable to problems where the selection of intermediate points are computationally feasible.

The approach in~\cite{frazzoli2001} involves the use of randomized motion planning algorithms to solve the constrained attitude control problem.
A graph is generated consisting of vertices from an initial attitude to a desired attitude. 
A random iterative search is conducted to determine a path through a directed graph such that a given cost functional is minimized.
The random search approach can only stochastically guarantee attitude convergence as it can be shown that as the number of vertices in the graph grow, the probability of nonconvergence goes to zero.
However, the computational demand grows as the size of the graph is increased. 
As a result, random search approaches are ill-suited to on-board implementation or in scenarios that require agile maneuvers.

Model predictive control for spacecraft attitude dynamics is studied in~\cite{guiggiani2014,kalabic2014,gupta2015}.
These methods rely on linear or non-linear state dynamics to repeatedly solve a finite-time optimal control problem.
As a result, model predictive control methods are also computational expensive and apply direct optimization methods to solve the necessary conditions for optimality.
Therefore these methods are complicated to implement and not applicable for real-time control applications.

% Previous potential function approach - developed using att parameterizations - singularities/ambiguities
Artificial potential functions are commonly used to handle kinematic constraints for a wide range of problems in robotics~\cite{rimon1992}.
The goal is the design of attractive and repulsive terms which drive the system toward or away from a certain state, respectively.
%The goal is the design of an attractive function which drives the system towards the desired state.
%Similarly, a repulsive function is constructed such that the system is directed away from the constraints. 
The superposition of the these functions allows one to apply standard feedback control schemes for stabilization and tracking.
More specifically, artificial potential functions have previously been applied to the spacecraft attitude control problem in~\cite{lee2011b,mcinnes1994}.
However, both of these approaches were developed using attitude parameterizations, namely Euler angles and quaternions, and as such, they are limited by the singularities of minimal representations or the ambiguity of quaternions.

This paper is focused on developing an adaptive attitude control scheme in the presence of attitude inequality constraints on \(\SO\).
We apply a potential function based approach developed directly on the nonlinear manifold \(\SO\). 
By characterizing the attitude both globally and uniquely on \(\SO\), our approach avoids the issues of attitude parameterizations, such as kinematic singularities and ambiguities, and is geometrically exact. 
A configuration error function on \(\SO\) with a logarithmic barrier function is proposed to avoid constrained regions. 
Instead of calculating a priori trajectories, as in the geometric and randomized approaches, our approach results in a closed-loop attitude control system. 
This makes it ideal for on-board implementation on UAV or spacecraft systems. 
In addition, unlike previous approaches our control system can handle an arbitrary number of constrained regions without modification.

Furthermore, we formulate an adaptive update law to enable attitude convergence in the presence of uncertain disturbances. 
The stability of the proposed control systems is verified via mathematically rigorous Lyapunov analysis on $\SO$.  
In short, the proposed attitude control system in the presence of inequality constraints is computationally efficient and able to handle uncertain disturbances. 
The effectiveness of this approach is illustrated via numerical simulation and experimental results.% on a hexrotor aerial vehicle.

\section{Problem Formulation}\label{sec:prob_form}
\subsection{Attitude Dynamics}\label{sec:att_dyn}
Consider the attitude dynamics of a rigid body--we define an inertial reference frame and a body frame whose origin is at the center of mass and aligned with the principle directions of the body. 
The configuration manifold of the attitude dynamics is the special orthogonal group:
\begin{align*}
	\SO = \{R\in\R^{3\times 3}\,|\, R^TR=I,\;\mathrm{det}[R]=1\} ,
\end{align*}
where a rotation matrix $R\in\SO$ represents the transformation of the representation of a vector from the body-fixed frame to the inertial reference frame. 
The equations of motion are given by
\begin{gather}
	J\dot\Omega + \Omega\times J\Omega = u+W(R,\Omega)\Delta ,\label{eqn:Wdot}\\
	\dot R = R\hat\Omega ,\label{eqn:Rdot}
\end{gather}
where $J\in\R^{3\times 3}$ is the inertia matrix, and $\Omega\in\R^{3}$ is the angular velocity represented with respect to the body-fixed frame. 
The control moment is denoted by $u\in\R^{3}$, and it is expressed with respect to the body-fixed frame. 
We assume that the external disturbance is expressed by $W(R,\Omega)\Delta$, where $W(R,\Omega):\SO\times\R^{3}\rightarrow \R^{3\times p}$ is a known function of the attitude and the angular velocity.
The disturbance is represented by $\Delta\in\R^{p}$ and is an unknown, but fixed uncertain parameter.
In addition, we assume that a bound on \( W(R, \Omega) \text{ and } \Delta \) is known and given by
\begin{equation}
	\norm{W} \leq B_W , \quad \norm{\Delta} \leq B_\Delta \,. \label{eqn:W_bound}
\end{equation}
This form of uncertainty enters the system dynamics through the input channel and as a result is referred to as a matched uncertainty. 
While this form of uncertainty is easier than the unmatched variety many physically realizable disturbances may be modeled in this manner.
For example, orbital spacecraft are subject to gravity gradient torques caused by the non-spherical distribution of mass of both the spacecraft and central gravitational body.
This form of disturbance may be represented as a body fixed torque on the vehicle.
In addition, for typical scenarios, where the spacecraft is significantly smaller than the orbital radius, the disturbance torque may be assumed constant over short time intervals.

In~\refeqn{Rdot}, the \textit{hat} map $\wedge :\R^{3}\rightarrow\so$ represents the transformation of a vector in $\R^{3}$ to a $3\times 3$ skew-symmetric matrix such that $\hat x y = x\times y$ for any $x,y\in\R^{3}$~\cite{bullo2004}. 
More explicitly, 
\begin{align*}
\hat x = \begin{bmatrix} 0 & -x_3 & x_2 \\ x_3 & 0 & -x_1 \\ -x_2 & x_1 & 0\end{bmatrix},
\end{align*}
for $x=[x_1,x_2,x_3]^T\in\R^{3}$. 
The inverse of the hat map is denoted by the \textit{vee} map $\vee:\so\rightarrow\R^{3}$. 
Several properties of the hat map are summarized as
\begin{gather}
%    \hat x y = x\times y = - y\times x = - \hat y x,\\
    x\cdot \hat y z = y\cdot \hat z x,\quad \hat x\hat y z = (x\cdot z) y - (x\cdot y ) z\label{eqn:STP},\\
%    \hat x\hat y z = (x\cdot z) y - (x\cdot y ) z,\label{eqn:VTP}\\
%    C^TC=-C^T\hat e_3^2 C = I_2
%    \hat x^T \hat x = (x^T x) I - x x^T,\\
%    \hat x \hat y \hat x=-(y^Tx)\hat x,\\
%    -\frac{1}{2}\tr{\hat x \hat y} = x^T y,\\
    \widehat{x\times y} = \hat x \hat y -\hat y \hat x = yx^T-xy^T,\label{eqn:hatxy}\\
    %\tr{\hat x A}=
    \tr{A\hat x }=\frac{1}{2}\tr{\hat x (A-A^T)}=-x^T (A-A^T)^\vee,\label{eqn:hat1}\\
%    \widehat{Ax} = \hat x \parenth{\frac{1}{2}\tr{A}I-A} + \parenth{\frac{1}{2}\tr{A}I-A}^T \hat x,\\
    \hat x  A+A^T\hat x=(\braces{\tr{A}I_{3\times 3}-A}x)^{\wedge},\label{eqn:xAAx}\\
R\hat x R^T = (Rx)^\wedge,\quad 
R(x\times y) = Rx\times Ry\label{eqn:RxR}
%,\label{eqn:Rxy}
\end{gather}
for any $x,y,z\in\R^{3}$, $A\in\R^{3\times 3}$ and $R\in\SO$. 
Throughout this paper, the dot product of two vectors is denoted by $x\cdot y = x^T y$ for any $x,y\in\R^n$ and the maximum eigenvalue and the minimum eigenvalue of $J$ are denoted by $\lambda_M$ and $\lambda_m$, respectively. 
The 2-norm of a matrix \( A \) is denoted by \( \norm{A} \), and its Frobenius norm is denoted by \( \norm{A} \leq \norm{A}_F = \sqrt{\tr{A^T A}} \leq \sqrt{\text{rank}(A)} \norm{A} \).

\subsection{State Inequality Constraint}

The two-sphere is the manifold of unit-vectors in \( \R^3 \) such that \( \Sph^2 = \{ q \in \R^3 \,  \vert \, \norm{q} = 1 \}\).
We define \( r \in \Sph^2 \) to be a unit vector from the mass center of the rigid body along a certain direction and it is represented with respect to the body-fixed frame.
For example, \( r \) may represent the pointing direction of an on-board optical sensor.
We define \( v \in \Sph^2 \) to be a unit vector from the mass center of the rigid body toward an undesired pointing direction and represented in the inertial reference frame.
For example, \( v \) may represent the inertial direction of a bright celestial object or the incoming direction of particles or other debris.
It is further assumed that optical sensor has a strict non-exposure constraint with respect to the celestial object.
We formulate this hard constraint as
\begin{align}
	r^T R^T v \leq \cos \theta , \label{eqn:constraint}
\end{align}
where we assume \( \ang{0} \leq \theta \leq \ang{90}  \) is the required minimum angular separation between \( r \) and \( R^T v \).

The objective is to a determine a control input \( u \) that stabilizes the system from an initial attitude \( R_0 \) to a desired attitude \( R_d \) while ensuring that~\cref{eqn:constraint} is always satisfied.

\section{Attitude Control on $\SO$ with Inequality Constraints}

The first step in designing a control system on a nonlinear manifold \( \Q \) is the selection of a proper configuration error function. 
This configuration error function, \( \Psi : \Q \times \Q \to \R \), is a smooth and proper positive definite function that measures the error between the current configuration and a desired configuration. 
Once an appropriate configuration error function is chosen, one can then define a configuration error vector and a velocity error vector in the tangent space \( \mathsf{T}_q \Q \) through the derivatives of \( \Psi \)~\cite{bullo2004}. 
With the configuration error function and vectors the remaining procedure is analogous to nonlinear control design on Euclidean vector spaces. 
One chooses control inputs as functions of the state through a Lyapunov analysis on \Q.

To handle the attitude inequality constraint, we propose a new attitude configuration error function. 
More explicitly, we extend the trace form used in~\cite{bullo2004,LeeITCST13} for attitude control on \(\SO\) with the addition of a logarithmic barrier function. 
Based on the proposed configuration error function,  nonlinear geometric attitude controllers are constructed. 
A smooth control system is first developed assuming that there is  no disturbance, and then it is extended to include an adaptive update law for stabilization in the presence of unknown disturbances. 
The proposed attitude configuration error function and several properties are summarized as follows.

\begin{prop}[Attitude Error Function] \label{prop:config_error}
%We assume a desired attitude command \( ( R_d, \Omega_d = 0 ) \), the current attitude and angular velocity \( ( R, \Omega) \), and a state constraint~\cref{eqn:constraint} are given.
Define an attitude error function \( \Psi : \SO \to \R \), an attitude error vector \( e_R \in \R^3 \), and an angular velocity error vector \( e_\Omega \in \R^3 \) as follows:
\begin{gather}
	\Psi(R) = A(R) B(R) , \label{eqn:psi} \\
	e_R = e_{R_A} B(R) + A(R) e_{R_B} , \label{eqn:eR} \\
	e_\Omega = \Omega , \label{eqn:eW}
\end{gather}
with
\begin{gather}
	A(R) = \frac{1}{2} \tr{G \left( I - R_d^T R\right)} , \label{eqn:A} \\
	B(R) = 1 - \frac{1}{\alpha} \ln \left( \frac{\cos \theta -  r^T R^T v}{1 + \cos \theta}\right) . \label{eqn:B} \\
	e_{R_A} = \frac{1}{2} \parenth{G R_d^T R - R^T R_d G} ^ \vee , \label{eqn:eRA} \\
	e_{R_B} = \frac{ \left( R^T v\right)^\vee r}{\alpha \left(r^T R^T v - \cos \theta \right)} . \label{eqn:eRB} 
\end{gather}	
where \( \alpha \in \R \) is defined as a positive constant and the matrix \( G \in \R^{3 \times 3} \) is defined as a diagonal matrix matrix for distinct, positive constants \( g_1, g_2, g_3 \in \R \).
Then, the following properties hold
\begin{enumerate}[(i)]
	\item \label{item:prop_psi_psd} \(\Psi\) is positive definite about \( R = R_d\)
	\item \label{item:prop_era}The variation of \( A(R) \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
	\begin{align}
		\dirDiff{A}{R} &= \eta \cdot e_{R_A} .
	\end{align}
	\item \label{item:prop_erb} The variation of \( B(R) \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
	\begin{align}
		\dirDiff{B}{R} &= \eta \cdot e_{R_{B}} .
	\end{align}
	\item \label{item:prop_crit}The critical points of \( \Psi \) are $R_d$, and $R_d \exp(\pi \hat{s})$ for $s \in \braces{e_1, e_2, e_3}$ satisfying $R^T v = \pm r$.
	\item \label{item:prop_era_upbound}An upper bound of \( \norm{e_{R_A}} \) is given as:
	\begin{align}
		\norm{e_{R_A}}^2 \leq \frac{A(R)}{b_1} , \label{eqn:psi_lower_bound}
	\end{align}
	where the constant \( b_1 \) is given by \( b_1 = \frac{h_1}{h_2 + h_3} \) for 
	\begin{align*}
		h_1 &= \min\braces{g_1 + g_2, g_2 + g_3 , g_3 + g_1} ,\\
		h_2 &= \min\braces{\parenth{g_1 -g_2}^2,\parenth{g_2 -g_3}^2 , \parenth{g_3 -g_1}^2} ,\\
		h_3 &= \min\braces{\parenth{g_1 + g_2}^2, \parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2}.		
	\end{align*}
\end{enumerate}
\end{prop}
\begin{proof}
See~\Cref{proof:config_error}.
\end{proof}

\Cref{eqn:psi} is composed of an attractive term, \( A (R) \) toward the desired attitude, and a repulsive term, \( B(R) \) away from the undesired direction \( R^T v \).
In order to visualize the attitude error function on \( \SO \) we utilize a spherical coordinate representation.
Recall that the spherical coordinate system represents the position of a point relative to an origin in terms of a radial distance, azimuth, and elevation.
This coordinate system is commonly used to define locations on the Earth in terms of a latitude and longitude.
Similarly, the positions of celestial objects are defined on the celestial sphere in terms of right ascension and declination. 
We apply this concept and parametrize the rotation matrix \( R \in \SO \) in terms of the spherical angles \( \SI{-180}{\degree} \leq \lambda \leq \SI{180}{\degree}  \) and \( \SI{-90}{\degree} \leq \beta \leq \SI{90}{\degree} \). 
Using the elementary Euler rotations the rotation matrix is now defined as \( R = \exp( \lambda \hat{e}_2) \exp( \beta \hat{e}_3) \).
We iterate over the domains of \( \lambda\) and \(\beta\) in order to rotate the body-fixed vector \( r \) throughout the two-sphere \( \S^2 \).
Applying this method,~\cref{fig:config_error} allows us to visualize the error function on \( \SO \).
The attractive error function, given by~\cref{eqn:A}, has been previously used for attitude control on \(\SO\).
The potential well of \( A(R)\) is illustrated in~\cref{fig:attract_error}, where the desired attitude lies at the minimum of \( A(R) \).

To incorporate the state inequality constraints we apply a logarithmic barrier term.
Barrier functions are typically used in optimal control and motion planning applications.
A visualization of the configuration error function is presented in~\cref{fig:avoid_error} which shows that as the boundary of the constraint is neared, or \( r^T R^T v \to \cos \theta \), the barrier term increases, \( B \to \infty\).
We use the scale factor~\(\frac{1}{1+\cos \theta} \) to ensure that \( \Psi \) remains positive definite.
The logarithmic function is popular as it quickly decays away from the constraint boundary.
The positive constant \( \alpha \) serves to shape the barrier function.
As \( \alpha \) is increased the impact of \( B(R) \) is reduced away from the constraint boundary. 
The superposition of the attractive and repulsive functions is shown in~\cref{fig:combined_error}.
The control system is defined such that the attitude trajectory follows the negative gradient of \( \Psi \) toward the minimum at \( R = R_d \), while avoiding the constrained region.
\begin{figure} 
	\centering 
	\begin{subfigure}[htbp]{0.45\columnwidth} 
		\includegraphics[width=\columnwidth]{attract_error} 
		\caption{Attractive \( A(R) \) } \label{fig:attract_error} 
	\end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
	\begin{subfigure}[htbp]{0.45\columnwidth} 
		\includegraphics[width=\columnwidth]{avoid_error} 
		\caption{Repulsive \( B(R) \)} \label{fig:avoid_error} 
	\end{subfigure}
	\centering
	\begin{subfigure}[htbp]{0.45\columnwidth} 
		\includegraphics[width=\columnwidth]{combined_error} 
		\caption{Configuration \( \Psi \)} \label{fig:combined_error} 
	\end{subfigure}
	\caption{Configuration error function visualization}
	\label{fig:config_error} 
\end{figure}

While~\cref{eqn:B} represents a single inequality constraint given as~\cref{eqn:constraint}, it is readily generalized to multiple constraints of an arbitrary form. 
For example, the configuration error function can be formulated as $\Psi=A[1+\sum_i C_i]$, where $C_i$ has the form of $C_i=B-1$ for the $i$-th constraint. 
In this manner, one may enforce multiple state inequality constraints, and we later demonstrate this through numerical simulation.

\begin{prop}[Error Dynamics]\label{prop:error_dyn}
	The attitude error dynamics for \( \Psi, e_R, e_\Omega \) satisfy 
	\begin{gather}
		\diff{}{t} \parenth{\Psi} = e_R \cdot e_\Omega , \label{eqn:psi_dot}\\
		\diff{}{t} \parenth{e_R} = \dot{e}_{R_A} B(R) + e_{R_A} \dot{B}(R) + \dot{A}(R)e_{R_B} + A \dot{e}_{R_B} , \label{eqn:eR_dot}\\
		\diff{}{t} \parenth{e_{R_A}} = E(R, R_d) e_\Omega , \label{eqn:eRA_dot} \\
		\diff{}{t} \parenth{e_{R_B}} = F(R) e_\Omega , \label{eqn:eRB_dot} \\
		\diff{}{t} \parenth{A(R)} = e_{R_A} \cdot e_\Omega , \label{eqn:A_dot} \\
		\diff{}{t} \parenth{B(R)} = e_{R_B} \cdot e_\Omega , \label{eqn:B_dot} \\
		\diff{}{t} \parenth{e_\Omega} = J^{-1} \parenth{-\Omega \times J \Omega + u + W(R, \Omega) \Delta} , \label{eqn:eW_dot}
	\end{gather}
	where the matrices \(E(R,R_d), F(R) \in \R^{3\times3} \) are given by
	\begin{gather}
		E(R,R_d) = \frac{1}{2} \parenth{\tr{R^T R_d G}I - R^T R_d G} , \label{eqn:E} \\
		F(R) = \frac{1}{\alpha \parenth{r^T R^T v - \cos \theta}} \left[\parenth{v^T R r} I - R^T v r^T + \right. \nonumber \\
		\left. \frac{R^T \hat{v} R r v^T R \hat{r}}{\parenth{r^T R^T v - \cos \theta}}\right] . \label{eqn:F}
	\end{gather}
\end{prop}
\begin{proof}
See~\Cref{proof:error_dyn}.
\end{proof}

\subsection{Attitude Control without Disturbance}
We introduce a nonlinear geometric controller for the attitude stabilization of a rigid body.
We first assume that there is no disturbance, i.e., \( \Delta = 0 \).
\begin{prop}[Attitude Control]\label{prop:att_control}
	Given a desired attitude command \( \parenth{R_d, \Omega_d = 0} \), which satisfies the constraint~\cref{eqn:constraint}, and positive constants \( k_R, k_\Omega \in \R \) we define a control input \( u \in \R^3 \) as follows
	\begin{gather}
		u = -k_R e_R - k_\Omega e_\Omega + \Omega \times J \Omega . \label{eqn:nodist_control}
	\end{gather}
	Then the zero equilibrium of the attitude error is asymptotically stable, and the inequality constraint is satisfied.
\end{prop}

\begin{proof}
See~\Cref{proof:att_control}.
\end{proof}

This proposition only guarantees that the attitude error vector \( e_R \) asymptotically converges to zero.
However, this does not necessarily imply that \( R \to R_d \) as \( t \to \infty \), since there are at most three additional critical points of \( \Psi \) where \( e_R = 0 \) and \( R^T v = \pm r\).
At an undesired equilibrium \( R = \exp{ \parenth{\pi \hat{e}_i}} R_d \) and \( e_\Omega =0 \).
However, we can show that these undesired equilibrium points are unstable in the sense of Lyapunov~\cite{LeeITCST13}.
As a result, we can claim that the desired equilibrium \( R = R_d \text{ and } e_\Omega = 0 \) is almost globally asymptotically stable, which means that the set of initial conditions that do not converge to the desired attitude has zero Lebesgue measure.

\subsection{Adaptive Control}
We extend the results of the previous section with the addition of a fixed but unknown disturbance \( \Delta \).
This scenario is typical of many mechanical systems and represents unmodeled dynamics or external moments acting on the system.
For example, Earth orbiting spacecraft typically experience a torque due to a gravitational gradient.
% as well as external torques to due solar radiation pressure.
Aerial vehicles will similarly experience external torques due to air currents or turbulence.
An adaptive control system is introduced to asymptotically stabilize the system to a desired attitude while ensuring that state constraints are satisfied. %We first show several properties of the controlled system.

\begin{prop}[Bound on \( \bm{\dot{e}_R} \)]\label{prop:eR_dot_bound}
Consider a domain \( D \) about the desired attitude defined as
\begin{align}
	D = \braces{R \in \SO \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta}. \label{eqn:domain}
\end{align}
Then the following statements hold:
\begin{enumerate}[(i)]
	\item \label{item:prop_eR_dot_bound_AB} Upper bounds of \( A(R) \) and \( B(R) \) are given by
	\begin{gather}
		\norm{A} < c_A  , \quad \norm{B} < c_B . \label{eqn:AB_bound}
	\end{gather}
	\item \label{item:prop_eR_dot_bound_EF} Upper bounds of \( E(R,R_d) \) and \( F(R) \) are given by
	\begin{gather}
		\norm{E} \leq \frac{1}{\sqrt{2}} \tr{G}  , \label{eqn:E_bound} \\
		\norm{F} \leq \frac{\parenth{\beta^2 + 1}\parenth{\beta - \cos \theta}^2 + 1 + \beta^2 \parenth{\beta^2-2}}{\alpha^2 \parenth{\beta-\cos \theta}^4} . \label{eqn:F_bound}
	\end{gather}
	\item Upper bounds of the attitude error vectors \( e_{R_A} \) and \( e_{R_B} \) are given by
	\begin{gather}
		\norm{e_{R_A}} \leq \sqrt{\frac{\psi}{b_1}}, \label{eqn:eRA_bound} \\
		\norm{e_{R_B}} \leq \frac{\sin\theta}{\alpha \parenth{\cos \theta - \beta}}. \label{eqn:eRB_bound}
	\end{gather}
\end{enumerate}
These results are combined to yield a maximum upper bound of the time derivative of the attitude error vector \( \dot{e}_R \) as
\begin{gather}
	\norm{\dot{e}_R} \leq H \norm{e_\Omega} ,\label{eqn:eR_bound}
\end{gather}
where  \( H \in \R \) is defined as
\begin{gather}
	H = \norm{B} \norm{E} + 2 \norm{e_{R_A}} \norm{e_{R_B}} + \norm{A}\norm{F}. \label{eqn:H}
\end{gather}
\end{prop}

\begin{proof}
See~\Cref{proof:eR_dot_bound}.
\end{proof}
\begin{prop}[Adaptive Attitude Control]\label{prop:adaptive_control}
Given  a desired attitude command \( (R_d, \Omega_d = 0 )\) and positive constants \( k_R, k_\Omega, k_\Delta, c \in \R \), we define a control input \( u \in \R^3\) and an adaptive update law for the estimated uncertainty \( \bar{\Delta} \) as follows:
\begin{align}
	u &= - k_R e_R - k_\Omega e_\Omega + \Omega \times J \Omega - W \bar{\Delta} , \label{eqn:adaptive_control} \\
	\dot{\bar{\Delta}} &= k_\Delta W^T \parenth{e_\Omega + c e_R} . \label{eqn:delta_dot}
\end{align}
If \( c \) is chosen such that
\begin{gather}
	0 < c < \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k-R \lambda_M H} , \label{eqn:c_bound}
\end{gather}
  the zero equilibrium of the error vectors is stable in the sense of Lyapunov. Furthermore, $e_R,e_\Omega\rightarrow 0$ as $t\rightarrow\infty$, and $\bar\Delta$ is uniformly bounded.
\end{prop}
\begin{proof}
See~\Cref{proof:adaptive_control}.
\end{proof}

Nonlinear adaptive controllers have been developed for attitude stabilization in terms of modified Rodriguez parameters and quaternions, as well as attitude tracking in terms of Euler angles. 
The proposed control system is developed on \(\SO\) and avoids the singularities of Euler angles and Rodriguez parameters while incorporating state inequality constraints. 
In addition, the unwinding and double coverage ambiguity of quaternions are also completely avoided. 
The control system handles uncertain disturbances while avoiding constrained regions.

Compared to the previous work on constrained attitude control, we present a geometrically exact control system without parameterizations.
In addition, we incorporate state inequality constraints for the first time on \( \SO \).
The presented control system is computed in real-time and offers significant computational advantages over previous iterative methods. 
In addition, the riguous mathematical proof guarantees stability.
\section{Numerical Examples}
We demonstrate the performance of the proposed control system via numerical simulation.
The inertia tensor of a rigid body is given as
\begin{gather*}
	J = \begin{bmatrix}
	\num{5.57e-3} & \num{6.17e-5} & \num{-2.50e-5} \\
	\num{6.17e-5} & \num{5.57e-3} & \num{1.00e-5} \\
	\num{-2.50e-5} & \num{1.00e-5} & \num{1.05e-2}
	\end{bmatrix} \si{\kilo\gram\meter\squared} .
\end{gather*} 
The control system parameters are chosen as
\begin{gather*}
	G = \text{diag} [0.9,1.1,1.0], \quad k_R = 0.4 , \quad	k_\Omega = 0.296 ,\\
	c = 1.0 , \quad k_\Delta = 0.5 , \quad \alpha = 15 .
\end{gather*}
A body fixed sensor is defined as \(r = [1,0,0]\), while multiple inequality constraints are defined in~\Cref{tab:constraints}.
The simulation parameters are chosen to be similar to those found in~\cite{lee2011b}, however we increase the size of the constraint regions to create a more challenging scenario for the control system.

The initial state is defined as \(R_0 =  \exp(\ang{225} \times \frac{\pi}{180} \hat{e}_3), \Omega_0 = 0\). 
The desired state is \( R_d = I,\Omega_d = 0\).
\begin{table}%[htbp]
\caption{Constraint Parameters~\label{tab:constraints}}
\begin{center}\begin{tabular}{lc}
Constraint Vector (\( v \)) & Angle (\( \theta \)) \\ \hline \hline 
\([0.174,\,-0.934,\, -0.034]^T\) & \ang{40} \\ \hline 
\([0 ,\, 0.7071 ,\, 0.7071]^T\) & \ang{40} \\ \hline 
\([-0.853 ,\, 0.436 ,\, -0.286]^T\) & \ang{40} \\ \hline 
\([-0.122 ,\,-0.140,\, -0.983]^T\) & \ang{20}\end{tabular} 
\end{center}
\end{table}
We show simulation results for the system stabilizing about the desired attitude with and without the adaptive update law from~\Cref{prop:adaptive_control}.
We assume a fixed disturbance of \(\Delta = \begin{bmatrix} 0.2 & 0.2 & 0.2 \end{bmatrix}^T \), with the function \( W(R,\Omega) = I \).
This form is equivalent to an integral control term which penalizes deviations from the desired configuration.
The first term of~\cref{eqn:delta_dot} has the effect of increasing the proportional gain of the control system, since the time derivative of the attitude error vector, \( \dot{e}_{R} \), is linear with respect to the angular velocity error vector \( e_\Omega\).
\begin{figure} 
	\centering 
	\subfigure{Attitude error vector \(e_R\) \label{fig:eR_con}{eR_con} 
	\begin{subfigure}[htbp]{0.5\columnwidth} 
		\includegraphics[width=\columnwidth]{Psi_con} 
		\caption{Configuration error \( \Psi \)} \label{fig:Psi_con} 
	\end{subfigure}
	\caption{Attitude stabilization without adaptive update law}
	\label{fig:con} 
\end{figure}
\begin{figure} 
	\centering 
	\begin{subfigure}[htbp]{0.5\columnwidth} 
		\includegraphics[width=\columnwidth]{Psi_adapt} 
		\caption{Configuration error \( \Psi \)} \label{fig:Psi_adapt} 
	\end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
	\begin{subfigure}[htbp]{0.5\columnwidth} 
		\includegraphics[width=\columnwidth]{constraint_angles} 
		\caption{Angle to constraints} \label{fig:con_angles} 
	\end{subfigure}

	\centering
	\begin{subfigure}[htbp]{0.5\columnwidth} 
		\includegraphics[width=\columnwidth]{delta_adapt} 
		\caption{Disturbance estimate \( \bar \Delta \)} \label{fig:delta_adapt} 
	\end{subfigure}~
	\begin{subfigure}[htbp]{0.5\columnwidth} 
		\includegraphics[trim=9cm 2.5cm 0 0,clip,width=1.29\columnwidth]{cad_adapt} 
		\caption{Attitude trajectory} \label{fig:cad_adapt} 
	\end{subfigure}
	\caption{Attitude stabilization with adaptive update law}
	\label{fig:adapt} 
\end{figure}

Simulation results without the adaptive update law are shown in~\cref{fig:con}.
Without the update law, the system does not achieve zero steady state error. 
\Cref{fig:Psi_con} shows that the configuration error function does not converge to zero and there exist steady state errors.
\Cref{fig:adapt} shows the results with the addition of the adaptive update law.
The addition of the adaptive update law allows the system to converge to the desired attitude in the presence of constraints.
The path of the body fixed sensor in the inertial frame, namely \( R r \), is illustrated in~\cref{fig:cad_adapt}.
The initial attitude is represented with the green circle while the final attitude is marked with a green \(\times\).
The inequality constraints from~\Cref{tab:constraints} are depicted as red cones, where the cone half angle is \( \theta \).
The control system is able to asymptotically converge to zero attitude error.
\Cref{fig:con_angles} shows that the angle \( \arccos(r^T R^T v_i) \) between the body fixed sensor and each constraint is satisfied for the entire maneuver.
In addition, the estimate of the disturbance converges to the the true value as shown in~\cref{fig:delta_adapt}.

Both control system are able to automatically avoid the constrained regions. 
In addition, these results show that it is straightforward to incorporate an arbitrary amount of large constraints.
In spite of this challenging configuration space, the proposed control system offers a simple method of avoiding constrained regions.
These closed-loop feedback results are computed in real time and offer a significant advantage over typical open-loop planning methods.
These results show that the proposed geometric adaptive approach is critical to attitude stabilization in the presence of state constraints and disturbances.
\section{Experiment on Hexrotor UAV}
A hexrotor unmanned aerial vehicle (UAV) has been developed at the Flight Dynamics and Controls Laboratory (FDCL) at the George Washington University~\cite{kaufman2014}.
The UAV is composed of three pairs of counter-rotating propellers. 
%Typical quadrotor UAVs are composed of four or more co-planar propellers.
%As a result, these systems are underactuated and unable to impart a force along every degree of freedom.
%For example, quadrotor UAVs are unable to translate laterally without first conducting a rotation.
%Conversely, the propeller pairs of the hexrotor are angled relative to one another to allow for a fully actuated rigid body.
The propeller pairs of the hexrotor are angled relative to one another to allow for a fully actuated rigid body.
%This allows the hexrotor to impart a force in any direction and a moment about any axis.

The hexrotor UAV, shown in~\cref{fig:hexrotor}, is composed of the following hardware:
\begin{itemize}
	\item Onboard ODROID XU3 computer module.
	\item VectorNav VN100 IMU operating via TTL serial %at over \SI{100}{\hertz} 
	\item BLDC motors with BL-Ctrl-2.0 ESC via I2C.
	\item Position and attitude over WiFi (TCP) communication from Vicon motion capture system.
	\item Commands sent over WiFi to  onboard controller. 
\end{itemize}
In order to constrain the motion and test only the attitude dynamics we attach the hexrotor to a spherical joint.
The center of rotation is below the center of gravity of the hexrotor.
As a result, there is a destabilizing gravitational moment and the resulting attitude dynamics are similar to an inverted pendulum model.
We augment the control input in~\cref{eqn:adaptive_control} with an additional term to negate the effect of the gravitational moment.

\begin{figure}
	\centering
	\includegraphics[width = 0.7\columnwidth]{hexrotor}
	\caption{Attitude control testbed~\label{fig:hexrotor}}
\end{figure}
A sensor pointing direction is defined in the body frame of the hexrotor as \( r = [1,0,0]^T \).
We define an obstacle in the inertial frame as \( v = [\frac{1}{\sqrt{2}}, \frac{1}{\sqrt{2}}, 0]^T \) with \( \theta = \ang{12} \).
An initial state is defined as \(R(0) = \exp( \frac{\pi}{2} \hat{e}_3) \), while the desired state is \(R_d =I \).
This results in the UAV performing a \ang{90} yaw rotation about the vertical axis of the spherical joint and the constrained region is on the shortest path connecting $R_0$ and $R_d$. 
The attitude control system is identical to the one presented in~\Cref{prop:adaptive_control} with the exception of a gravity moment term and the following parameters: \(k_R = 0.4, k_\Omega = 0.7 ,c = 0.1 , \alpha = 8 \text{ and } k_\Delta = 0.05\).
\begin{figure} 
	\centering 
	\begin{subfigure}[htbp]{0.5\columnwidth} 
		\includegraphics[width=\columnwidth]{eR_exp} 
		\caption{Attitude error vector \(e_R\) } \label{fig:eR_exp} 
	\end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
	\begin{subfigure}[htbp]{0.5\columnwidth} 
		\includegraphics[width=\columnwidth]{Psi_exp} 
		\caption{Configuration error \( \Psi \)} \label{fig:Psi_exp} 
	\end{subfigure}

	\begin{subfigure}[htbp]{0.5\columnwidth} 
		\includegraphics[width=\columnwidth]{u_exp} 
		\caption{Control input \( u\)} \label{fig:u_exp} 
	\end{subfigure}~
	\begin{subfigure}[htbp]{0.5\columnwidth} 
		\includegraphics[width=\columnwidth]{traj_exp} 
		\caption{Attitude Trajectory} \label{fig:traj_exp} 
	\end{subfigure}
	\caption{Constrained Attitude stabilization experiment}
	\label{fig:exp} 
\end{figure}

The experimental results are shown in~\Cref{fig:exp}.
In order to maneuver the system ``close" to the constrained zone we utilize several intermediary set points on either side of the obstacle.
From the initial attitude the hexrotor rotates to the first set point, pauses, and then continues around the obstacle to the second set point before continuing toward the desired attitude.
As a result this creates the stepped behavior of the configuration error history as shown in~\cref{fig:Psi_exp}.

The brushless motors of the hexrotor allow for large control inputs, which are critical to enable aggressive maneuvers. 
When constrained to the spherical joint, the hexrotor is capable of performing responsive attitude changes with high angular velocities.
In addition, The on-board control and motion capture system operate at a discrete interval of approximately \SI{100}{\hertz}.
It is possible for the system to violate the constraint between these discrete steps and cause numerical exceptions within the embedded software. 
As a result, conservative control gains are chosen to ensure the hexrotor operates in a sedate manner and to allow sufficient time for the measurement and control software to operate.

There exist several sources of error in the experimental setup.
The motion capture system uses a series of optical sensors to determine the relative position of several tracking markers. 
These markers as well as the cameras must remain fixed to ensure accurate attitude measurement.
In addition, the spherical joint is not fixed at the center of mass but is instead offset due to the physical structure of the hexrotor.
As a result a disturbance moment is induced on the resultant motion.

This results in a small steady state error in the vicinity of the desired attitude. 
Over time~\cref{eqn:delta_dot} will remain non-zero while \( e_R \neq 0 \).
This will cause an increase in control input until the steady-state error is reduced. 
Further tuning of the control gains would enable a faster response and a reduced settling time.

The hexrotor avoids the constrained region illustrated by the circular cone in~\cref{fig:traj_exp}, by rotating around the boundary of the constraint. 
This verifies that the proposed control system exhibits the desired performance in the experimental setting as well. 
A video clip showing the attitude maneuver is available \url{https://youtu.be/dsmAbwQram4}.
\section{Conclusions}\label{sec:conclusions}
We have developed a geometric adaptive control system which incorporates state inequality constraints on \(\SO\).
The presented control system is developed directly on \(\SO\) and it avoids singularities and ambiguities that are inherent to attitude parameterizations.
The attitude configuration error is augmented with a barrier function to avoid the constrained region, and an adaptive control law is proposed to cancel the effects of uncertainties. 
We show the stability of the  proposed control system through a rigorous mathematical analysis.
In addition, we have demonstrated the control system via numerical simulation and hardware experiments on a hexrotor UAV.
A novel feature of this control is that it is computed autonomously on-board the UAV.
This is in contrast to many state constrained attitude control systems which require an a priori attitude trajectory to be calculated. 
The presented method is simple, efficient and ideal for hardware implementation on embedded systems.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\subsection{Proof of~\Cref{prop:config_error}}\label{proof:config_error}
To prove~\cref{item:prop_psi_psd} we note that~\cref{eqn:A} is a positive definite function about \( R = R_d \)~\cite{bullo2004}.
The constraint angle is assumed \( \ang{0} \leq \theta \leq \ang{90} \) such that \( 0 \leq \cos \theta \).
The term \( r^T R^T v \) represents the cosine of the angle between the body fixed vector \( r \) and the inertial vector \( v \). 
It follows that
\begin{align*}
	0 \leq  \frac{\cos \theta -  r^T R^T v}{1 + \cos \theta} \leq 1 ,
\end{align*}
for all \( R \in \SO \). 
As a result, its negative logarithm is always positive and from~\cref{eqn:B}, \(1 < B\).
The error function \( \Psi = A B \) is composed of two positive terms and is therefore also positive definite, and it is minimized at \( R = R_d \).

Next, we consider~\cref{item:prop_era}.
The variation of~\cref{eqn:A} is taken with respect to \( \delta R = R \hat \eta \) as
\begin{align*}
	\dirDiff{A}{R} &= \eta \cdot \frac{1}{2} \left( G R_d^T R - R^T R_d G\right)^\vee ,
%	&= -\frac{1}{2} \tr{G R_d^T \left( R \hat{\eta}\right)} \\
\end{align*}
where we used~\cref{eqn:hat1}.

A straightforward application of the chain and product rules of differentiation allows us to show~\cref{item:prop_erb} as
\begin{align*}
	\dirDiff{B}{R} &=  \eta \cdot \frac{ - \left( R^T v\right)^\vee r}{\alpha \left(\cos \theta - r^T R^T v \right)} ,
%	-\frac{1}{\alpha} \left[\left(\frac{1+\cos \theta}{\cos \theta - r^T R^T v} \right) \left(\eta \cdot \frac{\left( R^T v\right)^\vee r}{1+\cos \theta} \right) \right]
\end{align*}
where the scalar triple product~\cref{eqn:STP} was used.

%To show~\cref{item:prop_crit}, we determine the critical points of~\cref{eqn:eRA}.
%The attitude error between \( R \) and \( R_d \) is defined by \( Q \in \SO \) as
%\begin{align*}
%	Q = R_d^T R = 
%	\begin{bmatrix}
%		q_{11} & q_{12} & q_{13} \\
%		q_{21} & q_{22} & q_{23} \\
%		q_{31} & q_{32} & q_{33}
%	\end{bmatrix} .
%\end{align*}
%Equating \( e_{R_{A}} = 0 \) yields the following equivalent relations
%\begin{subequations}
%\begin{align}
%	g_3 q_{32} &= g_2 q_{23} , \\
%	g_1 q_{13} &= g_3 q_{31} , \\
%	g_2 q_{21} &= g_1 q_{12} .
%\end{align}
%\end{subequations}
%These relations allow one to redefine the attitude error \( Q \) in terms of the independent upper diagonal elements.
%Noting that \( Q \in \SO \) is an orthonormal matrix, with unit length row and columns gives
%\begin{subequations}
%\begin{align}
%	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 + \parenth{1 - \frac{g_1^2}{g_3^2}}q_{13}^2 &= 0 , \\
%	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 - \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 , \\
%	\parenth{1-\frac{g_1^2}{g_3^2}} q_{13}^2 + \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 .
%\end{align}
%\end{subequations}
%As a result, all the off diagonal terms of \( Q = R_d^T R \) are zero, namely \( q_{12}= q_{13} = q_{23} = 0 \).
%Since \( Q \in \SO \), the diagonal elements \( q_{11}, q_{22}, \text{ and } q_{33} \) are either \( +1 \) or \(-1\).
The critical points of \( e_{R_A} \) are derived in~\cite{bullo2004}.
There are four critical points of \( e_{R_A} \), the desired attitude \( R_d \) as well as rotations about each body fixed axis by \ang{180}.
The repulsive error vector \( e_{R_{B}} \) is zero only when the numerator \( \parenth{R^T v}^\wedge r = 0 \). 
This condition only occurs if the desired attitude results in the body fixed vector \( r \) becoming aligned with \(R^T v \) while simultaneously satisfying \(\braces{R_d} \cup \braces{R_d \exp(\pi \hat{s}} \) for \( s \in \braces{e_1, e_2, e_3} \).
Since we assume the system will not operate in violation of the constraints, the addition of the barrier function does not add additional critical points to the control system.
The desired equilibrium is \( e_R = 0 \) and \( A = 0\).
The proof of \( \norm{e_{R_A}} \) given by~\cref{item:prop_era_upbound} is available in~\cite{LeeITCST13}.
\subsection{Proof of~\Cref{prop:error_dyn}}\label{proof:error_dyn}
From the kinematics~\cref{eqn:Rdot} and noting that \( \dot{R}_d = 0 \) the time derivative of \( R_d^T R \) is given as
\begin{gather*}
	\diff{}{t} \parenth{R_d^T R} = R_d^T R \hat{e}_\Omega .
\end{gather*}
Applying this to the time derivative of~\cref{eqn:A} gives
\begin{gather*}
	\diff{}{t} (A) = -\frac{1}{2} \tr{G R_d^T R \hat{e}_\Omega} .
\end{gather*}
Applying~\cref{eqn:hat1} into this shows~\cref{eqn:A_dot}.
Next, the time derivative of the repulsive error function is given by
\begin{gather*}
	\diff{}{t} (B) = \frac{r^T \parenth{\hat{\Omega} R^T} v}{\alpha \parenth{r^T R^T v - \cos \theta}} .
\end{gather*}
Using the scalar triple product, given by~\cref{eqn:STP}, one can reduce this to~\cref{eqn:B_dot}.
The time derivative of the attractive attitude error vector, \( e_{R_A} \), is given by
\begin{gather*}
	\diff{}{t} ( e_{R_A}) = \frac{1}{2} \parenth{\hat{e}_\Omega R^T R_d G + (R^T R_d G)^T \hat{e}_\Omega}^\vee .
\end{gather*}
Using the hat map property given in~\cref{eqn:xAAx} this is further reduced to~\cref{eqn:eRA_dot,eqn:E}.

We take the time derivative of the repulsive attitude error vector, \( e_{R_B} \), as
\begin{gather*}
	\diff{}{t}( e_{R_B} )= a \Omega v^T R r - a R^T v \Omega^T r + b R^T \hat{v} R r ,
\end{gather*}
with \( a \in \R \) and \( b \in \R\) given by 
\begin{gather*}
	a = \bracket{\alpha \parenth{r^T R^T v - \cos \theta}}^{-1} , \,
	b = \frac{r^T \hat{\Omega} R^T v}{\alpha \parenth{r^T R^T v - \cos \theta}^2} .
\end{gather*}
Using the scalar triple product from~\cref{eqn:STP} as \( r \cdot \Omega \times \parenth{R^T v} = \parenth{R^T v} \cdot r \times \Omega \) gives~\cref{eqn:eRB_dot,eqn:F}.

We show the time derivative of the configuration error function as
\begin{gather*}
	\diff{}{t} (\Psi) = \dot{A} B + A \dot{B} .
\end{gather*}
A straightforward substitution of~\cref{eqn:A_dot,eqn:B_dot,eqn:A,eqn:B} into this and appplying~\cref{eqn:eR} shows~\cref{eqn:psi_dot}.
We show~\cref{eqn:eW_dot} by rearranging~\cref{eqn:Wdot} as 
\begin{align*}
	\diff{}{t} e_\Omega = \dot{\Omega} = J^{-1} \parenth{u - \Omega \times J \Omega + W(R,\Omega) \Delta } .
\end{align*}

\subsection{Proof of~\Cref{prop:att_control}}\label{proof:att_control}
Consider the following Lyapunov function:
\begin{gather}
	\mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi(R,R_d) . \label{eqn:v_nodist}
\end{gather}
From~\cref{item:prop_psi_psd} of~\Cref{prop:config_error}, \(\mathcal{V} \geq 0 \).
Using~\cref{eqn:eW_dot,eqn:psi_dot} with \( \Delta = 0 \), the time derivative of \( \mathcal{V} \) is given by
\begin{align}
	\dot{\mathcal{V}} &= -k_\Omega \norm{e_\Omega}^2 . \label{eqn:vdot_nodist}
%	e_\Omega^T \parenth{ u - \Omega \times J \Omega } + k_R e_R \cdot e_\Omega \nonumber \\
\end{align}
Since \( \mathcal{V} \) is positive definite and \( \dot{\mathcal{V}} \) is negative semi-definite, the zero equilibrium point \( e_R, e_\Omega \) is stable in the sense of Lyapunov. 
This also implies \( \lim_{t\to\infty} \norm{e_\Omega} = 0 \) and \( \norm{e_R} \) is uniformly bounded, as the Lyapunov function is non-increasing. From \refeqn{eRA_dot} and \refeqn{eRB_dot}, $\lim_{t\to\infty} \dot e_R =0$. 
One can show that \( \norm{\ddot{e}_R} \) is bounded.
From Barbalat's Lemma, it follows \( \lim_{t\to\infty}\norm{\dot{e}_R} = 0 \)~\cite[Lemma 8.2]{khalil1996}. 
Therefore, the equilibrium is asymptotically stable.

Furthermore, since \( \dot{\mathcal{V}} \leq 0 \) the Lyapunov function is uniformly bounded which implies 
\begin{align*}
	\Psi(R(t)) \leq \mathcal{V}(t) \leq \mathcal{V}(0) .
\end{align*}
In addition, the logarithmic term in~\cref{eqn:B} ensures \( \Psi(R) \to \infty \) as \( r^T R^T v \to \cos \theta \).
Therefore, the inequality constraint is always satisfied given that the desired equilibrium lies in the feasible set.

\subsection{Proof of~\Cref{prop:eR_dot_bound}}\label{proof:eR_dot_bound}
%	We first show~\cref{eqn:A_bound,eqn:B_bound} through a proof by contradiction by noting that given the selected domain \( D \) we know the configuration error function is bounded by \( \Psi = A(R) B(R) < \psi\).
%	If we assume that \( A > \psi \) this means that \( B < 1 \) in order to satisfy the domain \( \Psi < \psi \).
%	However, this would be in contradiction with~\Cref{proof:config_error} as \( B > 1 \), therefore \( A \) must always be less than \( \psi \).
%	Next, we show that since the domain \( D \) does not contain the constraint region there is an upper bound of \(B\).
%	We know that \( B \to \infty \) as the constraint is neared. 
%	We assume that \( B > \psi \) which implies that \( A < 1 \).
%	As \( \psi \) is increased this implies that the system is approaching the constraint and that \( A \to 0 \) in order to remain in the domain \( D \).
%	However, since the chosen domain is assumed to exclude the constraint this situation is not possible and \( B < \psi \).
	The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
	This implies that that both \( A(R) \) and \( B(R) \) are bounded by constants \( c_A c_B < \psi < h_1\).
	Furthermore, since \( \norm{B} > 1 \) this ensures that \( c_A, c_B < \psi\) and shows~\cref{eqn:AB_bound}.

	Next, we show~~\cref{eqn:E_bound,eqn:F_bound} using the Frobenius norm.
	The Frobenius norm \( \norm{E}_F \) is given in~\cite{LeeITCST13} as
	\begin{gather*}
		\norm{E}_F = \sqrt{\tr{E^T E}} = \frac{1}{2} \sqrt{\tr{G^2} + \tr{R^T R_d G}^2} .
	\end{gather*}
	Applying Rodrigues' formula and the Matlab symbolic toolbox, this is simplified to
	\begin{gather*}
		\norm{E}^2_F \leq \frac{1}{4} \parenth{\tr{G^2} + \tr{G}^2} \leq \frac{1}{2} \tr{G}^2 ,
	\end{gather*}
	which shows~\cref{eqn:E_bound}, since \( \norm{E} \leq \norm{E}_F \).

	To show~\cref{eqn:F_bound}, we apply the Frobenius norm \( \norm{F}_F \):
	\begin{gather*}
		\norm{F}_F = \frac{1}{\alpha ^2 \parenth{r^T R^T v - \cos \theta}^2} \left[\tr{a^T a} - 2 \tr{a^T b} \right. \\
		\left.+ 2 \tr{a^T c } + \tr{b^T b}  - 2 \tr{b^T c} + \tr{c^T c}\right] .
	\end{gather*}
	where the terms \( a, b, \text{ and } c \) are given by
	\begin{gather*}
		a = r^T R r I , \quad	b = R^T v r^T , \quad c = \frac{R^T \hat{v} R r v^T R \hat{r}}{r^T R^T v - \cos \theta}.
	\end{gather*}
	A straightforward computation of \( a^T a \) shows that
	\begin{gather*}
		\tr{a^T a} = \parenth{v^T R r}^2 \tr{I} \leq 3 \beta^2 ,
	\end{gather*}
	where we used the fact that \( v^T R r = r^T R^T v < \beta \) from our given domain.
	Similarly, one can show that \( \tr{a^T b} \) is equivalent to
	\begin{gather*}
		\tr{a^T b} = v^T R r \tr{R^T v r^T} = \parenth{v^T R r}^2 \leq \beta^2 ,
	\end{gather*} 
	where we used the fact that \( \tr{x y^T} = x^T y \).
	The product \( \tr{a^T c} \) is given by
	\begin{gather*}
		\tr{a^T c} = \frac{v^T R r}{r^T R^T v - \cos \theta} \tr{\parenth{R^T v}^\vee \parenth{r v^T R} \hat{r} } ,
	\end{gather*}
	where we used the hat map property~\cref{eqn:RxR}.
	One can show that \(\mathrm{tr}[a^T c] \leq 0 \) over the range \( -1 \leq v^T R r \leq \cos \theta \). 
	Next, \( \tr{b^T b}\) is equivalent to
	\begin{gather*}
		\tr{b^T b} = \tr{r v^T R R^T v r^T} = 1 ,
	\end{gather*}
	since \( r,v \in \Sph^2\).
	Finally, \( \tr{c^T c} \) is reduced to
	\begin{gather*}
		\tr{c^T c} = \tr{\hat{r} R^T v r^T \bracket{-I + R^T v v^T R} r v^T R \hat{r}} ,
	\end{gather*}
	where we used the fact that \( \hat{x}^2 = - \norm{x}^2 I + x x^T\).
	Expanding and collecting like terms gives
	\begin{gather*}
		\tr{c^T c } = \frac{1 - 2\parenth{v^T R r}^2 + \parenth{v^T R r}^4}{\parenth{r^T R^T v - \cos \theta}^2} . 
	\end{gather*}
	Using the the given domain \( r^T R^T v \leq \beta \) gives the upper bound~\cref{eqn:F_bound}.
	The bound on \( e_{R_A} \) is given in~\cref{eqn:psi_lower_bound} while \( e_{R_B} \) arises from the definition of the cross product \( \norm{a \times b} = \norm{a} \norm{b} \sin \theta \).
	Finally, we can find the upper bound~\cref{eqn:eR_dot} as
	\begin{gather*}
		\norm{\dot{e}_R} \leq \parenth{\norm{B} \norm{E} + 2 \norm{e_{R_A}} \norm{e_{R_B}} + \norm{A}\norm{F}} \norm{e_\Omega} \, .
	\end{gather*}
	Using~\crefrange{eqn:AB_bound}{eqn:eRB_bound} one can define \( H \) in terms of known values.
\subsection{Proof of~\Cref{prop:adaptive_control}}\label{proof:adaptive_control}
	Consider the Lyapunov function \( \mathcal{V} \) given by
	\begin{gather}
		\mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi + c J e_\Omega \cdot e_R + \frac{1}{2 k_\Delta} e_\Delta \cdot e_\Delta , \label{eqn:v_adapt}
	\end{gather}
	over the domain \( D \) in~\cref{eqn:domain}.
	From~\Cref{prop:eR_dot_bound}, the Lyapunov function is bounded in \( D \) by
	\begin{gather}
		\mathcal{V} \leq z^T W z , \label{eqn:v_upper_bound}
	\end{gather}
	where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = [\|e_R\|,\|e_\Omega\|,\|e_\Delta\|]^T\in\R^3 \) and the matrix \(W \in \R^{3 \times 3}\) is given by
	\begin{gather*}
		W = \begin{bmatrix}
			k_R \psi & \frac{1}{2} c \lambda_M & 0 \\
			\frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_M & 0 \\
			0 & 0 & \frac{1}{2 k_\Delta}
		\end{bmatrix} .
	\end{gather*}
	The time derivative of \( \mathcal{V}\) with the control inputs~\cref{eqn:adaptive_control} is given by
	\begin{align}
		\dot{\mathcal{V}} =& - k_\Omega e_\Omega^T e_\Omega + \parenth{e_\Omega + c e_R}^T W e_\Delta - k_R c e_R^T e_R \nonumber\\
		&- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} , \label{eqn:vdot}
	\end{align}
	where we used \( \dot{e}_\Delta = - \dot{\bar{\Delta}} \).
	The terms linearly dependent on \( e_\Delta\) are combined with~\cref{eqn:delta_dot} to yield
	\begin{align*}
		 e_\Delta^T \parenth{W^T \parenth{e_\Omega + c e_R} - \frac{1}{k_\Delta} \dot{\bar{\Delta}}} = 0 . 
	\end{align*}
	Using~\Cref{prop:eR_dot_bound} an upper bound on \( \dot{\mathcal{V}} \) is written as
	\begin{gather*}
		\dot{\mathcal{V}} \leq -\zeta^T M \zeta ,
	\end{gather*}
	where $\zeta=[\|e_R\|,\|e_\Omega\|]\in\R^2$, and the matrix \( M \in \R^{2 \times 2} \) is 
	\begin{gather}
		M = \begin{bmatrix}
			k_R c & \frac{k_\Omega c}{2} \\
			\frac{k_\Omega c}{2} & k_\Omega - c \lambda_M H
		\end{bmatrix} .
	\end{gather}
	If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied the matrix \( M \) is positive definite.
	This implies that $\dot{\mathcal{V}}$ is negative semidefinite and $\lim_{t\to\infty} \zeta=0$. 
	As the Lyapunov function is non-increasing $z$ is uniformly bounded. 
%	
%	
%	This implies that the Lyapunov function \( V \) is non-increasing and bounded from below.
%	Furthermore, since \( V \) is nonincreasing the disturbance error \( e_\Delta\) is bounded.
%	Since \( \dot{V} \) is uniformly continuous in time this implies that the zero equilibrium \( e_R, e_\Omega\) is stable in the sense of Lyapunov
%	The domain \( D \) does that include the undesired equilibria and ensures that as \( e_R \to 0 \) the attitude also converges \( R \to R_d \).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

\bibliography{BibMaster,library}
\bibliographystyle{IEEEtran}

\biography{Wu_2}{Tse-Huai Wu}
    {received the M.S. degree from the George Washington University in 2013. He is currently pursuing a Ph.D. at GWU's Department of Mechanical and Aerospace Engineering. His research interests include the control system design for autonomous vehicles and the application of nonlinear control theory, such as spacecraft control and estimation.}

\biography{Lee}{Taeyoung Lee}
    {is an associate professor of Department of Mechanical and Aero- space Engineering at the George Washington University. He received his doctoral degree in Aerospace Engineering and his master's degree in Mathematics at the University of Michigan in 2008. His research interests include computational geometric mechanics and control of complex systems.}    
\clearafterbiography\relax
\clearafterbiography\relax
\end{multicols}
\end{document}

### 2016-08-12 manuscript.tex
Fix the stupid template. And get it to compile

@@
 
-% NEED TO CHANGE ALL SUBFIGURES TO USE THE OBSOLETE SUBFIGURE PACKAGE
-
-http://tug.ctan.org/obsolete/macros/latex/contrib/subfigure/subfigure.pdf
-http://tex.stackexchange.com/questions/313249/confict-between-the-subfigure-and-customized-captionside-by-side-subfigures
-
 \newcommand{\squeezeup}{\vspace{-2.5mm}}
-
-\newcommand{\EditTL}[1]{{\color{red}\protect #1}}
-%\renewcommand{\EditTL}[1]{{\protect #1}}
 
@@
 %% Authors do not have to modify this section.
-\journalvolumn{VV}
-\journalnumber{N}
-\journalyear{YYYY}
-\setarticlestartpagenumber{1}
+% \journalvolumn{VV}
+% \journalnumber{N}
+% \journalyear{YYYY}
+% \setarticlestartpagenumber{1}
 %%%% End of Editorial Information
@@
 \newtheorem{cor}{Corollary}
-\newtheorem{remark}{Remark}
 
 \begin{document}
+
 \title{\LARGE \bf
@@
 Then, the following properties hold
-\begin{enumerate}[(i)]
+\begin{enumerate}[i]
 	\item \label{item:prop_psi_psd} \(\Psi\) is positive definite about \( R = R_d\)
@@
 The control system is defined such that the attitude trajectory follows the negative gradient of \( \Psi \) toward the minimum at \( R = R_d \), while avoiding the constrained region.
-\begin{figure} 
+\begin{figure}[H] 
 	\centering 
-	\begin{subfigure}[htbp]{0.45\columnwidth} 
-		\includegraphics[width=\columnwidth]{attract_error} 
-		\caption{Attractive \( A(R) \) } \label{fig:attract_error} 
-	\end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
-	\begin{subfigure}[htbp]{0.45\columnwidth} 
-		\includegraphics[width=\columnwidth]{avoid_error} 
-		\caption{Repulsive \( B(R) \)} \label{fig:avoid_error} 
-	\end{subfigure}
-	\centering
-	\begin{subfigure}[htbp]{0.45\columnwidth} 
-		\includegraphics[width=\columnwidth]{combined_error} 
-		\caption{Configuration \( \Psi \)} \label{fig:combined_error} 
-	\end{subfigure}
+    \subfigure[Attractive \( A(R) \) \label{fig:attract_error}]{\includegraphics[width=0.45\columnwidth]{attract_error} }~
+	\subfigure[Repulsive \( B(R) \) \label{fig:avoid_error} ]{\includegraphics[width=0.45\columnwidth]{avoid_error} }\\ %add desired spacing between images, e.
+g.
+~, \quad, \qquad, \hfill etc.
+%(or a blank line to force the subfigure onto a new line)
+    \subfigure[Configuration \( \Psi \) \label{fig:combined_error}]{\includegraphics[width=0.45\columnwidth]{combined_error} }
 	\caption{Configuration error function visualization}
@@
 The first term of~\cref{eqn:delta_dot} has the effect of increasing the proportional gain of the control system, since the time derivative of the attitude error vector, \( \dot{e}_{R} \), is linear with respect to the angular velocity error vector \( e_\Omega\).
-\begin{figure} 
+\begin{figure}[H] 
 	\centering 
-	\subfigure{Attitude error vector \(e_R\) \label{fig:eR_con}{eR_con} 
-	\begin{subfigure}[htbp]{0.5\columnwidth} 
-		\includegraphics[width=\columnwidth]{Psi_con} 
-		\caption{Configuration error \( \Psi \)} \label{fig:Psi_con} 
-	\end{subfigure}
+	\subfigure[Attitude error vector \(e_R\) \label{fig:eR_con}]{\includegraphics[width=0.5\columnwidth]{eR_con}  }~
+	\subfigure[Configuration error \( \Psi \) \label{fig:Psi_con}]{\includegraphics[width=0.5\columnwidth]{figures/Psi_con.pdf} }  
 	\caption{Attitude stabilization without adaptive update law}
@@
 \end{figure}
-\begin{figure} 
+\begin{figure}[H] 
 	\centering 
-	\begin{subfigure}[htbp]{0.5\columnwidth} 
-		\includegraphics[width=\columnwidth]{Psi_adapt} 
-		\caption{Configuration error \( \Psi \)} \label{fig:Psi_adapt} 
-	\end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
-	\begin{subfigure}[htbp]{0.5\columnwidth} 
-		\includegraphics[width=\columnwidth]{constraint_angles} 
-		\caption{Angle to constraints} \label{fig:con_angles} 
-	\end{subfigure}
-
-	\centering
-	\begin{subfigure}[htbp]{0.5\columnwidth} 
-		\includegraphics[width=\columnwidth]{delta_adapt} 
-		\caption{Disturbance estimate \( \bar \Delta \)} \label{fig:delta_adapt} 
-	\end{subfigure}~
-	\begin{subfigure}[htbp]{0.5\columnwidth} 
-		\includegraphics[trim=9cm 2.5cm 0 0,clip,width=1.29\columnwidth]{cad_adapt} 
-		\caption{Attitude trajectory} \label{fig:cad_adapt} 
-	\end{subfigure}
+    \subfigure[Configuration error \( \Psi \)\label{fig:Psi_adapt}]{\includegraphics[width=0.5\columnwidth]{Psi_adapt} }~
+    \subfigure[Angle to constraints \label{fig:con_angles}]{\includegraphics[width=0.5\columnwidth]{constraint_angles} }\\
+    \subfigure[Disturbance estimate \( \bar \Delta \)  \label{fig:delta_adapt} ]{\includegraphics[width=0.5\columnwidth]{delta_adapt}}~
+    \subfigure[Attitude trajectory \label{fig:cad_adapt}]{\includegraphics[trim=9cm 2.5cm 0 0,clip,width=0.645\columnwidth]{cad_adapt} }
 	\caption{Attitude stabilization with adaptive update law}
@@
 
-\begin{figure}
+\begin{figure}[H]
 	\centering
@@
 The attitude control system is identical to the one presented in~\Cref{prop:adaptive_control} with the exception of a gravity moment term and the following parameters: \(k_R = 0.4, k_\Omega = 0.7 ,c = 0.1 , \alpha = 8 \text{ and } k_\Delta = 0.05\).
-\begin{figure} 
+\begin{figure}[H]
 	\centering 
-	\begin{subfigure}[htbp]{0.5\columnwidth} 
-		\includegraphics[width=\columnwidth]{eR_exp} 
-		\caption{Attitude error vector \(e_R\) } \label{fig:eR_exp} 
-	\end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
-	\begin{subfigure}[htbp]{0.5\columnwidth} 
-		\includegraphics[width=\columnwidth]{Psi_exp} 
-		\caption{Configuration error \( \Psi \)} \label{fig:Psi_exp} 
-	\end{subfigure}
-
-	\begin{subfigure}[htbp]{0.5\columnwidth} 
-		\includegraphics[width=\columnwidth]{u_exp} 
-		\caption{Control input \( u\)} \label{fig:u_exp} 
-	\end{subfigure}~
-	\begin{subfigure}[htbp]{0.5\columnwidth} 
-		\includegraphics[width=\columnwidth]{traj_exp} 
-		\caption{Attitude Trajectory} \label{fig:traj_exp} 
-	\end{subfigure}
+    \subfigure[{Attitude error vector \(e_R\)} \label{fig:eR_exp}]{\includegraphics[width=0.5\columnwidth]{eR_exp}  }~
+	\subfigure[{Configuration error \( \Psi \)} \label{fig:Psi_exp} ]{\includegraphics[width=0.5\columnwidth]{Psi_exp} }\\
+	\subfigure[{Control input \( u\) }\label{fig:u_exp}]{\includegraphics[width=0.5\columnwidth]{u_exp}  }~
+	\subfigure[{Attitude Trajectory } \label{fig:traj_exp}]{\includegraphics[width=0.5\columnwidth]{traj_exp} }
 	\caption{Constrained Attitude stabilization experiment}
@@
 
-\biography{Wu_2}{Tse-Huai Wu}
+\biography{profile}{Tse-Huai Wu}
     {received the M.S.
@@
 \end{multicols}
+
 \end{document}

### 2016-09-02 manuscript.tex
Working on paper and adding some more detail.
Also dealing with their shit class file that violates all the rules for LaTeX.

@@
 
-\runningtitle{1}{Gil-Dong Hong, Adam Smith, and Ikuro Mizumoto}{Manuscript Template for the International Journal of Control, Automation, and Systems: ICROS {\&} KIEE}
+\runningtitle{1}{Shankar Kulumani, Christopher Poole, and Taeyoung Lee}{Geometric Adaptive Control of Attitude Dynamics on \(\SO\) with State Inequality Constraints}
 
@@
 These attitude representations are not suitable for large angular slews.
-%In order to avoid singularities, the designer must carefully switch the chosen Euler angle sequence based on the operating region.
-%Another option is to artificially limit the operating region of the rigid body.
-%This ensures the system operates in a region free from singularities but limits the performance capabilities and ability to perform arbitrarily large angular maneuvers.
+In order to avoid singularities, the designer must carefully switch the chosen Euler angle sequence based on the operating region.
+Another option is to artificially limit the operating region of the rigid body.
+This ensures the system operates in a region free from singularities but limits the performance capabilities and ability to perform arbitrarily large angular maneuvers.
 Quaternions do not have singularities but they double cover the special orthogonal group.
 As a result, any physical attitude is represented by a pair of antipodal quaternions on the three-sphere.
-%An immediate implication of this ambiguity is that closed-loop stability properties derived using quaternions may not hold for the physical rigid body evolving on the special orthogonal group.
+An immediate implication of this ambiguity is that closed-loop stability properties derived using quaternions may not hold for the physical rigid body evolving on the special orthogonal group.
 During implementation, the designer must carefully resolve this non-unique representation in quaternion based attitude control systems to avoid undesirable unwinding behavior~\cite{bhat2000}.
@@
 These systems require retargeting while avoiding direct exposure to sunlight or other bright objects.
-%Determining a satisfactory attitude control maneuver in the presence of state constraints is a challenging task.
+Determining a satisfactory attitude control maneuver in the presence of state constraints is a challenging task.
 The removal of constrained regions from the rotational configuration space results in a \textit{nonconvex} region.
@@
 
-Model predictive control for spacecraft attitude dynamics is studied in~\cite{guiggiani2014,kalabic2014,gupta2015}.
+Model predictive control for spacecraft attitude dynamics is another popular approach and has been studied in~\cite{guiggiani2014,kalabic2014,gupta2015}.
 These methods rely on linear or non-linear state dynamics to repeatedly solve a finite-time optimal control problem.
-As a result, model predictive control methods are also computational expensive and apply direct optimization methods to solve the necessary conditions for optimality.
+Also known as receeding horizon control, the optimal control formulation allows for a straight forward method to incorporate state and control constraints.
+Computing the optimal control strategy over a moving horizon allows for a form of feedback type control rather than the more typical open-loop optimal control solution.
+As a result, model predictive control methods are also computational expensive and frequently apply direct optimization methods to solve the necessary conditions for optimality.
 Therefore these methods are complicated to implement and not applicable for real-time control applications.
@@
 The goal is the design of attractive and repulsive terms which drive the system toward or away from a certain state, respectively.
-%The goal is the design of an attractive function which drives the system towards the desired state.
-%Similarly, a repulsive function is constructed such that the system is directed away from the constraints. 
+The goal is the design of an attractive function which drives the system towards the desired state.
+Similarly, a repulsive function is constructed such that the system is directed away from the constraints. 
 The superposition of the these functions allows one to apply standard feedback control schemes for stabilization and tracking.
@@
     \widehat{x\times y} = \hat x \hat y -\hat y \hat x = yx^T-xy^T,\label{eqn:hatxy}\\
-    %\tr{\hat x A}=
     \tr{A\hat x }=\frac{1}{2}\tr{\hat x (A-A^T)}=-x^T (A-A^T)^\vee,\label{eqn:hat1}\\
    % \widehat{Ax} = \hat x \parenth{\frac{1}{2}\tr{A}I-A} + \parenth{\frac{1}{2}\tr{A}I-A}^T \hat x,\\
-    \hat x  A+A^T\hat x=(\braces{\tr{A}I_{3\times 3}-A}x)^{\wedge},\label{eqn:xAAx}\\
+    \hat x  A+A^T\hat x=(\braces{\tr{A}I_{3\times 3}-A}x)^{\wedge}, \label{eqn:xAAx} \\
     R\hat x R^T = (Rx)^\wedge,\quad 
     R(x\times y) = Rx\times Ry\label{eqn:RxR}
-%,\label{eqn:Rxy}
 \end{gather}
@@
 Similarly, the positions of celestial objects are defined on the celestial sphere in terms of right ascension and declination. 
+\begin{figure}[H]%
+    \centering 
+    \subfigure[Attractive \( A(R) \) \label{fig:attract_error}]{\includegraphics[width=0.45\columnwidth]{attract_error} }~
+    \subfigure[Repulsive \( B(R) \) \label{fig:avoid_error} ]{\includegraphics[width=0.45\columnwidth]{avoid_error} }\\%add desired spacing between images, e.
+g.
+~, \quad, \qquad, \hfill etc.
+%(or a blank line to force the subfigure onto a new line)
+    \subfigure[Configuration \( \Psi \) \label{fig:combined_error}]{\includegraphics[width=0.45\columnwidth]{combined_error} }%
+    \caption{Configuration error function visualization}
+    \label{fig:config_error} 
+\end{figure}%
 We apply this concept and parametrize the rotation matrix \( R \in \SO \) in terms of the spherical angles \( \SI{-180}{\degree} \leq \lambda \leq \SI{180}{\degree}  \) and \( \SI{-90}{\degree} \leq \beta \leq \SI{90}{\degree} \).
@@
 The control system is defined such that the attitude trajectory follows the negative gradient of \( \Psi \) toward the minimum at \( R = R_d \), while avoiding the constrained region.
-\begin{figure}[H] 
-	\centering 
-    \subfigure[Attractive \( A(R) \) \label{fig:attract_error}]{\includegraphics[width=0.45\columnwidth]{attract_error} }~
-	\subfigure[Repulsive \( B(R) \) \label{fig:avoid_error} ]{\includegraphics[width=0.45\columnwidth]{avoid_error} }\\ %add desired spacing between images, e.
-g.
-~, \quad, \qquad, \hfill etc.
-%(or a blank line to force the subfigure onto a new line)
-    \subfigure[Configuration \( \Psi \) \label{fig:combined_error}]{\includegraphics[width=0.45\columnwidth]{combined_error} }
-	\caption{Configuration error function visualization}
-	\label{fig:config_error} 
-\end{figure}
 
@@
 \end{proof}
+
 \begin{prop}[Adaptive Attitude Control]\label{prop:adaptive_control}
@@
 The simulation parameters are chosen to be similar to those found in~\cite{lee2011b}, however we increase the size of the constraint regions to create a more challenging scenario for the control system.
-
-The initial state is defined as \(R_0 =  \exp(\ang{225} \times \frac{\pi}{180} \hat{e}_3), \Omega_0 = 0\). 
-The desired state is \( R_d = I,\Omega_d = 0\).
-\begin{table}%[htbp]
+\begin{table}[H]
 \caption{Constraint Parameters~\label{tab:constraints}}
@@
 \end{table}
-We show simulation results for the system stabilizing about the desired attitude with and without the adaptive update law from~\Cref{prop:adaptive_control}.
-We assume a fixed disturbance of \(\Delta = \begin{bmatrix} 0.2 & 0.2 & 0.2 \end{bmatrix}^T \), with the function \( W(R,\Omega) = I \).
-This form is equivalent to an integral control term which penalizes deviations from the desired configuration.
-The first term of~\cref{eqn:delta_dot} has the effect of increasing the proportional gain of the control system, since the time derivative of the attitude error vector, \( \dot{e}_{R} \), is linear with respect to the angular velocity error vector \( e_\Omega\).
+
+The initial state is defined as \(R_0 =  \exp(\ang{225} \times \frac{\pi}{180} \hat{e}_3), \Omega_0 = 0\). 
+The desired state is \( R_d = I,\Omega_d = 0\).
 \begin{figure}[H] 
@@
 \end{figure}
+We show simulation results for the system stabilizing about the desired attitude with and without the adaptive update law from~\Cref{prop:adaptive_control}.
+We assume a fixed disturbance of \(\Delta = \begin{bmatrix} 0.2 & 0.2 & 0.2 \end{bmatrix}^T \), with the function \( W(R,\Omega) = I \).
+This form is equivalent to an integral control term which penalizes deviations from the desired configuration.
+The first term of~\cref{eqn:delta_dot} has the effect of increasing the proportional gain of the control system, since the time derivative of the attitude error vector, \( \dot{e}_{R} \), is linear with respect to the angular velocity error vector \( e_\Omega\).
 \begin{figure}[H] 
@@
 These results show that the proposed geometric adaptive approach is critical to attitude stabilization in the presence of state constraints and disturbances.
+\begin{figure}[H]
+    \centering
+    \includegraphics[width = 0.5\columnwidth]{hexrotor}
+    \caption{Attitude control testbed~\label{fig:hexrotor}}
+\end{figure}
 \section{Experiment on Hexrotor UAV}
-A hexrotor unmanned aerial vehicle (UAV) has been developed at the Flight Dynamics and Controls Laboratory (FDCL) at the George Washington University~\cite{kaufman2014}.
-The UAV is composed of three pairs of counter-rotating propellers. 
-%Typical quadrotor UAVs are composed of four or more co-planar propellers.
-%As a result, these systems are underactuated and unable to impart a force along every degree of freedom.
-%For example, quadrotor UAVs are unable to translate laterally without first conducting a rotation.
+A hexrotor unmanned aerial vehicle (UAV), as seen in~\cref{fig:hexrotor}, has been developed at the Flight Dynamics and Controls Laboratory (FDCL) at the George Washington University~\cite{kaufman2014}.
+% The UAV is composed of three pairs of counter-rotating propellers. 
+% Typical UAVs are composed of four or more co-planar propellers.
+% As a result, these systems are underactuated and unable to impart a force along every degree of freedom.
+% For example, quadrotor UAVs are unable to translate laterally without first conducting a rotation.
 %Conversely, the propeller pairs of the hexrotor are angled relative to one another to allow for a fully actuated rigid body.
 The propeller pairs of the hexrotor are angled relative to one another to allow for a fully actuated rigid body.
-%This allows the hexrotor to impart a force in any direction and a moment about any axis.
-
-The hexrotor UAV, shown in~\cref{fig:hexrotor}, is composed of the following hardware:
-\begin{itemize}
-	\item Onboard ODROID XU3 computer module.
-	\item VectorNav VN100 IMU operating via TTL serial %at over \SI{100}{\hertz} 
-	\item BLDC motors with BL-Ctrl-2.0 ESC via I2C.
-	\item Position and attitude over WiFi (TCP) communication from Vicon motion capture system.
-	\item Commands sent over WiFi to  onboard controller. 
-\end{itemize}
+% This allows the hexrotor to impart a force in any direction and a moment about any axis. 
+% Attitude information is measured by an onboard IMU and Vicon motion capture system.
+The control input is computed onboard the hexrotor using data transmitted via WiFi.
 In order to constrain the motion and test only the attitude dynamics we attach the hexrotor to a spherical joint.
-The center of rotation is below the center of gravity of the hexrotor.
-As a result, there is a destabilizing gravitational moment and the resulting attitude dynamics are similar to an inverted pendulum model.
+Since, the center of rotation is below the center of gravity of the hexrotor there is a destabilizing gravitational moment
+The resulting attitude dynamics are similar to an inverted pendulum model.
 We augment the control input in~\cref{eqn:adaptive_control} with an additional term to negate the effect of the gravitational moment.
 
-\begin{figure}[H]
-	\centering
-	\includegraphics[width = 0.7\columnwidth]{hexrotor}
-	\caption{Attitude control testbed~\label{fig:hexrotor}}
-\end{figure}
 A sensor pointing direction is defined in the body frame of the hexrotor as \( r = [1,0,0]^T \).
@@
 \end{figure}
-
 The experimental results are shown in~\Cref{fig:exp}.
@@
 A video clip showing the attitude maneuver is available \url{https://youtu.be/dsmAbwQram4}.
+
 \section{Conclusions}\label{sec:conclusions}
@@
 
-%To show~\cref{item:prop_crit}, we determine the critical points of~\cref{eqn:eRA}.
-%The attitude error between \( R \) and \( R_d \) is defined by \( Q \in \SO \) as
-%\begin{align*}
+% To show~\cref{item:prop_crit}, we determine the critical points of~\cref{eqn:eRA}.
+% The attitude error between \( R \) and \( R_d \) is defined by \( Q \in \SO \) as
+% \begin{align*}
 % 	Q = R_d^T R = 
@@
 % 	\end{bmatrix} .
-%\end{align*}
-%Equating \( e_{R_{A}} = 0 \) yields the following equivalent relations
-%\begin{subequations}
-%\begin{align}
+% \end{align*}
+% Equating \( e_{R_{A}} = 0 \) yields the following equivalent relations
+% \begin{align*}
 % 	g_3 q_{32} &= g_2 q_{23} , \\
@@
 % 	g_2 q_{21} &= g_1 q_{12} .
-%\end{align}
-%\end{subequations}
-%These relations allow one to redefine the attitude error \( Q \) in terms of the independent upper diagonal elements.
-%Noting that \( Q \in \SO \) is an orthonormal matrix, with unit length row and columns gives
-%\begin{subequations}
-%\begin{align}
+% \end{align*}
+% These relations allow one to redefine the attitude error \( Q \) in terms of the independent upper diagonal elements.
+% Noting that \( Q \in \SO \) is an orthonormal matrix, with unit length row and columns gives
+% \begin{align*}
 % 	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 + \parenth{1 - \frac{g_1^2}{g_3^2}}q_{13}^2 &= 0 , \\
@@
 % 	\parenth{1-\frac{g_1^2}{g_3^2}} q_{13}^2 + \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 .
-%\end{align}
-%\end{subequations}
-%As a result, all the off diagonal terms of \( Q = R_d^T R \) are zero, namely \( q_{12}= q_{13} = q_{23} = 0 \).
-%Since \( Q \in \SO \), the diagonal elements \( q_{11}, q_{22}, \text{ and } q_{33} \) are either \( +1 \) or \(-1\).
+% \end{align*}
+
+% As a result, all the off diagonal terms of \( Q = R_d^T R \) are zero, namely \( q_{12}= q_{13} = q_{23} = 0 \).
+% Since \( Q \in \SO \), the diagonal elements \( q_{11}, q_{22}, \text{ and } q_{33} \) are either \( +1 \) or \(-1\).
 The critical points of \( e_{R_A} \) are derived in~\cite{bullo2004}.
@@
 The proof of \( \norm{e_{R_A}} \) given by~\cref{item:prop_era_upbound} is available in~\cite{LeeITCST13}.
+
 \subsection{Proof of~\Cref{prop:error_dyn}}\label{proof:error_dyn}
@@
 Consider the following Lyapunov function:
-\begin{gather}
-	\mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi(R,R_d) . \label{eqn:v_nodist}
-\end{gather}
+\begin{gather*}%\label{eqn:v_nodist}
+	\mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi(R,R_d) . 
+\end{gather*}
 From~\cref{item:prop_psi_psd} of~\Cref{prop:config_error}, \(\mathcal{V} \geq 0 \).
 Using~\cref{eqn:eW_dot,eqn:psi_dot} with \( \Delta = 0 \), the time derivative of \( \mathcal{V} \) is given by
-\begin{align}
-	\dot{\mathcal{V}} &= -k_\Omega \norm{e_\Omega}^2 . \label{eqn:vdot_nodist}
+\begin{align*}%\label{eqn:vdot_nodist}
+	\dot{\mathcal{V}} &= -k_\Omega \norm{e_\Omega}^2 . 
 %	e_\Omega^T \parenth{ u - \Omega \times J \Omega } + k_R e_R \cdot e_\Omega \nonumber \\
-\end{align}
+\end{align*}
 Since \( \mathcal{V} \) is positive definite and \( \dot{\mathcal{V}} \) is negative semi-definite, the zero equilibrium point \( e_R, e_\Omega \) is stable in the sense of Lyapunov. 
@@
 Using~\crefrange{eqn:AB_bound}{eqn:eRB_bound} one can define \( H \) in terms of known values.
+
 \subsection{Proof of~\Cref{prop:adaptive_control}}\label{proof:adaptive_control}
 Consider the Lyapunov function \( \mathcal{V} \) given by
-	\begin{gather}
+\begin{align*}
 	\mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi + c J e_\Omega \cdot e_R + \frac{1}{2 k_\Delta} e_\Delta \cdot e_\Delta , \label{eqn:v_adapt}
-	\end{gather}
+\end{align*}
 over the domain \( D \) in~\cref{eqn:domain}.
 From~\Cref{prop:eR_dot_bound}, the Lyapunov function is bounded in \( D \) by
-	\begin{gather}
-		\mathcal{V} \leq z^T W z , \label{eqn:v_upper_bound}
-	\end{gather}
+\begin{align*} %\label{eqn:v_upper_bound}
+	\mathcal{V} \leq z^T W z ,
+\end{align*}
 where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = [\|e_R\|,\|e_\Omega\|,\|e_\Delta\|]^T\in\R^3 \) and the matrix \(W \in \R^{3 \times 3}\) is given by
@@
 The time derivative of \( \mathcal{V}\) with the control inputs~\cref{eqn:adaptive_control} is given by
-	\begin{align}
+\begin{align*}
 	\dot{\mathcal{V}} =& - k_\Omega e_\Omega^T e_\Omega + \parenth{e_\Omega + c e_R}^T W e_\Delta - k_R c e_R^T e_R \nonumber\\
 	&- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} , \label{eqn:vdot}
-	\end{align}
+\end{align*}
 where we used \( \dot{e}_\Delta = - \dot{\bar{\Delta}} \).
@@
 where $\zeta=[\|e_R\|,\|e_\Omega\|]\in\R^2$, and the matrix \( M \in \R^{2 \times 2} \) is 
-	\begin{gather}
+\begin{gather*}
 	M = \begin{bmatrix}
@@
 	\end{bmatrix} .
-	\end{gather}
+\end{gather*}
 If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied the matrix \( M \) is positive definite.
@@
 
-\biography{profile}{Tse-Huai Wu}
-    {received the M.S.
-degree from the George Washington University in 2013.
-He is currently pursuing a Ph.D.
-at GWU's Department of Mechanical and Aerospace Engineering.
-His research interests include the control system design for autonomous vehicles and the application of nonlinear control theory, such as spacecraft control and estimation.}
+\biography{profile}{Shankar Kulumani}
+    {is a PhD Candidate in the Department of Mechanical and Aerospace Engineering at George Washington University. 
+    He received his bachelor's degree in Astronautical Engineering from the United States Air Force Academy in 2009 and his master's in Aeronautical and Astronautical Engineering from Purdue University in 2013.
+    He previously served as Deputy Space Vehicles Lead for the ORS-1 (Operationally Responsive Space ) satellite program, and as Lead Test Engineer in the Guidance, Navigation, and Control group at Air Force Research Laboratory located at Kirtland AFB, NM.
+    % He is now currently a reserve air force officer where he serves as Threat Systems Engineer for the Missle and Space Intelligence Center, Defense Intelligence Agency.
+    His current research interests include the application of geometric mechanics and control for aerospace systems. 
+    }
 
 \biography{Lee}{Taeyoung Lee}
-    {is an associate professor of Department of Mechanical and Aero- space Engineering at the George Washington University.
+    {is an associate professor of Department of Mechanical and Aerospace Engineering at the George Washington University. 
     He received his doctoral degree in Aerospace Engineering and his master's degree in Mathematics at the University of Michigan in 2008. 

### 2016-09-03 manuscript.tex
working to get it under 10 pages

@@
 \makeAuthorInformation{
-Manuscript received January 20, 2015; revised February 10,2015; accepted March 10, 2015. Recommended by Associate Editor Soon-Shin Lee under the direction of Editor Milton John.
+Manuscript received DATE; revised DATE; accepted DATE. Recommended by Associate Editor Soon-Shin Lee under the direction of Editor Milton John.
 Shankar Kulumani, Christopher Poole, Taeyoung Lee, Mechanical and Aerospace Engineering, George Washington University, Washington DC 20052 {\tt \{skulumani,poolec,tylee\}@gwu.edu}
@@
 where we assume \( \ang{0} \leq \theta \leq \ang{90}  \) is the required minimum angular separation between \( r \) and \( R^T v \). 
-
 The objective is to a determine a control input \( u \) that stabilizes the system from an initial attitude \( R_0 \) to a desired attitude \( R_d \) while ensuring that~\cref{eqn:constraint} is always satisfied.
-
+\squeezeup
 \section{Attitude Control on $\SO$ with Inequality Constraints}
@@
 \begin{proof}
-See~\Cref{proof:config_error}.
+See~\Cref{proof:config_error}
 \end{proof}
@@
 \begin{proof}
-See~\Cref{proof:error_dyn}.
+See~\Cref{proof:error_dyn}
 \end{proof}
@@
 \end{prop}
-
 \begin{proof}
-See~\Cref{proof:att_control}.
+See~\Cref{proof:att_control}
 \end{proof}
@@
 \end{prop}
-
 \begin{proof}
-See~\Cref{proof:eR_dot_bound}.
+See~\Cref{proof:eR_dot_bound}
 \end{proof}
@@
 \begin{proof}
-See~\Cref{proof:adaptive_control}.
+See~\Cref{proof:adaptive_control}
 \end{proof}
@@
     He received his bachelor's degree in Astronautical Engineering from the United States Air Force Academy in 2009 and his master's in Aeronautical and Astronautical Engineering from Purdue University in 2013.
-    He previously served as Deputy Space Vehicles Lead for the ORS-1 (Operationally Responsive Space ) satellite program, and as Lead Test Engineer in the Guidance, Navigation, and Control group at Air Force Research Laboratory located at Kirtland AFB, NM.
+    % He previously served as Deputy Space Vehicles Lead for the ORS-1 (Operationally Responsive Space ) satellite program, and as Lead Test Engineer in the Guidance, Navigation, and Control group at Air Force Research Laboratory located at Kirtland AFB, NM.
     % He is now currently a reserve air force officer where he serves as Threat Systems Engineer for the Missle and Space Intelligence Center, Defense Intelligence Agency.

### 2016-09-09 manuscript.tex
Working on expanding and fixing mistakes

@@
 \title{\LARGE \bf
-Geometric Adaptive Control of Attitude Dynamics on \(\SO\)\\ with State Inequality Constraints}
+Constrained Attitude Control on \( \SO \) }
 
@@
 
-\runningtitle{1}{Shankar Kulumani, Christopher Poole, and Taeyoung Lee}{Geometric Adaptive Control of Attitude Dynamics on \(\SO\) with State Inequality Constraints}
+\runningtitle{1}{Shankar Kulumani, Christopher Poole, and Taeyoung Lee}{Constrained Attitude Control on \( \SO \) }
 
@@
 As a result, any physical attitude is represented by a pair of antipodal quaternions on the three-sphere.
-An immediate implication of this ambiguity is that closed-loop stability properties derived using quaternions may not hold for the physical rigid body evolving on the special orthogonal group.
+An immediate implication of this ambiguity is that closed-loop stability properties derived using quaternions may not hold for the physical rigid body evolving on the true configuration space, namely the special orthogonal group.
 During implementation, the designer must carefully resolve this non-unique representation in quaternion based attitude control systems to avoid undesirable unwinding behavior~\cite{bhat2000}.
-%, where the rigid body starts close to the desired attitude, yet the system unnecessarily rotates through a large angle even while the initial error is small.
+This behavior is characterized by situations where the rigid body starts close to the desired attitude, yet the system unnecessarily rotates through a large angle even while the initial error is small.
 
@@
 These systems require retargeting while avoiding direct exposure to sunlight or other bright objects.
+In addition, many ground based attitude testing environments, such as air bearing platforms, must operate in the presence of physical obstructions.
 Determining a satisfactory attitude control maneuver in the presence of state constraints is a challenging task.
@@
 Typically, an optimal or easily implementable on-board control scheme for attitude maneuvers is applied to maneuver the vehicle along these segments.
-In this manner it is possible to accomplish constraint avoidance by linking several intermediary unconstrained maneuvers.
+In this manner, it is possible to accomplish constraint avoidance by linking several intermediary unconstrained maneuvers.
 While this method is conceptually simple, it is difficult to generalize for an arbitrary number of constraints.
@@
 A graph is generated consisting of vertices from an initial attitude to a desired attitude. 
-A random iterative search is conducted to determine a path through a directed graph such that a given cost functional is minimized.
+A random iterative search is conducted to determine a path through a directed graph such that a given cost, which parameterizes the path cost, is minimized.
 The random search approach can only stochastically guarantee attitude convergence as it can be shown that as the number of vertices in the graph grow, the probability of nonconvergence goes to zero.
-However, the computational demand grows as the size of the graph is increased. 
+However, the computational demand grows as the size of the graph is increased and a new graph is required when constraints are modified. 
 As a result, random search approaches are ill-suited to on-board implementation or in scenarios that require agile maneuvers.
@@
 These methods rely on linear or non-linear state dynamics to repeatedly solve a finite-time optimal control problem.
-Also known as receeding horizon control, the optimal control formulation allows for a straight forward method to incorporate state and control constraints.
+Also known as receding horizon control, the optimal control formulation allows for a straight forward method to incorporate state and control constraints.
 Computing the optimal control strategy over a moving horizon allows for a form of feedback type control rather than the more typical open-loop optimal control solution.
-As a result, model predictive control methods are also computational expensive and frequently apply direct optimization methods to solve the necessary conditions for optimality.
-Therefore these methods are complicated to implement and not applicable for real-time control applications.
+Due to the iterative nature of solving optimization problems, model predictive control methods are computational expensive and frequently apply direct optimization methods to solve the necessary conditions for optimality.
+Therefore, these methods are complicated to implement and not applicable for real-time control applications.
 
-% Previous potential function approach - developed using att parameterizations - singularities/ambiguities
+% Previous potential function approach - developed using attitude parameterizations - singularities/ambiguities
 Artificial potential functions are commonly used to handle kinematic constraints for a wide range of problems in robotics~\cite{rimon1992}.
-The goal is the design of attractive and repulsive terms which drive the system toward or away from a certain state, respectively.
-The goal is the design of an attractive function which drives the system towards the desired state.
+The goal is the design of attractive and repulsive terms which drive the system toward or away from a certain obstacle, respectively.
+The attractive function is designed to drive the system towards the desired state.
 Similarly, a repulsive function is constructed such that the system is directed away from the constraints. 
@@
 A configuration error function on \(\SO\) with a logarithmic barrier function is proposed to avoid constrained regions. 
-Instead of calculating a priori trajectories, as in the geometric and randomized approaches, our approach results in a closed-loop attitude control system. 
+Instead of calculating a priori trajectories, as in the randomized approaches, our approach results in a closed-loop attitude control system. 
 This makes it ideal for on-board implementation on UAV or spacecraft systems. 
 In addition, unlike previous approaches our control system can handle an arbitrary number of constrained regions without modification.
+This approach results in a conceptually simple obstacle avoidance scheme which extends the previous work of artificial potential functions on Euclidean spaces to the more challenging Special Orthogonal Group.
 
-Furthermore, we formulate an adaptive update law to enable attitude convergence in the presence of uncertain disturbances. 
+Furthermore, we use this new configuration error function to design an adaptive update law to enable attitude convergence in the presence of uncertain disturbances. 
 The stability of the proposed control systems is verified via mathematically rigorous Lyapunov analysis on $\SO$.  
-In short, the proposed attitude control system in the presence of inequality constraints is computationally efficient and able to handle uncertain disturbances. 
-The effectiveness of this approach is illustrated via numerical simulation and experimental results.% on a hexrotor aerial vehicle.
+In short, the proposed attitude control system in the presence of inequality constraints is geometrically exact, computationally efficient and able to handle uncertain disturbances. 
+The effectiveness of this approach is illustrated via numerical simulation and demonstrated via experimental results.% on a hexrotor aerial vehicle.
 
@@
 This form of uncertainty enters the system dynamics through the input channel and as a result is referred to as a matched uncertainty. 
-While this form of uncertainty is easier than the unmatched variety many physically realizable disturbances may be modeled in this manner.
+While this form of uncertainty is easier than the unmatched variety, many physically realizable disturbances may be modeled in this manner.
 For example, orbital spacecraft are subject to gravity gradient torques caused by the non-spherical distribution of mass of both the spacecraft and central gravitational body.
@@
 In addition, for typical scenarios, where the spacecraft is significantly smaller than the orbital radius, the disturbance torque may be assumed constant over short time intervals.
+Another terrestrial example is frequently encountered by unmanned aerial vehicles. 
+Multiple actuator systems, such as quadrotor aerial vehicles, may exhibit an uneven mass distribution during load transportation or must operate in the presence of turbulence. 
+Treating these effects as disturbances is a popular method to design control systems.
 
@@
 Once an appropriate configuration error function is chosen, one can then define a configuration error vector and a velocity error vector in the tangent space \( \mathsf{T}_q \Q \) through the derivatives of \( \Psi \)~\cite{bullo2004}.
-With the configuration error function and vectors the remaining procedure is analogous to nonlinear control design on Euclidean vector spaces. 
+With the configuration error function and vectors, the remaining procedure is analogous to nonlinear control design on Euclidean vector spaces. 
 One chooses control inputs as functions of the state through a Lyapunov analysis on \Q.
@@
 A smooth control system is first developed assuming that there is  no disturbance, and then it is extended to include an adaptive update law for stabilization in the presence of unknown disturbances. 
-The proposed attitude configuration error function and several properties are summarized as follows.
+The proposed attitude configuration error function and several properties are summarized as follows in~\Cref{prop:config_error}
 
@@
 Then, the following properties hold
-\begin{enumerate}[i]
+\begin{enumerate}[(i)]
 	\item \label{item:prop_psi_psd} \(\Psi\) is positive definite about \( R = R_d\)
@@
 In order to visualize the attitude error function on \( \SO \) we utilize a spherical coordinate representation.
-Recall that the spherical coordinate system represents the position of a point relative to an origin in terms of a radial distance, azimuth, and elevation.
+Recall, that the spherical coordinate system represents the position of a point relative to an origin in terms of a radial distance, azimuth, and elevation.
 This coordinate system is commonly used to define locations on the Earth in terms of a latitude and longitude.
@@
 The potential well of \( A(R)\) is illustrated in~\cref{fig:attract_error}, where the desired attitude lies at the minimum of \( A(R) \).
+As shown in~\Cref{prop:config_error}, there are a maximum four possible critical points of~\cref{eqn:psi}.
+The addition of the repulsive barrier term places additional conditions on the critical points, namely that the undesired critical points of \( A(R) \) must also satisfy \( R^T v = \pm r \).
+As a result, there will frequently be fewer equilibrium points with the addition of the barrier term, \( B(R) \), than with \( A(R) \) alone.
 
@@
 
-While~\cref{eqn:B} represents a single inequality constraint given as~\cref{eqn:constraint}, it is readily generalized to multiple constraints of an arbitrary form. 
+While~\cref{eqn:B} represents a single inequality constraint given as~\cref{eqn:constraint}, it is readily generalized to multiple constraints of an arbitrary orientation. 
 For example, the configuration error function can be formulated as $\Psi=A[1+\sum_i C_i]$, where $C_i$ has the form of $C_i=B-1$ for the $i$-th constraint. 
 In this manner, one may enforce multiple state inequality constraints, and we later demonstrate this through numerical simulation. 
+This is in contrast to many previous approaches which are computationally difficult to extend to situations with multiple constraints.
+We present the dynamics of the configuration error function in~\Cref{prop:error_dyn}, which are used in the subsequent development of the nonlinear control system.
 
@@
 We introduce a nonlinear geometric controller for the attitude stabilization of a rigid body.
-We first assume that there is no disturbance, i.e., \( \Delta = 0 \).
+We first assume that there is no disturbance, i.e., \( \Delta = 0 \) and present a nonlinear controller in~\Cref{prop:att_control}.
 \begin{prop}[Attitude Control]\label{prop:att_control}
@@
 This proposition only guarantees that the attitude error vector \( e_R \) asymptotically converges to zero.
-However, this does not necessarily imply that \( R \to R_d \) as \( t \to \infty \), since there are at most three additional critical points of \( \Psi \) where \( e_R = 0 \) and \( R^T v = \pm r\).
+However, this does not necessarily imply that \( R \to R_d \) as \( t \to \infty \), since there are at most three additional critical points of \( A(R) \) where \( e_R = 0 \) and \( R^T v = \pm r\).
 At an undesired equilibrium \( R = \exp{ \parenth{\pi \hat{e}_i}} R_d \) and \( e_\Omega =0 \).
@@
 
+Adaptive control is typically used in dynamical systems with varying or uncertain components.
+In~\Cref{prop:adaptive_control}, we present an adaptive attitude controller which handles uncertain disturbances while satisfying the state inequality constraints.
+
 \begin{prop}[Adaptive Attitude Control]\label{prop:adaptive_control}
@@
 Compared to the previous work on constrained attitude control, we present a geometrically exact control system without parameterizations.
+The controller is designed on the true configuration manifold, \( \SO \), and is free from the issues associated with other attitude representations.
 In addition, we incorporate state inequality constraints for the first time on \( \SO \).
 The presented control system is computed in real-time and offers significant computational advantages over previous iterative methods. 
-In addition, the riguous mathematical proof guarantees stability.
+In addition, the rigorous mathematical proof guarantees stability.
+This is in contrast to many of the previous methods which offer no stability guarantees.
+The presented analysis offers provable bounds on the expected motion, which are critical for hardware implementation or mission critical applications.
+
 \section{Numerical Examples}
@@
 These results show that the proposed geometric adaptive approach is critical to attitude stabilization in the presence of state constraints and disturbances.
+
+\section{Experiment on Hexrotor UAV}
+
+A hexrotor unmanned aerial vehicle (UAV), as seen in~\cref{fig:hexrotor}, has been developed at the Flight Dynamics and Controls Laboratory (FDCL) at the George Washington University~\cite{kaufman2014}.
+The UAV is composed of three pairs of counter-rotating propellers. 
+Typical UAVs are composed of four or more co-planar propellers.
+As a result, these systems are underactuated and unable to impart a force along every degree of freedom.
+For example, quadrotor UAVs are unable to translate laterally without first conducting a rotation.
+Conversely, the propeller pairs of the hexrotor are angled relative to one another to allow for a fully actuated rigid body.
+This allows the hexrotor to impart a force in any direction and a moment about any axis.
+
 \begin{figure}[H]
     \centering
-    \includegraphics[width = 0.5\columnwidth]{hexrotor}
+    \includegraphics[width = 0.75\columnwidth]{hexrotor}
     \caption{Attitude control testbed~\label{fig:hexrotor}}
 \end{figure}
-\section{Experiment on Hexrotor UAV}
-A hexrotor unmanned aerial vehicle (UAV), as seen in~\cref{fig:hexrotor}, has been developed at the Flight Dynamics and Controls Laboratory (FDCL) at the George Washington University~\cite{kaufman2014}.
-% The UAV is composed of three pairs of counter-rotating propellers. 
-% Typical UAVs are composed of four or more co-planar propellers.
-% As a result, these systems are underactuated and unable to impart a force along every degree of freedom.
-% For example, quadrotor UAVs are unable to translate laterally without first conducting a rotation.
-%Conversely, the propeller pairs of the hexrotor are angled relative to one another to allow for a fully actuated rigid body.
-The propeller pairs of the hexrotor are angled relative to one another to allow for a fully actuated rigid body.
-% This allows the hexrotor to impart a force in any direction and a moment about any axis. 
-% Attitude information is measured by an onboard IMU and Vicon motion capture system.
-The control input is computed onboard the hexrotor using data transmitted via WiFi.
-In order to constrain the motion and test only the attitude dynamics we attach the hexrotor to a spherical joint.
+Attitude information is measured by an onboard IMU and a Vicon motion capture system in the test area.
+The control input is computed onboard the hexrotor using data transmitted via WiFi in a client/server model.
+In order to constrain the motion, allowing us to test only the attitude dynamics, we attach the hexrotor to a spherical joint.
 Since, the center of rotation is below the center of gravity of the hexrotor there is a destabilizing gravitational moment
@@
 When constrained to the spherical joint, the hexrotor is capable of performing responsive attitude changes with high angular velocities.
-In addition, The on-board control and motion capture system operate at a discrete interval of approximately \SI{100}{\hertz}.
+In addition, the on-board control and motion capture system operate at a discrete interval of approximately \SI{100}{\hertz}.
 It is possible for the system to violate the constraint between these discrete steps and cause numerical exceptions within the embedded software. 
@@
 The hexrotor avoids the constrained region illustrated by the circular cone in~\cref{fig:traj_exp}, by rotating around the boundary of the constraint. 
-This verifies that the proposed control system exhibits the desired performance in the experimental setting as well. 
+This further validates that the proposed control system exhibits the desired performance in the experimental setting as well. 
 A video clip showing the attitude maneuver is available \url{https://youtu.be/dsmAbwQram4}.
@@
     % He is now currently a reserve air force officer where he serves as Threat Systems Engineer for the Missle and Space Intelligence Center, Defense Intelligence Agency.
-    His current research interests include the application of geometric mechanics and control for aerospace systems. 
+    His current research interests include the application of geometric mechanics and control to aerospace systems. 
     }

### 2016-09-22 manuscript.tex
Add some comments from Dr. Lee

@@
 
-\author{Shankar Kulumani, Christopher Poole, and Taeyoung Lee}%
+\author{Shankar Kulumani* and Taeyoung Lee}%
 
@@
 \makeAuthorInformation{
-Manuscript received DATE; revised DATE; accepted DATE. Recommended by Associate Editor Soon-Shin Lee under the direction of Editor Milton John.
-Shankar Kulumani, Christopher Poole, Taeyoung Lee, Mechanical and Aerospace Engineering, George Washington University, Washington DC 20052 {\tt \{skulumani,poolec,tylee\}@gwu.edu}
+Manuscript received DATE; revised DATE; accepted DATE.
+Shankar Kulumani, Mechanical and Aerospace Engineering, George Washington University, Washington DC 20052 {\tt \{skulumani,tylee\}@gwu.edu}
 
-This research has been supported in part by NSF under the grants CMMI-1243000, CMMI-1335008, and CNS-1337722.
+This research has been supported in part by NSF under the grants CMMI-1243000, CMMI-1335008, and CNS-1337722.\\
 * Corresponding author.\vskip 0.5pc
@@
 The removal of constrained regions from the rotational configuration space results in a \textit{nonconvex} region.
-The attitude control problem in the absence of constraints has been extensively studied~\cite{bullo2004,MayTeePaCC11,LEEITAC15}.
+The attitude control problem in the feasible configuration space has been extensively studied~\cite{bullo2004,MayTeePaCC11,LEEITAC15}.
 However, the attitude control problem in the presence of constraints has received much less attention.
@@
 Typically, an optimal or easily implementable on-board control scheme for attitude maneuvers is applied to maneuver the vehicle along these segments.
-In this manner, it is possible to accomplish constraint avoidance by linking several intermediary unconstrained maneuvers.
+In this manner, it is possible to solve the constrained attitude control problem by linking several intermediary unconstrained maneuvers.
 While this method is conceptually simple, it is difficult to generalize for an arbitrary number of constraints.
@@
 Due to the iterative nature of solving optimization problems, model predictive control methods are computational expensive and frequently apply direct optimization methods to solve the necessary conditions for optimality.
-Therefore, these methods are complicated to implement and not applicable for real-time control applications.
+Therefore, these methods are complicated to implement and may not be suitable for real-time control applications.
 
@@
 In addition, unlike previous approaches our control system can handle an arbitrary number of constrained regions without modification.
-This approach results in a conceptually simple obstacle avoidance scheme which extends the previous work of artificial potential functions on Euclidean spaces to the more challenging Special Orthogonal Group.
+This approach results in a conceptually simple obstacle avoidance scheme which extends the previous work of artificial potential functions on Euclidean spaces to the special orthogonal group.
 
@@
 \subsection{Attitude Dynamics}\label{sec:att_dyn}
-Consider the attitude dynamics of a rigid body--we define an inertial reference frame and a body frame whose origin is at the center of mass and aligned with the principle directions of the body. 
+Consider the attitude dynamics of a rigid body.
+We define an inertial reference frame and a body-fixed frame whose origin is at the center of mass and aligned with the principle directions of the body. 
 The configuration manifold of the attitude dynamics is the special orthogonal group:
@@
 \begin{equation}
-	\norm{W} \leq B_W , \quad \norm{\Delta} \leq B_\Delta \,. \label{eqn:W_bound}
+	\norm{W} \leq B_W , \quad \norm{\Delta} \leq B_\Delta \,, \label{eqn:W_bound}
 \end{equation}
+for positive constants \( B_W, B_\Delta\).
 This form of uncertainty enters the system dynamics through the input channel and as a result is referred to as a matched uncertainty. 
@@
 
-The two-sphere is the manifold of unit-vectors in \( \R^3 \) such that \( \Sph^2 = \{ q \in \R^3 \,  \vert \, \norm{q} = 1 \}\).
+The two-sphere is the manifold of unit-vectors in \( \R^3 \), i.e., \( \Sph^2 = \{ q \in \R^3 \,  \vert \, \norm{q} = 1 \}\).
 We define \( r \in \Sph^2 \) to be a unit vector from the mass center of the rigid body along a certain direction and it is represented with respect to the body-fixed frame.
@@
 A smooth control system is first developed assuming that there is  no disturbance, and then it is extended to include an adaptive update law for stabilization in the presence of unknown disturbances. 
-The proposed attitude configuration error function and several properties are summarized as follows in~\Cref{prop:config_error}
+The proposed attitude configuration error function and several properties are summarized as follows.
 
@@
 	e_{R_A} = \frac{1}{2} \parenth{G R_d^T R - R^T R_d G} ^ \vee , \label{eqn:eRA} \\
-	e_{R_B} = \frac{ \left( R^T v\right)^\vee r}{\alpha \left(r^T R^T v - \cos \theta \right)} . \label{eqn:eRB} 
+	e_{R_B} = \frac{ \left( R^T v\right)^\wedge r}{\alpha \left(r^T R^T v - \cos \theta \right)} . \label{eqn:eRB} 
 \end{gather}	
@@
 	where the matrices \(E(R,R_d), F(R) \in \R^{3\times3} \) are given by
-	\begin{gather}
-		E(R,R_d) = \frac{1}{2} \parenth{\tr{R^T R_d G}I - R^T R_d G} , \label{eqn:E} \\
-		F(R) = \frac{1}{\alpha \parenth{r^T R^T v - \cos \theta}} \left[\parenth{v^T R r} I - R^T v r^T + \right. \nonumber \\
-		\left. \frac{R^T \hat{v} R r v^T R \hat{r}}{\parenth{r^T R^T v - \cos \theta}}\right] . \label{eqn:F}
-	\end{gather}
+	\begin{align}
+		E(R,R_d) = &\frac{1}{2} \parenth{\tr{R^T R_d G}I - R^T R_d G} , \label{eqn:E} \\
+		F(R) = &\frac{1}{\alpha \parenth{r^T R^T v - \cos \theta}} \left[\parenth{v^T R r} I - R^T v r^T + \right. \nonumber \\
+		& \left. \frac{R^T \hat{v} R r v^T R \hat{r}}{\parenth{r^T R^T v - \cos \theta}}\right] . \label{eqn:F}
+	\end{align}
 \end{prop}
@@
     \subfigure[Configuration error \( \Psi \) \label{fig:Psi_con}]{\includegraphics[width=0.5\columnwidth]{figures/Psi_con.pdf} }
+    \subfigure[Angle to constraints \label{fig:con_angles_con}]{\includegraphics[width=0.5\columnwidth]{figures/constraint_angles_con.pdf} }  
     \caption{Attitude stabilization without adaptive update law}
@@
 \Cref{fig:Psi_con} shows that the configuration error function does not converge to zero and there exist steady state errors.
+In spite of the uncompensated disturbance, the system is able to avoid the constrained regions as shown in~\cref{fig:con_angles_con}.
 \Cref{fig:adapt} shows the results with the addition of the adaptive update law.
@@
 	\subfigure[{Control input \( u\) }\label{fig:u_exp}]{\includegraphics[width=0.5\columnwidth]{u_exp}  }~
-	\subfigure[{Attitude Trajectory } \label{fig:traj_exp}]{\includegraphics[width=0.5\columnwidth]{traj_exp} }
+	\subfigure[{Attitude Trajectory } \label{fig:traj_exp}]{\includegraphics[width=0.5\columnwidth]{traj_exp} }\\
+    \subfigure[{Angle to constraint } \label{fig:con_angle_exp}]{\includegraphics[width=0.5\columnwidth]{figures/constraint_angles_exp.pdf} }
 	\caption{Constrained Attitude stabilization experiment}
@@
 \subsection{Proof of~\Cref{prop:config_error}}\label{proof:config_error}
-To prove~\cref{item:prop_psi_psd} we note that~\cref{eqn:A} is a positive definite function about \( R = R_d \)~\cite{bullo2004}.
+To prove~\cref{item:prop_psi_psd}, we note that~\cref{eqn:A} is a positive definite function about \( R = R_d \)~\cite{bullo2004}.
 The constraint angle is assumed \( \ang{0} \leq \theta \leq \ang{90} \) such that \( 0 \leq \cos \theta \).
@@
 \begin{align*}
-	\dirDiff{B}{R} &=  \eta \cdot \frac{ - \left( R^T v\right)^\vee r}{\alpha \left(\cos \theta - r^T R^T v \right)} ,
+	\dirDiff{B}{R} &=  \eta \cdot \frac{ - \left( R^T v\right)^\wedge r}{\alpha \left(\cos \theta - r^T R^T v \right)} ,
 %	-\frac{1}{\alpha} \left[\left(\frac{1+\cos \theta}{\cos \theta - r^T R^T v} \right) \left(\eta \cdot \frac{\left( R^T v\right)^\vee r}{1+\cos \theta} \right) \right]
@@
 \begin{gather*}
-	a = \bracket{\alpha \parenth{r^T R^T v - \cos \theta}}^{-1} , \,
+	a = \bracket{\alpha \parenth{r^T R^T v - \cos \theta}}^{-1} , \;
 	b = \frac{r^T \hat{\Omega} R^T v}{\alpha \parenth{r^T R^T v - \cos \theta}^2} .
@@
 To show~\cref{eqn:F_bound}, we apply the Frobenius norm \( \norm{F}_F \):
-\begin{gather*}
-	\norm{F}_F = \frac{1}{\alpha ^2 \parenth{r^T R^T v - \cos \theta}^2} \left[\tr{a^T a} - 2 \tr{a^T b} \right. \\
-	\left.+ 2 \tr{a^T c } + \tr{b^T b}  - 2 \tr{b^T c} + \tr{c^T c}\right] .
-\end{gather*}
+\begin{align*}
+	\norm{F}_F =& \frac{1}{\alpha ^2 \parenth{r^T R^T v - \cos \theta}^2} \left[\tr{a^T a} - 2 \tr{a^T b} \right. \\
+	&\left.+ 2 \tr{a^T c } + \tr{b^T b}  - 2 \tr{b^T c} + \tr{c^T c}\right] .
+\end{align*}
 where the terms \( a, b, \text{ and } c \) are given by

### 2016-09-22 manuscript.tex
Delete explanation of experiment steady state errors

@@
 
-The brushless motors of the hexrotor allow for large control inputs, which are critical to enable aggressive maneuvers. 
-When constrained to the spherical joint, the hexrotor is capable of performing responsive attitude changes with high angular velocities.
-In addition, the on-board control and motion capture system operate at a discrete interval of approximately \SI{100}{\hertz}.
-It is possible for the system to violate the constraint between these discrete steps and cause numerical exceptions within the embedded software. 
-As a result, conservative control gains are chosen to ensure the hexrotor operates in a sedate manner and to allow sufficient time for the measurement and control software to operate.
-
-There exist several sources of error in the experimental setup.
-The motion capture system uses a series of optical sensors to determine the relative position of several tracking markers. 
-These markers as well as the cameras must remain fixed to ensure accurate attitude measurement.
-In addition, the spherical joint is not fixed at the center of mass but is instead offset due to the physical structure of the hexrotor.
-As a result a disturbance moment is induced on the resultant motion.
-
-This results in a small steady state error in the vicinity of the desired attitude. 
-Over time~\cref{eqn:delta_dot} will remain non-zero while \( e_R \neq 0 \).
-This will cause an increase in control input until the steady-state error is reduced. 
-Further tuning of the control gains would enable a faster response and a reduced settling time.
-
 The hexrotor avoids the constrained region illustrated by the circular cone in~\cref{fig:traj_exp}, by rotating around the boundary of the constraint. 

### 2016-09-26 manuscript.tex
Modify title and author information in footer

@@
 
-\title{\LARGE \bf
-Constrained Attitude Control on \( \SO \) }
+\title{\LARGE \textbf{Constrained Geometric Attitude Control on \( \SO \)} }
 
@@
 Manuscript received DATE; revised DATE; accepted DATE.
-Shankar Kulumani, Mechanical and Aerospace Engineering, George Washington University, Washington DC 20052 {\tt \{skulumani,tylee\}@gwu.edu}
+
+Shankar Kulumani and Taeyoung Lee, Mechanical and Aerospace Engineering, George Washington University, Washington DC 20052 \texttt{ \{skulumani,tylee\}@gwu.edu}
 
@@
 
-\runningtitle{1}{Shankar Kulumani, Christopher Poole, and Taeyoung Lee}{Constrained Attitude Control on \( \SO \) }
+\runningtitle{1}{Shankar Kulumani and Taeyoung Lee}{Constrained Geometric Attitude Control on \( \SO \) }
 

### 2016-09-26 manuscript.tex
Add some additional detail and correct typos

@@
 Consider the attitude dynamics of a rigid body.
-We define an inertial reference frame and a body-fixed frame whose origin is at the center of mass and aligned with the principle directions of the body. 
+We define an inertial reference frame and a body-fixed frame, whose origin is at the center of mass and aligned with the principle directions of the body. 
 The configuration manifold of the attitude dynamics is the special orthogonal group:
@@
 \begin{enumerate}[(i)]
-	\item \label{item:prop_psi_psd} \(\Psi\) is positive definite about \( R = R_d\)
+	\item \label{item:prop_psi_psd} \(\Psi\) is positive definite about \( R = R_d\).
 	\item \label{item:prop_era}The variation of \( A(R) \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
@@
 \Cref{eqn:psi} is composed of an attractive term, \( A (R) \) toward the desired attitude, and a repulsive term, \( B(R) \) away from the undesired direction \( R^T v \).
-In order to visualize the attitude error function on \( \SO \) we utilize a spherical coordinate representation.
+In order to visualize the attitude error function on \( \SO \), we utilize a spherical coordinate representation.
 Recall, that the spherical coordinate system represents the position of a point relative to an origin in terms of a radial distance, azimuth, and elevation.
@@
 We apply this concept and parametrize the rotation matrix \( R \in \SO \) in terms of the spherical angles \( \SI{-180}{\degree} \leq \lambda \leq \SI{180}{\degree}  \) and \( \SI{-90}{\degree} \leq \beta \leq \SI{90}{\degree} \).
-Using the elementary Euler rotations the rotation matrix is now defined as \( R = \exp( \lambda \hat{e}_2) \exp( \beta \hat{e}_3) \).
+Using the elementary Euler rotations, the rotation matrix is now defined as \( R = \exp( \lambda \hat{e}_2) \exp( \beta \hat{e}_3) \).
 We iterate over the domains of \( \lambda\) and \(\beta\) in order to rotate the body-fixed vector \( r \) throughout the two-sphere \( \S^2 \).
@@
 However, we can show that these undesired equilibrium points are unstable in the sense of Lyapunov~\cite{LeeITCST13}.
-As a result, we can claim that the desired equilibrium \( R = R_d \text{ and } e_\Omega = 0 \) is almost globally asymptotically stable, which means that the set of initial conditions that do not converge to the desired attitude has zero Lebesgue measure.
 
@@
 In spite of the uncompensated disturbance, the system is able to avoid the constrained regions as shown in~\cref{fig:con_angles_con}.
+The angle to each of the constraints,  \( \arccos(r^T R^T v_i) \), is always greater than the specified angle, \( \theta_i \), in~\cref{tab:constraints}.
+
 \Cref{fig:adapt} shows the results with the addition of the adaptive update law.
@@
 In order to constrain the motion, allowing us to test only the attitude dynamics, we attach the hexrotor to a spherical joint.
-Since, the center of rotation is below the center of gravity of the hexrotor there is a destabilizing gravitational moment
+Since, the center of rotation is below the center of gravity of the hexrotor there is a destabilizing gravitational moment.
 The resulting attitude dynamics are similar to an inverted pendulum model.
@@
 
-A sensor pointing direction is defined in the body frame of the hexrotor as \( r = [1,0,0]^T \).
+A sensor pointing direction is defined in the body-fixed frame of the hexrotor as \( r = [1,0,0]^T \).
 We define an obstacle in the inertial frame as \( v = [\frac{1}{\sqrt{2}}, \frac{1}{\sqrt{2}}, 0]^T \) with \( \theta = \ang{12} \).
@@
 The hexrotor avoids the constrained region illustrated by the circular cone in~\cref{fig:traj_exp}, by rotating around the boundary of the constraint. 
+\Cref{fig:con_angle_exp} shows the angle, \( \arccos r^T R^T v \), between the body mounted sensor and the inertially fixed sensor.
+The experiment demonstrates that the minimum angular separation is \SI{14}{\degree} which satisfies the constraint of \( \theta = \SI{12}{\degree} \).
 This further validates that the proposed control system exhibits the desired performance in the experimental setting as well. 

### 2016-09-26 manuscript.tex
Add detail on additional critical point

@@
 	\end{align}
-	\item \label{item:prop_crit}The critical points of \( \Psi \) are $R_d$, and $R_d \exp(\pi \hat{s})$ for $s \in \braces{e_1, e_2, e_3}$ satisfying $R^T v = \pm r$.
+	\item \label{item:prop_crit}\(R_d\) is one of the critical points of \( \Psi \).
 	\item \label{item:prop_era_upbound}An upper bound of \( \norm{e_{R_A}} \) is given as:
@@
 This condition only occurs if the desired attitude results in the body fixed vector \( r \) becoming aligned with \(R^T v \) while simultaneously satisfying \(\braces{R_d} \cup \braces{R_d \exp(\pi \hat{s}} \) for \( s \in \braces{e_1, e_2, e_3} \).
-Since we assume the system will not operate in violation of the constraints, the addition of the barrier function does not add additional critical points to the control system.
+There is an additional critical point when the condition \( e_{R_A} B + e_{R_B} A = 0 \) is satisfied. 
+This critical point is equivalent to the following two conditions:
+\begin{align*}
+    e_{R_A} \cdot e_{R_B} &= - \norm{e_{R_A}} \norm{e_{R_B}} , \\
+    \norm{e_{R_A}} B &= A \norm{e_{R_B}}.
+\end{align*}
 The desired equilibrium is \( e_R = 0 \) and \( A = 0\).

### 2016-09-26 manuscript.tex
Remove discussion on critical points of \Psi

--- 2016-09-26 manuscript.tex
@@
 	\end{align}
-	\item \label{item:prop_crit}The critical points of \( \Psi \) are $R_d$, and $R_d \exp(\pi \hat{s})$ for $s \in \braces{e_1, e_2, e_3}$ satisfying $R^T v = \pm r$.
+	\item \label{item:prop_crit}The error function \( \Psi \) is minimized when \(R = R_d\).
 	\item \label{item:prop_era_upbound}An upper bound of \( \norm{e_{R_A}} \) is given as:
@@
 The potential well of \( A(R)\) is illustrated in~\cref{fig:attract_error}, where the desired attitude lies at the minimum of \( A(R) \).
-As shown in~\Cref{prop:config_error}, there are a maximum four possible critical points of~\cref{eqn:psi}.
-The addition of the repulsive barrier term places additional conditions on the critical points, namely that the undesired critical points of \( A(R) \) must also satisfy \( R^T v = \pm r \).
-As a result, there will frequently be fewer equilibrium points with the addition of the barrier term, \( B(R) \), than with \( A(R) \) alone.
 
@@
 \end{proof}
-
-This proposition only guarantees that the attitude error vector \( e_R \) asymptotically converges to zero.
-However, this does not necessarily imply that \( R \to R_d \) as \( t \to \infty \), since there are at most three additional critical points of \( A(R) \) where \( e_R = 0 \) and \( R^T v = \pm r\).
-At an undesired equilibrium \( R = \exp{ \parenth{\pi \hat{e}_i}} R_d \) and \( e_\Omega =0 \).
-However, we can show that these undesired equilibrium points are unstable in the sense of Lyapunov~\cite{LeeITCST13}.
 
@@
 As a result, its negative logarithm is always positive and from~\cref{eqn:B}, \(1 < B\).
-The error function \( \Psi = A B \) is composed of two positive terms and is therefore also positive definite, and it is minimized at \( R = R_d \).
+The error function \( \Psi = A B \) is composed of two positive terms and is therefore also positive definite.
 
@@
 
-% To show~\cref{item:prop_crit}, we determine the critical points of~\cref{eqn:eRA}.
-% The attitude error between \( R \) and \( R_d \) is defined by \( Q \in \SO \) as
-% \begin{align*}
-% 	Q = R_d^T R = 
-% 	\begin{bmatrix}
-% 		q_{11} & q_{12} & q_{13} \\
-% 		q_{21} & q_{22} & q_{23} \\
-% 		q_{31} & q_{32} & q_{33}
-% 	\end{bmatrix} .
-% \end{align*}
-% Equating \( e_{R_{A}} = 0 \) yields the following equivalent relations
-% \begin{align*}
-% 	g_3 q_{32} &= g_2 q_{23} , \\
-% 	g_1 q_{13} &= g_3 q_{31} , \\
-% 	g_2 q_{21} &= g_1 q_{12} .
-% \end{align*}
-% These relations allow one to redefine the attitude error \( Q \) in terms of the independent upper diagonal elements.
-% Noting that \( Q \in \SO \) is an orthonormal matrix, with unit length row and columns gives
-% \begin{align*}
-% 	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 + \parenth{1 - \frac{g_1^2}{g_3^2}}q_{13}^2 &= 0 , \\
-% 	\parenth{1 - \frac{g_1^2}{g_2^2}} q_{12}^2 - \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 , \\
-% 	\parenth{1-\frac{g_1^2}{g_3^2}} q_{13}^2 + \parenth{1 - \frac{g_2^2}{g_3^2}} q_{23}^2 &= 0 .
-% \end{align*}
+To show~\cref{item:prop_crit} we note that \( A(R) \) is a positive definite function about \( R = R_d\).
+As a result, there exists a neighborhood \(  U \) about \( R = R_d \) such that
+\begin{align*}
+  A(R) \geq A(R_d) \, \forall R \in U .
+\end{align*}
+Since the desired attitude, \( R_d \), must lie in the feasible set, i.e., \( r^T R^T v < \cos \theta \) the addition of the repulsive barrier function, \( B \), does not change the minimum value of \( \Psi \).
 
-% As a result, all the off diagonal terms of \( Q = R_d^T R \) are zero, namely \( q_{12}= q_{13} = q_{23} = 0 \).
-% Since \( Q \in \SO \), the diagonal elements \( q_{11}, q_{22}, \text{ and } q_{33} \) are either \( +1 \) or \(-1\).
-The critical points of \( e_{R_A} \) are derived in~\cite{bullo2004}.
-There are four critical points of \( e_{R_A} \), the desired attitude \( R_d \) as well as rotations about each body fixed axis by \ang{180}.
-The repulsive error vector \( e_{R_{B}} \) is zero only when the numerator \( \parenth{R^T v}^\wedge r = 0 \). 
-This condition only occurs if the desired attitude results in the body fixed vector \( r \) becoming aligned with \(R^T v \) while simultaneously satisfying \(\braces{R_d} \cup \braces{R_d \exp(\pi \hat{s}} \) for \( s \in \braces{e_1, e_2, e_3} \).
-Since we assume the system will not operate in violation of the constraints, the addition of the barrier function does not add additional critical points to the control system.
-The desired equilibrium is \( e_R = 0 \) and \( A = 0\).
+The desired equilibrium is occurs at \( R=R_d\) and results in \( e_R = 0 \) and \( \Psi = A = 0\).
 The proof of \( \norm{e_{R_A}} \) given by~\cref{item:prop_era_upbound} is available in~\cite{LeeITCST13}.

### 2016-09-27 manuscript.tex
Correct some more small typos

@@
 \begin{gather*}
+  \hspace{-5mm}
 	J = \begin{bmatrix}
@@
 
-To show~\cref{item:prop_crit} we note that \( A(R) \) is a positive definite function about \( R = R_d\).
+To show~\cref{item:prop_crit} we note that \( A(R) \) is a positive definite function about \( R = R_d\), with \( \Psi(R_d) = A(R_d) = 0 \).
 As a result, there exists a neighborhood \(  U \) about \( R = R_d \) such that
 \begin{align*}
-  A(R) \geq A(R_d) \, \forall R \in U .
+  A(R) \geq A(R_d) \; \forall \; R \in U .
 \end{align*}
-Since the desired attitude, \( R_d \), must lie in the feasible set, i.e., \( r^T R^T v < \cos \theta \) the addition of the repulsive barrier function, \( B \), does not change the minimum value of \( \Psi \).
-
-The desired equilibrium is occurs at \( R=R_d\) and results in \( e_R = 0 \) and \( \Psi = A = 0\).
+Since the desired attitude, \( R_d \), must lie in the feasible set, i.e., \( r^T R^T v < \cos \theta \), the addition of the repulsive barrier function, \( B \), does not change the minimum value of \( \Psi \).
+The desired equilibrium occurs at \( R=R_d\) and results in \( e_R = 0 \) and \( \Psi = A = 0\).
 The proof of \( \norm{e_{R_A}} \) given by~\cref{item:prop_era_upbound} is available in~\cite{LeeITCST13}.

### 2016-09-27 manuscript.tex
Modify minimum discussion of \Psi

@@
 \begin{enumerate}[(i)]
-	\item \label{item:prop_psi_psd} \(\Psi\) is positive definite about \( R = R_d\).
+	\item \label{item:prop_psi_psd} \(\Psi\) is positive definite about \( R = R_d\) on $\SO$.
 	\item \label{item:prop_era}The variation of \( A(R) \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
@@
 	\end{align}
-	\item \label{item:prop_crit}The error function \( \Psi \) is minimized when \(R = R_d\).
+%	\item \label{item:prop_crit}The error function \( \Psi \) is minimized when \(R = R_d\).
 	\item \label{item:prop_era_upbound}An upper bound of \( \norm{e_{R_A}} \) is given as:
@@
 
-To show~\cref{item:prop_crit} we note that \( A(R) \) is a positive definite function about \( R = R_d\), with \( \Psi(R_d) = A(R_d) = 0 \).
-As a result, there exists a neighborhood \(  U \) about \( R = R_d \) such that
-\begin{align*}
-  A(R) \geq A(R_d) \; \forall \; R \in U .
-\end{align*}
-Since the desired attitude, \( R_d \), must lie in the feasible set, i.e., \( r^T R^T v < \cos \theta \), the addition of the repulsive barrier function, \( B \), does not change the minimum value of \( \Psi \).
+%To show~\cref{item:prop_crit} we note that \( A(R) \) is a positive definite function about \( R = R_d\), with \( \Psi(R_d) = A(R_d) = 0 \).
+%As a result, there exists a neighborhood \(  U \) about \( R = R_d \) such that
+%\begin{align*}
+%  A(R) \geq A(R_d) \; \forall \; R \in U .
+%\end{align*}
+%Since the desired attitude, \( R_d \), must lie in the feasible set, i.e., \( r^T R^T v < \cos \theta \), the addition of the repulsive barrier function, \( B \), does not change the minimum value of \( \Psi \).
+
 The desired equilibrium occurs at \( R=R_d\) and results in \( e_R = 0 \) and \( \Psi = A = 0\).
-The proof of \( \norm{e_{R_A}} \) given by~\cref{item:prop_era_upbound} is available in~\cite{LeeITCST13}.
+The proof of \cref{item:prop_era_upbound} is available in~\cite{LeeITCST13}.
 

### 2016-11-23 setup_repo.sh
Add a setup repo script

@@ -1,0 +1,21 @@
+#!/bin/bash
+
+# add the correct remote repositories
+git_repo="git@github.com:skulumani/2016_IJCAS.git"
+bb_repo="git@bitbucket.org:shankarkulumani/2016_IJCAS.git"
+fdcl_repo="git@github.com:fdcl-gwu/2016_IJCAS.git"
+
+printf "Setting the origin remote to point to Github and Bitbucket:\n\n"
+printf "Github: $git_repo\n"
+printf "Bitbucket: $bb_repo\n"
+printf "FDCL: $fdcl_repo\n\n"
+
+git remote add origin $git_repo
+git remote set-url origin --push --add $bb_repo
+git remote set-url origin --push --add $git_repo
+git remote set-url origin --push --add $fdcl_repo
+
+printf "Finished! The new remotes are listed.\n"
+printf "\n"
+
+git remote -v

### 2016-11-23 Response.tex
Add review response example

\documentclass[11pt]{article}
\usepackage[letterpaper,text={6.5in,8.6in},centering]{geometry}
\usepackage{amssymb,amsmath,times,url}
\usepackage{xr,color}

\newcommand{\norm}[1]{\ensuremath{\left\| #1 \right\|}}
\newcommand{\bracket}[1]{\ensuremath{\left[ #1 \right]}}
\newcommand{\braces}[1]{\ensuremath{\left\{ #1 \right\}}}
\newcommand{\parenth}[1]{\ensuremath{\left( #1 \right)}}
\newcommand{\pair}[1]{\ensuremath{\langle #1 \rangle}}
\newcommand{\met}[1]{\ensuremath{\langle\langle #1 \rangle\rangle}}
\newcommand{\refeqn}[1]{(\ref{eqn:#1})}
\newcommand{\reffig}[1]{Fig. \ref{fig:#1}}
\newcommand{\tr}[1]{\mathrm{tr}\ensuremath{\negthickspace\bracket{#1}}}
\newcommand{\trs}[1]{\mathrm{tr}\ensuremath{[#1]}}
\newcommand{\deriv}[2]{\ensuremath{\frac{\partial #1}{\partial #2}}}
\newcommand{\SO}{\ensuremath{\mathsf{SO(3)}}}
\newcommand{\T}{\ensuremath{\mathsf{T}}}
\renewcommand{\L}{\ensuremath{\mathsf{L}}}
\newcommand{\so}{\ensuremath{\mathfrak{so}(3)}}
\newcommand{\SE}{\ensuremath{\mathsf{SE(3)}}}
\newcommand{\se}{\ensuremath{\mathfrak{se}(3)}}
\renewcommand{\Re}{\ensuremath{\mathbb{R}}}
\newcommand{\aSE}[2]{\ensuremath{\begin{bmatrix}#1&#2\\0&1\end{bmatrix}}}
\newcommand{\ase}[2]{\ensuremath{\begin{bmatrix}#1&#2\\0&0\end{bmatrix}}}
\newcommand{\D}{\ensuremath{\mathbf{D}}}
\newcommand{\Sph}{\ensuremath{\mathsf{S}}}
\renewcommand{\S}{\Sph}
\newcommand{\J}{\ensuremath{\mathbf{J}}}
\newcommand{\Ad}{\ensuremath{\mathrm{Ad}}}
\newcommand{\intp}{\ensuremath{\mathbf{i}}}
\newcommand{\extd}{\ensuremath{\mathbf{d}}}
\newcommand{\hor}{\ensuremath{\mathrm{hor}}}
\newcommand{\ver}{\ensuremath{\mathrm{ver}}}
\newcommand{\dyn}{\ensuremath{\mathrm{dyn}}}
\newcommand{\geo}{\ensuremath{\mathrm{geo}}}
\newcommand{\Q}{\ensuremath{\mathsf{Q}}}
\newcommand{\G}{\ensuremath{\mathsf{G}}}
\newcommand{\g}{\ensuremath{\mathfrak{g}}}
\newcommand{\Hess}{\ensuremath{\mathrm{Hess}}}
\newcommand{\refprop}[1]{Proposition \ref{prop:#1}}

\newcommand{\RNum}[1]{\uppercase\expandafter{\romannumeral #1\relax}}
\newcommand{\RI}{\text{\RNum{1}}}
\newcommand{\RII}{\text{\RNum{2}}}
\newcommand{\RIII}{\text{\RNum{3}}}

\newenvironment{correction}{\begin{list}{}{\setlength{\leftmargin}{1cm}\setlength{\rightmargin}{1cm}}\vspace{\parsep}\item[]``}{''\end{list}}

%\externaldocument{AUT13}

\begin{document}

%\pagestyle{empty}

\section*{Response to the Reviewers' Comments for 2014-12-G001229.R1}

I would like to thank the reviewers for their thoughtful comments, which are aimed
towards improving the quality of the paper and the clarity of the results. In accordance with the comments and suggestions, the paper has been revised, and the answers to all comments are addressed as follows.

(In the revised manuscript, the citation numbers for equations, assumptions, propositions, and references are changed. This answer is written according to the new item numbers.)

\subsection*{Reviewer 1}

\textit{The authors present nonlinear regression based estimation of UAV altitude and ground plane inclination for autonomous landing. 
The estimates are obtained using the proposed laser-camera sensor, where the laser projection on the surface are measured in the camera's image plane. 
The paper presents an interesting approach, and the application is relevant to the journal. 
The paper is sufficiently clear and easy to follow. 
The controller and trajectory generation are borrowed from the author's previous work. 
The main contribution is in the estimation method for altitude and ground plane inclination. Below are some of my major concerns:
}

\setlength{\leftmargini}{0pt}
\begin{itemize}\setlength{\itemsep}{2\parsep}

\item 
\textit{The laser-based approach to obtain artificial feature points using the presented image processing approach may not be suitable in many outdoor situations. 
It is very common to experience bright spots and reflections in sunny conditions, which would be difficult to distinguish from the laser points. 
I am aware that the authors have clearly stated that the method works well in shaded and indoor conditions but, in my opinion, that limits the applicability.
}

The image processing approach outlined in this paper is limited to conditions in which the thresholding works well, but the present approach may be extended using more robust techniques. 
It may be possible to incorporate color into the image processing, or to selectively choose regions of interest in the image based on expectations on where the laser pointer projections should appear in the image, for example. 
I think similar objections can be made to many other computer vision applications, which may work well in lab environments but require further development to perform robustly under any lighting condition. 
Nonetheless, the conclusion has been modified to make the limitations of this approach more clear:

\begin{correction}
... Contrary to other vision-based approaches, the system does not require features to be present at the landing site. 
However, the image processing approach employed here assumes that the intensity of the laser points in the image are much brighter than the rest of the image, an assumption that may break down under certain conditions, especially in bright sunlight.
The result of the estimation and landing trajectory ...
\end{correction}

\item
\textit{The authors states that the xy-coordinates of the landing position $x_L$ are known. 
I believe, without loss of generality, the authors could mention that the origin of the inertial frame can be assumed to coincide with $x_L$ to get rid of the assumption.
}

It is true that the origin of the inertial frame can be assumed to coincide with $x_L$ to eliminate the assumption of known horizontal position, but I do not agree that this assumption preserves generality. 
With the inertial frame coincident with $x_L$, it no longer becomes necessary to estimate $h$ (which in this case is simply the vertical component of position) since the position of the quadrotor is assumed to be known.
Assuming that the horizontal components of $x_L$ are known can be as simple as the quadrotor hovering over an arbitrary position to attempt a landing, so long as the flat ground plane assumption is met.

\item
\textit{The most limiting assumption is that the quadrotor hovers directly above the landing point and obtains a bunch of images to solve for the altitude and ground plane inclination. 
In practice, due to external disturbances such as wind gusts and light-weight construction of quadrotors, it is very difficult to hover them at one location.
}

Position control of quadrotors definitely varies in different conditions, such as wind gusts as you point out. 
However, the landing approach developed in this paper would be most applicable to large, expensive vehicles, where landing on an inclined surface without damage can not easily be achieved by cutting throttle near the ground, as might be done with a small lightweight vehicle.
Larger, heavier vehicles can be more robust to external disturbances, and recent advances in position control using optical flow could be useful. %Furthermore, the proposed algorithm to estimate the inclination of the landing surface is not sensitive to the horizontal movements of the quadrotor, as the lasers are fixed to the quadrotor body.

\item
\textit{Since the development in Section 3B and 3C is based on the above assumption, it is not clear how to obtain m images while maintaining constant altitude (as required to solve regression in Section 3C2). Do you only yaw to obtain a measurement vector of size 2mn? Please clarify.
}

Yawing is sufficient to obtain the measurement vector. 
In practice, since it is not possible to hover exactly in one position as you pointed out previously, simply attempting to hold position will yield distinct measurements suitable for the estimation procedure.
The following has been added to clarify how to obtain the $m$ frames:

\begin{correction}
Suppose the above image processing algorithm is repeated over a short time period to obtain $m$ image frames. 
Theoretically, in order to obtain the $m$ distinct frames while holding position, the quadrotor must change its attitude by yawing.
In practice, however, small disturbances ensure that the measurements are distinct even with the vehicle simply
attempting to hold position.
An estimation scheme is necessary ...
\end{correction}

\item
\textit{Formal approach to determine landing time and switching time might be necessary. 
The switching time satisfies the boundary conditions on the position of the UAV but the landing time is arbitrarily chosen. 
Although the authors state that since attitude dynamics are typically fast so that the desired orientation can be achieved in small amount of time, a formal proof to determine tL given tS and xS will greatly improve the paper.
}

As discussed at the end of Section IV.B, the boundary condition to align the attitude of the quadrotor to the landing surface is indirectly imposed by selecting $t_L$. In practice, $t_L-t_S$ should be sufficiently large such that the attitude is aligned to the landing surface before the moment of touchdown. However, it is determined by various factors, such as the controller gain, the moment of inertia of the quadrotor, and the maximum thrust of the quadrotor. As such, providing an analytic expression accounting these for the controlled attitude trajectories is beyond the scope of this technical note.

Instead, the last paragraph of Section IV.B has been revised as follow, to provide a guideline to select $t_L$ and other parameters.

\begin{correction}
As this problem of selecting $x_S,v_S,f,t_S$ and $t_L$ is underdetermined, one may consider optimizing the parameters with respect to a certain cost function. 
Instead, these parameters can be chosen according to the following heuristic approach.
Note the landing trajectory can be designed in the two dimensional plane normal to $b_{1_c}$. 
First, the landing time $t_L$ is chosen sufficiently large to avoid a rapid descent, and $t_S$ can be chosen about 0.5 second less than $t_L$ initially. 
Then, the switching point $x_S$ is selected such that it is on the line joining $x_H$ and $x_L$, and the distance between $x_S$ and $x_L$ is about one or two times of the quadrotor diameter. 
We can also restrict $v_S$ to be horizontal such that it does not cause any additional downward velocity at $t_L$. 
The remaining two parameters, namely $f$ and the horizontal component of $v_S$, are iterated numerically such that $x(t_L)$ becomes equal to $x_L$ within the plane normal to $b_{1_c}$. 
Finally, the switching time $t_S$ can be further iterated to ensure the attitude error becomes sufficiently small at $t=t_L$. 
These are illustrated by the following numerical examples. 
\end{correction}

\item
\textit{Although the presented approach using laser-based artificial features is interesting, it is difficult to see the advantage of using lasers over pure-vision based approaches. 
For example, nonlinear observer based methods can be applied to estimate the altitude (e.g., On-Line Estimation of Feature Depth
for Image-Based Visual Servoing Schemes by DeLuca) or homography-based approaches can be used to land the quadrotor using natural feature points (not IR markers) even without the knowledge of the desired or reference image.
}

As discussed in the introduction, the primary advantage of the present approach is that natural feature points are not required, meaning that this approach could succeed on a textureless flat plate where a feature-based approach would fail. 
Feature detectors have made significant progress but are not reliable on solid color surfaces lacking significant texture.

\end{itemize}

\noindent\textit{Minor edits:}

\begin{itemize}\setlength{\itemsep}{2\parsep}

\item
\textit{eq. 16 - change p3,e,3 to p3,e
}

In this equation, $p_{3,e,3}$ was intended to represent the third component of $p_{3,e}$. This equation has been modified as follows:

\begin{correction}
  $\beta_j = h p_{3,e}^T \vec{e_3} -
r_{j,c}^T R^T p_{3,e}$
\end{correction}

\item
\textit{the notation defined for r, l, and p uses bar but it was dropped in the subsequent analysis. 
please rectify.
}

This was intentional. In this manuscript, the bar is used to denote an abstract vector, and it is dropped for the representation of the vector with respect to a particular reference frame.
To make this more clear, a sentence was added as follows:
\begin{correction}
... a (virtual) image plane is
parallel to the $\vec{c}_1$-$\vec{c}_2$ plane and offset from the
aperture along $\vec{c}_3$ by the focal length $f_c$.
In the following discussion, an abstract vector is written with an arrow, e.g. $\vec{x}$, and the representation of the vector with respect to a particular reference frame is written without the arrow with a subscript indicating the reference frame, e.g. $x_e$.
\end{correction}

%\textcolor{red}{JAD: Do you agree?}

\item
\textit{page 12, line 29 - defined in (29)-(30) change that to "defined in (29) and (30)"
}

The text has been revised accordingly.

\end{itemize}

\subsection*{Reviewer 2}

\textit{The manuscript entitled "Monocular Estimation of Ground Orientation for Autonomous Landing of a Quadrotor" demonstrates a novel visual method for landing a quadrotor MAV on an inclined flat surface. 
Methods for visually estimate the height and inclination angles of the ground surface are presented as well as the needed visual calibration method. 
The manuscript also presents the online trajectory generation and tracking control to achieve smooth landing on the surface backed up by simulation and experimentation results. 
}

\textit{
In addition to the interesting visual method presented, the manuscript is well written and easy to follow. 
Well done. 
The notes provided are minor in nature, and they are split in two groups.
}

\textit{
The more serious notes are the following:
}

\setlength{\leftmargini}{0pt}
\begin{itemize}\setlength{\itemsep}{2\parsep}

\item 
\textit{The author review states that all relevant visual methods in the literature rely on fixed pre-known markers. A very relevant work that does not require such markers is "de Croon, G. CHE, et al. "Optic-flow based slope estimation for autonomous landing." International Journal of Micro Air Vehicles 5.4 (2013): 287-298." I suggest that the author acknowledge this work as it is more flexible in its requirements than the cited works as well as the author work (in the aspect of being completely passive).
}

This work is indeed very relevant and avoids many limitations of other vision-based approaches mentioned in the text. The text has been revised to acknowledge it as follows:

\begin{correction}
As described above, many vision-based approaches relying on feature detection impose the unrealistic constraint that a landing site have a known pattern present to be detected by the computer vision system. 
In most real flight situations, this is not a practical solution. 
Further, many algorithms suffer from slow computation times, especially on embedded hardware, although this problem is becoming less prevalent with advances in hardware and increasingly efficient computer vision algorithms. 
One approach free from these limitations is developed in [17], where the slope of the ground surface is extracted directly from the optic flow field. 
This purely vision-based approach shows promise in increasing the level of autonomy in landing, although the problem of landing on a sloped surface is not considered.
\end{correction}

\item
\textit{The author has stated eq. 38 with no comments at all. It would be better to briefly highlight the rationale behind its formulation in this form. 
}

Equation (38) is chosen such that it satisfies four boundary conditions, namely $x(0)=x_H$, $v(0)=0$, $x(t_S)=x_S$, and $v(t_S)=v_S$. Additional fifth boundary condition for the zero initial acceleration is imposed for smooth initial transition. These determine the five coefficients of the selected fourth order polynomial uniquely.

When $v(t_S)=0$, the selected trajectory has additional property that $\min\{x_H,x_S\}\leq x_d(t) \leq \max\{x_H,x_S\}$ for any $0\leq t \leq t_S$. This may be used to ensure that the quadrotor does not fly below the switching point $x_S$ for safety.

To clarify these, the paragraph including (38) has been revised as follows.

\begin{correction}
The desired landing trajectory satisfying these four boundary conditions and another boundary condition of zero initial acceleration is parameterized by $t$ as follows. 
For $1\leq i\leq 3$, its $i$-th component is given by
\begin{align}
x_{d_i}(t)& =(v_{S_i}t_S+3(x_{H_i}-x_{S_i}))\frac{t^4}{t_S^4} -(v_{S_i}t_S+4(x_{H_i}-x_{S_i}))\frac{t^3}{t_S^3}
+x_{H_i}.
\end{align}
When $v_{S_i}=0$, the above trajectory exhibits the additional property that $x_{d_i}(t)$ lies between $x_{H_i}$ and $x_{S_i}$ when $0\leq t\leq t_S$. This can be used to guarantee that the quadrotor does not fly below the switching point during its descent for safety. 
\end{correction}

\item
\textit{This author emphasise that any pre-requirements on the landing site is not practical for a truly autonomous landing system. While I agree on this, the work seems to rely on very accurate method (Vicon system) for estimating the quadrotor’s state (the position, velocity, attitude and attitude rates). In principle the same estimates could be obtained using an onboard IMU and GPS modules, but with far less accuracy. With no robustness analysis to state estimation errors and no experimentation performed outdoor using IMU/GPS sensors the practical applicability of the system is still questionable. I suggest that the authors address this point, either fully or partially followed up by future work, if the current text size does not allow.
}

While it is true that the use of a motion capture system for position and attitude estimation limits the applicability of the experimental results presented, the problem of state estimation of the quadrotor's pose is beyond the scope of this paper.
The following has been added to the end of the results section to address this:

\begin{correction}
For these landing experiments, a pose estimate was provided by the Vicon system. 
For a truly autonomous landing, it is unreasonable to use a motion
capture system, but onboard pose estimation of the quadrotor is beyond the scope of this paper.
Future work should aim to recreate these landing results  without any requirement on external sensors.
\end{correction}

\item
\textit{Same practicality issue can be raised against the image processing technique and the threshold selection in varying light conditions in real life application.
}

Please see the above comment to Reviewer 1 regarding the practicality of the image processing procedure.

\item
\textit{There is no quantification of the number (m) of measurements needed to acceptably estimate the required parameters. More importantly, there is also no mention on the conditions under which these measurements should be taken for observability of the estimated parameters. For instance, if m>1 then images should be captured under distinct conditions, so would it be sufficient to vary the altitude, or the attitude or both? is a simple motion enough or a special manoeuvre has to be designed for this purpose? are the images taken while descending to xH enough for estimation purposes?
}

%\textcolor{red}{JAD: how to quantify m?}

To obtain the $m$ image frames, the quadrotor should hold position, since $h$ must be estimated. 
No special maneuvre is necessary; yawing would ensure distinct measurements. 
In practice, due to disturbances, simply attempting to hold position will yield distinct measurements suitable for the estimation procedure.

The accuracy of the estimation can be quantified via the size of the posterior covariance matrix. If needed, the number of the measurements can be increased until the covariance matrix is less than a prescribed threshold. But, at the presented experimental setup, the sensor measurements are obtained at the rate of $16 Hz$, and taking the measurements over a few seconds was enough.

This has been clarified in the text as follows:

\begin{correction}
Suppose the above image processing algorithm is repeated over a short time period to obtain $m$ image frames. Theoretically, in order to obtain the $m$ distinct frames while holding position, the quadrotor must change its attitude by yawing. In practice, however, small disturbances ensure that the measurements are distinct even with the vehicle simply attempting to hold position. An estimation scheme is necessary ...
\end{correction}

\item
\textit{
More analysis or guidelines for choosing tS, xS, tL, vS, f would be appreciated by the reader.
}

The last paragraph of Section IV.B has been revised as follow, to provide a guideline to select those parameters.

\begin{correction}
As this problem of selecting $x_S,v_S,f,t_S$ and $t_L$ is underdetermined, one may consider optimizing the parameters with respect to a certain cost function. Instead, these parameters can be chosen according to the following heuristic way. Note the landing trajectory can be designed in the two dimensional plane normal to $b_{1_c}$. First, the landing time $t_L$ is chosen sufficiently large such that a rapid descending is avoided, and $t_S$ can be chosen about 0.5 second less than $t_L$ initially. Then, the switching point $x_S$ is selected such that it is on the line joining the $x_H$ and $x_L$, and the distance between $x_S$ and $x_L$ is about 1 or 2 times of the quadrotor diameter. We can also restrict $v_S$ to be horizontal such that it does not cause any additional downward velocity at $t_L$. The remaining two parameters, namely $f$ and the horizontal component of $v_S$ are iterated numerically such that $x(t_L)$ becomes equal to $x_L$ within the plane normal to $b_{1_c}$. Finally, the switching time $t_S$ can be further iterated to ensure the attitude error becomes sufficiently small at $t=t_L$. These are illustrated by the following numerical examples. 
\end{correction}

\end{itemize}

\noindent\textit{The other less serious comments are:}

\begin{itemize}\setlength{\itemsep}{2\parsep}

\item
\textit{
In P.3 L.30, in the author comments on ref 15; How image processing is done offline? do you mean off-board? The word “offline” indicates that the image processing is performed not at the time of the experiment, which does not make sense in this context.
}

Image processing is done off-board. The text has been updated to use ``off-board'' instead of ``offline.''

\item
\textit{
In P.4 L.28: Using the term "fully controlled" in the first sentence is inaccurate and can be misleading. The quadrotor system is fully controllable as the 6DoF pose can be reached in a finite time using the available control. However, because it is underactuated then not all 6DoF states can be controlled simultaneously as the second sentence clearly states. The first sentence can be removed to avoid this issue.
}

This sentence has been removed.

\item
\textit{
I suggest using the term "laser pointers modules" (for instance) instead of "laser modules" used through the text to avoid confusion with laser range finder modules which are much more often used on MAVs that laser pointers.
}

The term ``laser modules'' can indeed be ambiguous. The text has been updated to use the term ``laser pointers.'' I don't believe any meaning is lost in dropping the word ``modules.''

\item
\textit{
In P.6 L.41, either the word "and" after p3 has to be removed or the sentence has to be rephrased.
}

This sentence has been revised as follows:

\begin{correction}
During flight, $\vec{p}_3$ and the vertical component of $x_L$ must be measured with onboard sensors. 
\end{correction}

\item
\textit{
In P.7 L.35: Please state explicitly that the laser pointer direction vector (ell) is in the body frame or the camera frame (subscript b or c, even if they are the same in this paper). 
It may be a good idea as well to state in the same point in the text that these direction vectors will be estimated using an offline calibration method, rather than later in the text. 
}

At this point in the discussion, $\vec{l}$ is defined as an abstract vector, not in terms of any particular reference frame. Later, the representation of this abstract vector with respect to the camera frame is defined as $l_c$. The text has been revised as follows to mention how these vectors are to be estimated:

\begin{correction}
They point downward but are not
  necessarily parallel to $\vec{c}_3$, and the direction of each
laser is defined by $\vec{l_j}$ such that $\| \vec{l_j} \| = 1$. 
In this paper, $\vec{r_j}$ and $\vec{l_j}$ may be regarded as parameters
to be estimated in an offline procedure that is outlined in Section IIIC.
The $j$-th laser beam intersects ...
\end{correction}

\item
\textit{
In P.10 L.44, (laster) typo? 
}

Fixed typo.

\end{itemize}

\noindent\textit{
Thus I recommend that the manuscript is accepted after a minor revision addressing the points above.
}

\end{document}

### 2016-11-23 Response.tex
Add reviewer comments

@@
 \documentclass[11pt]{article}
-\usepackage[letterpaper,text={6.5in,8.6in},centering]{geometry}
+\usepackage[letterpaper,margin=1in,centering]{geometry}
 \usepackage{amssymb,amsmath,times,url}
@@
 
-\section*{Response to the Reviewers' Comments for 2014-12-G001229.R1}
+\section*{Response to the Reviewers' Comments for JCAS-D-16-00607}
 
@@
 
-\subsection*{Reviewer 1}
+\subsection*{Reviewer 2}
 
-\textit{The authors present nonlinear regression based estimation of UAV altitude and ground plane inclination for autonomous landing. 
-The estimates are obtained using the proposed laser-camera sensor, where the laser projection on the surface are measured in the camera's image plane. 
-The paper presents an interesting approach, and the application is relevant to the journal. 
-The paper is sufficiently clear and easy to follow. 
-The controller and trajectory generation are borrowed from the author's previous work. 
-The main contribution is in the estimation method for altitude and ground plane inclination. Below are some of my major concerns:
+\textit{A new geometric adaptive control scheme for the stabilization of the attitude dynamics of a rigid body with state inequality constraints is studied in this paper and ensures that the closed-loop system is asymptotically stable in the sense of Lyapunov stability.
+The main contribution and result are well presented and organized.
+Therefore, it is sufficient to be accepted in this journal provided that the following minor problems are considered in the revised version.
 }
 
-\setlength{\leftmargini}{0pt}
-\begin{itemize}\setlength{\itemsep}{2\parsep}
+% \setlength{\leftmargini}{0pt}
+\begin{enumerate}
 
-\item 
-\textit{The laser-based approach to obtain artificial feature points using the presented image processing approach may not be suitable in many outdoor situations. 
-It is very common to experience bright spots and reflections in sunny conditions, which would be difficult to distinguish from the laser points. 
-I am aware that the authors have clearly stated that the method works well in shaded and indoor conditions but, in my opinion, that limits the applicability.
-}
+\item \textit{ In general, the external disturbance is a time-varying signal even though it is bounded. Thus, authors should consider the time-varying disturbance case.}
 
-The image processing approach outlined in this paper is limited to conditions in which the thresholding works well, but the present approach may be extended using more robust techniques. 
-It may be possible to incorporate color into the image processing, or to selectively choose regions of interest in the image based on expectations on where the laser pointer projections should appear in the image, for example.
-I think similar objections can be made to many other computer vision applications, which may work well in lab environments but require further development to perform robustly under any lighting condition.
-Nonetheless, the conclusion has been modified to make the limitations of this approach more clear:
+\item \textit{If the inertia matrix is unknown, how to modify the suggested control system guaranteeing the asymptotic stability?}
 
-\begin{correction}
-... Contrary to other vision-based approaches, the system does not require features to be present at the landing site. 
-However, the image processing approach employed here assumes that the intensity of the laser points in the image are much brighter than the rest of the image, an assumption that may break down under certain conditions, especially in bright sunlight.
-The result of the estimation and landing trajectory ...
-\end{correction}
+\item \textit{The state inequality constraint is not violated based on adding the repulsive term in the attitude error function. Is this result still valid if this constraint becomes time-dependent?}
 
-\item
-\textit{The authors states that the xy-coordinates of the landing position $x_L$ are known. 
-I believe, without loss of generality, the authors could mention that the origin of the inertial frame can be assumed to coincide with $x_L$ to get rid of the assumption.
-}
+\end{enumerate}
 
-It is true that the origin of the inertial frame can be assumed to coincide with $x_L$ to eliminate the assumption of known horizontal position, but I do not agree that this assumption preserves generality.
-With the inertial frame coincident with $x_L$, it no longer becomes necessary to estimate $h$ (which in this case is simply the vertical component of position) since the position of the quadrotor is assumed to be known.
-Assuming that the horizontal components of $x_L$ are known can be as simple as the quadrotor hovering over an arbitrary position to attempt a landing, so long as the flat ground plane assumption is met.
+\subsection*{Reviewer 3}
 
-\item
-\textit{The most limiting assumption is that the quadrotor hovers directly above the landing point and obtains a bunch of images to solve for the altitude and ground plane inclination. 
-In practice, due to external disturbances such as wind gusts and light-weight construction of quadrotors, it is very difficult to hover them at one location.
-}
+\textit{This paper considers the attitude control with inequality constraints.
+Attitude dynamics with matched uncertainty which is parameterized by a unknown constant matrix, and hard constants expressed by rotation matrix are considered.
+Although the problem is very interesting, the proofs for major results on the case with plant uncertainty are far from complete.
+Some comments are listed below.}
 
-Position control of quadrotors definitely varies in different conditions, such as wind gusts as you point out. 
-However, the landing approach developed in this paper would be most applicable to large, expensive vehicles, where landing on an inclined surface without damage can not easily be achieved by cutting throttle near the ground, as might be done with a small lightweight vehicle.
-Larger, heavier vehicles can be more robust to external disturbances, and recent advances in position control using optical flow could be useful.
-%Furthermore, the proposed algorithm to estimate the inclination of the landing surface is not sensitive to the horizontal movements of the quadrotor, as the lasers are fixed to the quadrotor body.
+\begin{enumerate}
+\item \textit{Please give a precise definition of variation used in the paper, e.g., eq. (17) and (18)}
+\item \textit{This is serious.
+In section 2, the upper bounds listed in Proposition 4 are given.
+Well, these should be the properties that your controller guarantees not come from the set D you've defined.
+Since these properties are used to derive the bound H which is used to derive the result in Proposition 5, the stability proof under the proposed controller is far from complete.}
+\item \textit{Typo in eq. (40).}
+\item \textit{Abuse of notation 'hat' and 'vee' in equations (6)-(8)}
+\end{enumerate}
 
-\item
-\textit{Since the development in Section 3B and 3C is based on the above assumption, it is not clear how to obtain m images while maintaining constant altitude (as required to solve regression in Section 3C2).
-Do you only yaw to obtain a measurement vector of size 2mn?
-Please clarify.
-}
+\subsection*{Reviewer 4}
+\textit{This paper presents a new geometric adaptive control system with state inequality constraints for the attitude dynamics of a rigid body.
+The controlled attitude trajectory avoids undesired regions defined by the inequality constraint, and an adaptive update law that enables attitude stabilization in the presence of unknown disturbances is developed.
+However, the paper can be improved and some revisions are required.}
 
-Yawing is sufficient to obtain the measurement vector. 
-In practice, since it is not possible to hover exactly in one position as you pointed out previously, simply attempting to hold position will yield distinct measurements suitable for the estimation procedure.
-The following has been added to clarify how to obtain the $m$ frames:
+\begin{enumerate}
+\item \textit{Probably, the weak point is that the underlying experiments are not solid.
+The author claims that the attitude dynamics and the proposed control systems are developed on the special orthogonal group such that singularities and ambiguities of other attitude parameterizations, such as Euler angles and quaternions are completely avoided.
+But the numerical simulations and experimental results don't demonstrate the effectiveness of the proposed control system.
+How is the singularity avoided in the Euler angles?
+Please give the detail.}
+\item \textit{The units of y axis of Figures 1 - 3 and 5 should be mentioned in the manuscript.}
+\item \textit{Please check and correct Page 2 Line 60.}
+\item \textit{The units of the parameters are missing. These should be added in the manuscript.}
+\item \textit{What are the design parameters of the proposed method and how the design parameters are selected? These should be included in the manuiscript.}
+\item \textit{Specification of the sensors in the experiments should be included in the manuscript.}
+\end{enumerate}
 
-\begin{correction}
-Suppose the above image processing algorithm is repeated over a short time period to obtain $m$ image frames. 
-Theoretically, in order to obtain the $m$ distinct frames while holding position, the quadrotor must change its attitude by yawing.
-In practice, however, small disturbances ensure that the measurements are distinct even with the vehicle simply
-attempting to hold position.
-An estimation scheme is necessary ...
-\end{correction}
+\subsection*{Reviewer 5}
+\textit{This paper studies adaptive control design for the attitude dynamics of a rigid body system with state inequality constraints.
+The designed controller is proved to be asymptotically stabilized and may enable attitude stabilization in the presence of unknown disturbances.
+The attitude trajectory by the controller may avoid undesired regions.
+The effectiveness of the proposed control system is demonstrated through numerical simulations and experimental results.
+This paper is well written and the research contents are interesting.
+The main contributions of this paper are the new geometric adaptive control system proposed by the authors and its experimental verification.
+This paper is well organized and almost need not to make any changes.
+This reviewer suggests that it can be accepted for publication in International Journal of Control, Automation and Systems.}
 
-\item
-\textit{Formal approach to determine landing time and switching time might be necessary. 
-The switching time satisfies the boundary conditions on the position of the UAV but the landing time is arbitrarily chosen. 
-Although the authors state that since attitude dynamics are typically fast so that the desired orientation can be achieved in small amount of time, a formal proof to determine tL given tS and xS will greatly improve the paper.
-}
-
-As discussed at the end of Section IV.B, the boundary condition to align the attitude of the quadrotor to the landing surface is indirectly imposed by selecting $t_L$.
-In practice, $t_L-t_S$ should be sufficiently large such that the attitude is aligned to the landing surface before the moment of touchdown.
-However, it is determined by various factors, such as the controller gain, the moment of inertia of the quadrotor, and the maximum thrust of the quadrotor.
-As such, providing an analytic expression accounting these for the controlled attitude trajectories is beyond the scope of this technical note.
-
-Instead, the last paragraph of Section IV.B has been revised as follow, to provide a guideline to select $t_L$ and other parameters.
-
-\begin{correction}
-As this problem of selecting $x_S,v_S,f,t_S$ and $t_L$ is underdetermined, one may consider optimizing the parameters with respect to a certain cost function. 
-Instead, these parameters can be chosen according to the following heuristic approach.
-Note the landing trajectory can be designed in the two dimensional plane normal to $b_{1_c}$. 
-First, the landing time $t_L$ is chosen sufficiently large to avoid a rapid descent, and $t_S$ can be chosen about 0.5 second less than $t_L$ initially. 
-Then, the switching point $x_S$ is selected such that it is on the line joining $x_H$ and $x_L$, and the distance between $x_S$ and $x_L$ is about one or two times of the quadrotor diameter. 
-We can also restrict $v_S$ to be horizontal such that it does not cause any additional downward velocity at $t_L$. 
-The remaining two parameters, namely $f$ and the horizontal component of $v_S$, are iterated numerically such that $x(t_L)$ becomes equal to $x_L$ within the plane normal to $b_{1_c}$. 
-Finally, the switching time $t_S$ can be further iterated to ensure the attitude error becomes sufficiently small at $t=t_L$. 
-These are illustrated by the following numerical examples. 
-\end{correction}
-
-\item
-\textit{Although the presented approach using laser-based artificial features is interesting, it is difficult to see the advantage of using lasers over pure-vision based approaches. 
-For example, nonlinear observer based methods can be applied to estimate the altitude (e.g., On-Line Estimation of Feature Depth
-for Image-Based Visual Servoing Schemes by DeLuca) or homography-based approaches can be used to land the quadrotor using natural feature points (not IR markers) even without the knowledge of the desired or reference image.
-}
-
-As discussed in the introduction, the primary advantage of the present approach is that natural feature points are not required, meaning that this approach could succeed on a textureless flat plate where a feature-based approach would fail.
-Feature detectors have made significant progress but are not reliable on solid color surfaces lacking significant texture.
-
-\end{itemize}
-
-\noindent\textit{Minor edits:}
-
-\begin{itemize}\setlength{\itemsep}{2\parsep}
-
-\item
-\textit{eq. 16 - change p3,e,3 to p3,e
-}
-
-In this equation, $p_{3,e,3}$ was intended to represent the third component of $p_{3,e}$. This equation has been modified as follows:
-
-\begin{correction}
-  $\beta_j = h p_{3,e}^T \vec{e_3} -
-r_{j,c}^T R^T p_{3,e}$
-\end{correction}
-
-\item
-\textit{the notation defined for r, l, and p uses bar but it was dropped in the subsequent analysis. 
-please rectify.
-}
-
-This was intentional. In this manuscript, the bar is used to denote an abstract vector, and it is dropped for the representation of the vector with respect to a particular reference frame.
-To make this more clear, a sentence was added as follows:
-\begin{correction}
-... a (virtual) image plane is
-parallel to the $\vec{c}_1$-$\vec{c}_2$ plane and offset from the
-aperture along $\vec{c}_3$ by the focal length $f_c$.
-In the following discussion, an abstract vector is written with an arrow, e.g.
-$\vec{x}$, and the representation of the vector with respect to a particular reference frame is written without the arrow with a subscript indicating the reference frame, e.g.
-$x_e$.
-\end{correction}
-
-%\textcolor{red}{JAD: Do you agree?}
-
-\item
-\textit{page 12, line 29 - defined in (29)-(30) change that to "defined in (29) and (30)"
-}
-
-The text has been revised accordingly.
-
-\end{itemize}
-
-\subsection*{Reviewer 2}
-
-\textit{The manuscript entitled "Monocular Estimation of Ground Orientation for Autonomous Landing of a Quadrotor" demonstrates a novel visual method for landing a quadrotor MAV on an inclined flat surface.
-Methods for visually estimate the height and inclination angles of the ground surface are presented as well as the needed visual calibration method. 
-The manuscript also presents the online trajectory generation and tracking control to achieve smooth landing on the surface backed up by simulation and experimentation results. 
-}
-
-\textit{
-In addition to the interesting visual method presented, the manuscript is well written and easy to follow. 
-Well done. 
-The notes provided are minor in nature, and they are split in two groups.
-}
-
-\textit{
-The more serious notes are the following:
-}
-
-\setlength{\leftmargini}{0pt}
-\begin{itemize}\setlength{\itemsep}{2\parsep}
-
-\item 
-\textit{The author review states that all relevant visual methods in the literature rely on fixed pre-known markers.
-A very relevant work that does not require such markers is "de Croon, G.
-CHE, et al.
-"Optic-flow based slope estimation for autonomous landing." International Journal of Micro Air Vehicles 5.4 (2013): 287-298." I suggest that the author acknowledge this work as it is more flexible in its requirements than the cited works as well as the author work (in the aspect of being completely passive).
-}
-
-This work is indeed very relevant and avoids many limitations of other vision-based approaches mentioned in the text. The text has been revised to acknowledge it as follows:
-
-\begin{correction}
-As described above, many vision-based approaches relying on feature detection impose the unrealistic constraint that a landing site have a known pattern present to be detected by the computer vision system.
-In most real flight situations, this is not a practical solution. 
-Further, many algorithms suffer from slow computation times, especially on embedded hardware, although this problem is becoming less prevalent with advances in hardware and increasingly efficient computer vision algorithms.
-One approach free from these limitations is developed in [17], where the slope of the ground surface is extracted directly from the optic flow field. 
-This purely vision-based approach shows promise in increasing the level of autonomy in landing, although the problem of landing on a sloped surface is not considered.
-\end{correction}
-
-\item
-\textit{The author has stated eq. 38 with no comments at all. It would be better to briefly highlight the rationale behind its formulation in this form. 
-}
-
-Equation (38) is chosen such that it satisfies four boundary conditions, namely $x(0)=x_H$, $v(0)=0$, $x(t_S)=x_S$, and $v(t_S)=v_S$.
-Additional fifth boundary condition for the zero initial acceleration is imposed for smooth initial transition.
-These determine the five coefficients of the selected fourth order polynomial uniquely.
-
-When $v(t_S)=0$, the selected trajectory has additional property that $\min\{x_H,x_S\}\leq x_d(t) \leq \max\{x_H,x_S\}$ for any $0\leq t \leq t_S$.
-This may be used to ensure that the quadrotor does not fly below the switching point $x_S$ for safety.
-
-To clarify these, the paragraph including (38) has been revised as follows.
-
-\begin{correction}
-The desired landing trajectory satisfying these four boundary conditions and another boundary condition of zero initial acceleration is parameterized by $t$ as follows. 
-For $1\leq i\leq 3$, its $i$-th component is given by
-\begin{align}
-x_{d_i}(t)& =(v_{S_i}t_S+3(x_{H_i}-x_{S_i}))\frac{t^4}{t_S^4} -(v_{S_i}t_S+4(x_{H_i}-x_{S_i}))\frac{t^3}{t_S^3}
-+x_{H_i}.
-\end{align}
-When $v_{S_i}=0$, the above trajectory exhibits the additional property that $x_{d_i}(t)$ lies between $x_{H_i}$ and $x_{S_i}$ when $0\leq t\leq t_S$.
-This can be used to guarantee that the quadrotor does not fly below the switching point during its descent for safety.
-\end{correction}
-
-\item
-\textit{This author emphasise that any pre-requirements on the landing site is not practical for a truly autonomous landing system.
-While I agree on this, the work seems to rely on very accurate method (Vicon system) for estimating the quadrotor’s state (the position, velocity, attitude and attitude rates).
-In principle the same estimates could be obtained using an onboard IMU and GPS modules, but with far less accuracy.
-With no robustness analysis to state estimation errors and no experimentation performed outdoor using IMU/GPS sensors the practical applicability of the system is still questionable.
-I suggest that the authors address this point, either fully or partially followed up by future work, if the current text size does not allow.
-}
-
-While it is true that the use of a motion capture system for position and attitude estimation limits the applicability of the experimental results presented, the problem of state estimation of the quadrotor's pose is beyond the scope of this paper.
-The following has been added to the end of the results section to address this:
-
-\begin{correction}
-For these landing experiments, a pose estimate was provided by the Vicon system. 
-For a truly autonomous landing, it is unreasonable to use a motion
-capture system, but onboard pose estimation of the quadrotor is beyond the scope of this paper.
-Future work should aim to recreate these landing results  without any requirement on external sensors.
-\end{correction}
-
-\item
-\textit{Same practicality issue can be raised against the image processing technique and the threshold selection in varying light conditions in real life application.
-}
-
-Please see the above comment to Reviewer 1 regarding the practicality of the image processing procedure.
-
-\item
-\textit{There is no quantification of the number (m) of measurements needed to acceptably estimate the required parameters.
-More importantly, there is also no mention on the conditions under which these measurements should be taken for observability of the estimated parameters.
-For instance, if m>1 then images should be captured under distinct conditions, so would it be sufficient to vary the altitude, or the attitude or both?
-is a simple motion enough or a special manoeuvre has to be designed for this purpose?
-are the images taken while descending to xH enough for estimation purposes?
-}
-
-%\textcolor{red}{JAD: how to quantify m?}
-
-To obtain the $m$ image frames, the quadrotor should hold position, since $h$ must be estimated. 
-No special maneuvre is necessary; yawing would ensure distinct measurements. 
-In practice, due to disturbances, simply attempting to hold position will yield distinct measurements suitable for the estimation procedure.
-
-The accuracy of the estimation can be quantified via the size of the posterior covariance matrix.
-If needed, the number of the measurements can be increased until the covariance matrix is less than a prescribed threshold.
-But, at the presented experimental setup, the sensor measurements are obtained at the rate of $16 Hz$, and taking the measurements over a few seconds was enough.
-
-This has been clarified in the text as follows:
-
-\begin{correction}
-Suppose the above image processing algorithm is repeated over a short time period to obtain $m$ image frames.
-Theoretically, in order to obtain the $m$ distinct frames while holding position, the quadrotor must change its attitude by yawing.
-In practice, however, small disturbances ensure that the measurements are distinct even with the vehicle simply attempting to hold position.
-An estimation scheme is necessary ...
-\end{correction}
-
-\item
-\textit{
-More analysis or guidelines for choosing tS, xS, tL, vS, f would be appreciated by the reader.
-}
-
-The last paragraph of Section IV.B has been revised as follow, to provide a guideline to select those parameters.
-
-\begin{correction}
-As this problem of selecting $x_S,v_S,f,t_S$ and $t_L$ is underdetermined, one may consider optimizing the parameters with respect to a certain cost function.
-Instead, these parameters can be chosen according to the following heuristic way.
-Note the landing trajectory can be designed in the two dimensional plane normal to $b_{1_c}$.
-First, the landing time $t_L$ is chosen sufficiently large such that a rapid descending is avoided, and $t_S$ can be chosen about 0.5 second less than $t_L$ initially.
-Then, the switching point $x_S$ is selected such that it is on the line joining the $x_H$ and $x_L$, and the distance between $x_S$ and $x_L$ is about 1 or 2 times of the quadrotor diameter.
-We can also restrict $v_S$ to be horizontal such that it does not cause any additional downward velocity at $t_L$.
-The remaining two parameters, namely $f$ and the horizontal component of $v_S$ are iterated numerically such that $x(t_L)$ becomes equal to $x_L$ within the plane normal to $b_{1_c}$.
-Finally, the switching time $t_S$ can be further iterated to ensure the attitude error becomes sufficiently small at $t=t_L$.
-These are illustrated by the following numerical examples.
-\end{correction}
-
-\end{itemize}
-
-\noindent\textit{The other less serious comments are:}
-
-\begin{itemize}\setlength{\itemsep}{2\parsep}
-
-\item
-\textit{
-In P.3 L.30, in the author comments on ref 15; How image processing is done offline?
-do you mean off-board?
-The word “offline” indicates that the image processing is performed not at the time of the experiment, which does not make sense in this context.
-}
-
-Image processing is done off-board. The text has been updated to use ``off-board'' instead of ``offline.''
-
-\item
-\textit{
-In P.4 L.28: Using the term "fully controlled" in the first sentence is inaccurate and can be misleading.
-The quadrotor system is fully controllable as the 6DoF pose can be reached in a finite time using the available control.
-However, because it is underactuated then not all 6DoF states can be controlled simultaneously as the second sentence clearly states.
-The first sentence can be removed to avoid this issue.
-}
-
-This sentence has been removed.
-
-\item
-\textit{
-I suggest using the term "laser pointers modules" (for instance) instead of "laser modules" used through the text to avoid confusion with laser range finder modules which are much more often used on MAVs that laser pointers.
-}
-
-The term ``laser modules'' can indeed be ambiguous. The text has been updated to use the term ``laser pointers.'' I don't believe any meaning is lost in dropping the word ``modules.''
-
-\item
-\textit{
-In P.6 L.41, either the word "and" after p3 has to be removed or the sentence has to be rephrased.
-}
-
-This sentence has been revised as follows:
-
-\begin{correction}
-During flight, $\vec{p}_3$ and the vertical component of $x_L$ must be measured with onboard sensors. 
-\end{correction}
-
-\item
-\textit{
-In P.7 L.35: Please state explicitly that the laser pointer direction vector (ell) is in the body frame or the camera frame (subscript b or c, even if they are the same in this paper). 
-It may be a good idea as well to state in the same point in the text that these direction vectors will be estimated using an offline calibration method, rather than later in the text. 
-}
-
-At this point in the discussion, $\vec{l}$ is defined as an abstract vector, not in terms of any particular reference frame.
-Later, the representation of this abstract vector with respect to the camera frame is defined as $l_c$.
-The text has been revised as follows to mention how these vectors are to be estimated:
-
-\begin{correction}
-They point downward but are not
-  necessarily parallel to $\vec{c}_3$, and the direction of each
-laser is defined by $\vec{l_j}$ such that $\| \vec{l_j} \| = 1$. 
-In this paper, $\vec{r_j}$ and $\vec{l_j}$ may be regarded as parameters
-to be estimated in an offline procedure that is outlined in Section IIIC.
-The $j$-th laser beam intersects ...
-\end{correction}
-
-\item
-\textit{
-In P.10 L.44, (laster) typo? 
-}
-
-Fixed typo.
-
-\end{itemize}
-
-\noindent\textit{
-Thus I recommend that the manuscript is accepted after a minor revision addressing the points above.
-}
+\begin{enumerate}
+\item \textit{The only question is that all the figures in this paper are too small and are not legible. The meanings of different lines in one figure should be explained in the title content.}
+\end{enumerate}
 

### 2016-11-26 Response.tex
Remove xr package
Draft answer for time varying disturbances

@@
 \usepackage{amssymb,amsmath,times,url}
-\usepackage{xr,color}
+\usepackage{color}
 
@@
 
+It is true that in general, the external disturbances on a system will be time varying.
+However, the form of uncertainty shown in \( (1) \) is commonly used in the adaptive control literature~\cite{lee2013b,ioannou2012}.
+As a result, we use this same form of uncertainty, namely that the uncertain disturbance is additive in nature and enters through the input channel.
+In addition, a wide variety of disturbances is accurately represented by this formulation in the aerospace engineering field and several examples are given in the article.
+Furthermore, it has been shown in~\cite{ioannou2012} that this form of adaptive control is able to handle time-varying uncertainties in which the uncertain term is varying sufficiently slowly as compared to the controlled dynamics.
+
 \item \textit{If the inertia matrix is unknown, how to modify the suggested control system guaranteeing the asymptotic stability?}
@@
 
+\bibliography{library}
+\bibliographystyle{ieeetr}
 \end{document}

### 2016-11-26 Response.tex
Draft answer to address uncertain inertia matrix

@@
 \item \textit{If the inertia matrix is unknown, how to modify the suggested control system guaranteeing the asymptotic stability?}
+Even with an uncertainty in the inertia matrix, one could redefine the system and treat this as an unknonw external disturbance instead.
+
+Show the algebra that allows for either a multiplicative or additive uncertainty in the inertia matrix as equivalent to an external torque
 

### 2016-11-27 manuscript.tex
Fix file name of figure
Add definition of variation of the rotation matrix

@@
     \subfigure[Angle to constraints \label{fig:con_angles}]{\includegraphics[width=0.5\columnwidth]{constraint_angles} }\\
-    \subfigure[Disturbance estimate \( \bar \Delta \)  \label{fig:delta_adapt} ]{\includegraphics[width=0.5\columnwidth]{delta_adapt}}~
+    \subfigure[Disturbance estimate \( \bar \Delta \)  \label{fig:delta_adapt} ]{\includegraphics[width=0.5\columnwidth]{Delta_adapt}}~
     \subfigure[Attitude trajectory \label{fig:cad_adapt}]{\includegraphics[trim=9cm 2.5cm 0 0,clip,width=0.645\columnwidth]{cad_adapt} }
@@
 Next, we consider~\cref{item:prop_era}.
-The variation of~\cref{eqn:A} is taken with respect to \( \delta R = R \hat \eta \) as
+The infinitesimal variation of a rotation matrix is defined as
+\begin{align*}
+    \delta R = \left. \diff{}{\epsilon} \right|_{\epsilon=0} R \exp{\epsilon \hat{\eta}} = R \hat{\eta} .
+\end{align*}
+Using this the variation of~\cref{eqn:A} is taken with respect to \( R \) as
 \begin{align*}
@@
 \end{align*}
-where we used~\cref{eqn:hat1}.
+where we used~\cref{eqn:hat1} to achieve the simplified form.
 

### 2016-11-27 Response.tex
Draft answer for time varying disturbance simulation
Add a question for further study
Add packages and macros
Add response and include variation of R

@@
 \usepackage[letterpaper,margin=1in,centering]{geometry}
-\usepackage{amssymb,amsmath,times,url}
+\usepackage{amssymb}  
+\usepackage{amsmath}
+\usepackage{amsfonts}
+\usepackage{mathtools}
+\usepackage{microtype}
 \usepackage{color}
+\usepackage{hyperref}
+\usepackage[]{cleveref} % get fancy referencing
 
+%%%%%%%%%%%%%%%%%%%%%%%%%
+% CUSTOM MACROS
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\newcommand{\linearize}[3]{\ensuremath{\left. \frac{\partial #1}{\partial #2} \right|_{#3} \delta #2}}
 \newcommand{\norm}[1]{\ensuremath{\left\| #1 \right\|}}
+\newcommand{\Real}[1]{\ensuremath{\Re \left\{ #1 \right\}}}
 \newcommand{\bracket}[1]{\ensuremath{\left[ #1 \right]}}
@@
 \newcommand{\deriv}[2]{\ensuremath{\frac{\partial #1}{\partial #2}}}
+\newcommand{\diff}[2]{\ensuremath{\frac{d #1}{d #2}}}
+\newcommand{\dirDiff}[2]{\ensuremath{\mathbf{D}_{#2} #1 \cdot \delta #2}} % directional derivative
 \newcommand{\SO}{\ensuremath{\mathsf{SO(3)}}}
@@
 \newcommand{\se}{\ensuremath{\mathfrak{se}(3)}}
-\renewcommand{\Re}{\ensuremath{\mathbb{R}}}
+\newcommand{\R}{\ensuremath{\mathbb{R}}}
 \newcommand{\aSE}[2]{\ensuremath{\begin{bmatrix}#1&#2\\0&1\end{bmatrix}}}
@@
 \newcommand{\refprop}[1]{Proposition \ref{prop:#1}}
+\newcommand{\mypaper}{}
 
@@
 \newenvironment{correction}{\begin{list}{}{\setlength{\leftmargin}{1cm}\setlength{\rightmargin}{1cm}}\vspace{\parsep}\item[]``}{''\end{list}}
-
-%\externaldocument{AUT13}
 
@@
 
+How slowly do the uncertainties have to behave for the simulation?
+
 \item \textit{If the inertia matrix is unknown, how to modify the suggested control system guaranteeing the asymptotic stability?}
@@
 \item \textit{The state inequality constraint is not violated based on adding the repulsive term in the attitude error function. Is this result still valid if this constraint becomes time-dependent?}
+
+Run another simulation showing that for a restricted class of time-varying error functions, the system is stable
 
@@
 \item \textit{Please give a precise definition of variation used in the paper, e.g., eq. (17) and (18)}
+The variation of the rotation matrix is defined as
+\begin{align*}
+    \delta R = \left. \diff{}{\epsilon} \right|_{\epsilon=0} R \exp{\epsilon \hat{\eta}} = R \hat{\eta} .
+\end{align*}
+We have augmented the proof of Proposition 1, which is given in Appendix 1, to include the definition of the variation as:
+\begin{correction}
+The infinitesimal variation of a rotation matrix is defined as
+\begin{align*}
+    \delta R = \left. \diff{}{\epsilon} \right|_{\epsilon=0} R \exp{\epsilon \hat{\eta}} = R \hat{\eta} .
+\end{align*}
+\end{correction}
+
 \item \textit{This is serious.

### 2016-11-27 Response.tex
Correct typo in equatino 40
Add response to notation choice

@@
 \item \textit{Typo in eq. (40).}
+
+The equation has been modified as:
+\begin{correction}
+\begin{gather}
+    0 < c < \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H} ,
+\end{gather}
+\end{correction}
+
 \item \textit{Abuse of notation 'hat' and 'vee' in equations (6)-(8)}
+
+The \( \wedge : \R^3 \to \so \) and \( \vee : \so \to \R^3 \) operators are used according to the convention that is common in the literature~\cite{lee2010,lee2011a}.
+In this case, the \textit{hat} operator is equivalently represented as \( \hat{x} = \parenth{x}^\wedge \).
+This dual representation eases the resulting typesetting for particularly long terms, such as those used in Equations~\((6) - (8)\).
+
 \end{enumerate}

### 2016-11-28 manuscript.tex
Correct typo in equatino 40
Uppercase for table reference

@@
 \begin{gather}
-	0 < c < \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k-R \lambda_M H} , \label{eqn:c_bound}
+	0 < c < \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H} , \label{eqn:c_bound}
 \end{gather}
@@
 In spite of the uncompensated disturbance, the system is able to avoid the constrained regions as shown in~\cref{fig:con_angles_con}.
-The angle to each of the constraints,  \( \arccos(r^T R^T v_i) \), is always greater than the specified angle, \( \theta_i \), in~\cref{tab:constraints}.
+The angle to each of the constraints,  \( \arccos(r^T R^T v_i) \), is always greater than the specified angle, \( \theta_i \), in~\Cref{tab:constraints}.
 

### 2016-11-28 manuscript.tex
Start adding more detail on problems with Euler angles and quaternions

@@
 
+% Discuss the benefits of using this geometric representation as compared to Euler angles or quaternions
+Attitude parameterizations, such as Euler angles and Quaternions, are frequently used in the aerospace and astrodynamics communities~\cite{vallado2001,bate1971,wertz1978}.
+For example, Euler angle sequences are frequently used to describe the transformation between a variety of reference frames used to describe the position and orientation of the orbit of Earth satellites~\cite{vallado2001}.
+In addition, quaternions were used during the operation of Skylab and the NASA Space Shuttle~\cite{hughes2004}.
+However, the choice of attitude parameterization plays a critical role in control design and the resulting motion of the system.
+
+% singularities and the problems involved with using Euler angles
+Euler angle sequences are a minimum, three-parameter set of angles which describe the transformation between two reference frames.
+A general rotation is decomposed as the sequence of three rotations.
+
+% discuss what a singularitly in the euler angle actually means (infinite angular velocity) and divide by zero condition
+% show common euler angle sequences
+
+% discuss the unwinding phenomenon with quaternions
 \section{Experiment on Hexrotor UAV}

### 2016-11-28 Response.tex
Add additional packages and macros
Add macros
Add some additional detail on euler angles

@@
 \usepackage{color}
+\usepackage{bm}
+\usepackage{xr}
 \usepackage{hyperref}
@@
 
+\externaldocument{manuscript}
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \newcommand{\mypaper}{}
+\newcommand{\vecbf}[1]{\bm{#1}}
+\newcommand{\slfrac}[2]{\left.#1\middle/#2\right.}
 
@@
 Please give the detail.}
+
+The primary purpose of this article is to present the formulation of constrained attitude control on the special orthogonal group, \( \SO \).
+There have been many references which have explicitly demonstrated the issues of singularities and ambiguities of other attitude parameterizations~\cite{chaturvedi2011a,bhat2000,hughes2004}.
+{\large ADD MORE REFERENCES WHICH SHOW THIS} 
+As a result, the numerical simulations and hardware experiments were designed to demonstrate the feasibility of the proposed attitude control and the application of general attitude constraints on \( \SO \), rather than highlight the deficiences of attitude parameterizations.
+However, additional detail has been added in the numerical simulation section demonstrating and highlighting the singularities inherent in the Euler angle parameterization.
+
+\begin{correction}
+    % Discuss the benefits of using this geometric representation as compared to Euler angles or quaternions
+Attitude parameterizations, such as Euler angles and Quaternions, are frequently used in the aerospace and astrodynamics communities~\cite{vallado2001,bate1971,wertz1978}.
+For example, Euler angle sequences are frequently used to describe the transformation between a variety of reference frames used to describe the position and orientation of the orbit of Earth satellites~\cite{vallado2001}.
+In addition, quaternions were used during the operation of Skylab and the NASA Space Shuttle~\cite{hughes2004}.
+However, the choice of attitude parameterization plays a critical role in control design and the resulting motion of the system.
+
+% singularities and the problems involved with using Euler angles
+Euler angle sequences are a minimum, three-parameter set of angles which describe the transformation between two reference frames.
+Euler angles represent any general rotation as a sequence of three intermediate rotations.
+By convention, there are \( 24 \) possible Euler angle sequences for any given rotation.
+In addition, Euler angles are a minimum representation, as only three angles, and the associated sequence, are required to describe the three angular degrees of freedom of the rigid body.
+However, there is great ambiguity in the representation of the attitude as there are many equivalent Euler angle sequences for a given attitude of the system.
+Therefore, great care must be taken in the control system design to ensure that a consistent sequence is used. 
+Furthermore, it has been shown that no minimal attitude representation can describe orientations both globally and without singularities~\cite{hughes2004,bhat2000}.
+These singularities can cause significant difficulties during control design and hardware implementation.
+
+To demonstrate the effect of the kinematic singularities inherent with Euler angles we will represent the attitude of the body fixed reference frame, \( \vecbf{b}_i \), with respect to the inertial frame, \( \vecbf{e}_i\), in terms of the \( 3-1-3\) Euler angle sequence.
+More explicitly, this corresponds to the rotation sequence \( \theta_1 \vecbf{b}_3 , \theta_2 \vecbf{b}_1, \theta_3 \vecbf{b}_3 \).
+The rotation matrix, \( R(\theta_1, \theta_2, \theta_3) \), corresponding to this sequence is 
+\begin{align}\label{eq:euler313}
+    \begin{bmatrix}
+        -s_1 c_2 s_3 + c_3 c_1 & -s_1 c_2 c_3 - s_3 c_1 & s_1s_2 \\
+        c_1 c_2 s_3 + c_3 s_1 & c_1 c_2 c_3 - s_3 s_1 & - c_1 s_2 \\
+        s_2 s_3 & s_2 c_3 & c_2
+    \end{bmatrix} ,
+\end{align}
+where \( s_i, c_i \) represent \( \sin \theta_i, \cos \theta_i \) for \( i = \braces{1,2,3}\).
+Using this representation that kinematic differential equations for the associated Euler angles are given as
+\begin{align}\label{eq:euler313_diff}
+    \begin{bmatrix}
+        \dot{\theta}_1 \\ \dot{\theta}_2 \\ \dot{\theta}_3 
+    \end{bmatrix}
+    =
+    \begin{bmatrix}
+        \slfrac{\parenth{\Omega_1 s_3 + \Omega_2 c_3}}{s_2} \\
+        \Omega_1 c_3 - \Omega_2 s_3 \\
+        -\slfrac{\parenth{\Omega_1 s_3 + \omega_2 c_3}c_2}{s_2} + \Omega_3
+    \end{bmatrix} .
+\end{align}
+From~\cref{eq:euler313_diff}, it is immediately clear that a singularity exists when \( \sin \theta_2 = 0 \) or \( \theta_2 = 0, \pm \pi \). 
+In the vicinity of the singularity, the angular velocities of the Euler angles will tend to approach \( \pm \infty \) and the angular velocities will experience instantaneous sign changes.
+Furthermore, all Euler angle sequences will exhibit a similar singularity at either \( \theta_2 = 0, \pm \pi \) or \( \theta_2 = \pm \frac{\pi}{2}, \pm \frac{3\pi}{2} \) and switching the sequence does not alleviate the issue.
+As a result, Euler angles are not appropriate for systems which experience large angular rotations, such as those demonstrated in~\cref{fig:adapt}, or control systems which rely on the angular velocities \( \theta_i \).
+\end{correction}
+
 \item \textit{The units of y axis of Figures 1 - 3 and 5 should be mentioned in the manuscript.}

### 2016-11-28 manuscript.tex
Add some additional detail on euler angles

@@
 Euler angle sequences are a minimum, three-parameter set of angles which describe the transformation between two reference frames.
-A general rotation is decomposed as the sequence of three rotations.
+Euler angles represent any general rotation as a sequence of three intermediate rotations.
+By convention, there are \num{24} possible Euler angle sequences for any given rotation.
+In addition, Euler angles are a minimum representation, as only three angles, and the associated sequence, are required to describe the three angular degrees of freedom of the rigid body.
+However, there is great ambiguity in the representation of the attitude as there are many equivalent Euler angle sequences for a given attitude of the system.
+Therefore, great care must be taken in the control system design to ensure that a consistent sequence is used. 
+Furthermore, it has been shown that no minimal attitude representation can describe orientations both globally and without singularities~\cite{hughes2004,bhat2000}.
+These singularities can cause significant difficulties during control design and hardware implementation.
 
-% discuss what a singularitly in the euler angle actually means (infinite angular velocity) and divide by zero condition
-% show common euler angle sequences
+To demonstrate the effect of the kinematic singularities inherent with Euler angles we will represent the attitude of the body fixed reference frame, \( \vecbf{b}_i \), with respect to the inertial frame, \( \vecbf{e}_i\), in terms of the \( 3-1-3\) Euler angle sequence.
+More explicitly, this corresponds to the rotation sequence \( \theta_1 \vecbf{b}_3 , \theta_2 \vecbf{b}_1, \theta_3 \vecbf{b}_3 \).
+The rotation matrix, \( R(\theta_1, \theta_2, \theta_3) \), corresponding to this sequence is 
+\begin{align}\label{eq:euler313}
+    \begin{bmatrix}
+        -s_1 c_2 s_3 + c_3 c_1 & -s_1 c_2 c_3 - s_3 c_1 & s_1s_2 \\
+        c_1 c_2 s_3 + c_3 s_1 & c_1 c_2 c_3 - s_3 s_1 & - c_1 s_2 \\
+        s_2 s_3 & s_2 c_3 & c_2
+    \end{bmatrix} ,
+\end{align}
+where \( s_i, c_i \) represent \( \sin \theta_i, \cos \theta_i \) for \( i = \braces{1,2,3}\).
+Using this representation that kinematic differential equations for the associated Euler angles are given as
+\begin{align}\label{eq:euler313_diff}
+    \begin{bmatrix}
+        \dot{\theta}_1 \\ \dot{\theta}_2 \\ \dot{\theta}_3 
+    \end{bmatrix}
+    =
+    \begin{bmatrix}
+        \slfrac{\parenth{\Omega_1 s_3 + \Omega_2 c_3}}{s_2} \\
+        \Omega_1 c_3 - \Omega_2 s_3 \\
+        -\slfrac{\parenth{\Omega_1 s_3 + \omega_2 c_3}c_2}{s_2} + \Omega_3
+    \end{bmatrix} .
+\end{align}
+From~\cref{eq:euler313_diff}, it is immediately clear that a singularity exists when \( \sin \theta_2 = 0 \) or \( \theta_2 = 0, \pm \pi \). 
+In the vicinity of the singularity, the angular velocities of the Euler angles will tend to approach \( \pm \infty \) and the angular velocities will experience instantaneous sign changes.
+Furthermore, all Euler angle sequences will exhibit a similar singularity at either \( \theta_2 = 0, \pm \pi \) or \( \theta_2 = \pm \frac{\pi}{2}, \pm \frac{3\pi}{2} \) and switching the sequence does not alleviate the issue.
+As a result, Euler angles are not appropriate for systems which experience large angular rotations, such as those demonstrated in~\cref{fig:adapt}, or control systems which rely on the angular velocities \( \theta_i \).
 

### 2016-11-28 Response.tex
Add cleveref macros
Start addressing reviewer 4 #2. Include units for axes

@@
 \usepackage[]{cleveref} % get fancy referencing
+% edit cref citations for IEEE format
+\crefformat{equation}{(#2#1#3)} % no abbreviation for equation numbers
+\Crefformat{equation}{Equation~(#2#1#3)} % no abbreviation for equation numbers
+\crefrangeformat{equation}{(#3#1#4--#5#2#6)}
+\Crefrangeformat{equation}{(#3#1#4--#5#2#6)}
+\crefmultiformat{equation}{(#2#1#3)}{ and~(#2#1#3)}{, (#2#1#3)}{ and~(#2#1#3)}
+% edit cref citations for IEEE format
+\crefformat{figure}{Fig.~#2#1#3} % no abbreviation for equation numbers
+\Crefformat{figure}{Fig.~#2#1#3} % no abbreviation for equation numbers
+\crefrangeformat{figure}{Figs.~#3#1#4--#5#2#6}
+\Crefrangeformat{figure}{Figs.~#3#1#4--#5#2#6}
+\crefmultiformat{figure}{Figs.~#2#1#3}{ and~#2#1#3}{, #2#1#3}{ and~#2#1#3}
+% for items in a list
+\crefformat{enumi}{(#2#1#3)}
+\Crefformat{enumi}{Item~(#2#1#3)} 
+\crefrangeformat{enumi}{(#3#1#4--#5#2#6)}
+\Crefrangeformat{enumi}{Items~(#3#1#4--#5#2#6)}
+\crefmultiformat{enumi}{(#2#1#3)}{ and~(#2#1#3)}{, (#2#1#3)}{ and~(#2#1#3)}
 
@@
 \item \textit{The units of y axis of Figures 1 - 3 and 5 should be mentioned in the manuscript.}
+
+The discussion of~\cref{fig:config_error} was updated to include:
+\begin{correction}
+    The horizontal axes of~\cref{fig:config_error} represent the spherical angles \( \lambda \) and \( \beta \), while the vertical axes represent the unitless magnitude of the error functions defined in~\cref{eqn:psi,eqn:A,eqn:B}.
+\end{correction}
 \item \textit{Please check and correct Page 2 Line 60.}

### 2016-11-29 Response.tex
Add units for figure 1. Address reviewer 4 #2

@@
 \begin{correction}
-    The horizontal axes of~\cref{fig:config_error} represent the spherical angles \( \lambda \) and \( \beta \), while the vertical axes represent the unitless magnitude of the error functions defined in~\cref{eqn:psi,eqn:A,eqn:B}.
+    The horizontal axes of~\cref{fig:config_error} represent the domain of the spherical angles \( \lambda \) and \( \beta \) in degrees, while the vertical axes represent the unitless magnitude of the error functions defined in~\cref{eqn:psi,eqn:A,eqn:B}.
 \end{correction}

### 2016-11-29 manuscript.tex
Start addressing reviewer 4 #2. Include units for axes
Add units for figure 1. Address reviewer 4 #2
Add units for disturbance

@@
 Applying this method,~\cref{fig:config_error} allows us to visualize the error function on \( \SO \).
+The horizontal axes of~\cref{fig:config_error} represent the domain of the spherical angles \( \lambda \) and \( \beta \) in degrees, while the vertical axes represent the unitless magnitude of the error functions defined in~\cref{eqn:psi,eqn:A,eqn:B}.
 The attractive error function, given by~\cref{eqn:A}, has been previously used for attitude control on \(\SO\).
@@
 We show simulation results for the system stabilizing about the desired attitude with and without the adaptive update law from~\Cref{prop:adaptive_control}.
-We assume a fixed disturbance of \(\Delta = \begin{bmatrix} 0.2 & 0.2 & 0.2 \end{bmatrix}^T \), with the function \( W(R,\Omega) = I \).
+We assume a fixed disturbance of \(\Delta = \begin{bmatrix} 0.2 & 0.2 & 0.2 \end{bmatrix}^T \si{\newton\meter}\), with the function \( W(R,\Omega) = I \).
 This form is equivalent to an integral control term which penalizes deviations from the desired configuration.

### 2016-11-29 Response.tex
Add units for disturbance
Add more detail for figures 2-3 and talk about the units

@@
 \end{correction}
+
+Additional detail has been added for~\cref{fig:con}:
+\begin{correction}
+    \Cref{fig:eR_con} shows each component of the attitude error vector,~\cref{eqn:eR}, over the simulation time span.
+    \Cref{fig:Psi_con} shows the  magnitude of the combined error function,~\cref{eqn:psi}.
+\end{correction}
+\begin{correction}
+    The angle to each of the constraints, which is measured in degrees and given by \( \arccos(r^T R^T v_i) \), is always greater than the specified angle, \( \theta_i \), in~\Cref{tab:constraints}.
+\end{correction}
+and some more detail for~\cref{fig:adapt}:
+\begin{correction}
+    \Cref{fig:Psi_adapt,fig:con_angles} are equivalent to~\cref{fig:Psi_con,fig:con_angles_con} except include the addition of the adaptive update law.
+\end{correction}
+\begin{correction}
+    \Cref{fig:con_angles} shows that the angle, \( \arccos(r^T R^T v_i) \) and measured in degrees, between the body fixed sensor and each constraint is satisfied for the entire maneuver.
+\end{correction}
 \item \textit{Please check and correct Page 2 Line 60.}
 \item \textit{The units of the parameters are missing. These should be added in the manuscript.}
+
+The units of the disturbance have been included:
+\begin{correction}
+    We assume a fixed disturbance of \(\Delta = \begin{bmatrix} 0.2 & 0.2 & 0.2 \end{bmatrix}^T \si{\newton\meter}\), with the function \( W(R,\Omega) = I \).
+\end{correction}
 \item \textit{What are the design parameters of the proposed method and how the design parameters are selected? These should be included in the manuiscript.}

### 2016-11-29 manuscript.tex
Add more detail for figures 2-3 and talk about the units

@@
 Simulation results without the adaptive update law are shown in~\cref{fig:con}.
+\Cref{fig:eR_con} shows each component of the attitude error vector,~\cref{eqn:eR}, over the simulation time span.
+\Cref{fig:Psi_con} shows the  magnitude of the combined error function,~\cref{eqn:psi}.
 Without the update law, the system does not achieve zero steady state error. 
@@
 In spite of the uncompensated disturbance, the system is able to avoid the constrained regions as shown in~\cref{fig:con_angles_con}.
-The angle to each of the constraints,  \( \arccos(r^T R^T v_i) \), is always greater than the specified angle, \( \theta_i \), in~\Cref{tab:constraints}.
+The angle to each of the constraints, which is measured in degrees and given by \( \arccos(r^T R^T v_i) \), is always greater than the specified angle, \( \theta_i \), in~\Cref{tab:constraints}.
 
 \Cref{fig:adapt} shows the results with the addition of the adaptive update law.
+\Cref{fig:Psi_adapt,fig:con_angles} are equivalent to~\cref{fig:Psi_con,fig:con_angles_con} except include the addition of the adaptive update law.
 The addition of the adaptive update law allows the system to converge to the desired attitude in the presence of constraints.
@@
 The control system is able to asymptotically converge to zero attitude error.
-\Cref{fig:con_angles} shows that the angle \( \arccos(r^T R^T v_i) \) between the body fixed sensor and each constraint is satisfied for the entire maneuver.
+\Cref{fig:con_angles} shows that the angle, \( \arccos(r^T R^T v_i) \) and measured in degrees, between the body fixed sensor and each constraint is satisfied for the entire maneuver.
 In addition, the estimate of the disturbance converges to the the true value as shown in~\cref{fig:delta_adapt}.

### 2016-11-29 Response.tex
Add siunitx for excerpt from manuscript
Add some additional detail for figure 5, experimental results

@@
 \usepackage{amsfonts}
+\usepackage{siunitx}
 \usepackage{mathtools}
@@
 \end{correction}
+
+Additional detail has been added for~\cref{fig:exp}:
+\begin{correction}
+    \Cref{fig:eR_exp} shows the behavior of each of the components of the attitude error vector, defined by~\cref{eqn:eR}, over the experiment time span.
+    \Cref{fig:Psi_exp} shows the time history of the attitude error function, defined by~\cref{eqn:psi}.
+    \Cref{fig:u_exp} shows the magnitude of each component of the control input in \si{\newton\meter}, which is computed from~\cref{eqn:adaptive_control}.
+    Finally,~\cref{fig:con_angle_exp} shows the angle between the body-fixed sensor and the obstacle in degrees.
+\end{correction}
 \item \textit{Please check and correct Page 2 Line 60.}

### 2016-11-29 manuscript.tex
Add some additional detail for figure 5, experimental results

@@
 The experimental results are shown in~\Cref{fig:exp}.
+\Cref{fig:eR_exp} shows the behavior of each of the components of the attitude error vector, defined by~\cref{eqn:eR}, over the experiment time span.
+\Cref{fig:Psi_exp} shows the time history of the attitude error function, defined by~\cref{eqn:psi}.
+\Cref{fig:u_exp} shows the magnitude of each component of the control input in \si{\newton\meter}, which is computed from~\cref{eqn:adaptive_control}.
+Finally,~\cref{fig:con_angle_exp} shows the angle between the body-fixed sensor and the obstacle in degrees.
 In order to maneuver the system ``close" to the constrained zone we utilize several intermediary set points on either side of the obstacle.

### 2016-11-29 Response.tex
Correct typo. Reviewer 4 #3
Add additional detail about choice of control parameters

@@
 \item \textit{Please check and correct Page 2 Line 60.}
+
+Thank you for noticing this oversight. 
+The sentence has been corrected as
+\begin{correction}
+    The superposition of these functions allows one to apply standard feedback control schemes for stabilization and tracking.
+\end{correction}
+
 \item \textit{The units of the parameters are missing. These should be added in the manuscript.}
 
-The units of the disturbance have been included:
+The units of the disturbance has been included:
 \begin{correction}
@@
 \end{correction}
+
+There are several parameters used in the controller, namely \( G, k_R, k_\Omega, c, k_\Delta\) and \(\alpha\).
+Each of these parameters are chosen by the designer to modify the closed loop behavior of the system dynamics. 
+As a result, there is great flexibility to modify these parameters to shape the resulting closed loop dynamics. 
+Additional detail is provided in for the numerical simulation:
+\begin{correction}
+    The diagonal matrix \( G \) serves as a weighting matrix for the relative difference between \( R \) and \( R_d \). 
+    Using this term, the control designer can modify the shape of the attractive error function, given in~\cref{eqn:A}, and the resulting behavior of the closed loop system.
+    Similarly, the constant \( \alpha \) is used to modify the shape of the repulsive error function, given in~\cref{eqn:B}.
+    In general, this term is derived from the system design and the nature of the obstacles in the dynamic environment.
+    For example, a system wishing to avoid pointing at a diffuse obstacle, such as incoming debris, may chose an appropriate value of \( \theta \), based on the best available information, and a relatively low \( \alpha \) to ensure additional safety margin near the constraint boundary.
+    Similarly, in an environment with several densely spaced obstacles, such as that presented in~\cref{fig:cad_adapt}, a much larger \( \alpha \) would enable more aggressive manuevers which pass closer to the constraint boundary without violation.
+    This would increase the allowable region of operation in a highly constrained environment.
+    The parameters \( k_R, k_\Omega, c, k_\Delta\) are control parameters used to modify the closed-loop behavior of the system.
+    It is straightforward to chose \( k_R, k_\Omega, k_\Delta\), using a linear analysis, to satisfy desired response criteria, such as settling time or percent overshoot~\cite{nise2007}.
+\end{correction}
+
+In addition, an additional sentence was added to highlight the difference in parameters for the experimental results:
+\begin{correction}
+    The parameters are modified to account for the differences in the hardware model of the hexrotor.
+\end{correction}
+
 \item \textit{What are the design parameters of the proposed method and how the design parameters are selected? These should be included in the manuiscript.}

### 2016-11-29 manuscript.tex
Correct typo. Reviewer 4 #3
Add additional detail about choice of control parameters

@@
 Similarly, a repulsive function is constructed such that the system is directed away from the constraints. 
-The superposition of the these functions allows one to apply standard feedback control schemes for stabilization and tracking.
+The superposition of these functions allows one to apply standard feedback control schemes for stabilization and tracking.
 More specifically, artificial potential functions have previously been applied to the spacecraft attitude control problem in~\cite{lee2011b,mcinnes1994}.
@@
 \end{gather*}
+The diagonal matrix \( G \) serves as a weighting matrix for the relative difference between \( R \) and \( R_d \). 
+Using this term, the control designer can modify the shape of the attractive error function, given in~\cref{eqn:A}, and the resulting behavior of the closed loop system.
+Similarly, the constant \( \alpha \) is used to modify the shape of the repulsive error function, given in~\cref{eqn:B}.
+In general, this term is derived from the system design and the nature of the obstacles in the dynamic environment.
+For example, a system wishing to avoid pointing at a diffuse obstacle, such as incoming debris, may chose an appropriate value of \( \theta \), based on the best available information, and a relatively low \( \alpha \) to ensure additional safety margin near the constraint boundary.
+Similarly, in an environment with several densely spaced obstacles, such as that presented in~\cref{fig:cad_adapt}, a much larger \( \alpha \) would enable more aggressive manuevers which pass closer to the constraint boundary without violation.
+This would increase the allowable region of operation in a highly constrained environment.
+The parameters \( k_R, k_\Omega, c, k_\Delta\) are control parameters used to modify the closed-loop behavior of the system.
+It is straightforward to chose \( k_R, k_\Omega, k_\Delta\), using a linear analysis, to satisfy desired response criteria, such as settling time or percent overshoot~\cite{nise2007}.
 A body fixed sensor is defined as \(r = [1,0,0]\), while multiple inequality constraints are defined in~\Cref{tab:constraints}.
@@
 The attitude control system is identical to the one presented in~\Cref{prop:adaptive_control} with the exception of a gravity moment term and the following parameters: \(k_R = 0.4, k_\Omega = 0.7 ,c = 0.1 , \alpha = 8 \text{ and } k_\Delta = 0.05\).
+The parameters are modified to account for the differences in the hardware model of the hexrotor.
 \begin{figure}[H]

### 2016-11-29 manuscript.tex
Add section labels

@@
 
-\section{Numerical Examples}
+\section{Numerical Examples}\label{sec:numerical_simulation}
 We demonstrate the performance of the proposed control system via numerical simulation.
@@
 % discuss the unwinding phenomenon with quaternions
-\section{Experiment on Hexrotor UAV}
+\section{Experiment on Hexrotor UAV}\label{sec:experiment}
 

### 2016-11-29 Response.tex
remove labels from included manuscript excerpts
Add more detail about the sensor on the hexrotor
Reviewer 4 #6

@@
 The rotation matrix, \( R(\theta_1, \theta_2, \theta_3) \), corresponding to this sequence is 
-\begin{align}\label{eq:euler313}
+\begin{align}
     \begin{bmatrix}
@@
 Using this representation that kinematic differential equations for the associated Euler angles are given as
-\begin{align}\label{eq:euler313_diff}
+\begin{align}
     \begin{bmatrix}
@@
 \item \textit{What are the design parameters of the proposed method and how the design parameters are selected? These should be included in the manuiscript.}
+
+Additional detail has been added to describe the selection of the controller gains and error function parameters. 
+This has been described in the response above.
+
 \item \textit{Specification of the sensors in the experiments should be included in the manuscript.}
+
+Additional detail on the sensors and their operation has been included:
+\begin{correction}
+    Attitude information is measured by a combination of both on and off board sensor systems.
+    The VectorNav VN-100 is a rugged, miniature high-performance inertial measurement unit which provides high frequency angular velocity measurements.
+    A Vicon motion capture system is installed within the test environment and used to provide high accuracy attitude measurements. 
+    A series of reflective markers are placed on the hexrotor and their relative position is captured by a series of infrared optical cameras. 
+    Assuming a fixed rigid body, the Vicon system is able to derive the attitude of the hexrotor and transmit this data to the processor onboard the hexrotor.
+    The control input is computed on-board, using the full state measurement, and implemented at approximately \SI{100}{\hertz}.
+\end{correction}
 \end{enumerate}

### 2016-11-29 manuscript.tex
Add more detail about the sensor on the hexrotor
Reviewer 4 #6

@@
 \end{figure}
-Attitude information is measured by an onboard IMU and a Vicon motion capture system in the test area.
-The control input is computed onboard the hexrotor using data transmitted via WiFi in a client/server model.
+Attitude information is measured by a combination of both on and off board sensor systems.
+The VectorNav VN-100 is a rugged, miniature high-performance inertial measurement unit which provides high frequency angular velocity measurements.
+A Vicon motion capture system is installed within the test environment and used to provide high accuracy attitude measurements. 
+A series of reflective markers are placed on the hexrotor and their relative position is captured by a series of infrared optical cameras. 
+Assuming a fixed rigid body, the Vicon system is able to derive the attitude of the hexrotor and transmit this data to the processor onboard the hexrotor.
+The control input is computed on-board, using the full state measurement, and implemented at approximately \SI{100}{\hertz}.
 In order to constrain the motion, allowing us to test only the attitude dynamics, we attach the hexrotor to a spherical joint.

### 2016-11-30 manuscript.tex
Bigger figures which span both columns

@@
 Similarly, the positions of celestial objects are defined on the celestial sphere in terms of right ascension and declination. 
+\end{multicols}
 \begin{figure}[H]%
     \centering 
-    \subfigure[Attractive \( A(R) \) \label{fig:attract_error}]{\includegraphics[width=0.45\columnwidth]{attract_error} }~
-    \subfigure[Repulsive \( B(R) \) \label{fig:avoid_error} ]{\includegraphics[width=0.45\columnwidth]{avoid_error} }\\%add desired spacing between images, e.
-g.
-~, \quad, \qquad, \hfill etc.
-%(or a blank line to force the subfigure onto a new line)
-    \subfigure[Configuration \( \Psi \) \label{fig:combined_error}]{\includegraphics[width=0.45\columnwidth]{combined_error} }%
-    \caption{Configuration error function visualization}
+    \subfigure[Attractive \( A(R) \) \label{fig:attract_error}]{\includegraphics[width=0.3\columnwidth]{attract_error} }~
+    \subfigure[Repulsive \( B(R) \) \label{fig:avoid_error} ]{\includegraphics[width=0.3\columnwidth]{avoid_error} }~
+    \subfigure[Combined \( \Psi \) \label{fig:combined_error}]{\includegraphics[width=0.3\columnwidth]{combined_error} }%
+    \caption{Visualization of Configuration Error Functions using spherical coordinate representation}
     \label{fig:config_error} 
 \end{figure}%
+\begin{multicols}{2}
 We apply this concept and parametrize the rotation matrix \( R \in \SO \) in terms of the spherical angles \( \SI{-180}{\degree} \leq \lambda \leq \SI{180}{\degree}  \) and \( \SI{-90}{\degree} \leq \beta \leq \SI{90}{\degree} \).
@@
 The desired state is \( R_d = I,\Omega_d = 0\).
-\begin{figure}[H] 
+\end{multicols}
+\begin{figure}
     \centering 
-    \subfigure[Attitude error vector \(e_R\) \label{fig:eR_con}]{\includegraphics[width=0.5\columnwidth]{eR_con}  }~
-    \subfigure[Configuration error \( \Psi \) \label{fig:Psi_con}]{\includegraphics[width=0.5\columnwidth]{figures/Psi_con.pdf} }
-    \subfigure[Angle to constraints \label{fig:con_angles_con}]{\includegraphics[width=0.5\columnwidth]{figures/constraint_angles_con.pdf} }  
+    \subfigure[Attitude error vector \(e_R\) components \label{fig:eR_con}]{\includegraphics[width=0.3\columnwidth]{eR_con}  }~
+    \subfigure[Configuration error \( \Psi \) \label{fig:Psi_con}]{\includegraphics[width=0.3\columnwidth]{figures/Psi_con.pdf} }
+    \subfigure[Angle to each constraint \label{fig:con_angles_con}]{\includegraphics[width=0.3\columnwidth]{figures/constraint_angles_con.pdf} } 
     \caption{Attitude stabilization without adaptive update law}
@@
 \end{figure}
+\begin{multicols}{2}
 We show simulation results for the system stabilizing about the desired attitude with and without the adaptive update law from~\Cref{prop:adaptive_control}.
@@
 The first term of~\cref{eqn:delta_dot} has the effect of increasing the proportional gain of the control system, since the time derivative of the attitude error vector, \( \dot{e}_{R} \), is linear with respect to the angular velocity error vector \( e_\Omega\).
-\begin{figure}[H] 
+\end{multicols}
+\begin{figure} 
 	\centering 
-    \subfigure[Configuration error \( \Psi \)\label{fig:Psi_adapt}]{\includegraphics[width=0.5\columnwidth]{Psi_adapt} }~
-    \subfigure[Angle to constraints \label{fig:con_angles}]{\includegraphics[width=0.5\columnwidth]{constraint_angles} }\\
-    \subfigure[Disturbance estimate \( \bar \Delta \)  \label{fig:delta_adapt} ]{\includegraphics[width=0.5\columnwidth]{Delta_adapt}}~
-    \subfigure[Attitude trajectory \label{fig:cad_adapt}]{\includegraphics[trim=9cm 2.5cm 0 0,clip,width=0.645\columnwidth]{cad_adapt} }
+    \subfigure[Configuration error \( \Psi \)\label{fig:Psi_adapt}]{\includegraphics[width=0.4\columnwidth]{Psi_adapt} }~
+    \subfigure[Angle to each constraint \label{fig:con_angles}]{\includegraphics[width=0.4\columnwidth]{constraint_angles} }\\
+    \subfigure[Disturbance estimate \( \bar \Delta \) components \label{fig:delta_adapt} ]{\includegraphics[width=0.4\columnwidth]{Delta_adapt}}~
+    \subfigure[Attitude trajectory \label{fig:cad_adapt}]{\includegraphics[trim={10cm 0 10cm 0},clip,width=0.4\columnwidth]{cad_adapt} }
 	\caption{Attitude stabilization with adaptive update law}
@@
 \end{figure}
-
+\begin{multicols}{2}
 Simulation results without the adaptive update law are shown in~\cref{fig:con}.
@@
 The parameters are modified to account for the differences in the hardware model of the hexrotor.
-\begin{figure}[H]
+\end{multicols}
+\begin{figure}
 	\centering 
-    \subfigure[{Attitude error vector \(e_R\)} \label{fig:eR_exp}]{\includegraphics[width=0.5\columnwidth]{eR_exp}  }~
-	\subfigure[{Configuration error \( \Psi \)} \label{fig:Psi_exp} ]{\includegraphics[width=0.5\columnwidth]{Psi_exp} }\\
-	\subfigure[{Control input \( u\) }\label{fig:u_exp}]{\includegraphics[width=0.5\columnwidth]{u_exp}  }~
-	\subfigure[{Attitude Trajectory } \label{fig:traj_exp}]{\includegraphics[width=0.5\columnwidth]{traj_exp} }\\
-    \subfigure[{Angle to constraint } \label{fig:con_angle_exp}]{\includegraphics[width=0.5\columnwidth]{figures/constraint_angles_exp.pdf} }
+    \subfigure[{Attitude error vector \(e_R\)} components\label{fig:eR_exp}]{\includegraphics[width=0.3\columnwidth]{eR_exp}  }~
+	\subfigure[{Configuration error \( \Psi \)} \label{fig:Psi_exp} ]{\includegraphics[width=0.3\columnwidth]{Psi_exp} }~
+	\subfigure[{Control input \( u\) } components\label{fig:u_exp}]{\includegraphics[width=0.3\columnwidth]{u_exp}  }\\
+	\subfigure[{Attitude Trajectory } \label{fig:traj_exp}]{\includegraphics[width=0.3\columnwidth]{traj_exp} }~
+    \subfigure[{Angle to constraint } \label{fig:con_angle_exp}]{\includegraphics[width=0.3\columnwidth]{figures/constraint_angles_exp.pdf} }
 	\caption{Constrained Attitude stabilization experiment}
@@
 \end{figure}
+\begin{multicols}{2}
 The experimental results are shown in~\Cref{fig:exp}.

### 2016-11-30 Response.tex
Bigger figures which span both columns
Draft response for reveriwer 1 #3

@@
 
-Run another simulation showing that for a restricted class of time-varying error functions, the system is stable
+We're focused on the stationary obstacle in this manuscript. 
+We are considering the addition of a time-varying obstacle in a future research
 
@@
 \item \textit{The only question is that all the figures in this paper are too small and are not legible. The meanings of different lines in one figure should be explained in the title content.}
+
+All of the figures have been enlarged and modified to span the entire page rather than a single column. 
+In addition, the captions of~\cref{fig:config_error,fig:adapt,fig:con} have been modified to mention the fact that they are plotting the components of a vector in a single plot or using a subplot.
 \end{enumerate}

### 2016-11-30 Response.tex
Address reviewer 3 #2, stability proof and domain D

@@
 Since these properties are used to derive the bound H which is used to derive the result in Proposition 5, the stability proof under the proposed controller is far from complete.}
+
+Lyapunov stability is valid if the given properties of \( V \) are satisfied in an open neighborhood of the desired attitude configuration. 
+The details in~\cref{proof:att_control,proof:eR_dot_bound} are valid in the selected domain \( D \) about the desired attitude.
+Therefore, Lyapunov stability is valid if \( D \) is also an open neighborhood of the desired attitude.
+
+The set \( D = \braces{R \in \SO \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta} \) of the metric space \( \parenth{R \in \SO, \Psi(R,R_d)} \) is an open neighborhood of \( R_d \) if there exists a \( \epsilon > 0 \) such that for any \( R \in \SO | \Psi(R,R_d) < \epsilon \), it is also true that \( R \in D \).
+The selected domain \( D \) excludes the undesired equilibrium points of \( A(R) \) and the infeasible regions defined by the constraints \( r^T R^T v_i \), i.e.
+the desired attitude should be sufficiently far away from the constraints.
+We can ensure that \( D \) is an open neighborhood of \( R_d \) by choosing \( \epsilon = \min \braces{\psi, \Psi(R|r^T R^T v = \beta,R_d)}\).
+
+{\Large Add an excerpt of a similar discussion in the manuscript}
+
 \item \textit{Typo in eq. (40).}

### 2016-12-05 Response.tex
Reviewer 2 #2 response
Address not looking at J uncertainty

@@
 \item \textit{If the inertia matrix is unknown, how to modify the suggested control system guaranteeing the asymptotic stability?}
-Even with an uncertainty in the inertia matrix, one could redefine the system and treat this as an unknonw external disturbance instead.
 
-Show the algebra that allows for either a multiplicative or additive uncertainty in the inertia matrix as equivalent to an external torque
+In this work, we are focused on the design of attitude controllers in the presence of state constraints. 
+The addition of an adaptive update law allows the system to stabilize in the presence of unknown external disturbances.
+We are not considering the case of an unknown inertia matrix, but rather assume that there exists accurate knowledge of the rigid body. 
+This assumption is relatively simple to satisfy as any physical control system will first have an accurate model of the system itself.
+For example, the mass and inertia properties of all spacecraft are accurately measured and verified prior to launch.
+
+In addition, the uncertainty model presented in the paper is commonly used in the adaptive control literature.
+Also, it is possible to represent a uncertain or varying inertia matrix as an external disturbance torque. 
+For example, Euler's law gives the relationship for the rate of change of angular momentum
+\begin{align*}
+    M_{ext} = \dot{\vecbf{H}} = \dot{J} \vecbf{\Omega} + J \dot{\vecbf{\Omega}} .
+\end{align*}
+Using this, we can see that an instantaneous change in \( J \) is proportional to an external moment. 
+In this manner, it is possible to represent a wide array of possible forms of system uncertainty.
 

### 2016-12-05 Response.tex
Reviewer 2 #3 response
Address issue of time-varying constraints and why we're not looking at them in
this paper

@@
 
-We're focused on the stationary obstacle in this manuscript. 
-We are considering the addition of a time-varying obstacle in a future research
+In this work, we are specifically concerned with presenting a geometric attitude controller on \( \SO \) in the presence of state inequality constraints.
+More specifically, we are assuming that these constraints are time-invariant rather than time dependent. 
+This type of constraint is representative of the attitude constraints that are frequently experienced in the attitude control of spacecraft. 
+For example, various keep-out zones for sensitive electro-optical sensors are well represented as a fixed constraint in the inertial frame. 
+In addition, the time scale of the attitude dynamics, and therefore any attitude control maneuver, is much shorter than the time scale of the translational dynamics.
+In other words, a time-dependent constraint in the inertial frame will evolve at a much slower rate as compared to the attitude dynamics. 
+As a result, it is possible to model the time-varying constraints as a series of time-invariant constraints in the inertial frame. 
+In this situation, the presented approach allows for a straightforward method to design an attitude stabilization control law. 
+However, this is a very applicable suggestion and it is an area of current research efforts.
 

### 2016-12-05 Response.tex
Reviewer 3 #2 response
Add more detail about the open neighborhood properties of the domain D

@@
 Lyapunov stability is valid if the given properties of \( V \) are satisfied in an open neighborhood of the desired attitude configuration. 
-The details in~\cref{proof:att_control,proof:eR_dot_bound} are valid in the selected domain \( D \) about the desired attitude.
+The presented details, which are shown in~\cref{proof:att_control,proof:eR_dot_bound}, are valid in the selected domain \( D \) about the desired attitude.
 Therefore, Lyapunov stability is valid if \( D \) is also an open neighborhood of the desired attitude.
 
-The set \( D = \braces{R \in \SO \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta} \) of the metric space \( \parenth{R \in \SO, \Psi(R,R_d)} \) is an open neighborhood of \( R_d \) if there exists a \( \epsilon > 0 \) such that for any \( R \in \SO | \Psi(R,R_d) < \epsilon \), it is also true that \( R \in D \).
+The set \( D = \braces{R \in \SO \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta} \) of the metric space \( \parenth{R \in \SO, \Psi(R,R_d)} \) is an open neighborhood of \( R_d \) if there exists an \( \epsilon > 0 \) such that for any \( R \in \SO | \Psi(R,R_d) < \epsilon \), it is also true that \( R \in D \).
 The selected domain \( D \) excludes the undesired equilibrium points of \( A(R) \) and the infeasible regions defined by the constraints \( r^T R^T v_i \), i.e.
@@
 We can ensure that \( D \) is an open neighborhood of \( R_d \) by choosing \( \epsilon = \min \braces{\psi, \Psi(R|r^T R^T v = \beta,R_d)}\).
+Therefore, the given domain \( D \) is an open neighborhood of the desired attitude configuration, \(R_d\), and the Lyapunov stability results are valid in this domain.
 
-{\Large Add an excerpt of a similar discussion in the manuscript}
+The domain \( D \) is chosen to both exclude the undesired critical points of \( A(R)\) as well as the infeasible regions defined by the constraints. 
+In general, this is not a difficult assumption to satisfy as the desired attitude will typically be located far from the constrained regions.
+We have augmented the manuscript with some additional discussion of the chosen domain \( D \) in~\Cref{proof:eR_dot_bound}.
 
+\begin{correction}
+    We choose the domain \( D \) to exclude the undesired critical points of \( A(R) \) as well as the infeasible regions defined by the state inequality constraints. 
+    Furthermore, we can show that the set \( D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
+\end{correction}
 \item \textit{Typo in eq. (40).}

### 2016-12-05 manuscript.tex
Reviewer 3 #2 response
Add more detail about the open neighborhood properties of the domain D

@@
 %	However, since the chosen domain is assumed to exclude the constraint this situation is not possible and \( B < \psi \).
-The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
+We choose the domain \( D \) to exclude the undesired critical points of \( A(R) \) as well as the infeasible regions defined by the state inequality constraints. 
+Furthermore, we can show that the set \( D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
+Therefore, the selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
 This implies that that both \( A(R) \) and \( B(R) \) are bounded by constants \( c_A c_B < \psi < h_1\).

### 2016-12-05 Response.tex
Reviewer 3 #3 response
More detail on why we're using a slight abuse of notation

@@
 In this case, the \textit{hat} operator is equivalently represented as \( \hat{x} = \parenth{x}^\wedge \).
-This dual representation eases the resulting typesetting for particularly long terms, such as those used in Equations~\((6) - (8)\).
+This representation enables a consistent notation for both short/simple terms, such as \( \hat{x} \) and more complicated terms such as \(\parenth{\hat{e}_\Omega R^T R_d G + (R^T R_d G)^T \hat{e}_\Omega}^\vee\).
+Finally, this dual usage of the notation drastically improves the quality of the resulting typography.
 

### 2016-12-05 manuscript.tex
Try to get author bios onto the last page
Move figure in paper

@@
-\documentclass[fleqn]{IJCAS}  % Comment this line out if you need a4paper
+\documentclass[10pt,fleqn]{IJCAS}  % Comment this line out if you need a4paper
 \usepackage{ijcas_packages}
@@
 The first term of~\cref{eqn:delta_dot} has the effect of increasing the proportional gain of the control system, since the time derivative of the attitude error vector, \( \dot{e}_{R} \), is linear with respect to the angular velocity error vector \( e_\Omega\).
-\end{multicols}
-\begin{figure} 
-	\centering 
-    \subfigure[Configuration error \( \Psi \)\label{fig:Psi_adapt}]{\includegraphics[width=0.4\columnwidth]{Psi_adapt} }~
-    \subfigure[Angle to each constraint \label{fig:con_angles}]{\includegraphics[width=0.4\columnwidth]{constraint_angles} }\\
-    \subfigure[Disturbance estimate \( \bar \Delta \) components \label{fig:delta_adapt} ]{\includegraphics[width=0.4\columnwidth]{Delta_adapt}}~
-    \subfigure[Attitude trajectory \label{fig:cad_adapt}]{\includegraphics[trim={10cm 0 10cm 0},clip,width=0.4\columnwidth]{cad_adapt} }
-	\caption{Attitude stabilization with adaptive update law}
-	\label{fig:adapt} 
-\end{figure}
-\begin{multicols}{2}
+
 Simulation results without the adaptive update law are shown in~\cref{fig:con}.
@@
 These singularities can cause significant difficulties during control design and hardware implementation.
-
+\end{multicols}
+\begin{figure} 
+  \centering 
+    \subfigure[Configuration error \( \Psi \)\label{fig:Psi_adapt}]{\includegraphics[width=0.4\columnwidth]{Psi_adapt} }~
+    \subfigure[Angle to each constraint \label{fig:con_angles}]{\includegraphics[width=0.4\columnwidth]{constraint_angles} }\\
+    \subfigure[Disturbance estimate \( \bar \Delta \) components \label{fig:delta_adapt} ]{\includegraphics[width=0.4\columnwidth]{Delta_adapt}}~
+    \subfigure[Attitude trajectory \label{fig:cad_adapt}]{\includegraphics[trim={10cm 0 10cm 0},clip,width=0.4\columnwidth]{cad_adapt} }
+  \caption{Attitude stabilization with adaptive update law}
+  \label{fig:adapt} 
+\end{figure}
+\begin{multicols}{2}
 To demonstrate the effect of the kinematic singularities inherent with Euler angles we will represent the attitude of the body fixed reference frame, \( \vecbf{b}_i \), with respect to the inertial frame, \( \vecbf{e}_i\), in terms of the \( 3-1-3\) Euler angle sequence.
@@
 
-%\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
-                                  % on the last page of the document manually. It shortens
-                                  % the textheight of the last page by a suitable amount.
-                                  % This command does not take effect until the next page
-                                  % so it should come on the page before the last. Make
-                                  % sure that you do not shorten the textheight too much.
-
 \bibliography{BibMaster,library}
@@
     }
-
 \biography{Lee}{Taeyoung Lee}
@@
 \clearafterbiography\relax
-\clearafterbiography\relax
+
 \end{multicols}

### 2016-12-05 manuscript.tex
Add a subsection for the discussion about euler angles
Add time varying disturbance simulation

@@
 
+\subsection{Attitude Parameterizations}
 % Discuss the benefits of using this geometric representation as compared to Euler angles or quaternions
@@
 As a result, Euler angles are not appropriate for systems which experience large angular rotations, such as those demonstrated in~\cref{fig:adapt}, or control systems which rely on the angular velocities \( \theta_i \).
+% discuss the unwinding phenomenon with quaternions
 
-% discuss the unwinding phenomenon with quaternions
+\subsection{Time-varying Disturbance}\label{ssec:time_varying}
+
+The form of the uncertainty, given in~\cref{eqn:Wdot}, is commonly used in the adaptive control literature~\cite{lee2013b,ioannou2012}. 
+A wide variety of realistic disturbances, such as gravitational gradients or malfunctioning thrusters, are accurately represented via this model. 
+In addition, it is possible to represent the uncertainty of a time-varying inertia matrix as an equivalent external disturbance. 
+For example, Euler's law gives the relationship for the rate of change of angular momentum
+\begin{align*}
+    M_{ext} = \dot{\vecbf{H}} = \dot{J} \vecbf{\Omega} + J \dot{\vecbf{\Omega}} .
+\end{align*}
+Using this, we can see that an instantaneous change in \( J \) is proportional to an external moment.
+Finally, it has been shown that this adaptive control formulation is able to handle time-varying disturbances under some mild assumptions~\cite{ioannou2012}.
+
+We demonstrate the ability to handle an uncertain time-varying disturbance via numerical example.
+The system is identical to the one presented in~\Cref{sec:numerical_simulation}, however we modify the external disturbance. 
+We model the external disturbance as the superposition of constant and time-varying terms as
+\begin{align*}
+    \Delta = \begin{bmatrix} 0.2 \\ 0.2 \\0.2 \end{bmatrix} + 0.02 \begin{bmatrix} \sin 9 t \\ \cos 9 t \\ \frac{1}{2} \parenth{\sin 9t + \cos 9t}\end{bmatrix} \si{\newton\meter}.
+\end{align*}
+We define a constraint in the inertial frame as \( v = [\frac{1}{\sqrt{2}}, \frac{1}{\sqrt{2}}, 0]^T \) with \( \theta = \ang{12} \).
+The initial state is defined as \(R(0) = \exp( \frac{\pi}{2} \hat{e}_3) \), while the desired state is \(R_d =I \).
+The goal is to rotate the vehicle about the \( e_3 \) axis while avoiding the obstacle and compensating for the time-varying disturbance.
+
+\Cref{fig:tv} demonstrates the ability for the adaptive controller, presented in~\cref{prop:adaptive_control}, to handle time-varying disturbances.
+We can see in~\cref{fig:Delta_tv} that that estimate \(\bar \Delta \) accurately tracks the true disturbance after approximately~\SI{5}{\second}.
+In addition,~\cref{fig:con_angle_tv} shows that the constraint is never verified as the angle between the body-fixed sensor \( r \) and the constraint \( v \) is greater than \SI{12}{\degree} over the entire attitude maneuver.
+\end{multicols}
+\begin{figure}[H]
+    \centering 
+    \subfigure[{Configuration error \( \Psi \)} \label{fig:Psi_tv} ]{\includegraphics[width=0.3\columnwidth]{Psi_tv} }~
+    \subfigure[{Angle to constraint } \label{fig:con_angle_tv}]{\includegraphics[width=0.3\columnwidth]{figures/constraint_angle_tv.pdf} }~
+    \subfigure[{Disturbance estimate \(\bar\Delta\) components} \label{fig:Delta_tv}]{\includegraphics[width=0.3\columnwidth]{figures/delta_tv} }
+    \caption{Time-varying external disturbance simulation}
+    \label{fig:tv} 
+\end{figure}
+\begin{multicols}{2}
 \section{Experiment on Hexrotor UAV}\label{sec:experiment}

### 2016-12-05 manuscript.tex
Update keywords
Fix some typos and rearrange to look better

@@
 \begin{keywords}
-attitude control, asymptotic stability, special orthogonal group, constraint
+adaptive control, attitude control, constraint, obstacle, special orthogonal group
 %At least four key words or phrases in alphabetical order, separated by commas.
@@
 Barrier functions are typically used in optimal control and motion planning applications.
-A visualization of the configuration error function is presented in~\cref{fig:avoid_error} which shows that as the boundary of the constraint is neared, or \( r^T R^T v \to \cos \theta \), the barrier term increases, \( B \to \infty\).
+A visualization of the repulsive error function is presented in~\cref{fig:avoid_error} which shows that as the boundary of the constraint is neared, or \( r^T R^T v \to \cos \theta \), the barrier term increases, \( B \to \infty\).
 We use the scale factor~\(\frac{1}{1+\cos \theta} \) to ensure that \( \Psi \) remains positive definite.
@@
 The parameters \( k_R, k_\Omega, c, k_\Delta\) are control parameters used to modify the closed-loop behavior of the system.
-It is straightforward to chose \( k_R, k_\Omega, k_\Delta\), using a linear analysis, to satisfy desired response criteria, such as settling time or percent overshoot~\cite{nise2007}.
+It is straightforward to chose \( k_R, k_\Omega, k_\Delta\), using a linear analysis, to satisfy desired response criteria, such as settling time or percent overshoot~\cite{nise2004}.
 A body fixed sensor is defined as \(r = [1,0,0]\), while multiple inequality constraints are defined in~\Cref{tab:constraints}.
@@
 \Cref{fig:adapt} shows the results with the addition of the adaptive update law.
-\Cref{fig:Psi_adapt,fig:con_angles} are equivalent to~\cref{fig:Psi_con,fig:con_angles_con} except include the addition of the adaptive update law.
+\Cref{fig:Psi_adapt,fig:con_angles} are equivalent to~\cref{fig:Psi_con,fig:con_angles_con} with the exception of the addition of the adaptive update law.
 The addition of the adaptive update law allows the system to converge to the desired attitude in the presence of constraints.
-The path of the body fixed sensor in the inertial frame, namely \( R r \), is illustrated in~\cref{fig:cad_adapt}.
-The initial attitude is represented with the green circle while the final attitude is marked with a green \(\times\).
+The path of the body fixed sensor in the inertial frame, namely \( R r \), is illustrated in~\cref{fig:cad_adapt} by the blue trajectory.
+The rendering of the spacecraft is presented in the desired, or final, orientation of the simulation.
 The inequality constraints from~\Cref{tab:constraints} are depicted as red cones, where the cone half angle is \( \theta \).
@@
 % Discuss the benefits of using this geometric representation as compared to Euler angles or quaternions
-Attitude parameterizations, such as Euler angles and Quaternions, are frequently used in the aerospace and astrodynamics communities~\cite{vallado2001,bate1971,wertz1978}.
-For example, Euler angle sequences are frequently used to describe the transformation between a variety of reference frames used to describe the position and orientation of the orbit of Earth satellites~\cite{vallado2001}.
+Attitude parameterizations, such as Euler angles and Quaternions, are frequently used in the aerospace and astrodynamics communities~\cite{vallado2007}.
+For example, Euler angle sequences are frequently used to describe the transformation between a variety of reference frames used to describe the position and orientation of the orbit of Earth satellites~\cite{vallado2007}.
 In addition, quaternions were used during the operation of Skylab and the NASA Space Shuttle~\cite{hughes2004}.
@@
 Euler angle sequences are a minimum, three-parameter set of angles which describe the transformation between two reference frames.
-Euler angles represent any general rotation as a sequence of three intermediate rotations.
+Using Euler angles, we can represent any general rotation as a sequence of three intermediate rotations~\cite{shuster1993}.
 By convention, there are \num{24} possible Euler angle sequences for any given rotation.
@@
 \end{align}
-From~\cref{eq:euler313_diff}, it is immediately clear that a singularity exists when \( \sin \theta_2 = 0 \) or \( \theta_2 = 0, \pm \pi \). 
+From~\cref{eq:euler313_diff}, it is immediately clear that a singularity exists when \( \sin \theta_2 = 0 \) or equivalently, \( \theta_2 = 0, \pm \pi \). 
 In the vicinity of the singularity, the angular velocities of the Euler angles will tend to approach \( \pm \infty \) and the angular velocities will experience instantaneous sign changes.
-Furthermore, all Euler angle sequences will exhibit a similar singularity at either \( \theta_2 = 0, \pm \pi \) or \( \theta_2 = \pm \frac{\pi}{2}, \pm \frac{3\pi}{2} \) and switching the sequence does not alleviate the issue.
+Furthermore, all Euler angle sequences will exhibit a similar singularity at either \( \theta_2 = 0, \pm \pi \) or \( \theta_2 = \pm \frac{\pi}{2}, \pm \frac{3\pi}{2} \).
+Therefore simply switching the sequence does not alleviate the issue, but rather only moves the singularity.
 As a result, Euler angles are not appropriate for systems which experience large angular rotations, such as those demonstrated in~\cref{fig:adapt}, or control systems which rely on the angular velocities \( \theta_i \).
@@
 The system is identical to the one presented in~\Cref{sec:numerical_simulation}, however we modify the external disturbance. 
-We model the external disturbance as the superposition of constant and time-varying terms as
+The external disturbance is the superposition of constant and time-varying terms as
 \begin{align*}
@@
 
-\Cref{fig:tv} demonstrates the ability for the adaptive controller, presented in~\cref{prop:adaptive_control}, to handle time-varying disturbances.
-We can see in~\cref{fig:Delta_tv} that that estimate \(\bar \Delta \) accurately tracks the true disturbance after approximately~\SI{5}{\second}.
-In addition,~\cref{fig:con_angle_tv} shows that the constraint is never verified as the angle between the body-fixed sensor \( r \) and the constraint \( v \) is greater than \SI{12}{\degree} over the entire attitude maneuver.
+\Cref{fig:tv} demonstrates the ability for the adaptive controller, which is presented in~\Cref{prop:adaptive_control}, to handle time-varying disturbances.
+\Cref{fig:Psi_tv} shows the non-dimensional value of the configuration error function and demonstrates that the adaptive controller is able to stabilize the system to the desired attitude configuration.
+In addition,~\cref{fig:con_angle_tv} shows that the constraint is never violated as the angle between the body-fixed sensor \( r \) and the constraint \( v \) is greater than \SI{12}{\degree} over the entire attitude maneuver.
+We can see in~\cref{fig:Delta_tv} that that estimate \(\bar \Delta \) for each of the components, accurately tracks the true disturbance after approximately~\SI{5}{\second}.
 \end{multicols}
@@
 \section{Experiment on Hexrotor UAV}\label{sec:experiment}
-
+\begin{figure}[H]
+    \centering
+    \includegraphics[width = 0.75\columnwidth]{hexrotor}
+    \caption{Attitude control testbed~\label{fig:hexrotor}}
+\end{figure}
 A hexrotor unmanned aerial vehicle (UAV), as seen in~\cref{fig:hexrotor}, has been developed at the Flight Dynamics and Controls Laboratory (FDCL) at the George Washington University~\cite{kaufman2014}.
@@
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width = 0.75\columnwidth]{hexrotor}
-    \caption{Attitude control testbed~\label{fig:hexrotor}}
-\end{figure}
 Attitude information is measured by a combination of both on and off board sensor systems.
@@
 The parameters are modified to account for the differences in the hardware model of the hexrotor.
+
+The experimental results are shown in~\Cref{fig:exp}.
+\Cref{fig:eR_exp} shows the behavior of each of the components of the attitude error vector, defined by~\cref{eqn:eR}, over the experiment time span.
+\Cref{fig:Psi_exp} shows the time history of the attitude error function, defined by~\cref{eqn:psi}.
+\Cref{fig:u_exp} shows the magnitude of each component of the control input in \si{\newton\meter}, which is computed from~\cref{eqn:adaptive_control}.
+Finally,~\cref{fig:con_angle_exp} shows the angle between the body-fixed sensor and the obstacle in degrees.
+In order to maneuver the system ``close" to the constrained zone we utilize several intermediary set points on either side of the obstacle.
+From the initial attitude the hexrotor rotates to the first set point, pauses, and then continues around the obstacle to the second set point before continuing toward the desired attitude.
+As a result this creates the stepped behavior of the configuration error history as shown in~\cref{fig:Psi_exp}.
+
 \end{multicols}
-\begin{figure}
+\begin{figure}[H]
     \centering 
@@
 \begin{multicols}{2}
-The experimental results are shown in~\Cref{fig:exp}.
-\Cref{fig:eR_exp} shows the behavior of each of the components of the attitude error vector, defined by~\cref{eqn:eR}, over the experiment time span.
-\Cref{fig:Psi_exp} shows the time history of the attitude error function, defined by~\cref{eqn:psi}.
-\Cref{fig:u_exp} shows the magnitude of each component of the control input in \si{\newton\meter}, which is computed from~\cref{eqn:adaptive_control}.
-Finally,~\cref{fig:con_angle_exp} shows the angle between the body-fixed sensor and the obstacle in degrees.
-In order to maneuver the system ``close" to the constrained zone we utilize several intermediary set points on either side of the obstacle.
-From the initial attitude the hexrotor rotates to the first set point, pauses, and then continues around the obstacle to the second set point before continuing toward the desired attitude.
-As a result this creates the stepped behavior of the configuration error history as shown in~\cref{fig:Psi_exp}.
-
 The hexrotor avoids the constrained region illustrated by the circular cone in~\cref{fig:traj_exp}, by rotating around the boundary of the constraint. 
@@
 This further validates that the proposed control system exhibits the desired performance in the experimental setting as well. 
-A video clip showing the attitude maneuver is available \url{https://youtu.be/dsmAbwQram4}.
+A video clip is available at \url{https://youtu.be/dsmAbwQram4}.
 
@@
 \end{align*}
-Using this the variation of~\cref{eqn:A} is taken with respect to \( R \) as
+Using this, the variation of~\cref{eqn:A} is taken with respect to \( R \) as
 \begin{align*}
@@
 \bibliographystyle{IEEEtran}
-
 \biography{profile}{Shankar Kulumani}
     {is a PhD Candidate in the Department of Mechanical and Aerospace Engineering at George Washington University. 
-    He received his bachelor's degree in Astronautical Engineering from the United States Air Force Academy in 2009 and his master's in Aeronautical and Astronautical Engineering from Purdue University in 2013.
+    He received his bachelor's degree in Astronautical Engineering from the United States Air Force Academy in 2009 and his master's degree in Aeronautical and Astronautical Engineering from Purdue University in 2013.
     % He previously served as Deputy Space Vehicles Lead for the ORS-1 (Operationally Responsive Space ) satellite program, and as Lead Test Engineer in the Guidance, Navigation, and Control group at Air Force Research Laboratory located at Kirtland AFB, NM.
@@
 \clearafterbiography\relax
+\clearafterbiography\relax
 

### 2016-12-05 manuscript.tex
Fix some typos in the manuscript

@@
 
-\subsection{Attitude Parameterizations}
+\subsection{Attitude Parameterizations}\label{ssec:attitude_parameterization}
 % Discuss the benefits of using this geometric representation as compared to Euler angles or quaternions
@@
 In addition,~\cref{fig:con_angle_tv} shows that the constraint is never violated as the angle between the body-fixed sensor \( r \) and the constraint \( v \) is greater than \SI{12}{\degree} over the entire attitude maneuver.
-We can see in~\cref{fig:Delta_tv} that that estimate \(\bar \Delta \) for each of the components, accurately tracks the true disturbance after approximately~\SI{5}{\second}.
+We can see in~\cref{fig:Delta_tv} that that estimate \(\bar \Delta \) for each of the components accurately tracks the true disturbance after approximately~\SI{5}{\second}.
 \end{multicols}
@@
 We choose the domain \( D \) to exclude the undesired critical points of \( A(R) \) as well as the infeasible regions defined by the state inequality constraints. 
-Furthermore, we can show that the set \( D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
+Furthermore, one can show that the set \( D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
 Therefore, the selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).

### 2016-12-05 Response.tex
Add time varying disturbance simulation
Add the latest version from the paper and some new packages for the subfigures

@@
 \usepackage[letterpaper,margin=1in,centering]{geometry}
+\usepackage{graphicx}
+\usepackage{subfigure}
 \usepackage{amssymb}  
@@
 \usepackage{xr}
+\externaldocument{manuscript}
 \usepackage{hyperref}
@@
 
-\externaldocument{manuscript}
 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-I would like to thank the reviewers for their thoughtful comments, which are aimed
-towards improving the quality of the paper and the clarity of the results.
+I would like to thank the reviewers for their thoughtful comments, which are aimed towards improving the quality of the paper and the clarity of the results. 
 In accordance with the comments and suggestions, the paper has been revised, and the answers to all comments are addressed as follows.
@@
 
-It is true that in general, the external disturbances on a system will be time varying.
+It is true that typically, the external disturbances on a system will be time varying.
 However, the form of uncertainty shown in \( (1) \) is commonly used in the adaptive control literature~\cite{lee2013b,ioannou2012}.
 As a result, we use this same form of uncertainty, namely that the uncertain disturbance is additive in nature and enters through the input channel.
-In addition, a wide variety of disturbances is accurately represented by this formulation in the aerospace engineering field and several examples are given in the article.
+In addition, a wide variety of disturbances in the aerospace engineering field are accurately represented by this formulation and several examples are given in the article.
 Furthermore, it has been shown in~\cite{ioannou2012} that this form of adaptive control is able to handle time-varying uncertainties in which the uncertain term is varying sufficiently slowly as compared to the controlled dynamics.
+We have improved the manuscript with an additional numerical experiment in Section~\ref{ssec:time_varying} demonstrating the ability of the adaptive controller to handle time-varying disturbances.
+The additional content is duplicated here:
+\begin{correction}
+    The form of the uncertainty, given in~\cref{eqn:Wdot}, is commonly used in the adaptive control literature~\cite{lee2013b,ioannou2012}. 
+    A wide variety of realistic disturbances, such as gravitational gradients or malfunctioning thrusters, are accurately represented via this model. 
+    In addition, it is possible to represent the uncertainty of a time-varying inertia matrix as an equivalent external disturbance. 
+    For example, Euler's law gives the relationship for the rate of change of angular momentum
+    \begin{align*}
+        M_{ext} = \dot{\vecbf{H}} = \dot{J} \vecbf{\Omega} + J \dot{\vecbf{\Omega}} .
+    \end{align*}
+    Using this, we can see that an instantaneous change in \( J \) is proportional to an external moment.
+    Finally, it has been shown that this adaptive control formulation is able to handle time-varying disturbances under some mild assumptions~\cite{ioannou2012}.
 
-How slowly do the uncertainties have to behave for the simulation?
+    We demonstrate the ability to handle an uncertain time-varying disturbance via numerical example.
+    The system is identical to the one presented in~\Cref{sec:numerical_simulation}, however we modify the external disturbance. 
+    The external disturbance is the superposition of constant and time-varying terms as
+    \begin{align*}
+        \Delta = \begin{bmatrix} 0.2 \\ 0.2 \\0.2 \end{bmatrix} + 0.02 \begin{bmatrix} \sin 9 t \\ \cos 9 t \\ \frac{1}{2} \parenth{\sin 9t + \cos 9t}\end{bmatrix} \si{\newton\meter}.
+    \end{align*}
+    We define a constraint in the inertial frame as \( v = [\frac{1}{\sqrt{2}}, \frac{1}{\sqrt{2}}, 0]^T \) with \( \theta = \ang{12} \).
+    The initial state is defined as \(R(0) = \exp( \frac{\pi}{2} \hat{e}_3) \), while the desired state is \(R_d =I \).
+    The goal is to rotate the vehicle about the \( e_3 \) axis while avoiding the obstacle and compensating for the time-varying disturbance.
 
+    \Cref{fig:tv} demonstrates the ability for the adaptive controller, which is presented in Proposition~\ref{prop:adaptive_control}, to handle time-varying disturbances.
+    \Cref{fig:Psi_tv} shows the non-dimensional value of the configuration error function and demonstrates that the adaptive controller is able to stabilize the system to the desired attitude configuration.
+    In addition,~\cref{fig:con_angle_tv} shows that the constraint is never violated as the angle between the body-fixed sensor \( r \) and the constraint \( v \) is greater than \SI{12}{\degree} over the entire attitude maneuver.
+    We can see in~\cref{fig:Delta_tv} that that estimate \(\bar \Delta \) for each of the components, accurately tracks the true disturbance after approximately~\SI{5}{\second}.
+
+    \begin{figure}
+        \centering 
+        \subfigure[{Configuration error \( \Psi \)}  ]{\includegraphics[width=0.3\columnwidth]{figures/Psi_tv} }~
+        \subfigure[{Angle to constraint } ]{\includegraphics[width=0.3\columnwidth]{figures/constraint_angle_tv.pdf} }~
+        \subfigure[{Disturbance estimate \(\bar\Delta\) components} ]{\includegraphics[width=0.3\columnwidth]{figures/delta_tv} }
+        \caption{Time-varying external disturbance simulation}
+
+    \end{figure}
+
+\end{correction}
 \item \textit{If the inertia matrix is unknown, how to modify the suggested control system guaranteeing the asymptotic stability?}
 
-In this work, we are focused on the design of attitude controllers in the presence of state constraints. 
+In this work, we are focused on the design of attitude controllers in the presence of state inequality constraints. 
 The addition of an adaptive update law allows the system to stabilize in the presence of unknown external disturbances.
@@
 Also, it is possible to represent a uncertain or varying inertia matrix as an external disturbance torque. 
-For example, Euler's law gives the relationship for the rate of change of angular momentum
-\begin{align*}
-    M_{ext} = \dot{\vecbf{H}} = \dot{J} \vecbf{\Omega} + J \dot{\vecbf{\Omega}} .
-\end{align*}
-Using this, we can see that an instantaneous change in \( J \) is proportional to an external moment. 
-In this manner, it is possible to represent a wide array of possible forms of system uncertainty.
+Additional detail has been added to the manuscript in~\Cref{ssec:time_varying} and is duplicated in the previous answer.
 
@@
 In this situation, the presented approach allows for a straightforward method to design an attitude stabilization control law. 
-However, this is a very applicable suggestion and it is an area of current research efforts.
+However, this is a very good suggestion and it is an area of current research effort.
 
@@
 Lyapunov stability is valid if the given properties of \( V \) are satisfied in an open neighborhood of the desired attitude configuration. 
-The presented details, which are shown in~\cref{proof:att_control,proof:eR_dot_bound}, are valid in the selected domain \( D \) about the desired attitude.
+The presented details, which are shown in~\Cref{proof:att_control,proof:eR_dot_bound}, are valid in the selected domain \( D \) about the desired attitude.
 Therefore, Lyapunov stability is valid if \( D \) is also an open neighborhood of the desired attitude.
@@
     We choose the domain \( D \) to exclude the undesired critical points of \( A(R) \) as well as the infeasible regions defined by the state inequality constraints. 
-    Furthermore, we can show that the set \( D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
+    Furthermore, one can show that the set \( D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
+    Therefore, the selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
+    This implies that that both \( A(R) \) and \( B(R) \) are bounded by constants \( c_A c_B < \psi < h_1\).
+    Furthermore, since \( \norm{B} > 1 \) this ensures that \( c_A, c_B < \psi\) and shows~\cref{eqn:AB_bound}.
 \end{correction}
+
 \item \textit{Typo in eq. (40).}
@@
 The primary purpose of this article is to present the formulation of constrained attitude control on the special orthogonal group, \( \SO \).
-There have been many references which have explicitly demonstrated the issues of singularities and ambiguities of other attitude parameterizations~\cite{chaturvedi2011a,bhat2000,hughes2004}.
-{\large ADD MORE REFERENCES WHICH SHOW THIS} 
-As a result, the numerical simulations and hardware experiments were designed to demonstrate the feasibility of the proposed attitude control and the application of general attitude constraints on \( \SO \), rather than highlight the deficiences of attitude parameterizations.
-However, additional detail has been added in the numerical simulation section demonstrating and highlighting the singularities inherent in the Euler angle parameterization.
+There have been many references which have explicitly demonstrated the issues of singularities and ambiguities of other attitude parameterizations~\cite{chaturvedi2011a,bhat2000,hughes2004,shuster1993}.
+As a result, the numerical simulations and hardware experiments were designed to demonstrate the feasibility of the proposed attitude control and the application of general attitude constraints on \( \SO \), rather than highlight the deficiencies of attitude parameterizations.
+However, additional detail has been added in the numerical simulation section demonstrating and highlighting the singularities inherent in the Euler angle parameterization and is given in~\Cref{ssec:attitude_parameterization}.
 
 \begin{correction}
-    % Discuss the benefits of using this geometric representation as compared to Euler angles or quaternions
-Attitude parameterizations, such as Euler angles and Quaternions, are frequently used in the aerospace and astrodynamics communities~\cite{vallado2001,bate1971,wertz1978}.
-For example, Euler angle sequences are frequently used to describe the transformation between a variety of reference frames used to describe the position and orientation of the orbit of Earth satellites~\cite{vallado2001}.
+    Attitude parameterizations, such as Euler angles and Quaternions, are frequently used in the aerospace and astrodynamics communities~\cite{vallado2007}.
+For example, Euler angle sequences are frequently used to describe the transformation between a variety of reference frames used to describe the position and orientation of the orbit of Earth satellites~\cite{vallado2007}.
 In addition, quaternions were used during the operation of Skylab and the NASA Space Shuttle~\cite{hughes2004}.
@@
 Euler angle sequences are a minimum, three-parameter set of angles which describe the transformation between two reference frames.
-Euler angles represent any general rotation as a sequence of three intermediate rotations.
-By convention, there are \( 24 \) possible Euler angle sequences for any given rotation.
+Using Euler angles, we can represent any general rotation as a sequence of three intermediate rotations~\cite{shuster1993}.
+By convention, there are \num{24} possible Euler angle sequences for any given rotation.
 In addition, Euler angles are a minimum representation, as only three angles, and the associated sequence, are required to describe the three angular degrees of freedom of the rigid body.
@@
 The rotation matrix, \( R(\theta_1, \theta_2, \theta_3) \), corresponding to this sequence is 
-\begin{align}
+\begin{align}\label{eq:euler313}
     \begin{bmatrix}
@@
 Using this representation that kinematic differential equations for the associated Euler angles are given as
-\begin{align}
+\begin{align}\label{eq:euler313_diff}
     \begin{bmatrix}
@@
 \begin{correction}
-    \Cref{fig:Psi_adapt,fig:con_angles} are equivalent to~\cref{fig:Psi_con,fig:con_angles_con} except include the addition of the adaptive update law.
+    \Cref{fig:Psi_adapt,fig:con_angles} are equivalent to~\cref{fig:Psi_con,fig:con_angles_con} with the exception of the addition of the adaptive update law.
 \end{correction}
@@
 
+Similarly, another simulation result is presented demonstrating the ability to handle time-varying disturbances. 
+The results include discussion of the vertical axes
+\begin{correction}
+    \Cref{fig:tv} demonstrates the ability for the adaptive controller, which is presented in Proposition~\ref{prop:adaptive_control}, to handle time-varying disturbances.
+    \Cref{fig:Psi_tv} shows the non-dimensional value of the configuration error function and demonstrates that the adaptive controller is able to stabilize the system to the desired attitude configuration.
+    In addition,~\cref{fig:con_angle_tv} shows that the constraint is never violated as the angle between the body-fixed sensor \( r \) and the constraint \( v \) is greater than \SI{12}{\degree} over the entire attitude maneuver.
+    We can see in~\cref{fig:Delta_tv} that that estimate \(\bar \Delta \) for each of the components accurately tracks the true disturbance after approximately~\SI{5}{\second}.
+\end{correction}
 Additional detail has been added for~\cref{fig:exp}:
@@
 \end{correction}
-
+And also in the time-varying case:
+\begin{correction}
+    \begin{align*}
+    \Delta = \begin{bmatrix} 0.2 \\ 0.2 \\0.2 \end{bmatrix} + 0.02 \begin{bmatrix} \sin 9 t \\ \cos 9 t \\ \frac{1}{2} \parenth{\sin 9t + \cos 9t}\end{bmatrix} \si{\newton\meter}.
+    \end{align*}
+\end{correction}
 There are several parameters used in the controller, namely \( G, k_R, k_\Omega, c, k_\Delta\) and \(\alpha\).
@@
     The parameters \( k_R, k_\Omega, c, k_\Delta\) are control parameters used to modify the closed-loop behavior of the system.
-    It is straightforward to chose \( k_R, k_\Omega, k_\Delta\), using a linear analysis, to satisfy desired response criteria, such as settling time or percent overshoot~\cite{nise2007}.
+    It is straightforward to chose \( k_R, k_\Omega, k_\Delta\), using a linear analysis, to satisfy desired response criteria, such as settling time or percent overshoot~\cite{nise2004}.
 \end{correction}
@@
 All of the figures have been enlarged and modified to span the entire page rather than a single column. 
-In addition, the captions of~\cref{fig:config_error,fig:adapt,fig:con} have been modified to mention the fact that they are plotting the components of a vector in a single plot or using a subplot.
+In addition, the captions of~\cref{fig:config_error,fig:adapt,fig:con,fig:tv} have been modified to mention the fact that they are plotting the components of a vector in a single plot or using a subplot.
 \end{enumerate}

### 2016-12-15 Response.tex
xr referencing works even though there are errors

@@
 \usepackage{xr}
-\externaldocument{manuscript}
 \usepackage{hyperref}
 \usepackage[]{cleveref} % get fancy referencing
+
+\externaldocument{manuscript}
+
 % edit cref citations for IEEE format
@@
 Furthermore, it has been shown in~\cite{ioannou2012} that this form of adaptive control is able to handle time-varying uncertainties in which the uncertain term is varying sufficiently slowly as compared to the controlled dynamics.
-We have improved the manuscript with an additional numerical experiment in Section~\ref{ssec:time_varying} demonstrating the ability of the adaptive controller to handle time-varying disturbances.
+We have improved the manuscript with an additional numerical experiment in~\Cref{ssec:time_varying} demonstrating the ability of the adaptive controller to handle time-varying disturbances.
 The additional content is duplicated here:

### 2016-12-15 Response.tex
use xr-hyper instead. Bunch of errors but it seems to work in the end
Remove duplicate labels
Add Reviewer 2 Dr. Lee comment

@@
 \usepackage{bm}
-\usepackage{xr}
+\usepackage{xr-hyper}
 \usepackage{hyperref}
@@
 
-\externaldocument{manuscript}
+\externaldocument[]{manuscript}[manuscript.pdf]
 
@@
 For example, various keep-out zones for sensitive electro-optical sensors are well represented as a fixed constraint in the inertial frame. 
-In addition, the time scale of the attitude dynamics, and therefore any attitude control maneuver, is much shorter than the time scale of the translational dynamics.
+Also, as discussed above, the revised manuscript includes additional numerical results illustrating that the proposed approach can handle time-varying uncertainties while satisfying the inequality constraints.
+
+Furthermore, the time scale of the attitude dynamics, and therefore any attitude control manuever, is much shorter than the time scale of the translational dynamics.
 In other words, a time-dependent constraint in the inertial frame will evolve at a much slower rate as compared to the attitude dynamics. 

### 2016-12-15 Response.tex
Add Dr. Lee Reviewer 3 comments

@@
 \newcommand{\RIII}{\text{\RNum{3}}}
+
+\newtheorem{definition}{Definition}
+\newtheorem{lem}{Lemma}
+\newtheorem{prop}{Proposition}
+\newtheorem{cor}{Corollary}
 
@@
 \item \textit{Please give a precise definition of variation used in the paper, e.g., eq. (17) and (18)}
+
 The variation of the rotation matrix is defined as
@@
 \end{align*}
+
 \end{correction}
 
+In addition,~\Cref{prop:config_error} was modified to include additional detail on the notation \( \dirDiff{f}{x}\) as
+\begin{correction}
+    The variation of \( B(R) \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
+    \begin{align*}
+        \dirDiff{B}{R} &= \eta \cdot e_{R_{B}} ,
+    \end{align*}
+  where the notation \( \D_R A \) and \(\D_R B\) represents the derivative of \( A \) or \( B \) with respect to \( R\).
+\end{correction}
 \item \textit{This is serious.
@@
 In this case, the \textit{hat} operator is equivalently represented as \( \hat{x} = \parenth{x}^\wedge \).
-This representation enables a consistent notation for both short/simple terms, such as \( \hat{x} \) and more complicated terms such as \(\parenth{\hat{e}_\Omega R^T R_d G + (R^T R_d G)^T \hat{e}_\Omega}^\vee\).
+This representation enables a consistent notation for both short/simple terms, such as \( \hat{x} \) and more complicated terms such as \(\parenth{R^T v}^\wedge\). 
 Finally, this dual usage of the notation drastically improves the quality of the resulting typography.
 
+Explicit detail has been added to the manuscript to explain this dual notation of the \textit{hat} and \textit{vee} maps.
+\begin{correction}
+We use the notation \( \hat{x}, x\) and \( \parenth{x}^\wedge\) interchangeably.
+In particular, we use the latter form when the expression for the argument of the \textit{hat} map is long. 
+\end{correction}
 \end{enumerate}

### 2016-12-15 manuscript.tex
Add Dr. Lee Reviewer 3 comments

@@
 The inverse of the hat map is denoted by the \textit{vee} map $\vee:\so\rightarrow\R^{3}$. 
+We use the notation \( \hat{x}\) and \( \parenth{x}^\wedge\) interchangeably.
+In particular, we use the latter form when the expression for the argument of the \textit{hat} map is long. 
 Several properties of the hat map are summarized as
@@
 	\begin{align}
-		\dirDiff{B}{R} &= \eta \cdot e_{R_{B}} .
+		\dirDiff{B}{R} &= \eta \cdot e_{R_{B}} ,
 	\end{align}
+  where the notation \( \D_R A \) and \(\D_R B\) represents the derivative of \( A \) or \( B \) with respect to \( R\).
 %	\item \label{item:prop_crit}The error function \( \Psi \) is minimized when \(R = R_d\).

### 2016-12-15 manuscript.tex
Add Dr. Lee's modifications for fixing the adaptive control proof

@@
 \end{gather}
-  the zero equilibrium of the error vectors is stable in the sense of Lyapunov. Furthermore, $e_R,e_\Omega\rightarrow 0$ as $t\rightarrow\infty$, and $\bar\Delta$ is uniformly bounded.
+  the zero equilibrium of the error vectors is stable in the sense of Lyapunov. Furthermore, $e_R,e_\Omega\rightarrow 0$ as $t\rightarrow\infty$, and $\bar\Delta$ is  bounded.
 \end{prop}
@@
 \begin{align*}
-	\mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi + c J e_\Omega \cdot e_R + \frac{1}{2 k_\Delta} e_\Delta \cdot e_\Delta , \label{eqn:v_adapt}
+	\mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi + c J e_\Omega \cdot e_R + \frac{1}{2 k_\Delta} e_\Delta \cdot e_\Delta , %\label{eqn:v_adapt}
 \end{align*}
@@
 From~\Cref{prop:eR_dot_bound}, the Lyapunov function is bounded in \( D \) by
-\begin{align*} %\label{eqn:v_upper_bound}
-	\mathcal{V} \leq z^T W z ,
-\end{align*}
-where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = [\|e_R\|,\|e_\Omega\|,\|e_\Delta\|]^T\in\R^3 \) and the matrix \(W \in \R^{3 \times 3}\) is given by
-\begin{gather*}
-	W = \begin{bmatrix}
+\begin{align} %\label{eqn:v_upper_bound}
+	z^T W_1 z \leq \mathcal{V} \leq z^T W_2 z ,
+\end{align}
+where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = [\|e_R\|,\|e_\Omega\|,\|e_\Delta\|]^T\in\R^3 \) and the matrix \(W_1,W_2 \in \R^{3 \times 3}\) are given by
+\begin{align*}
+	W_1 & = \begin{bmatrix}
+		k_R \psi?? & -\frac{1}{2} c \lambda_M & 0 \\
+		-\frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_M & 0 \\
+		0 & 0 & \frac{1}{2 k_\Delta}
+	\end{bmatrix},\\
+	W_2 & = \begin{bmatrix}
 		k_R \psi & \frac{1}{2} c \lambda_M & 0 \\
@@
 	\end{bmatrix} .
-\end{gather*}
+\end{align*}
 The time derivative of \( \mathcal{V}\) with the control inputs~\cref{eqn:adaptive_control} is given by
-\begin{align*}
+\begin{align}
 	\dot{\mathcal{V}} =& - k_\Omega e_\Omega^T e_\Omega + \parenth{e_\Omega + c e_R}^T W e_\Delta - k_R c e_R^T e_R \nonumber\\
 	&- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} , \label{eqn:vdot}
-\end{align*}
+\end{align}
 where we used \( \dot{e}_\Delta = - \dot{\bar{\Delta}} \).
@@
 \end{gather*}
-If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied the matrix \( M \) is positive definite.
-This implies that $\dot{\mathcal{V}}$ is negative semidefinite and $\lim_{t\to\infty} \zeta=0$. 
-As the Lyapunov function is non-increasing $z$ is uniformly bounded. 
+If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied then all of the matrices \( W_1, W_2 \) and \( M \) are positive definite.
+This implies that $\mathcal{V}$ is positive definite and decrescent, and $\dot{\mathcal{V}}$ is negative semidefinite in the domain $D$.
+As such, the zero equilibrium is stable in the sense of Lyapunov, and all of the error variables are bounded.
+Furthermore, $\lim_{t\to\infty} \zeta=0$ according to the LaShalle-Yoshizawa theorem~\cite{khalil1996}.
+
+%and 
+%As the Lyapunov function is non-increasing $z$ is uniformly bounded. 
 %	

### 2016-12-15 manuscript.tex
Change citation to use Dr. Lee's document
Modify er_dot proposition to include bound on A(R)

@@
 	\begin{gather}
-		\norm{A} < c_A  , \quad \norm{B} < c_B . \label{eqn:AB_bound}
+		\norm{A} < b_2 \norm{e_{R_A}}^2 = c_A  , \quad \norm{B} < c_B . \label{eqn:AB_bound}
 	\end{gather}
+  where the constant \( b_2\) is given by \( b_2 = \frac{h_1 h_4}{h_5 \parenth{h_1 - \psi}}\) for
+  \begin{align*}
+    h_4 &= \min\braces{g_1 + g_2, g_2 + g_3 , g_3 + g_1} ,\\
+    h_5 &= \min\braces{\parenth{g_1 + g_2}^2,\parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2} .\\
+  \end{align*}
 	\item \label{item:prop_eR_dot_bound_EF} Upper bounds of \( E(R,R_d) \) and \( F(R) \) are given by
@@
 	\end{gather}
+
 \end{enumerate}
@@
 
-The form of the uncertainty, given in~\cref{eqn:Wdot}, is commonly used in the adaptive control literature~\cite{lee2013b,ioannou2012}. 
+The form of the uncertainty, given in~\cref{eqn:Wdot}, is commonly used in the adaptive control literature~\cite{LeeITCST13,ioannou2012}. 
 A wide variety of realistic disturbances, such as gravitational gradients or malfunctioning thrusters, are accurately represented via this model. 
@@
 Furthermore, one can show that the set \( D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
-Therefore, the selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
+The proof of the upper bound of \( A(R) \) is given in~\cite{LeeITCST13}.
+The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
 This implies that that both \( A(R) \) and \( B(R) \) are bounded by constants \( c_A c_B < \psi < h_1\).

### 2016-12-15 manuscript.tex
Fix adaptive control proposition

@@
 \begin{gather}
-	0 < c < \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H} , \label{eqn:c_bound}
+	0 < c < \min \braces{\sqrt{\frac{2 k_R b_1}{\lambda_m}},\sqrt{\frac{2 k_R b_2}{\lambda_M}}, \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H}} , \label{eqn:c_bound}
 \end{gather}
@@
 over the domain \( D \) in~\cref{eqn:domain}.
-From~\Cref{prop:eR_dot_bound}, the Lyapunov function is bounded in \( D \) by
-\begin{align} %\label{eqn:v_upper_bound}
+From~\Cref{prop:eR_dot_bound,prop:config_error}, the configuration error function is bounded in \( D \) by
+\begin{align*}
+    b_1 \norm{e_{R_A}}^2 < b_1 \norm{e_{R}}^2 < \Psi < b_2 \norm{e_{R_A}}^2 < b_2 \norm{e_{R}}^2 .
+\end{align*}
+Using this the Lyapunov function \( \mathcal{V} \) is bounded by
+\begin{align*} %\label{eqn:v_upper_bound}
 	z^T W_1 z \leq \mathcal{V} \leq z^T W_2 z ,
-\end{align}
-where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = [\|e_R\|,\|e_\Omega\|,\|e_\Delta\|]^T\in\R^3 \) and the matrix \(W_1,W_2 \in \R^{3 \times 3}\) are given by
+\end{align*}
+where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = [\|e_R\|,\|e_\Omega\|,\|e_\Delta\|]^T\in\R^3 \) and the matrices \(W_1,W_2 \in \R^{3 \times 3}\) are given by
 \begin{align*}
 	W_1 & = \begin{bmatrix}
-		k_R \psi?? & -\frac{1}{2} c \lambda_M & 0 \\
-		-\frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_M & 0 \\
+		k_R b_1 & \frac{1}{2} c \lambda_m & 0 \\
+		\frac{1}{2} c \lambda_m & \frac{1}{2} \lambda_m & 0 \\
 		0 & 0 & \frac{1}{2 k_\Delta}
@@
 	W_2 & = \begin{bmatrix}
-		k_R \psi & \frac{1}{2} c \lambda_M & 0 \\
+		k_R b_2 & \frac{1}{2} c \lambda_M & 0 \\
 		\frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_M & 0 \\
@@
 \end{align*}
-The time derivative of \( \mathcal{V}\) with the control inputs~\cref{eqn:adaptive_control} is given by
+The time derivative of \( \mathcal{V}\) with the control input defined by~\cref{eqn:adaptive_control} is given as
 \begin{align}
@@
 \end{gather*}
-If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied then all of the matrices \( W_1, W_2 \) and \( M \) are positive definite.
+If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied then the matrices \( W_1, W_2 \) and \( M \) are positive definite.
 This implies that $\mathcal{V}$ is positive definite and decrescent, and $\dot{\mathcal{V}}$ is negative semidefinite in the domain $D$.

### 2016-12-15 manuscript.tex
Rearrange the figures to flow better

@@
 
+\end{multicols}
+\begin{figure}[b]
+    \centering 
+    \subfigure[Attitude error vector \(e_R\) components \label{fig:eR_con}]{\includegraphics[width=0.3\columnwidth]{eR_con}  }~
+    \subfigure[Configuration error \( \Psi \) \label{fig:Psi_con}]{\includegraphics[width=0.3\columnwidth]{figures/Psi_con.pdf} }
+    \subfigure[Angle to each constraint \label{fig:con_angles_con}]{\includegraphics[width=0.3\columnwidth]{figures/constraint_angles_con.pdf} } 
+    \caption{Attitude stabilization without adaptive update law}
+    \label{fig:con} 
+\end{figure}
+\begin{multicols}{2}
 \section{Numerical Examples}\label{sec:numerical_simulation}
+
 We demonstrate the performance of the proposed control system via numerical simulation.
@@
 The desired state is \( R_d = I,\Omega_d = 0\).
-\end{multicols}
-\begin{figure}
-    \centering 
-    \subfigure[Attitude error vector \(e_R\) components \label{fig:eR_con}]{\includegraphics[width=0.3\columnwidth]{eR_con}  }~
-    \subfigure[Configuration error \( \Psi \) \label{fig:Psi_con}]{\includegraphics[width=0.3\columnwidth]{figures/Psi_con.pdf} }
-    \subfigure[Angle to each constraint \label{fig:con_angles_con}]{\includegraphics[width=0.3\columnwidth]{figures/constraint_angles_con.pdf} } 
-    \caption{Attitude stabilization without adaptive update law}
-    \label{fig:con} 
-\end{figure}
-\begin{multicols}{2}
 We show simulation results for the system stabilizing about the desired attitude with and without the adaptive update law from~\Cref{prop:adaptive_control}.
@@
 \subsection{Attitude Parameterizations}\label{ssec:attitude_parameterization}
+\end{multicols}
+\begin{figure} 
+  \centering 
+    \subfigure[Configuration error \( \Psi \)\label{fig:Psi_adapt}]{\includegraphics[width=0.4\columnwidth]{Psi_adapt} }~
+    \subfigure[Angle to each constraint \label{fig:con_angles}]{\includegraphics[width=0.4\columnwidth]{constraint_angles} }\\
+    \subfigure[Disturbance estimate \( \bar \Delta \) components \label{fig:delta_adapt} ]{\includegraphics[width=0.4\columnwidth]{Delta_adapt}}~
+    \subfigure[Attitude trajectory \label{fig:cad_adapt}]{\includegraphics[trim={10cm 0 10cm 0},clip,width=0.4\columnwidth]{cad_adapt} }
+  \caption{Attitude stabilization with adaptive update law}
+  \label{fig:adapt} 
+\end{figure}
+\begin{multicols}{2}
 % Discuss the benefits of using this geometric representation as compared to Euler angles or quaternions
@@
 These singularities can cause significant difficulties during control design and hardware implementation.
-\end{multicols}
-\begin{figure} 
-  \centering 
-    \subfigure[Configuration error \( \Psi \)\label{fig:Psi_adapt}]{\includegraphics[width=0.4\columnwidth]{Psi_adapt} }~
-    \subfigure[Angle to each constraint \label{fig:con_angles}]{\includegraphics[width=0.4\columnwidth]{constraint_angles} }\\
-    \subfigure[Disturbance estimate \( \bar \Delta \) components \label{fig:delta_adapt} ]{\includegraphics[width=0.4\columnwidth]{Delta_adapt}}~
-    \subfigure[Attitude trajectory \label{fig:cad_adapt}]{\includegraphics[trim={10cm 0 10cm 0},clip,width=0.4\columnwidth]{cad_adapt} }
-  \caption{Attitude stabilization with adaptive update law}
-  \label{fig:adapt} 
-\end{figure}
-\begin{multicols}{2}
+
 To demonstrate the effect of the kinematic singularities inherent with Euler angles we will represent the attitude of the body fixed reference frame, \( \vecbf{b}_i \), with respect to the inertial frame, \( \vecbf{e}_i\), in terms of the \( 3-1-3\) Euler angle sequence.
@@
 
+\end{multicols}
+\begin{figure}[H]
+    \centering 
+    \subfigure[{Configuration error \( \Psi \)} \label{fig:Psi_tv} ]{\includegraphics[width=0.3\columnwidth]{Psi_tv} }~
+    \subfigure[{Angle to constraint } \label{fig:con_angle_tv}]{\includegraphics[width=0.3\columnwidth]{figures/constraint_angle_tv.pdf} }~
+    \subfigure[{Disturbance estimate \(\bar\Delta\) components} \label{fig:Delta_tv}]{\includegraphics[width=0.3\columnwidth]{figures/delta_tv} }
+    \caption{Time-varying external disturbance simulation}
+    \label{fig:tv} 
+\end{figure}
+\begin{multicols}{2}
 \subsection{Time-varying Disturbance}\label{ssec:time_varying}
@@
 We can see in~\cref{fig:Delta_tv} that that estimate \(\bar \Delta \) for each of the components accurately tracks the true disturbance after approximately~\SI{5}{\second}.
-\end{multicols}
-\begin{figure}[H]
-    \centering 
-    \subfigure[{Configuration error \( \Psi \)} \label{fig:Psi_tv} ]{\includegraphics[width=0.3\columnwidth]{Psi_tv} }~
-    \subfigure[{Angle to constraint } \label{fig:con_angle_tv}]{\includegraphics[width=0.3\columnwidth]{figures/constraint_angle_tv.pdf} }~
-    \subfigure[{Disturbance estimate \(\bar\Delta\) components} \label{fig:Delta_tv}]{\includegraphics[width=0.3\columnwidth]{figures/delta_tv} }
-    \caption{Time-varying external disturbance simulation}
-    \label{fig:tv} 
-\end{figure}
-\begin{multicols}{2}
+
 \section{Experiment on Hexrotor UAV}\label{sec:experiment}

### 2016-12-16 Response.tex
Add detail about the modified stability proof and added cleveref commands for propositions.
Also mention that the bounds on c have been modified in the paper

@@
 \crefmultiformat{enumi}{(#2#1#3)}{ and~(#2#1#3)}{, (#2#1#3)}{ and~(#2#1#3)}
+% Proposition format
+\crefformat{prop}{Proposition~#2#1#3} % no abbreviation for equation numbers
+\Crefformat{prop}{Proposition~#2#1#3} % no abbreviation for equation numbers
+\crefrangeformat{prop}{Proposition~#3#1#4--#5#2#6}
+\Crefrangeformat{prop}{Propositions~#3#1#4--#5#2#6}
+\crefmultiformat{prop}{Propositions~#2#1#3}{ and~#2#1#3}{, #2#1#3}{ and~#2#1#3}
 
@@
 
+The proof of~\Cref{prop:adaptive_control} given in~\Cref{proof:adaptive_control} has been improved. 
+Originally, the positive definiteness of \( \mathcal{V}\) was not explicitly defined. 
+\Cref{prop:eR_dot_bound} has been modified to include additional detail on the upper bound of \( A(R) \) as:
+\begin{correction}
+    Upper bounds of \( A(R) \) and \( B(R) \) are given by
+    \begin{gather}
+        \norm{A} < b_2 \norm{e_{R_A}}^2 = c_A  , \quad \norm{B} < c_B . 
+    \end{gather}
+  where the constant \( b_2\) is given by \( b_2 = \frac{h_1 h_4}{h_5 \parenth{h_1 - \psi}}\) for
+  \begin{align*}
+    h_4 &= \min\braces{g_1 + g_2, g_2 + g_3 , g_3 + g_1} ,\\
+    h_5 &= \min\braces{\parenth{g_1 + g_2}^2,\parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2} .\\
+  \end{align*}
+\end{correction}
+
 The domain \( D \) is chosen to both exclude the undesired critical points of \( A(R)\) as well as the infeasible regions defined by the constraints. 
@@
     Furthermore, one can show that the set \( D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
-    Therefore, the selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
+    The proof of the upper bound of \( A(R) \) is given in~\cite{LeeITCST13}.
+    The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
     This implies that that both \( A(R) \) and \( B(R) \) are bounded by constants \( c_A c_B < \psi < h_1\).
@@
 
+Subsequently,~\Cref{prop:adaptive_control} was modified to explicitly demonstrate that \( \mathcal{V} \) is positive definite.
+\begin{correction}
+    Consider the Lyapunov function \( \mathcal{V} \) given by
+\begin{align*}
+    \mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi + c J e_\Omega \cdot e_R + \frac{1}{2 k_\Delta} e_\Delta \cdot e_\Delta , %\label{eqn:v_adapt}
+\end{align*}
+over the domain \( D \) in~\cref{eqn:domain}.
+From~\Cref{prop:eR_dot_bound,prop:config_error}, the configuration error function is bounded in \( D \) by
+\begin{align*}
+    b_1 \norm{e_{R_A}}^2 < b_1 \norm{e_{R}}^2 < \Psi < b_2 \norm{e_{R_A}}^2 < b_2 \norm{e_{R}}^2 .
+\end{align*}
+Using this the Lyapunov function \( \mathcal{V} \) is bounded by
+\begin{align*} %\label{eqn:v_upper_bound}
+    z^T W_1 z \leq \mathcal{V} \leq z^T W_2 z ,
+\end{align*}
+where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = [\|e_R\|,\|e_\Omega\|,\|e_\Delta\|]^T\in\R^3 \) and the matrices \(W_1,W_2 \in \R^{3 \times 3}\) are given by
+\begin{align*}
+    W_1 & = \begin{bmatrix}
+        k_R b_1 & \frac{1}{2} c \lambda_m & 0 \\
+        \frac{1}{2} c \lambda_m & \frac{1}{2} \lambda_m & 0 \\
+        0 & 0 & \frac{1}{2 k_\Delta}
+    \end{bmatrix},\\
+    W_2 & = \begin{bmatrix}
+        k_R b_2 & \frac{1}{2} c \lambda_M & 0 \\
+        \frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_M & 0 \\
+        0 & 0 & \frac{1}{2 k_\Delta}
+    \end{bmatrix} .
+\end{align*}
+The time derivative of \( \mathcal{V}\) with the control input defined by~\cref{eqn:adaptive_control} is given as
+\begin{align}
+    \dot{\mathcal{V}} =& - k_\Omega e_\Omega^T e_\Omega + \parenth{e_\Omega + c e_R}^T W e_\Delta - k_R c e_R^T e_R \nonumber\\
+    &- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} , \label{eqn:vdot}
+\end{align}
+where we used \( \dot{e}_\Delta = - \dot{\bar{\Delta}} \).
+The terms linearly dependent on \( e_\Delta\) are combined with~\cref{eqn:delta_dot} to yield
+\begin{align*}
+     e_\Delta^T \parenth{W^T \parenth{e_\Omega + c e_R} - \frac{1}{k_\Delta} \dot{\bar{\Delta}}} = 0 . 
+\end{align*}
+Using~\Cref{prop:eR_dot_bound} an upper bound on \( \dot{\mathcal{V}} \) is written as
+\begin{gather*}
+    \dot{\mathcal{V}} \leq -\zeta^T M \zeta ,
+\end{gather*}
+where $\zeta=[\|e_R\|,\|e_\Omega\|]\in\R^2$, and the matrix \( M \in \R^{2 \times 2} \) is 
+\begin{gather*}
+    M = \begin{bmatrix}
+        k_R c & \frac{k_\Omega c}{2} \\
+        \frac{k_\Omega c}{2} & k_\Omega - c \lambda_M H
+    \end{bmatrix} .
+\end{gather*}
+If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied then the matrices \( W_1, W_2 \) and \( M \) are positive definite.
+This implies that $\mathcal{V}$ is positive definite and decrescent, and $\dot{\mathcal{V}}$ is negative semidefinite in the domain $D$.
+As such, the zero equilibrium is stable in the sense of Lyapunov, and all of the error variables are bounded.
+Furthermore, $\lim_{t\to\infty} \zeta=0$ according to the LaShalle-Yoshizawa theorem~\cite{khalil1996}.
+\end{correction}
+
+Finally, the bounds on \( c \), given in~\cref{eqn:c_bound}, have been modified to ensure that \( W_1, W_2\) and \( M \) are all positive definite.
+\begin{correction}
+    If \( c \) is chosen such that
+    \begin{gather}
+        0 < c < \min \braces{\sqrt{\frac{2 k_R b_1}{\lambda_m}},\sqrt{\frac{2 k_R b_2}{\lambda_M}}, \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H}} .
+    \end{gather}
+    the zero equilibrium of the error vectors is stable in the sense of Lyapunov. Furthermore, $e_R,e_\Omega\rightarrow 0$ as $t\rightarrow\infty$, and $\bar\Delta$ is  bounded.
+\end{correction}
 \item \textit{Typo in eq. (40).}
+
+The bounds on \( c \) have been modified due to the additional detail in the stability proof shown in~\Cref{proof:adaptive_control}.
 
@@
     \begin{gather}
-    0 < c < \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H} ,
+        0 < c < \min \braces{\sqrt{\frac{2 k_R b_1}{\lambda_m}},\sqrt{\frac{2 k_R b_2}{\lambda_M}}, \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H}} .
     \end{gather}
@@
 
-\bibliography{library}
+\bibliography{library,BibMaster}
 \bibliographystyle{ieeetr}

### 2017-01-05 manuscript.tex
Add additional hat map property for proof
Add local quadratic property of \Psi and proof

@@
 \begin{gather}
-   % \hat x y = x\times y = - y\times x = - \hat y x,\\
+   \hat x y = x\times y = - y\times x = - \hat y x, \label{eqn:cross_product}\\
     x\cdot \hat y z = y\cdot \hat z x,\quad \hat x\hat y z = (x\cdot z) y - (x\cdot y ) z\label{eqn:STP},\\
@@
   where the notation \( \D_R A \) and \(\D_R B\) represents the derivative of \( A \) or \( B \) with respect to \( R\).
+    \item \label{item:prop_psi_quadratic} \( \Psi \) is locally quadratic on the domain 
+    \begin{align}\label{eq:psi_quadratic_domain}
+        D_1 = \braces{R \in \SO \vert \Psi = 0, e_{R} = 0 \iff R = R_d } 
+    \end{align}
 %	\item \label{item:prop_crit}The error function \( \Psi \) is minimized when \(R = R_d\).
@@
 %Since the desired attitude, \( R_d \), must lie in the feasible set, i.e., \( r^T R^T v < \cos \theta \), the addition of the repulsive barrier function, \( B \), does not change the minimum value of \( \Psi \).
+We show~\cref{item:prop_psi_quadratic} by computing the hessian of \( \Psi \), \( \Hess{\Psi} \),  using the chain rule as 
+\begin{align*}
+    \Hess \Psi =& \parenth{\mathbf{D}^2 A \cdot \delta^2 R} B + \parenth{\dirDiff{A}{R} }\parenth{\dirDiff{B}{R}}^T \\
+    &+ \parenth{\dirDiff{B}{R} }\parenth{\dirDiff{A}{R}}^T +\parenth{\mathbf{D}^2 B \cdot \delta^2 R} A .
+\end{align*}
+The first order derivative of \( A(R) \) and \( B(R) \) are given by~\cref{eqn:eRA,eqn:eRB}. 
+The hessian of \( A(R) \) is computed as 
+\begin{align*}
+    \dirDiff{\parenth{\dirDiff{A}{R}}}{R} &= \eta \cdot \frac{1}{2}\parenth{G R_d^T R \delta R - \delta R^T R_d G}^\vee , \\
+    &= \eta \cdot \frac{1}{2} \parenth{G R_d^T R \hat \eta + \hat \eta R^T R_d G}^\vee,\\
+    &= \eta \cdot \frac{1}{2} \bracket{\parenth{\braces{\tr{R^T R_d G} I - R^T R_d G} \eta}^\wedge}^\vee , \\
+    &= \eta \cdot \frac{1}{2} \parenth{\tr{R^T R_d G} I - R^T R_d G}\eta ,
+\end{align*}
+where we used the scalar triple product rule, from~\cref{eqn:STP}, to arrive at the final form.
+The hessian of \( B(R) \) is computed as
+\begin{align*}
+    \dirDiff{\parenth{\dirDiff{B}{R}}}{R} =& \eta \cdot \left[\frac{\parenth{\delta R^T v}^\wedge r}{\alpha\parenth{r^T R^T v - \cos \theta}} \right. \\
+    & \left. - \frac{\alpha \parenth{R^T v}^\wedge r \parenth{r^T \delta R^T v}}{\alpha^2 \parenth{r^TR^Tv - \cos \theta}^2}   \right] .
+\end{align*}
+The term \( \parenth{\delta R^T v}^\wedge r\) is simplified as
+\begin{align*}
+    \parenth{\delta R^T v}^\wedge r &= - \hat{r} \delta R ^T v , \\
+    &= - \hat{r} \parenth{R \hat \eta}^T v , \\
+    &= \hat{r} \parenth{\hat{\eta} R^T } v , \\
+    &= - \hat{r} \parenth{R^T v}^\wedge \eta ,
+\end{align*}
+where we utilized the hat map property from~\cref{eqn:cross_product}.
+Similarly, the term \( r^t \delta R^T v \) is simplified as
+\begin{align*}
+    r^T \delta R^T v &= r^T \parenth{-\hat \eta R^T}v , \\
+    &= r^T \parenth{R^T v}^\wedge \eta .
+\end{align*}
+The hessian of \( B(R) \) then becomes
+\begin{align*}
+    \dirDiff{\parenth{\dirDiff{B}{R}}}{R} =& \eta \cdot \left[ - \frac{ \hat r \parenth{R^T v}^\wedge}{\alpha \parenth{r^T R^T v - \cos \theta}} \right. \\ 
+    & \left. - \frac{\parenth{R^T v}^\wedge r r^T \parenth{R^T v}^\wedge }{ \alpha\parenth{r^T R^T v - \cos \theta}^2}  \right] \eta .
+\end{align*}
+Using these terms, we evaluate \( \Hess{\Psi} \) at the desired attitude \( R = R_d \) as
+\begin{align*}
+    \Hess{\Psi} = \eta^T \frac{1}{2} B \parenth{\tr{G}I -  G} \eta , 
+\end{align*}
+which is positive definite since \( B > 1\) and \( \sum g_i > g_i\). 
+From~\cite[Proposition 6.30]{bullo2004}, \( \Psi \) is locally quadratic on the set \( D_1 \) which proves~\cref{item:prop_psi_quadratic}.
 

### 2017-01-05 manuscript.tex
Update domain for control proof
Update stability proof with quadratic function domain

@@
 \begin{align}
-	D = \braces{R \in \SO \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta}. \label{eqn:domain}
+	D_2 = \braces{R \in \SO \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta}. \label{eqn:domain}
 \end{align}
@@
 	\begin{gather}
-		\norm{A} < b_2 \norm{e_{R_A}}^2 = c_A  , \quad \norm{B} < c_B . \label{eqn:AB_bound}
+		\norm{A} < b_2 \norm{e_{R_A}}^2 < c_A  , \quad \norm{B} < c_B . \label{eqn:AB_bound}
 	\end{gather}
@@
 \begin{gather}
-	0 < c < \min \braces{\sqrt{\frac{2 k_R b_1}{\lambda_m}},\sqrt{\frac{2 k_R b_2}{\lambda_M}}, \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H}} , \label{eqn:c_bound}
+	0 < c < \min \braces{\sqrt{\frac{2 k_R n_1}{\lambda_m}},\sqrt{\frac{2 k_R n_2}{\lambda_M}}, \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H}} , \label{eqn:c_bound}
 \end{gather}
@@
 \end{align*}
-over the domain \( D \) in~\cref{eqn:domain}.
-From~\Cref{prop:eR_dot_bound,prop:config_error}, the configuration error function is bounded in \( D \) by
+over the domain \( D_3 = D_1 \cup D_2\), which ensures that the properties of~\Cref{prop:config_error,prop:error_dyn} are satisfied.
+
+From~\Cref{prop:config_error}, the configuration error function is locally quadratic and it is bounded in \( D_3 \) by
 \begin{align*}
-    b_1 \norm{e_{R_A}}^2 < b_1 \norm{e_{R}}^2 < \Psi < b_2 \norm{e_{R_A}}^2 < b_2 \norm{e_{R}}^2 .
+    n_1 \norm{e_R} < \Psi <  n_2 \norm{e_{R}}^2 ,
 \end{align*}
+for constants \( 0 < n_1 \leq n_2 \)~\cite[Definition 6.28]{bullo2004}.
 Using this the Lyapunov function \( \mathcal{V} \) is bounded by
@@
 	W_1 & = \begin{bmatrix}
-		k_R b_1 & \frac{1}{2} c \lambda_m & 0 \\
+		k_R n_1 & \frac{1}{2} c \lambda_m & 0 \\
 		\frac{1}{2} c \lambda_m & \frac{1}{2} \lambda_m & 0 \\
@@
 	W_2 & = \begin{bmatrix}
-		k_R b_2 & \frac{1}{2} c \lambda_M & 0 \\
+		k_R n_2 & \frac{1}{2} c \lambda_M & 0 \\
 		\frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_M & 0 \\
@@
 If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied then the matrices \( W_1, W_2 \) and \( M \) are positive definite.
-This implies that $\mathcal{V}$ is positive definite and decrescent, and $\dot{\mathcal{V}}$ is negative semidefinite in the domain $D$.
+This implies that $\mathcal{V}$ is positive definite and decrescent, and $\dot{\mathcal{V}}$ is negative semidefinite in the domain $D_3$.
 As such, the zero equilibrium is stable in the sense of Lyapunov, and all of the error variables are bounded.

### 2017-01-05 manuscript.tex
Fix typo in domain of quadratic function

@@
     where the notation \( \D_R A \) and \(\D_R B\) represents the derivative of \( A \) or \( B \) with respect to \( R\).
-    \item \label{item:prop_psi_quadratic} \( \Psi \) is locally quadratic on the domain 
+    \item \label{item:prop_psi_quadratic} \( \Psi \) is a locally quadratic function on the domain 
     \begin{align}\label{eq:psi_quadratic_domain}
-        D_1 = \braces{R \in \SO \vert \Psi = 0, e_{R} = 0 \iff R = R_d } 
+        D_1 = \braces{R \in \SO \vert \Psi = 0, e_{R} = 0 \iff R = R_d } ,
+    \end{align}
+    and it is bounded by constants \( 0 < n_1 \leq n_2 \) as
+    \begin{align}\label{eq:psi_bound}
+        n_1 \norm{e_R}^2 \leq \Psi(R) \leq n_2 \norm{e_R}^2 .
     \end{align}
@@
 \end{align*}
-over the domain \( D_3 = D_1 \cup D_2\), which ensures that the properties of~\Cref{prop:config_error,prop:error_dyn} are satisfied.
+over the domain \( D_3 = D_1 \cap D_2\), which ensures that the properties of~\Cref{prop:config_error,prop:error_dyn} are satisfied.
 
-From~\Cref{prop:config_error}, the configuration error function is locally quadratic and it is bounded in \( D_3 \) by
-\begin{align*}
-    n_1 \norm{e_R} < \Psi <  n_2 \norm{e_{R}}^2 ,
-\end{align*}
-for constants \( 0 < n_1 \leq n_2 \)~\cite[Definition 6.28]{bullo2004}.
+From~\Cref{prop:config_error}, the configuration error function is locally quadratic and it is bounded in \( D_3 \) by~\cref{eq:psi_bound}~\cite[Definition 6.28]{bullo2004}.
 Using this the Lyapunov function \( \mathcal{V} \) is bounded by

### 2017-01-05 Response.tex
Copy updated proof of hessian of \Psi and V > 0

@@
 \end{correction}
+
 \item \textit{This is serious.
@@
 
-The proof of~\Cref{prop:adaptive_control} given in~\Cref{proof:adaptive_control} has been improved. 
-Originally, the positive definiteness of \( \mathcal{V}\) was not explicitly defined. 
 \Cref{prop:eR_dot_bound} has been modified to include additional detail on the upper bound of \( A(R) \) as:
@@
 
+The proof of~\Cref{prop:adaptive_control} given in~\Cref{proof:adaptive_control} has been improved. 
+Originally, the positive definiteness of \( \mathcal{V}\) was not explicitly defined. 
+In order to prove that the Lyapunov function is positive definite an additional quadratic property of the configuration error function was derived.
+A function \( \psi \) is quadratic on the domain \( D \) about the critical zero \( x_0 \in D \) if there exists two constants \( 0 < b_1 \leq b_2 \) such that
+\begin{align*}
+    b_1 \norm{\text{d} \psi}^2 \leq \psi(x) b_2 \leq \norm{\text{d} \psi}^2 ,
+\end{align*}
+for all \( x \in D \, \setminus \, x_0\)~\cite[Definition 6.28]{bullo2004}.
+To show that \( \Psi \) is quadratic we compute the hessian of \( \Psi \) at the desired attitude \( R = R_d \).
+This additional detail was included in~\cref{prop:config_error}, as shown here:
+\begin{correction}
+     \( \Psi \) is a locally quadratic function on the domain 
+        \begin{align}\label{eq:psi_quadratic_domain}
+            D_1 = \braces{R \in \SO \vert \Psi = 0, e_{R} = 0 \iff R = R_d } ,
+        \end{align}
+        and it is bounded by constants \( 0 < n_1 \leq n_2 \) as
+        \begin{align}\label{eq:psi_bound}
+            n_1 \norm{e_R}^2 \leq \Psi(R) \leq n_2 \norm{e_R}^2 .
+        \end{align}
+\end{correction}
+and proven in~\Cref{proof:config_error}, as shown here:
+\begin{correction}
+    We show~\cref{item:prop_psi_quadratic} by computing the hessian of \( \Psi \), \( \Hess{\Psi} \),  using the chain rule as 
+    \begin{align*}
+        \Hess \Psi =& \parenth{\mathbf{D}^2 A \cdot \delta^2 R} B + \parenth{\dirDiff{A}{R} }\parenth{\dirDiff{B}{R}}^T \\
+        &+ \parenth{\dirDiff{B}{R} }\parenth{\dirDiff{A}{R}}^T +\parenth{\mathbf{D}^2 B \cdot \delta^2 R} A .
+    \end{align*}
+    The first order derivative of \( A(R) \) and \( B(R) \) are given by~\cref{eqn:eRA,eqn:eRB}. 
+    The hessian of \( A(R) \) is computed as 
+    \begin{align*}
+        \dirDiff{\parenth{\dirDiff{A}{R}}}{R} &= \eta \cdot \frac{1}{2}\parenth{G R_d^T R \delta R - \delta R^T R_d G}^\vee , \\
+        &= \eta \cdot \frac{1}{2} \parenth{G R_d^T R \hat \eta + \hat \eta R^T R_d G}^\vee,\\
+        &= \eta \cdot \frac{1}{2} \bracket{\parenth{\braces{\tr{R^T R_d G} I - R^T R_d G} \eta}^\wedge}^\vee , \\
+        &= \eta \cdot \frac{1}{2} \parenth{\tr{R^T R_d G} I - R^T R_d G}\eta ,
+    \end{align*}
+    where we used the scalar triple product rule, from~\cref{eqn:STP}, to arrive at the final form.
+    The hessian of \( B(R) \) is computed as
+    \begin{align*}
+        \dirDiff{\parenth{\dirDiff{B}{R}}}{R} =& \eta \cdot \left[\frac{\parenth{\delta R^T v}^\wedge r}{\alpha\parenth{r^T R^T v - \cos \theta}} \right. \\
+        & \left. - \frac{\alpha \parenth{R^T v}^\wedge r \parenth{r^T \delta R^T v}}{\alpha^2 \parenth{r^TR^Tv - \cos \theta}^2}   \right] .
+    \end{align*}
+    The term \( \parenth{\delta R^T v}^\wedge r\) is simplified as
+    \begin{align*}
+        \parenth{\delta R^T v}^\wedge r &= - \hat{r} \delta R ^T v , \\
+        &= - \hat{r} \parenth{R \hat \eta}^T v , \\
+        &= \hat{r} \parenth{\hat{\eta} R^T } v , \\
+        &= - \hat{r} \parenth{R^T v}^\wedge \eta ,
+    \end{align*}
+    where we utilized the hat map property from~\cref{eqn:cross_product}.
+    Similarly, the term \( r^t \delta R^T v \) is simplified as
+    \begin{align*}
+        r^T \delta R^T v &= r^T \parenth{-\hat \eta R^T}v , \\
+        &= r^T \parenth{R^T v}^\wedge \eta .
+    \end{align*}
+    The hessian of \( B(R) \) then becomes
+    \begin{align*}
+        \dirDiff{\parenth{\dirDiff{B}{R}}}{R} =& \eta \cdot \left[ - \frac{ \hat r \parenth{R^T v}^\wedge}{\alpha \parenth{r^T R^T v - \cos \theta}} \right. \\ 
+        & \left. - \frac{\parenth{R^T v}^\wedge r r^T \parenth{R^T v}^\wedge }{ \alpha\parenth{r^T R^T v - \cos \theta}^2}  \right] \eta .
+    \end{align*}
+    Using these terms, we evaluate \( \Hess{\Psi} \) at the desired attitude \( R = R_d \) as
+    \begin{align*}
+        \Hess{\Psi} = \eta^T \frac{1}{2} B \parenth{\tr{G}I -  G} \eta , 
+    \end{align*}
+    which is positive definite since \( B > 1\) and \( \sum g_i > g_i\). 
+    From~\cite[Proposition 6.30]{bullo2004}, \( \Psi \) is locally quadratic on the set \( D_1 \) which proves~\cref{item:prop_psi_quadratic}.
+\end{correction}
+
 Subsequently,~\Cref{prop:adaptive_control} was modified to explicitly demonstrate that \( \mathcal{V} \) is positive definite.
@@
     \end{align*}
-over the domain \( D \) in~\cref{eqn:domain}.
-From~\Cref{prop:eR_dot_bound,prop:config_error}, the configuration error function is bounded in \( D \) by
-\begin{align*}
-    b_1 \norm{e_{R_A}}^2 < b_1 \norm{e_{R}}^2 < \Psi < b_2 \norm{e_{R_A}}^2 < b_2 \norm{e_{R}}^2 .
-\end{align*}
+    over the domain \( D_3 = D_1 \cap D_2\), which ensures that the properties of~\Cref{prop:config_error,prop:error_dyn} are satisfied.
+
+    From~\Cref{prop:config_error}, the configuration error function is locally quadratic and it is bounded in \( D_3 \) by~\cref{eq:psi_bound}~\cite[Definition 6.28]{bullo2004}.
     Using this the Lyapunov function \( \mathcal{V} \) is bounded by
@@
     W_1 & = \begin{bmatrix}
-        k_R b_1 & \frac{1}{2} c \lambda_m & 0 \\
+        k_R n_1 & \frac{1}{2} c \lambda_m & 0 \\
         \frac{1}{2} c \lambda_m & \frac{1}{2} \lambda_m & 0 \\
@@
     W_2 & = \begin{bmatrix}
-        k_R b_2 & \frac{1}{2} c \lambda_M & 0 \\
+        k_R n_2 & \frac{1}{2} c \lambda_M & 0 \\
         \frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_M & 0 \\
@@
     If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied then the matrices \( W_1, W_2 \) and \( M \) are positive definite.
-This implies that $\mathcal{V}$ is positive definite and decrescent, and $\dot{\mathcal{V}}$ is negative semidefinite in the domain $D$.
+    This implies that $\mathcal{V}$ is positive definite and decrescent, and $\dot{\mathcal{V}}$ is negative semidefinite in the domain $D_3$.
 As such, the zero equilibrium is stable in the sense of Lyapunov, and all of the error variables are bounded.

### 2017-01-05 manuscript.tex
Improve surface plots

@@
     \centering 
-    \subfigure[Attractive \( A(R) \) \label{fig:attract_error}]{\includegraphics[width=0.3\columnwidth]{attract_error} }~
-    \subfigure[Repulsive \( B(R) \) \label{fig:avoid_error} ]{\includegraphics[width=0.3\columnwidth]{avoid_error} }~
-    \subfigure[Combined \( \Psi \) \label{fig:combined_error}]{\includegraphics[width=0.3\columnwidth]{combined_error} }%
+    \subfigure[Attractive \( A(R) \) \label{fig:attract_error}]{\includegraphics[width=0.33\columnwidth]{attract_error} }~
+    \subfigure[Repulsive \( B(R) \) \label{fig:avoid_error} ]{\includegraphics[width=0.33\columnwidth]{avoid_error} }~
+    \subfigure[Combined \( \Psi \) \label{fig:combined_error}]{\includegraphics[width=0.33\columnwidth]{combined_error} }%
     \caption{Visualization of Configuration Error Functions using spherical coordinate representation}

### 2017-01-06 manuscript.tex
Allow page breaks in long equations
Make it clear what a quadratic function really is
Fix some typos

@@
 \usepackage{ijcas_packages}
+\allowdisplaybreaks[1]
 
@@
     where the notation \( \D_R A \) and \(\D_R B\) represents the derivative of \( A \) or \( B \) with respect to \( R\).
-    \item \label{item:prop_psi_quadratic} \( \Psi \) is a locally quadratic function on the domain 
+    \item \label{item:prop_psi_quadratic} \( \Psi \) is a locally quadratic function, which means there exists constants \( 0 < n_1 \leq n_2 \) such that
+    \begin{align}\label{eq:psi_bound}
+        n_1 \norm{e_R}^2 \leq \Psi(R) \leq n_2 \norm{e_R}^2 ,
+    \end{align}
+    on the domain
     \begin{align}\label{eq:psi_quadratic_domain}
-        D_1 = \braces{R \in \SO \vert \Psi = 0, e_{R} = 0 \iff R = R_d } ,
-    \end{align}
-    and it is bounded by constants \( 0 < n_1 \leq n_2 \) as
-    \begin{align}\label{eq:psi_bound}
-        n_1 \norm{e_R}^2 \leq \Psi(R) \leq n_2 \norm{e_R}^2 .
+        D_1 = \braces{R \in \SO \vert e_{R} = 0 \iff R = R_d } .
     \end{align}
@@
 		\diff{}{t} \parenth{\Psi} = e_R \cdot e_\Omega , \label{eqn:psi_dot}\\
-		\diff{}{t} \parenth{e_R} = \dot{e}_{R_A} B(R) + e_{R_A} \dot{B}(R) + \dot{A}(R)e_{R_B} + A \dot{e}_{R_B} , \label{eqn:eR_dot}\\
+		\diff{}{t} \parenth{e_R} = \dot{e}_{R_A} B + e_{R_A} \dot{B} + \dot{A}e_{R_B} + A \dot{e}_{R_B} , \label{eqn:eR_dot} \\
 		\diff{}{t} \parenth{e_{R_A}} = E(R, R_d) e_\Omega , \label{eqn:eRA_dot} \\
@@
 \begin{prop}[Bound on \( \bm{\dot{e}_R} \)]\label{prop:eR_dot_bound}
-Consider a domain \( D \) about the desired attitude defined as
+Consider a domain \( D_2 \) about the desired attitude defined as
 \begin{align}
@@
 \end{multicols}
-\begin{figure}[H]
+\begin{figure}[t]
     \centering 
@@
 where we utilized the hat map property from~\cref{eqn:cross_product}.
-Similarly, the term \( r^t \delta R^T v \) is simplified as
+Similarly, the term \( r^T \delta R^T v \) is simplified as
 \begin{align*}
@@
 %	However, since the chosen domain is assumed to exclude the constraint this situation is not possible and \( B < \psi \).
-We choose the domain \( D \) to exclude the undesired critical points of \( A(R) \) as well as the infeasible regions defined by the state inequality constraints. 
-Furthermore, one can show that the set \( D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
+We choose the domain \( D_2 \) to exclude the undesired critical points of \( A(R) \) as well as the infeasible regions defined by the state inequality constraints. 
+Furthermore, one can show that the set \( D_2 \) is an open neighborhood of the desired attitude configuration, \( R_d\).
 The proof of the upper bound of \( A(R) \) is given in~\cite{LeeITCST13}.
@@
 over the domain \( D_3 = D_1 \cap D_2\), which ensures that the properties of~\Cref{prop:config_error,prop:error_dyn} are satisfied.
+Furthermore, the domain \( D_3 \) is an open neighborhood of the desired attitude.
 
@@
 The time derivative of \( \mathcal{V}\) with the control input defined by~\cref{eqn:adaptive_control} is given as
-\begin{align}
+\begin{align*}
 	\dot{\mathcal{V}} =& - k_\Omega e_\Omega^T e_\Omega + \parenth{e_\Omega + c e_R}^T W e_\Delta - k_R c e_R^T e_R \nonumber\\
 	&- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} , \label{eqn:vdot}
-\end{align}
+\end{align*}
 where we used \( \dot{e}_\Delta = - \dot{\bar{\Delta}} \).
@@
     {is a PhD Candidate in the Department of Mechanical and Aerospace Engineering at George Washington University. 
-    He received his bachelor's degree in Astronautical Engineering from the United States Air Force Academy in 2009 and his master's degree in Aeronautical and Astronautical Engineering from Purdue University in 2013.
+    He received his bachelor's degree in Astronautical Engineering from the US Air Force Academy in 2009 and his master's degree in Aeronautical and Astronautical Engineering from Purdue University in 2013.
     % He previously served as Deputy Space Vehicles Lead for the ORS-1 (Operationally Responsive Space ) satellite program, and as Lead Test Engineer in the Guidance, Navigation, and Control group at Air Force Research Laboratory located at Kirtland AFB, NM.

### 2017-01-06 Response.tex
Remove redundant labels from response
Fix appendix references

@@
 \crefmultiformat{prop}{Propositions~#2#1#3}{ and~#2#1#3}{, #2#1#3}{ and~#2#1#3}
+% Appendix
+\crefformat{appendix}{Appendix~#2#1#3..} % no abbreviation for equation numbers
+\Crefformat{appendix}{Appendix~#2#1#3} % no abbreviation for equation numbers
+\crefrangeformat{appendix}{Appendices~#3#1#4--#5#2#6}
+\Crefrangeformat{appendix}{Appendices~#3#1#4--#5#2#6}
+\crefmultiformat{appendix}{Appendices~#2#1#3}{ and~#2#1#3}{, #2#1#3}{ and~#2#1#3}
 
@@
 
-I would like to thank the reviewers for their thoughtful comments, which are aimed towards improving the quality of the paper and the clarity of the results. 
-In accordance with the comments and suggestions, the paper has been revised, and the answers to all comments are addressed as follows.
+I would like to thank the reviewers for their thoughtful comments, which are aimed towards improving the quality of the manuscript and the clarity of the results. 
+In accordance with the comments and suggestions, the manuscript has been revised, and the answers to all comments are addressed as follows.
 
@@
 \end{align*}
-We have augmented the proof of Proposition 1, which is given in Appendix 1, to include the definition of the variation as:
+We have augmented the proof of~\cref{prop:config_error}, which is given in~\cref{proof:config_error}, to include the definition of the variation as:
 \begin{correction}
@@
      \( \Psi \) is a locally quadratic function on the domain 
-        \begin{align}\label{eq:psi_quadratic_domain}
+        \begin{align}%\label{eq:psi_quadratic_domain}
             D_1 = \braces{R \in \SO \vert \Psi = 0, e_{R} = 0 \iff R = R_d } ,
@@
         and it is bounded by constants \( 0 < n_1 \leq n_2 \) as
-        \begin{align}\label{eq:psi_bound}
+        \begin{align}%\label{eq:psi_bound}
             n_1 \norm{e_R}^2 \leq \Psi(R) \leq n_2 \norm{e_R}^2 .
@@
     \dot{\mathcal{V}} =& - k_\Omega e_\Omega^T e_\Omega + \parenth{e_\Omega + c e_R}^T W e_\Delta - k_R c e_R^T e_R \nonumber\\
-    &- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} , \label{eqn:vdot}
+    &- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} , %\label{eqn:vdot}
     \end{align}

### 2017-01-06 Response.tex
Rearrange response for updated stability proofs

@@
 % Appendix
-\crefformat{appendix}{Appendix~#2#1#3..} % no abbreviation for equation numbers
+\crefformat{appendix}{Appendix~#2#1#3} % no abbreviation for equation numbers
 \Crefformat{appendix}{Appendix~#2#1#3} % no abbreviation for equation numbers
@@
 
-Lyapunov stability is valid if the given properties of \( V \) are satisfied in an open neighborhood of the desired attitude configuration. 
-The presented details, which are shown in~\Cref{proof:att_control,proof:eR_dot_bound}, are valid in the selected domain \( D \) about the desired attitude.
-Therefore, Lyapunov stability is valid if \( D \) is also an open neighborhood of the desired attitude.
+The stability proof has been improved and several modifications have been included in the manuscript:
+\begin{itemize}
+    \item An additional quadratic property has been derived for \( \Psi \) and shown in~\cref{prop:config_error},
+    \item The quadratic property of \( \Psi \) requires the derivation of the hessian of \( \Psi \) given in~\cref{proof:config_error},
+    \item Additional detail has been included on the set \( D \) and it's properties in~\cref{proof:eR_dot_bound}.
+    \item The Lyapunov function in~\cref{proof:adaptive_control} is shown to be positive definite,
+    \item The revised stability proof includes a modified requirement for the constant \( c \) shown in~\cref{eqn:c_bound},
+\end{itemize}
+Here we present the modifications and provide additional detail. 
+In addition, we duplicate the modifications from the manuscript in this section as well.
 
-The set \( D = \braces{R \in \SO \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta} \) of the metric space \( \parenth{R \in \SO, \Psi(R,R_d)} \) is an open neighborhood of \( R_d \) if there exists an \( \epsilon > 0 \) such that for any \( R \in \SO | \Psi(R,R_d) < \epsilon \), it is also true that \( R \in D \).
-The selected domain \( D \) excludes the undesired equilibrium points of \( A(R) \) and the infeasible regions defined by the constraints \( r^T R^T v_i \), i.e.
-the desired attitude should be sufficiently far away from the constraints.
-We can ensure that \( D \) is an open neighborhood of \( R_d \) by choosing \( \epsilon = \min \braces{\psi, \Psi(R|r^T R^T v = \beta,R_d)}\).
-Therefore, the given domain \( D \) is an open neighborhood of the desired attitude configuration, \(R_d\), and the Lyapunov stability results are valid in this domain.
-
-\Cref{prop:eR_dot_bound} has been modified to include additional detail on the upper bound of \( A(R) \) as:
-\begin{correction}
-    Upper bounds of \( A(R) \) and \( B(R) \) are given by
-    \begin{gather}
-        \norm{A} < b_2 \norm{e_{R_A}}^2 = c_A  , \quad \norm{B} < c_B . 
-    \end{gather}
-  where the constant \( b_2\) is given by \( b_2 = \frac{h_1 h_4}{h_5 \parenth{h_1 - \psi}}\) for
-  \begin{align*}
-    h_4 &= \min\braces{g_1 + g_2, g_2 + g_3 , g_3 + g_1} ,\\
-    h_5 &= \min\braces{\parenth{g_1 + g_2}^2,\parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2} .\\
-  \end{align*}
-\end{correction}
-
-The domain \( D \) is chosen to both exclude the undesired critical points of \( A(R)\) as well as the infeasible regions defined by the constraints. 
-In general, this is not a difficult assumption to satisfy as the desired attitude will typically be located far from the constrained regions.
-We have augmented the manuscript with some additional discussion of the chosen domain \( D \) in~\Cref{proof:eR_dot_bound}.
-
-\begin{correction}
-    We choose the domain \( D \) to exclude the undesired critical points of \( A(R) \) as well as the infeasible regions defined by the state inequality constraints. 
-    Furthermore, one can show that the set \( D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
-    The proof of the upper bound of \( A(R) \) is given in~\cite{LeeITCST13}.
-    The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
-    This implies that that both \( A(R) \) and \( B(R) \) are bounded by constants \( c_A c_B < \psi < h_1\).
-    Furthermore, since \( \norm{B} > 1 \) this ensures that \( c_A, c_B < \psi\) and shows~\cref{eqn:AB_bound}.
-\end{correction}
-
-The proof of~\Cref{prop:adaptive_control} given in~\Cref{proof:adaptive_control} has been improved. 
-Originally, the positive definiteness of \( \mathcal{V}\) was not explicitly defined. 
 In order to prove that the Lyapunov function is positive definite an additional quadratic property of the configuration error function was derived.
@@
 
-Subsequently,~\Cref{prop:adaptive_control} was modified to explicitly demonstrate that \( \mathcal{V} \) is positive definite.
+Lyapunov stability is valid if the given properties of \( V \) are satisfied in an open neighborhood of the desired attitude configuration. 
+The presented details, which are shown in~\Cref{proof:att_control,proof:eR_dot_bound}, are valid in the selected domain \( D \) about the desired attitude.
+Therefore, Lyapunov stability is valid if \( D \) is also an open neighborhood of the desired attitude.
+
+The set 
+\[ D = \braces{R \in \SO \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta} \]
+of the metric space \( \parenth{R \in \SO, \Psi(R,R_d)} \) is an open neighborhood of \( R_d \) if there exists an \( \epsilon > 0 \) such that for any \( R \in \SO | \Psi(R,R_d) < \epsilon \), it is also true that \( R \in D \).
+The selected domain \( D \) excludes the undesired equilibrium points of \( A(R) \) and the infeasible regions defined by the constraints \( r^T R^T v_i \), i.e.
+the desired attitude should be sufficiently far away from the constraints.
+We can ensure that \( D \) is an open neighborhood of \( R_d \) by choosing \( \epsilon = \min \braces{\psi, \Psi(R|r^T R^T v = \beta,R_d)}\).
+Therefore, the given domain \( D \) is an open neighborhood of the desired attitude configuration, \(R_d\), and the Lyapunov stability results are valid in this domain.
+
+\Cref{prop:eR_dot_bound} has been modified to include additional detail on the upper bound of \( A(R) \) as:
+\begin{correction}
+    Upper bounds of \( A(R) \) and \( B(R) \) are given by
+    \begin{gather}
+        \norm{A} < b_2 \norm{e_{R_A}}^2 = c_A  , \quad \norm{B} < c_B . 
+    \end{gather}
+  where the constant \( b_2\) is given by \( b_2 = \frac{h_1 h_4}{h_5 \parenth{h_1 - \psi}}\) for
+  \begin{align*}
+    h_4 &= \min\braces{g_1 + g_2, g_2 + g_3 , g_3 + g_1} ,\\
+    h_5 &= \min\braces{\parenth{g_1 + g_2}^2,\parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2} .\\
+  \end{align*}
+\end{correction}
+
+The domain \( D \) is chosen to both exclude the undesired critical points of \( A(R)\) as well as the infeasible regions defined by the constraints. 
+In general, this is not a difficult assumption to satisfy as the desired attitude will typically be located far from the constrained regions.
+We have augmented the manuscript with some additional discussion of the chosen domain \( D \) in~\Cref{proof:eR_dot_bound}.
+
+\begin{correction}
+    We choose the domain \( D \) to exclude the undesired critical points of \( A(R) \) as well as the infeasible regions defined by the state inequality constraints. 
+    Furthermore, one can show that the set \( D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
+    The proof of the upper bound of \( A(R) \) is given in~\cite{LeeITCST13}.
+    The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
+    This implies that that both \( A(R) \) and \( B(R) \) are bounded by constants \( c_A c_B < \psi < h_1\).
+    Furthermore, since \( \norm{B} > 1 \) this ensures that \( c_A, c_B < \psi\) and shows~\cref{eqn:AB_bound}.
+\end{correction}
+
+The proof of~\Cref{prop:adaptive_control} given in~\Cref{proof:adaptive_control} has been improved to explicitly demonstrate that \( \mathcal{V} \) is positive definite.
 \begin{correction}
@@
     \begin{gather}
-        0 < c < \min \braces{\sqrt{\frac{2 k_R b_1}{\lambda_m}},\sqrt{\frac{2 k_R b_2}{\lambda_M}}, \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H}} .
+        0 < c < \min \braces{\sqrt{\frac{2 k_R n_1}{\lambda_m}},\sqrt{\frac{2 k_R n_2}{\lambda_M}}, \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H}} .
     \end{gather}

### 2017-01-06 Response.tex
Add thanks for last reviewer

--- 2017-01-05 Response.tex
@@
 \end{correction}
-
 \item \textit{This is serious.
@@
 
+The proof of~\Cref{prop:adaptive_control} given in~\Cref{proof:adaptive_control} has been improved. 
+Originally, the positive definiteness of \( \mathcal{V}\) was not explicitly defined. 
 \Cref{prop:eR_dot_bound} has been modified to include additional detail on the upper bound of \( A(R) \) as:
@@
 
-The proof of~\Cref{prop:adaptive_control} given in~\Cref{proof:adaptive_control} has been improved. 
-Originally, the positive definiteness of \( \mathcal{V}\) was not explicitly defined. 
-In order to prove that the Lyapunov function is positive definite an additional quadratic property of the configuration error function was derived.
-A function \( \psi \) is quadratic on the domain \( D \) about the critical zero \( x_0 \in D \) if there exists two constants \( 0 < b_1 \leq b_2 \) such that
-\begin{align*}
-    b_1 \norm{\text{d} \psi}^2 \leq \psi(x) b_2 \leq \norm{\text{d} \psi}^2 ,
-\end{align*}
-for all \( x \in D \, \setminus \, x_0\)~\cite[Definition 6.28]{bullo2004}.
-To show that \( \Psi \) is quadratic we compute the hessian of \( \Psi \) at the desired attitude \( R = R_d \).
-This additional detail was included in~\cref{prop:config_error}, as shown here:
-\begin{correction}
-     \( \Psi \) is a locally quadratic function on the domain 
-        \begin{align}\label{eq:psi_quadratic_domain}
-            D_1 = \braces{R \in \SO \vert \Psi = 0, e_{R} = 0 \iff R = R_d } ,
-        \end{align}
-        and it is bounded by constants \( 0 < n_1 \leq n_2 \) as
-        \begin{align}\label{eq:psi_bound}
-            n_1 \norm{e_R}^2 \leq \Psi(R) \leq n_2 \norm{e_R}^2 .
-        \end{align}
-\end{correction}
-and proven in~\Cref{proof:config_error}, as shown here:
-\begin{correction}
-    We show~\cref{item:prop_psi_quadratic} by computing the hessian of \( \Psi \), \( \Hess{\Psi} \),  using the chain rule as 
-    \begin{align*}
-        \Hess \Psi =& \parenth{\mathbf{D}^2 A \cdot \delta^2 R} B + \parenth{\dirDiff{A}{R} }\parenth{\dirDiff{B}{R}}^T \\
-        &+ \parenth{\dirDiff{B}{R} }\parenth{\dirDiff{A}{R}}^T +\parenth{\mathbf{D}^2 B \cdot \delta^2 R} A .
-    \end{align*}
-    The first order derivative of \( A(R) \) and \( B(R) \) are given by~\cref{eqn:eRA,eqn:eRB}. 
-    The hessian of \( A(R) \) is computed as 
-    \begin{align*}
-        \dirDiff{\parenth{\dirDiff{A}{R}}}{R} &= \eta \cdot \frac{1}{2}\parenth{G R_d^T R \delta R - \delta R^T R_d G}^\vee , \\
-        &= \eta \cdot \frac{1}{2} \parenth{G R_d^T R \hat \eta + \hat \eta R^T R_d G}^\vee,\\
-        &= \eta \cdot \frac{1}{2} \bracket{\parenth{\braces{\tr{R^T R_d G} I - R^T R_d G} \eta}^\wedge}^\vee , \\
-        &= \eta \cdot \frac{1}{2} \parenth{\tr{R^T R_d G} I - R^T R_d G}\eta ,
-    \end{align*}
-    where we used the scalar triple product rule, from~\cref{eqn:STP}, to arrive at the final form.
-    The hessian of \( B(R) \) is computed as
-    \begin{align*}
-        \dirDiff{\parenth{\dirDiff{B}{R}}}{R} =& \eta \cdot \left[\frac{\parenth{\delta R^T v}^\wedge r}{\alpha\parenth{r^T R^T v - \cos \theta}} \right. \\
-        & \left. - \frac{\alpha \parenth{R^T v}^\wedge r \parenth{r^T \delta R^T v}}{\alpha^2 \parenth{r^TR^Tv - \cos \theta}^2}   \right] .
-    \end{align*}
-    The term \( \parenth{\delta R^T v}^\wedge r\) is simplified as
-    \begin{align*}
-        \parenth{\delta R^T v}^\wedge r &= - \hat{r} \delta R ^T v , \\
-        &= - \hat{r} \parenth{R \hat \eta}^T v , \\
-        &= \hat{r} \parenth{\hat{\eta} R^T } v , \\
-        &= - \hat{r} \parenth{R^T v}^\wedge \eta ,
-    \end{align*}
-    where we utilized the hat map property from~\cref{eqn:cross_product}.
-    Similarly, the term \( r^t \delta R^T v \) is simplified as
-    \begin{align*}
-        r^T \delta R^T v &= r^T \parenth{-\hat \eta R^T}v , \\
-        &= r^T \parenth{R^T v}^\wedge \eta .
-    \end{align*}
-    The hessian of \( B(R) \) then becomes
-    \begin{align*}
-        \dirDiff{\parenth{\dirDiff{B}{R}}}{R} =& \eta \cdot \left[ - \frac{ \hat r \parenth{R^T v}^\wedge}{\alpha \parenth{r^T R^T v - \cos \theta}} \right. \\ 
-        & \left. - \frac{\parenth{R^T v}^\wedge r r^T \parenth{R^T v}^\wedge }{ \alpha\parenth{r^T R^T v - \cos \theta}^2}  \right] \eta .
-    \end{align*}
-    Using these terms, we evaluate \( \Hess{\Psi} \) at the desired attitude \( R = R_d \) as
-    \begin{align*}
-        \Hess{\Psi} = \eta^T \frac{1}{2} B \parenth{\tr{G}I -  G} \eta , 
-    \end{align*}
-    which is positive definite since \( B > 1\) and \( \sum g_i > g_i\). 
-    From~\cite[Proposition 6.30]{bullo2004}, \( \Psi \) is locally quadratic on the set \( D_1 \) which proves~\cref{item:prop_psi_quadratic}.
-\end{correction}
-
 Subsequently,~\Cref{prop:adaptive_control} was modified to explicitly demonstrate that \( \mathcal{V} \) is positive definite.
@@
 \end{align*}
-    over the domain \( D_3 = D_1 \cap D_2\), which ensures that the properties of~\Cref{prop:config_error,prop:error_dyn} are satisfied.
-
-    From~\Cref{prop:config_error}, the configuration error function is locally quadratic and it is bounded in \( D_3 \) by~\cref{eq:psi_bound}~\cite[Definition 6.28]{bullo2004}.
+over the domain \( D \) in~\cref{eqn:domain}.
+From~\Cref{prop:eR_dot_bound,prop:config_error}, the configuration error function is bounded in \( D \) by
+\begin{align*}
+    b_1 \norm{e_{R_A}}^2 < b_1 \norm{e_{R}}^2 < \Psi < b_2 \norm{e_{R_A}}^2 < b_2 \norm{e_{R}}^2 .
+\end{align*}
 Using this the Lyapunov function \( \mathcal{V} \) is bounded by
@@
     W_1 & = \begin{bmatrix}
-        k_R n_1 & \frac{1}{2} c \lambda_m & 0 \\
+        k_R b_1 & \frac{1}{2} c \lambda_m & 0 \\
         \frac{1}{2} c \lambda_m & \frac{1}{2} \lambda_m & 0 \\
@@
     W_2 & = \begin{bmatrix}
-        k_R n_2 & \frac{1}{2} c \lambda_M & 0 \\
+        k_R b_2 & \frac{1}{2} c \lambda_M & 0 \\
         \frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_M & 0 \\
@@
 If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied then the matrices \( W_1, W_2 \) and \( M \) are positive definite.
-    This implies that $\mathcal{V}$ is positive definite and decrescent, and $\dot{\mathcal{V}}$ is negative semidefinite in the domain $D_3$.
+This implies that $\mathcal{V}$ is positive definite and decrescent, and $\dot{\mathcal{V}}$ is negative semidefinite in the domain $D$.
 As such, the zero equilibrium is stable in the sense of Lyapunov, and all of the error variables are bounded.
@@
 
+Thank you for the helpful suggestion.
 All of the figures have been enlarged and modified to span the entire page rather than a single column. 

### 2017-01-09 manuscript.tex

@@
     where the notation \( \D_R A \) and \(\D_R B\) represents the derivative of \( A \) or \( B \) with respect to \( R\).
-    \item \label{item:prop_psi_quadratic} \( \Psi \) is a locally quadratic function, which means there exists constants \( 0 < n_1 \leq n_2 \) such that
-    \begin{align}\label{eq:psi_bound}
-        n_1 \norm{e_R}^2 \leq \Psi(R) \leq n_2 \norm{e_R}^2 ,
-    \end{align}
-    on the domain
-    \begin{align}\label{eq:psi_quadratic_domain}
-        D_1 = \braces{R \in \SO \vert e_{R} = 0 \iff R = R_d } .
-    \end{align}
 %	\item \label{item:prop_crit}The error function \( \Psi \) is minimized when \(R = R_d\).
@@
 	\end{align*}
+    \item \label{item:prop_psi_quadratic} \( \Psi \) is a locally quadratic function, which means there exists constants \( 0 < n_1 \leq n_2 \) such that
+    \begin{align}\label{eq:psi_bound}
+        n_1 \norm{e_R}^2 \leq \Psi(R) \leq n_2 \norm{e_R}^2 ,
+    \end{align}
+    on the domain \( D \) about the desired attitude \( R_d \)
+    \begin{align}\label{eq:psi_quadratic_domain}
+        D = \braces{R  \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta} .
+    \end{align}
 \end{enumerate}
@@
 \begin{prop}[Bound on \( \bm{\dot{e}_R} \)]\label{prop:eR_dot_bound}
-Consider a domain \( D_2 \) about the desired attitude defined as
-\begin{align}
-	D_2 = \braces{R \in \SO \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta}. \label{eqn:domain}
-\end{align}
-Then the following statements hold:
+Consider the domain \( D \), given in~\cref{prop:config_error}, about the desired attitude, then the following statements hold:
 \begin{enumerate}[(i)]
@@
 which is positive definite since \( B > 1\) and \( \sum g_i > g_i\). 
-From~\cite[Proposition 6.30]{bullo2004}, \( \Psi \) is locally quadratic on the set \( D_1 \) which proves~\cref{item:prop_psi_quadratic}.
+The domain \( D \) is an open neighborhood of the desired attitude \( R_d \).
+More explicitly, the set \( D \) of the metric space \( \parenth{R \in \SO, \Psi(R,R_d)} \) is an open neighborhood of \( R_d \) if there exists an \( \epsilon > 0 \) such that for any \( R \in \SO | \Psi(R,R_d) < \epsilon \), it is also true that \( R \in D \).
+We can ensure that \( D \) is an open neighborhood of \( R_d \) by choosing \( \epsilon = \min \braces{\psi, \Psi(R|r^T R^T v = \beta,R_d)}\).
+The selected domain \( D \) excludes the undesired equilibrium points of \( A(R) \) and the infeasible regions defined by the constraints \( r^T R^T v_i \), i.e.
+the desired attitude should be sufficiently far away from the constraints.
+The single equilibrium point occurs at \( R=R_d\) and results in \( e_R = 0 \) and \( \Psi = A = 0\).
+Therefore, in \( D \) the configuration error function is quadratic and the bounds in~\cref{item:prop_psi_quadratic} are valid~\cite[Proposition 6.30]{bullo2004}.
 
-The desired equilibrium occurs at \( R=R_d\) and results in \( e_R = 0 \) and \( \Psi = A = 0\).
 The proof of \cref{item:prop_era_upbound} is available in~\cite{LeeITCST13}.
@@
 %	However, since the chosen domain is assumed to exclude the constraint this situation is not possible and \( B < \psi \).
-We choose the domain \( D_2 \) to exclude the undesired critical points of \( A(R) \) as well as the infeasible regions defined by the state inequality constraints. 
-Furthermore, one can show that the set \( D_2 \) is an open neighborhood of the desired attitude configuration, \( R_d\).
+We choose the domain \( D \) to exclude the undesired critical points of \( A(R) \) as well as the infeasible regions defined by the state inequality constraints. 
+Furthermore,~\cref{proof:config_error} shows that \(D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
 The proof of the upper bound of \( A(R) \) is given in~\cite{LeeITCST13}.
@@
 \end{align*}
-over the domain \( D_3 = D_1 \cap D_2\), which ensures that the properties of~\Cref{prop:config_error,prop:error_dyn} are satisfied.
-Furthermore, the domain \( D_3 \) is an open neighborhood of the desired attitude.
+over the domain \( D \), defined in~\cref{prop:config_error}. 
+In this set, the properties of~\Cref{prop:config_error,prop:error_dyn} are satisfied.
+Furthermore, the set \( D \) is an open neighborhood of the desired attitude and Lyapunov stability results are valid in this set.
 
-From~\Cref{prop:config_error}, the configuration error function is locally quadratic and it is bounded in \( D_3 \) by~\cref{eq:psi_bound}~\cite[Definition 6.28]{bullo2004}.
+From~\Cref{prop:config_error}, the configuration error function is locally quadratic and it is bounded in \( D \) by~\cref{eq:psi_bound}~\cite[Definition 6.28]{bullo2004}.
 Using this the Lyapunov function \( \mathcal{V} \) is bounded by

### 2017-01-09 Response.tex
Dr. Lee updates on Dropbox

@@
 \usepackage{bm}
-\usepackage{xr-hyper}
+%\usepackage{xr-hyper}
+\usepackage{nameref,zref-xr}
 \usepackage{hyperref}
@@
 
-\externaldocument[]{manuscript}[manuscript.pdf]
+\zexternaldocument{manuscript}
+%\externaldocument[]{manuscript}[manuscript.pdf]
 
@@
 \crefmultiformat{prop}{Propositions~#2#1#3}{ and~#2#1#3}{, #2#1#3}{ and~#2#1#3}
+% Appendix
+\crefformat{appendix}{Appendix~#2#1#3} % no abbreviation for equation numbers
+\Crefformat{appendix}{Appendix~#2#1#3} % no abbreviation for equation numbers
+\crefrangeformat{appendix}{Appendices~#3#1#4--#5#2#6}
+\Crefrangeformat{appendix}{Appendices~#3#1#4--#5#2#6}
+\crefmultiformat{appendix}{Appendices~#2#1#3}{ and~#2#1#3}{, #2#1#3}{ and~#2#1#3}
 
@@
 \begin{correction}
-    The variation of \( B(R) \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
-    \begin{align*}
-        \dirDiff{B}{R} &= \eta \cdot e_{R_{B}} ,
-    \end{align*}
-  where the notation \( \D_R A \) and \(\D_R B\) represents the derivative of \( A \) or \( B \) with respect to \( R\).
+The variation of \( A(R) \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
+	\begin{align}
+		\dirDiff{A}{R} &= \eta \cdot e_{R_A} ,
+	\end{align}
+	where the notation \( \dirDiff{A}{R} \) represents the directional derivative of $A$ with respect to $R$ along $\delta R$.
 	\end{correction}
+
 \item \textit{This is serious.
@@
 
-Lyapunov stability is valid if the given properties of \( V \) are satisfied in an open neighborhood of the desired attitude configuration. 
-The presented details, which are shown in~\Cref{proof:att_control,proof:eR_dot_bound}, are valid in the selected domain \( D \) about the desired attitude.
-Therefore, Lyapunov stability is valid if \( D \) is also an open neighborhood of the desired attitude.
+The stability proof has been improved and several modifications have been included in the manuscript:
+\begin{itemize}
+    \item An additional quadratic property has been derived for \( \Psi \) and shown in~\cref{prop:config_error},
+    \item The quadratic property of \( \Psi \) requires the derivation of the hessian of \( \Psi \) given in~\cref{proof:config_error},
+    \item Additional detail has been included on the set \( D \) and it's properties in~\cref{proof:eR_dot_bound}.
+    \item The Lyapunov function in~\cref{proof:adaptive_control} is shown to be positive definite,
+    \item The revised stability proof includes a modified requirement for the constant \( c \) shown in~\cref{eqn:c_bound},
+\end{itemize}
 
-The set \( D = \braces{R \in \SO \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta} \) of the metric space \( \parenth{R \in \SO, \Psi(R,R_d)} \) is an open neighborhood of \( R_d \) if there exists an \( \epsilon > 0 \) such that for any \( R \in \SO | \Psi(R,R_d) < \epsilon \), it is also true that \( R \in D \).
-The selected domain \( D \) excludes the undesired equilibrium points of \( A(R) \) and the infeasible regions defined by the constraints \( r^T R^T v_i \), i.e.
+The revised manuscript, through Propositions 1 and 4, the several properties of the error function and the error variables are shown in the open neighborhood $D$ of the desired attitude, defined in~\cref{eq:psi_quadratic_domain}.
+Later in the stability proof of Proposition 5, it is shown that the chosen Lyapunov function is positive definite in the same domain $D$, and its time-derivative is negative-semidefinite in $D$.
+As $D$ is an open neighborhood of the desired attitude, the revised manuscript completes the stability proof.
+
+%Here we present the modifications and provide additional detail. 
+%In addition, we duplicate the modifications from the manuscript in this section as well.
+%
+%In order to prove that the Lyapunov function is positive definite an additional quadratic property of the configuration error function was derived.
+%A function \( \psi \) is quadratic on the domain \( D \) about the critical zero \( x_0 \in D \) if there exists two constants \( 0 < b_1 \leq b_2 \) such that
+%\begin{align*}
+%    b_1 \norm{\text{d} \psi}^2 \leq \psi(x) b_2 \leq \norm{\text{d} \psi}^2 ,
+%\end{align*}
+%for all \( x \in D \, \setminus \, x_0\)~\cite[Definition 6.28]{bullo2004}.
+%To show that \( \Psi \) is quadratic we compute the hessian of \( \Psi \) at the desired attitude \( R = R_d \).
+%This additional detail was included in~\cref{prop:config_error}, as shown here:
+%\begin{correction}
+%     \( \Psi \) is a locally quadratic function on the domain 
+%        \begin{align}%\label{eq:psi_quadratic_domain}
+%            D_1 = \braces{R \in \SO \vert \Psi = 0, e_{R} = 0 \iff R = R_d } ,
+%        \end{align}
+%        and it is bounded by constants \( 0 < n_1 \leq n_2 \) as
+%        \begin{align}%\label{eq:psi_bound}
+%            n_1 \norm{e_R}^2 \leq \Psi(R) \leq n_2 \norm{e_R}^2 .
+%        \end{align}
+%\end{correction}
+%and proven in~\Cref{proof:config_error}, as shown here:
+%\begin{correction}
+%    We show~\cref{item:prop_psi_quadratic} by computing the hessian of \( \Psi \), \( \Hess{\Psi} \),  using the chain rule as 
+%    \begin{align*}
+%        \Hess \Psi =& \parenth{\mathbf{D}^2 A \cdot \delta^2 R} B + \parenth{\dirDiff{A}{R} }\parenth{\dirDiff{B}{R}}^T \\
+%        &+ \parenth{\dirDiff{B}{R} }\parenth{\dirDiff{A}{R}}^T +\parenth{\mathbf{D}^2 B \cdot \delta^2 R} A .
+%    \end{align*}
+%    The first order derivative of \( A(R) \) and \( B(R) \) are given by~\cref{eqn:eRA,eqn:eRB}. 
+%    The hessian of \( A(R) \) is computed as 
+%    \begin{align*}
+%        \dirDiff{\parenth{\dirDiff{A}{R}}}{R} &= \eta \cdot \frac{1}{2}\parenth{G R_d^T R \delta R - \delta R^T R_d G}^\vee , \\
+%        &= \eta \cdot \frac{1}{2} \parenth{G R_d^T R \hat \eta + \hat \eta R^T R_d G}^\vee,\\
+%        &= \eta \cdot \frac{1}{2} \bracket{\parenth{\braces{\tr{R^T R_d G} I - R^T R_d G} \eta}^\wedge}^\vee , \\
+%        &= \eta \cdot \frac{1}{2} \parenth{\tr{R^T R_d G} I - R^T R_d G}\eta ,
+%    \end{align*}
+%    where we used the scalar triple product rule, from~\cref{eqn:STP}, to arrive at the final form.
+%    The hessian of \( B(R) \) is computed as
+%    \begin{align*}
+%        \dirDiff{\parenth{\dirDiff{B}{R}}}{R} =& \eta \cdot \left[\frac{\parenth{\delta R^T v}^\wedge r}{\alpha\parenth{r^T R^T v - \cos \theta}} \right. \\
+%        & \left. - \frac{\alpha \parenth{R^T v}^\wedge r \parenth{r^T \delta R^T v}}{\alpha^2 \parenth{r^TR^Tv - \cos \theta}^2}   \right] .
+%    \end{align*}
+%    The term \( \parenth{\delta R^T v}^\wedge r\) is simplified as
+%    \begin{align*}
+%        \parenth{\delta R^T v}^\wedge r &= - \hat{r} \delta R ^T v , \\
+%        &= - \hat{r} \parenth{R \hat \eta}^T v , \\
+%        &= \hat{r} \parenth{\hat{\eta} R^T } v , \\
+%        &= - \hat{r} \parenth{R^T v}^\wedge \eta ,
+%    \end{align*}
+%    where we utilized the hat map property from~\cref{eqn:cross_product}.
+%    Similarly, the term \( r^t \delta R^T v \) is simplified as
+%    \begin{align*}
+%        r^T \delta R^T v &= r^T \parenth{-\hat \eta R^T}v , \\
+%        &= r^T \parenth{R^T v}^\wedge \eta .
+%    \end{align*}
+%    The hessian of \( B(R) \) then becomes
+%    \begin{align*}
+%        \dirDiff{\parenth{\dirDiff{B}{R}}}{R} =& \eta \cdot \left[ - \frac{ \hat r \parenth{R^T v}^\wedge}{\alpha \parenth{r^T R^T v - \cos \theta}} \right. \\ 
+%        & \left. - \frac{\parenth{R^T v}^\wedge r r^T \parenth{R^T v}^\wedge }{ \alpha\parenth{r^T R^T v - \cos \theta}^2}  \right] \eta .
+%    \end{align*}
+%    Using these terms, we evaluate \( \Hess{\Psi} \) at the desired attitude \( R = R_d \) as
+%    \begin{align*}
+%        \Hess{\Psi} = \eta^T \frac{1}{2} B \parenth{\tr{G}I -  G} \eta , 
+%    \end{align*}
+%    which is positive definite since \( B > 1\) and \( \sum g_i > g_i\). 
+%    From~\cite[Proposition 6.30]{bullo2004}, \( \Psi \) is locally quadratic on the set \( D_1 \) which proves~\cref{item:prop_psi_quadratic}.
+%\end{correction}
+%
+%Lyapunov stability is valid if the given properties of \( V \) are satisfied in an open neighborhood of the desired attitude configuration. 
+%The presented details, which are shown in~\Cref{proof:att_control,proof:eR_dot_bound}, are valid in the selected domain \( D \) about the desired attitude.
+%Therefore, Lyapunov stability is valid if \( D \) is also an open neighborhood of the desired attitude.
+%
+%The set 
+%\[ D = \braces{R \in \SO \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta} \]
+%of the metric space \( \parenth{R \in \SO, \Psi(R,R_d)} \) is an open neighborhood of \( R_d \) if there exists an \( \epsilon > 0 \) such that for any \( R \in \SO | \Psi(R,R_d) < \epsilon \), it is also true that \( R \in D \).
+%The selected domain \( D \) excludes the undesired equilibrium points of \( A(R) \) and the infeasible regions defined by the constraints \( r^T R^T v_i \), i.e.
 the desired attitude should be sufficiently far away from the constraints.
-We can ensure that \( D \) is an open neighborhood of \( R_d \) by choosing \( \epsilon = \min \braces{\psi, \Psi(R|r^T R^T v = \beta,R_d)}\).
-Therefore, the given domain \( D \) is an open neighborhood of the desired attitude configuration, \(R_d\), and the Lyapunov stability results are valid in this domain.
-
-The proof of~\Cref{prop:adaptive_control} given in~\Cref{proof:adaptive_control} has been improved. 
-Originally, the positive definiteness of \( \mathcal{V}\) was not explicitly defined. 
-\Cref{prop:eR_dot_bound} has been modified to include additional detail on the upper bound of \( A(R) \) as:
-\begin{correction}
-    Upper bounds of \( A(R) \) and \( B(R) \) are given by
-    \begin{gather}
-        \norm{A} < b_2 \norm{e_{R_A}}^2 = c_A  , \quad \norm{B} < c_B . 
-    \end{gather}
-  where the constant \( b_2\) is given by \( b_2 = \frac{h_1 h_4}{h_5 \parenth{h_1 - \psi}}\) for
-  \begin{align*}
-    h_4 &= \min\braces{g_1 + g_2, g_2 + g_3 , g_3 + g_1} ,\\
-    h_5 &= \min\braces{\parenth{g_1 + g_2}^2,\parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2} .\\
-  \end{align*}
-\end{correction}
-
-The domain \( D \) is chosen to both exclude the undesired critical points of \( A(R)\) as well as the infeasible regions defined by the constraints. 
-In general, this is not a difficult assumption to satisfy as the desired attitude will typically be located far from the constrained regions.
-We have augmented the manuscript with some additional discussion of the chosen domain \( D \) in~\Cref{proof:eR_dot_bound}.
-
-\begin{correction}
-    We choose the domain \( D \) to exclude the undesired critical points of \( A(R) \) as well as the infeasible regions defined by the state inequality constraints. 
-    Furthermore, one can show that the set \( D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
-    The proof of the upper bound of \( A(R) \) is given in~\cite{LeeITCST13}.
-    The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
-    This implies that that both \( A(R) \) and \( B(R) \) are bounded by constants \( c_A c_B < \psi < h_1\).
-    Furthermore, since \( \norm{B} > 1 \) this ensures that \( c_A, c_B < \psi\) and shows~\cref{eqn:AB_bound}.
-\end{correction}
-
-Subsequently,~\Cref{prop:adaptive_control} was modified to explicitly demonstrate that \( \mathcal{V} \) is positive definite.
-\begin{correction}
-    Consider the Lyapunov function \( \mathcal{V} \) given by
-\begin{align*}
-    \mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi + c J e_\Omega \cdot e_R + \frac{1}{2 k_\Delta} e_\Delta \cdot e_\Delta , %\label{eqn:v_adapt}
-\end{align*}
-over the domain \( D \) in~\cref{eqn:domain}.
-From~\Cref{prop:eR_dot_bound,prop:config_error}, the configuration error function is bounded in \( D \) by
-\begin{align*}
-    b_1 \norm{e_{R_A}}^2 < b_1 \norm{e_{R}}^2 < \Psi < b_2 \norm{e_{R_A}}^2 < b_2 \norm{e_{R}}^2 .
-\end{align*}
-Using this the Lyapunov function \( \mathcal{V} \) is bounded by
-\begin{align*} %\label{eqn:v_upper_bound}
-    z^T W_1 z \leq \mathcal{V} \leq z^T W_2 z ,
-\end{align*}
-where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = [\|e_R\|,\|e_\Omega\|,\|e_\Delta\|]^T\in\R^3 \) and the matrices \(W_1,W_2 \in \R^{3 \times 3}\) are given by
-\begin{align*}
-    W_1 & = \begin{bmatrix}
-        k_R b_1 & \frac{1}{2} c \lambda_m & 0 \\
-        \frac{1}{2} c \lambda_m & \frac{1}{2} \lambda_m & 0 \\
-        0 & 0 & \frac{1}{2 k_\Delta}
-    \end{bmatrix},\\
-    W_2 & = \begin{bmatrix}
-        k_R b_2 & \frac{1}{2} c \lambda_M & 0 \\
-        \frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_M & 0 \\
-        0 & 0 & \frac{1}{2 k_\Delta}
-    \end{bmatrix} .
-\end{align*}
-The time derivative of \( \mathcal{V}\) with the control input defined by~\cref{eqn:adaptive_control} is given as
-\begin{align}
-    \dot{\mathcal{V}} =& - k_\Omega e_\Omega^T e_\Omega + \parenth{e_\Omega + c e_R}^T W e_\Delta - k_R c e_R^T e_R \nonumber\\
-    &- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} , \label{eqn:vdot}
-\end{align}
-where we used \( \dot{e}_\Delta = - \dot{\bar{\Delta}} \).
-The terms linearly dependent on \( e_\Delta\) are combined with~\cref{eqn:delta_dot} to yield
-\begin{align*}
-     e_\Delta^T \parenth{W^T \parenth{e_\Omega + c e_R} - \frac{1}{k_\Delta} \dot{\bar{\Delta}}} = 0 . 
-\end{align*}
-Using~\Cref{prop:eR_dot_bound} an upper bound on \( \dot{\mathcal{V}} \) is written as
-\begin{gather*}
-    \dot{\mathcal{V}} \leq -\zeta^T M \zeta ,
-\end{gather*}
-where $\zeta=[\|e_R\|,\|e_\Omega\|]\in\R^2$, and the matrix \( M \in \R^{2 \times 2} \) is 
-\begin{gather*}
-    M = \begin{bmatrix}
-        k_R c & \frac{k_\Omega c}{2} \\
-        \frac{k_\Omega c}{2} & k_\Omega - c \lambda_M H
-    \end{bmatrix} .
-\end{gather*}
-If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied then the matrices \( W_1, W_2 \) and \( M \) are positive definite.
-This implies that $\mathcal{V}$ is positive definite and decrescent, and $\dot{\mathcal{V}}$ is negative semidefinite in the domain $D$.
+%We can ensure that \( D \) is an open neighborhood of \( R_d \) by choosing \( \epsilon = \min \braces{\psi, \Psi(R|r^T R^T v = \beta,R_d)}\).
+%Therefore, the given domain \( D \) is an open neighborhood of the desired attitude configuration, \(R_d\), and the Lyapunov stability results are valid in this domain.
+%
+%\Cref{prop:eR_dot_bound} has been modified to include additional detail on the upper bound of \( A(R) \) as:
+%\begin{correction}
+%    Upper bounds of \( A(R) \) and \( B(R) \) are given by
+%    \begin{gather}
+%        \norm{A} < b_2 \norm{e_{R_A}}^2 = c_A  , \quad \norm{B} < c_B . 
+%    \end{gather}
+%  where the constant \( b_2\) is given by \( b_2 = \frac{h_1 h_4}{h_5 \parenth{h_1 - \psi}}\) for
+%  \begin{align*}
+%    h_4 &= \min\braces{g_1 + g_2, g_2 + g_3 , g_3 + g_1} ,\\
+%    h_5 &= \min\braces{\parenth{g_1 + g_2}^2,\parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2} .\\
+%  \end{align*}
+%\end{correction}
+%
+%The domain \( D \) is chosen to both exclude the undesired critical points of \( A(R)\) as well as the infeasible regions defined by the constraints. 
+%In general, this is not a difficult assumption to satisfy as the desired attitude will typically be located far from the constrained regions.
+%We have augmented the manuscript with some additional discussion of the chosen domain \( D \) in~\Cref{proof:eR_dot_bound}.
+%
+%\begin{correction}
+%    We choose the domain \( D \) to exclude the undesired critical points of \( A(R) \) as well as the infeasible regions defined by the state inequality constraints. 
+%    Furthermore, one can show that the set \( D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
+%    The proof of the upper bound of \( A(R) \) is given in~\cite{LeeITCST13}.
+%    The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
+%    This implies that that both \( A(R) \) and \( B(R) \) are bounded by constants \( c_A c_B < \psi < h_1\).
+%    Furthermore, since \( \norm{B} > 1 \) this ensures that \( c_A, c_B < \psi\) and shows~\cref{eqn:AB_bound}.
+%\end{correction}
+%
+%The proof of~\Cref{prop:adaptive_control} given in~\Cref{proof:adaptive_control} has been improved to explicitly demonstrate that \( \mathcal{V} \) is positive definite.
+%\begin{correction}
+%    Consider the Lyapunov function \( \mathcal{V} \) given by
+%    \begin{align*}
+%    \mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi + c J e_\Omega \cdot e_R + \frac{1}{2 k_\Delta} e_\Delta \cdot e_\Delta , %\label{eqn:v_adapt}
+%    \end{align*}
+%    over the domain \( D_3 = D_1 \cap D_2\), which ensures that the properties of~\Cref{prop:config_error,prop:error_dyn} are satisfied.
+%
+%    From~\Cref{prop:config_error}, the configuration error function is locally quadratic and it is bounded in \( D_3 \) by~\cref{eq:psi_bound}~\cite[Definition 6.28]{bullo2004}.
+%    Using this the Lyapunov function \( \mathcal{V} \) is bounded by
+%    \begin{align*} %\label{eqn:v_upper_bound}
+%    z^T W_1 z \leq \mathcal{V} \leq z^T W_2 z ,
+%    \end{align*}
+%    where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = [\|e_R\|,\|e_\Omega\|,\|e_\Delta\|]^T\in\R^3 \) and the matrices \(W_1,W_2 \in \R^{3 \times 3}\) are given by
+%    \begin{align*}
+%    W_1 & = \begin{bmatrix}
+%        k_R n_1 & \frac{1}{2} c \lambda_m & 0 \\
+%        \frac{1}{2} c \lambda_m & \frac{1}{2} \lambda_m & 0 \\
+%        0 & 0 & \frac{1}{2 k_\Delta}
+%    \end{bmatrix},\\
+%    W_2 & = \begin{bmatrix}
+%        k_R n_2 & \frac{1}{2} c \lambda_M & 0 \\
+%        \frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_M & 0 \\
+%        0 & 0 & \frac{1}{2 k_\Delta}
+%    \end{bmatrix} .
+%    \end{align*}
+%    The time derivative of \( \mathcal{V}\) with the control input defined by~\cref{eqn:adaptive_control} is given as
+%    \begin{align}
+%    \dot{\mathcal{V}} =& - k_\Omega e_\Omega^T e_\Omega + \parenth{e_\Omega + c e_R}^T W e_\Delta - k_R c e_R^T e_R \nonumber\\
+%    &- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} , %\label{eqn:vdot}
+%    \end{align}
+%    where we used \( \dot{e}_\Delta = - \dot{\bar{\Delta}} \).
+%    The terms linearly dependent on \( e_\Delta\) are combined with~\cref{eqn:delta_dot} to yield
+%    \begin{align*}
+%     e_\Delta^T \parenth{W^T \parenth{e_\Omega + c e_R} - \frac{1}{k_\Delta} \dot{\bar{\Delta}}} = 0 . 
+%    \end{align*}
+%    Using~\Cref{prop:eR_dot_bound} an upper bound on \( \dot{\mathcal{V}} \) is written as
+%    \begin{gather*}
+%    \dot{\mathcal{V}} \leq -\zeta^T M \zeta ,
+%    \end{gather*}
+%    where $\zeta=[\|e_R\|,\|e_\Omega\|]\in\R^2$, and the matrix \( M \in \R^{2 \times 2} \) is 
+%    \begin{gather*}
+%    M = \begin{bmatrix}
+%        k_R c & \frac{k_\Omega c}{2} \\
+%        \frac{k_\Omega c}{2} & k_\Omega - c \lambda_M H
+%    \end{bmatrix} .
+%    \end{gather*}
+%    If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied then the matrices \( W_1, W_2 \) and \( M \) are positive definite.
+%    This implies that $\mathcal{V}$ is positive definite and decrescent, and $\dot{\mathcal{V}}$ is negative semidefinite in the domain $D_3$.
 As such, the zero equilibrium is stable in the sense of Lyapunov, and all of the error variables are bounded.
 Furthermore, $\lim_{t\to\infty} \zeta=0$ according to the LaShalle-Yoshizawa theorem~\cite{khalil1996}.
-\end{correction}
+%\end{correction}
+%
+%Finally, the bounds on \( c \), given in~\cref{eqn:c_bound}, have been modified to ensure that \( W_1, W_2\) and \( M \) are all positive definite.
+%\begin{correction}
+%    If \( c \) is chosen such that
+%    \begin{gather}
+%        0 < c < \min \braces{\sqrt{\frac{2 k_R n_1}{\lambda_m}},\sqrt{\frac{2 k_R n_2}{\lambda_M}}, \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H}} .
+%    \end{gather}
+%    the zero equilibrium of the error vectors is stable in the sense of Lyapunov. Furthermore, $e_R,e_\Omega\rightarrow 0$ as $t\rightarrow\infty$, and $\bar\Delta$ is  bounded.
+%\end{correction}
 
-Finally, the bounds on \( c \), given in~\cref{eqn:c_bound}, have been modified to ensure that \( W_1, W_2\) and \( M \) are all positive definite.
-\begin{correction}
-    If \( c \) is chosen such that
-    \begin{gather}
-        0 < c < \min \braces{\sqrt{\frac{2 k_R b_1}{\lambda_m}},\sqrt{\frac{2 k_R b_2}{\lambda_M}}, \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H}} .
-    \end{gather}
-    the zero equilibrium of the error vectors is stable in the sense of Lyapunov. Furthermore, $e_R,e_\Omega\rightarrow 0$ as $t\rightarrow\infty$, and $\bar\Delta$ is  bounded.
-\end{correction}
 \item \textit{Typo in eq. (40).}
@@
 \begin{correction}
-    \begin{gather}
-        0 < c < \min \braces{\sqrt{\frac{2 k_R b_1}{\lambda_m}},\sqrt{\frac{2 k_R b_2}{\lambda_M}}, \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H}} .
-    \end{gather}
+\begin{gather*}
+	0 < c < \min \braces{\sqrt{\frac{2 \lambda_m k_R n_1}{\lambda_M^2}},
+	%\sqrt{\frac{2 k_R n_2}{\lambda_M}}, 
+	\frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H}}. %\label{eqn:c_bound}
+\end{gather*}
 \end{correction}
@@
 
-Thank you for the helpful suggestion.
 All of the figures have been enlarged and modified to span the entire page rather than a single column. 

### 2017-01-09 manuscript.tex
Dr. Lee updates on Dropbox

@@
 	\begin{align}
-		\dirDiff{A}{R} &= \eta \cdot e_{R_A} .
+		\dirDiff{A}{R} &= \eta \cdot e_{R_A} ,
 	\end{align}
+	where the notation \( \dirDiff{A}{R} \) represents the directional derivative of $A$ with respect to $R$ along $\delta R$.
 	\item \label{item:prop_erb} The variation of \( B(R) \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
 	\begin{align}
-		\dirDiff{B}{R} &= \eta \cdot e_{R_{B}} ,
+		\dirDiff{B}{R} &= \eta \cdot e_{R_{B}}.
 	\end{align}
-    where the notation \( \D_R A \) and \(\D_R B\) represents the derivative of \( A \) or \( B \) with respect to \( R\).
+%    where the notation \( \D_R A \) and \(\D_R B\) represents the derivative of \( A \) or \( B \) with respect to \( R\).
 %	\item \label{item:prop_crit}The error function \( \Psi \) is minimized when \(R = R_d\).
@@
 	\end{align*}
-    \item \label{item:prop_psi_quadratic} \( \Psi \) is a locally quadratic function, which means there exists constants \( 0 < n_1 \leq n_2 \) such that
+    \item \label{item:prop_psi_quadratic} \( \Psi \) is a locally quadratic function, which means there exist constants \( 0 < n_1 \leq n_2 \) such that
     \begin{align}\label{eq:psi_bound}
@@
     \end{align}
-    on the domain \( D \) about the desired attitude \( R_d \)
+    on the neighborhood $D$ of the desired attitude \( R_d \)
     \begin{align}\label{eq:psi_quadratic_domain}
-        D = \braces{R  \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta} .
+        D = \braces{R\in\SO  \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta}
     \end{align}
+    for $0<\psi < h_1 $ and $0< \beta<\cos\theta$. 
 \end{enumerate}
@@
 \begin{gather}
-	0 < c < \min \braces{\sqrt{\frac{2 k_R n_1}{\lambda_m}},\sqrt{\frac{2 k_R n_2}{\lambda_M}}, \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H}} , \label{eqn:c_bound}
+	0 < c < \min \braces{\sqrt{\frac{2 \lambda_m k_R n_1}{\lambda_M^2}},
+	%\sqrt{\frac{2 k_R n_2}{\lambda_M}}, 
+	\frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H}} , \label{eqn:c_bound}
 \end{gather}
@@
 %Since the desired attitude, \( R_d \), must lie in the feasible set, i.e., \( r^T R^T v < \cos \theta \), the addition of the repulsive barrier function, \( B \), does not change the minimum value of \( \Psi \).
-We show~\cref{item:prop_psi_quadratic} by computing the hessian of \( \Psi \), \( \Hess{\Psi} \),  using the chain rule as 
+We show~\cref{item:prop_psi_quadratic} by computing the hessian of \( \Psi \), namely \( \Hess(\Psi) \),  using the chain rule as 
 \begin{align*}
-    \Hess \Psi =& \parenth{\mathbf{D}^2 A \cdot \delta^2 R} B + \parenth{\dirDiff{A}{R} }\parenth{\dirDiff{B}{R}}^T \\
-    &+ \parenth{\dirDiff{B}{R} }\parenth{\dirDiff{A}{R}}^T +\parenth{\mathbf{D}^2 B \cdot \delta^2 R} A .
+    \Hess &(\Psi)\cdot (\delta R,\delta R)= (\mathbf{D}_R\parenth{\mathbf{D}_R A \cdot \delta R}\cdot \delta R) B\\
+    & + \parenth{\dirDiff{A}{R} }\parenth{\dirDiff{B}{R}} 
+    + \parenth{\dirDiff{B}{R} }\parenth{\dirDiff{A}{R}}\\ &+(\mathbf{D}_R\parenth{\mathbf{D}_R B \cdot \delta R}\cdot \delta R) A.
 \end{align*}
@@
 \begin{align*}
-    \dirDiff{\parenth{\dirDiff{A}{R}}}{R} &= \eta \cdot \frac{1}{2}\parenth{G R_d^T R \delta R - \delta R^T R_d G}^\vee , \\
+    \dirDiff{\parenth{\dirDiff{A}{R}}}{R} &= \eta \cdot \frac{1}{2}\parenth{G R_d^T \delta R - \delta R^T R_d G}^\vee , \\
     &= \eta \cdot \frac{1}{2} \parenth{G R_d^T R \hat \eta + \hat \eta R^T R_d G}^\vee,\\
@@
     \dirDiff{\parenth{\dirDiff{B}{R}}}{R} =& \eta \cdot \left[\frac{\parenth{\delta R^T v}^\wedge r}{\alpha\parenth{r^T R^T v - \cos \theta}} \right. \\
-    & \left. - \frac{\alpha \parenth{R^T v}^\wedge r \parenth{r^T \delta R^T v}}{\alpha^2 \parenth{r^TR^Tv - \cos \theta}^2}   \right] .
+    & \left. - \frac{\parenth{R^T v}^\wedge r \parenth{r^T \delta R^T v}}{\alpha \parenth{r^TR^Tv - \cos \theta}^2}   \right] .
 \end{align*}
@@
 \end{align*}
-Using these terms, we evaluate \( \Hess{\Psi} \) at the desired attitude \( R = R_d \) as
+Using these terms, we evaluate \( \Hess{\Psi} \) at the desired attitude \( R = R_d \) as follows. Since $A=0$ and $\mathbf{D}_R A=0$ at $R=R_d$, 
 \begin{align*}
-    \Hess{\Psi} = \eta^T \frac{1}{2} B \parenth{\tr{G}I -  G} \eta , 
+    \Hess(\Psi)\cdot (\delta R,\delta R)\big|_{R=R_d} = \eta^T \frac{1}{2} B \parenth{\tr{G}I -  G} \eta , 
 \end{align*}
@@
 %	However, since the chosen domain is assumed to exclude the constraint this situation is not possible and \( B < \psi \).
-We choose the domain \( D \) to exclude the undesired critical points of \( A(R) \) as well as the infeasible regions defined by the state inequality constraints. 
-Furthermore,~\cref{proof:config_error} shows that \(D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
-The proof of the upper bound of \( A(R) \) is given in~\cite{LeeITCST13}.
+%We choose the domain \( D \) to exclude the undesired critical points of \( A(R) \) as well as the infeasible regions defined by the state inequality constraints. 
+%Furthermore,~\cref{proof:config_error} shows that \(D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
+%The proof of the upper bound of \( A(R) \) is given in~\cite{LeeITCST13}.
+
+Consider the open neighborhood $D$ of $R=R_d$ defined in~\cref{proof:config_error} The proof of the upper bound of \( A(R) \) is given in~\cite{LeeITCST13}.
 The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
@@
 In this set, the properties of~\Cref{prop:config_error,prop:error_dyn} are satisfied.
-Furthermore, the set \( D \) is an open neighborhood of the desired attitude and Lyapunov stability results are valid in this set.
+%Furthermore, the set \( D \) is an open neighborhood of the desired attitude and Lyapunov stability results are valid in this set.
 
-From~\Cref{prop:config_error}, the configuration error function is locally quadratic and it is bounded in \( D \) by~\cref{eq:psi_bound}~\cite[Definition 6.28]{bullo2004}.
-Using this the Lyapunov function \( \mathcal{V} \) is bounded by
+From~\Cref{prop:config_error}, the configuration error function is locally quadratic and it is bounded in \( D \) by~\cref{eq:psi_bound}.
+Using this, the Lyapunov function \( \mathcal{V} \) is bounded by
 \begin{align*} %\label{eqn:v_upper_bound}
@@
 	W_1 & = \begin{bmatrix}
-		k_R n_1 & \frac{1}{2} c \lambda_m & 0 \\
-		\frac{1}{2} c \lambda_m & \frac{1}{2} \lambda_m & 0 \\
+		k_R n_1 & -\frac{1}{2} c \lambda_M & 0 \\
+		-\frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_m & 0 \\
 		0 & 0 & \frac{1}{2 k_\Delta}
@@
 \end{align*}
+%\begin{gather*}
+%\frac{1}{2}\lambda_m k_R n_1 - \frac{1}{4}c^2 \lambda_M^2 >0\\
+%\frac{2\lambda_m k_R n_1}{\lambda_M^2} > c^2 \\
+%\end{gather*}
 The time derivative of \( \mathcal{V}\) with the control input defined by~\cref{eqn:adaptive_control} is given as
@@
 \end{align*}
-Using~\Cref{prop:eR_dot_bound} an upper bound on \( \dot{\mathcal{V}} \) is written as
+Using~\Cref{prop:eR_dot_bound}, an upper bound on \( \dot{\mathcal{V}} \) is written as
 \begin{gather*}
@@
 \end{gather*}
+%\begin{gather*}
+%k_R c (k_\Omega -c \lambda_M H) -\frac{1}{4}k_\Omega^2 c^2 < 0\\
+%k_R (k_\Omega -c \lambda_M H) -\frac{1}{4}k_\Omega^2 c < 0\\
+%4k_R k_\Omega -c(4k_R \lambda_M H +k_\Omega^2) <0
+%\end{gather*}
+
 If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied then the matrices \( W_1, W_2 \) and \( M \) are positive definite.
-This implies that $\mathcal{V}$ is positive definite and decrescent, and $\dot{\mathcal{V}}$ is negative semidefinite in the domain $D_3$.
+This implies that $\mathcal{V}$ is positive definite and decrescent, and $\dot{\mathcal{V}}$ is negative semidefinite in the domain $D$.
 As such, the zero equilibrium is stable in the sense of Lyapunov, and all of the error variables are bounded.

### 2017-01-09 Response.tex
Use xr-hyper for cross referencing. even though it doesn't really work well.
Fix labels in reviewer comments

@@
 \usepackage{bm}
-%\usepackage{xr-hyper}
-\usepackage{nameref,zref-xr}
+\usepackage{xr-hyper}
+% \usepackage{nameref,zref-xr}
 \usepackage{hyperref}
@@
 
-\zexternaldocument{manuscript}
-%\externaldocument[]{manuscript}[manuscript.pdf]
+% \zexternaldocument{manuscript}
+\externaldocument[]{manuscript}[manuscript.pdf]
 
@@
 \begin{enumerate}
-\item \textit{Please give a precise definition of variation used in the paper, e.g., eq. (17) and (18)}
+\item \textit{Please give a precise definition of variation used in the paper, e.g.,~\cref{eq:dirDiff_A,eq:dirDiff_B}}
 
@@
 \item \textit{This is serious.
-In section 2, the upper bounds listed in Proposition 4 are given.
+In~\cref{sec:attitude_control}, the upper bounds listed in~\cref{prop:eR_dot_bound} are given.
 Well, these should be the properties that your controller guarantees not come from the set D you've defined.
-Since these properties are used to derive the bound H which is used to derive the result in Proposition 5, the stability proof under the proposed controller is far from complete.}
+Since these properties are used to derive the bound H which is used to derive the result in~\cref{prop:adaptive_control}, the stability proof under the proposed controller is far from complete.}
 
@@
 
-\item \textit{Abuse of notation 'hat' and 'vee' in equations (6)-(8)}
+\item \textit{Abuse of notation 'hat' and 'vee' in~\crefrange{eqn:hatxy}{eqn:xAAx}}
 
@@
 
-\item \textit{The units of y axis of Figures 1 - 3 and 5 should be mentioned in the manuscript.}
+\item \textit{The units of y axis of~\Cref{fig:config_error,fig:con,fig:adapt,fig:tv,fig:exp} should be mentioned in the manuscript.}
 
@@
 All of the figures have been enlarged and modified to span the entire page rather than a single column. 
-In addition, the captions of~\cref{fig:config_error,fig:adapt,fig:con,fig:tv} have been modified to mention the fact that they are plotting the components of a vector in a single plot or using a subplot.
+In addition, the captions of~\Cref{fig:config_error,fig:adapt,fig:con,fig:tv,fig:exp} have been modified to mention the fact that they are plotting the components of a vector in a single plot or using a subplot.
 \end{enumerate}

### 2017-01-09 Response.tex
Remove all the commented out excerpts from the manuscript

@@
 
-The revised manuscript, through Propositions 1 and 4, the several properties of the error function and the error variables are shown in the open neighborhood $D$ of the desired attitude, defined in~\cref{eq:psi_quadratic_domain}.
-Later in the stability proof of Proposition 5, it is shown that the chosen Lyapunov function is positive definite in the same domain $D$, and its time-derivative is negative-semidefinite in $D$.
+The revised manuscript, through~\cref{prop:config_error,prop:adaptive_control}, demonstrates several properties of the error function and the error variables which are shown in the open neighborhood $D$ of the desired attitude, defined in~\cref{eq:psi_quadratic_domain}.
+Later in the stability proof of~\cref{prop:adaptive_control}, it is shown that the chosen Lyapunov function is positive definite in the same domain $D$, and its time-derivative is negative-semidefinite in $D$.
 As $D$ is an open neighborhood of the desired attitude, the revised manuscript completes the stability proof.
 
-%Here we present the modifications and provide additional detail. 
-%In addition, we duplicate the modifications from the manuscript in this section as well.
-%
-%In order to prove that the Lyapunov function is positive definite an additional quadratic property of the configuration error function was derived.
-%A function \( \psi \) is quadratic on the domain \( D \) about the critical zero \( x_0 \in D \) if there exists two constants \( 0 < b_1 \leq b_2 \) such that
-%\begin{align*}
-%    b_1 \norm{\text{d} \psi}^2 \leq \psi(x) b_2 \leq \norm{\text{d} \psi}^2 ,
-%\end{align*}
-%for all \( x \in D \, \setminus \, x_0\)~\cite[Definition 6.28]{bullo2004}.
-%To show that \( \Psi \) is quadratic we compute the hessian of \( \Psi \) at the desired attitude \( R = R_d \).
-%This additional detail was included in~\cref{prop:config_error}, as shown here:
-%\begin{correction}
-%     \( \Psi \) is a locally quadratic function on the domain 
-%        \begin{align}%\label{eq:psi_quadratic_domain}
-%            D_1 = \braces{R \in \SO \vert \Psi = 0, e_{R} = 0 \iff R = R_d } ,
-%        \end{align}
-%        and it is bounded by constants \( 0 < n_1 \leq n_2 \) as
-%        \begin{align}%\label{eq:psi_bound}
-%            n_1 \norm{e_R}^2 \leq \Psi(R) \leq n_2 \norm{e_R}^2 .
-%        \end{align}
-%\end{correction}
-%and proven in~\Cref{proof:config_error}, as shown here:
-%\begin{correction}
-%    We show~\cref{item:prop_psi_quadratic} by computing the hessian of \( \Psi \), \( \Hess{\Psi} \),  using the chain rule as 
-%    \begin{align*}
-%        \Hess \Psi =& \parenth{\mathbf{D}^2 A \cdot \delta^2 R} B + \parenth{\dirDiff{A}{R} }\parenth{\dirDiff{B}{R}}^T \\
-%        &+ \parenth{\dirDiff{B}{R} }\parenth{\dirDiff{A}{R}}^T +\parenth{\mathbf{D}^2 B \cdot \delta^2 R} A .
-%    \end{align*}
-%    The first order derivative of \( A(R) \) and \( B(R) \) are given by~\cref{eqn:eRA,eqn:eRB}. 
-%    The hessian of \( A(R) \) is computed as 
-%    \begin{align*}
-%        \dirDiff{\parenth{\dirDiff{A}{R}}}{R} &= \eta \cdot \frac{1}{2}\parenth{G R_d^T R \delta R - \delta R^T R_d G}^\vee , \\
-%        &= \eta \cdot \frac{1}{2} \parenth{G R_d^T R \hat \eta + \hat \eta R^T R_d G}^\vee,\\
-%        &= \eta \cdot \frac{1}{2} \bracket{\parenth{\braces{\tr{R^T R_d G} I - R^T R_d G} \eta}^\wedge}^\vee , \\
-%        &= \eta \cdot \frac{1}{2} \parenth{\tr{R^T R_d G} I - R^T R_d G}\eta ,
-%    \end{align*}
-%    where we used the scalar triple product rule, from~\cref{eqn:STP}, to arrive at the final form.
-%    The hessian of \( B(R) \) is computed as
-%    \begin{align*}
-%        \dirDiff{\parenth{\dirDiff{B}{R}}}{R} =& \eta \cdot \left[\frac{\parenth{\delta R^T v}^\wedge r}{\alpha\parenth{r^T R^T v - \cos \theta}} \right. \\
-%        & \left. - \frac{\alpha \parenth{R^T v}^\wedge r \parenth{r^T \delta R^T v}}{\alpha^2 \parenth{r^TR^Tv - \cos \theta}^2}   \right] .
-%    \end{align*}
-%    The term \( \parenth{\delta R^T v}^\wedge r\) is simplified as
-%    \begin{align*}
-%        \parenth{\delta R^T v}^\wedge r &= - \hat{r} \delta R ^T v , \\
-%        &= - \hat{r} \parenth{R \hat \eta}^T v , \\
-%        &= \hat{r} \parenth{\hat{\eta} R^T } v , \\
-%        &= - \hat{r} \parenth{R^T v}^\wedge \eta ,
-%    \end{align*}
-%    where we utilized the hat map property from~\cref{eqn:cross_product}.
-%    Similarly, the term \( r^t \delta R^T v \) is simplified as
-%    \begin{align*}
-%        r^T \delta R^T v &= r^T \parenth{-\hat \eta R^T}v , \\
-%        &= r^T \parenth{R^T v}^\wedge \eta .
-%    \end{align*}
-%    The hessian of \( B(R) \) then becomes
-%    \begin{align*}
-%        \dirDiff{\parenth{\dirDiff{B}{R}}}{R} =& \eta \cdot \left[ - \frac{ \hat r \parenth{R^T v}^\wedge}{\alpha \parenth{r^T R^T v - \cos \theta}} \right. \\ 
-%        & \left. - \frac{\parenth{R^T v}^\wedge r r^T \parenth{R^T v}^\wedge }{ \alpha\parenth{r^T R^T v - \cos \theta}^2}  \right] \eta .
-%    \end{align*}
-%    Using these terms, we evaluate \( \Hess{\Psi} \) at the desired attitude \( R = R_d \) as
-%    \begin{align*}
-%        \Hess{\Psi} = \eta^T \frac{1}{2} B \parenth{\tr{G}I -  G} \eta , 
-%    \end{align*}
-%    which is positive definite since \( B > 1\) and \( \sum g_i > g_i\). 
-%    From~\cite[Proposition 6.30]{bullo2004}, \( \Psi \) is locally quadratic on the set \( D_1 \) which proves~\cref{item:prop_psi_quadratic}.
-%\end{correction}
-%
-%Lyapunov stability is valid if the given properties of \( V \) are satisfied in an open neighborhood of the desired attitude configuration. 
-%The presented details, which are shown in~\Cref{proof:att_control,proof:eR_dot_bound}, are valid in the selected domain \( D \) about the desired attitude.
-%Therefore, Lyapunov stability is valid if \( D \) is also an open neighborhood of the desired attitude.
-%
-%The set 
-%\[ D = \braces{R \in \SO \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta} \]
-%of the metric space \( \parenth{R \in \SO, \Psi(R,R_d)} \) is an open neighborhood of \( R_d \) if there exists an \( \epsilon > 0 \) such that for any \( R \in \SO | \Psi(R,R_d) < \epsilon \), it is also true that \( R \in D \).
-%The selected domain \( D \) excludes the undesired equilibrium points of \( A(R) \) and the infeasible regions defined by the constraints \( r^T R^T v_i \), i.e.
-the desired attitude should be sufficiently far away from the constraints.
-%We can ensure that \( D \) is an open neighborhood of \( R_d \) by choosing \( \epsilon = \min \braces{\psi, \Psi(R|r^T R^T v = \beta,R_d)}\).
-%Therefore, the given domain \( D \) is an open neighborhood of the desired attitude configuration, \(R_d\), and the Lyapunov stability results are valid in this domain.
-%
-%\Cref{prop:eR_dot_bound} has been modified to include additional detail on the upper bound of \( A(R) \) as:
-%\begin{correction}
-%    Upper bounds of \( A(R) \) and \( B(R) \) are given by
-%    \begin{gather}
-%        \norm{A} < b_2 \norm{e_{R_A}}^2 = c_A  , \quad \norm{B} < c_B . 
-%    \end{gather}
-%  where the constant \( b_2\) is given by \( b_2 = \frac{h_1 h_4}{h_5 \parenth{h_1 - \psi}}\) for
-%  \begin{align*}
-%    h_4 &= \min\braces{g_1 + g_2, g_2 + g_3 , g_3 + g_1} ,\\
-%    h_5 &= \min\braces{\parenth{g_1 + g_2}^2,\parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2} .\\
-%  \end{align*}
-%\end{correction}
-%
-%The domain \( D \) is chosen to both exclude the undesired critical points of \( A(R)\) as well as the infeasible regions defined by the constraints. 
-%In general, this is not a difficult assumption to satisfy as the desired attitude will typically be located far from the constrained regions.
-%We have augmented the manuscript with some additional discussion of the chosen domain \( D \) in~\Cref{proof:eR_dot_bound}.
-%
-%\begin{correction}
-%    We choose the domain \( D \) to exclude the undesired critical points of \( A(R) \) as well as the infeasible regions defined by the state inequality constraints. 
-%    Furthermore, one can show that the set \( D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
-%    The proof of the upper bound of \( A(R) \) is given in~\cite{LeeITCST13}.
-%    The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
-%    This implies that that both \( A(R) \) and \( B(R) \) are bounded by constants \( c_A c_B < \psi < h_1\).
-%    Furthermore, since \( \norm{B} > 1 \) this ensures that \( c_A, c_B < \psi\) and shows~\cref{eqn:AB_bound}.
-%\end{correction}
-%
-%The proof of~\Cref{prop:adaptive_control} given in~\Cref{proof:adaptive_control} has been improved to explicitly demonstrate that \( \mathcal{V} \) is positive definite.
-%\begin{correction}
-%    Consider the Lyapunov function \( \mathcal{V} \) given by
-%    \begin{align*}
-%    \mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi + c J e_\Omega \cdot e_R + \frac{1}{2 k_\Delta} e_\Delta \cdot e_\Delta , %\label{eqn:v_adapt}
-%    \end{align*}
-%    over the domain \( D_3 = D_1 \cap D_2\), which ensures that the properties of~\Cref{prop:config_error,prop:error_dyn} are satisfied.
-%
-%    From~\Cref{prop:config_error}, the configuration error function is locally quadratic and it is bounded in \( D_3 \) by~\cref{eq:psi_bound}~\cite[Definition 6.28]{bullo2004}.
-%    Using this the Lyapunov function \( \mathcal{V} \) is bounded by
-%    \begin{align*} %\label{eqn:v_upper_bound}
-%    z^T W_1 z \leq \mathcal{V} \leq z^T W_2 z ,
-%    \end{align*}
-%    where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = [\|e_R\|,\|e_\Omega\|,\|e_\Delta\|]^T\in\R^3 \) and the matrices \(W_1,W_2 \in \R^{3 \times 3}\) are given by
-%    \begin{align*}
-%    W_1 & = \begin{bmatrix}
-%        k_R n_1 & \frac{1}{2} c \lambda_m & 0 \\
-%        \frac{1}{2} c \lambda_m & \frac{1}{2} \lambda_m & 0 \\
-%        0 & 0 & \frac{1}{2 k_\Delta}
-%    \end{bmatrix},\\
-%    W_2 & = \begin{bmatrix}
-%        k_R n_2 & \frac{1}{2} c \lambda_M & 0 \\
-%        \frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_M & 0 \\
-%        0 & 0 & \frac{1}{2 k_\Delta}
-%    \end{bmatrix} .
-%    \end{align*}
-%    The time derivative of \( \mathcal{V}\) with the control input defined by~\cref{eqn:adaptive_control} is given as
-%    \begin{align}
-%    \dot{\mathcal{V}} =& - k_\Omega e_\Omega^T e_\Omega + \parenth{e_\Omega + c e_R}^T W e_\Delta - k_R c e_R^T e_R \nonumber\\
-%    &- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} , %\label{eqn:vdot}
-%    \end{align}
-%    where we used \( \dot{e}_\Delta = - \dot{\bar{\Delta}} \).
-%    The terms linearly dependent on \( e_\Delta\) are combined with~\cref{eqn:delta_dot} to yield
-%    \begin{align*}
-%     e_\Delta^T \parenth{W^T \parenth{e_\Omega + c e_R} - \frac{1}{k_\Delta} \dot{\bar{\Delta}}} = 0 . 
-%    \end{align*}
-%    Using~\Cref{prop:eR_dot_bound} an upper bound on \( \dot{\mathcal{V}} \) is written as
-%    \begin{gather*}
-%    \dot{\mathcal{V}} \leq -\zeta^T M \zeta ,
-%    \end{gather*}
-%    where $\zeta=[\|e_R\|,\|e_\Omega\|]\in\R^2$, and the matrix \( M \in \R^{2 \times 2} \) is 
-%    \begin{gather*}
-%    M = \begin{bmatrix}
-%        k_R c & \frac{k_\Omega c}{2} \\
-%        \frac{k_\Omega c}{2} & k_\Omega - c \lambda_M H
-%    \end{bmatrix} .
-%    \end{gather*}
-%    If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied then the matrices \( W_1, W_2 \) and \( M \) are positive definite.
-%    This implies that $\mathcal{V}$ is positive definite and decrescent, and $\dot{\mathcal{V}}$ is negative semidefinite in the domain $D_3$.
-As such, the zero equilibrium is stable in the sense of Lyapunov, and all of the error variables are bounded.
-Furthermore, $\lim_{t\to\infty} \zeta=0$ according to the LaShalle-Yoshizawa theorem~\cite{khalil1996}.
-%\end{correction}
-%
-%Finally, the bounds on \( c \), given in~\cref{eqn:c_bound}, have been modified to ensure that \( W_1, W_2\) and \( M \) are all positive definite.
-%\begin{correction}
-%    If \( c \) is chosen such that
-%    \begin{gather}
-%        0 < c < \min \braces{\sqrt{\frac{2 k_R n_1}{\lambda_m}},\sqrt{\frac{2 k_R n_2}{\lambda_M}}, \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H}} .
-%    \end{gather}
-%    the zero equilibrium of the error vectors is stable in the sense of Lyapunov. Furthermore, $e_R,e_\Omega\rightarrow 0$ as $t\rightarrow\infty$, and $\bar\Delta$ is  bounded.
-%\end{correction}
-
-\item \textit{Typo in eq. (40).}
+\item \textit{Typo in~\cref{eqn:c_bound}}
 

### 2017-01-10 manuscript.tex
Fix labels in reviewer comments
Correct some typos

@@
 \squeezeup
-\section{Attitude Control on $\SO$ with Inequality Constraints}
+\section{Attitude Control on $\SO$ with Inequality Constraints}\label{sec:attitude_control}
 
@@
 \begin{gather}
-	\Psi(R) = A(R) B(R) , \label{eqn:psi} \\
-	e_R = e_{R_A} B(R) + A(R) e_{R_B} , \label{eqn:eR} \\
+	\Psi(R, R_d) = A(R, R_d) B(R) , \label{eqn:psi} \\
+	e_R = e_{R_A} B(R) + A(R,R_d) e_{R_B} , \label{eqn:eR} \\
 	e_\Omega = \Omega , \label{eqn:eW}
@@
 \begin{gather}
-	A(R) = \frac{1}{2} \tr{G \left( I - R_d^T R\right)} , \label{eqn:A} \\
+	A(R,R_d) = \frac{1}{2} \tr{G \left( I - R_d^T R\right)} , \label{eqn:A} \\
 	B(R) = 1 - \frac{1}{\alpha} \ln \left( \frac{\cos \theta -  r^T R^T v}{1 + \cos \theta}\right) . \label{eqn:B} \\
@@
 	\item \label{item:prop_era}The variation of \( A(R) \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
-	\begin{align}
+	\begin{align}\label{eq:dirDiff_A}
 		\dirDiff{A}{R} &= \eta \cdot e_{R_A} ,
@@
 	\item \label{item:prop_erb} The variation of \( B(R) \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
-	\begin{align}
+	\begin{align}\label{eq:dirDiff_B}
 		\dirDiff{B}{R} &= \eta \cdot e_{R_{B}}.
@@
 We introduce a nonlinear geometric controller for the attitude stabilization of a rigid body.
-We first assume that there is no disturbance, i.e., \( \Delta = 0 \) and present a nonlinear controller in~\Cref{prop:att_control}.
+We first assume that there is no disturbance, i.e., \( \Delta = 0 \), and present a nonlinear controller in~\Cref{prop:att_control}.
 \begin{prop}[Attitude Control]\label{prop:att_control}
@@
 \begin{prop}[Bound on \( \bm{\dot{e}_R} \)]\label{prop:eR_dot_bound}
-Consider the domain \( D \), given in~\cref{prop:config_error}, about the desired attitude, then the following statements hold:
+Consider the neighborhood \( D \), given in~\cref{prop:config_error}, about the desired attitude, then the following statements hold:
 \begin{enumerate}[(i)]
@@
 where \( s_i, c_i \) represent \( \sin \theta_i, \cos \theta_i \) for \( i = \braces{1,2,3}\).
-Using this representation that kinematic differential equations for the associated Euler angles are given as
+Using this representation, the kinematic differential equations for the associated Euler angles are given as
 \begin{align}\label{eq:euler313_diff}
@@
 The form of the uncertainty, given in~\cref{eqn:Wdot}, is commonly used in the adaptive control literature~\cite{LeeITCST13,ioannou2012}. 
-A wide variety of realistic disturbances, such as gravitational gradients or malfunctioning thrusters, are accurately represented via this model. 
+A wide variety of realistic disturbances, such as gravitational gradients or malfunctioning thrusters for spacecraft scenarios, are accurately represented via this model. 
 In addition, it is possible to represent the uncertainty of a time-varying inertia matrix as an equivalent external disturbance. 
-For example, Euler's law gives the relationship for the rate of change of angular momentum
+For example, Euler's law gives the relationship for the rate of change of angular momentum as
 \begin{align*}
@@
 This results in the UAV performing a \ang{90} yaw rotation about the vertical axis of the spherical joint and the constrained region is on the shortest path connecting $R_0$ and $R_d$. 
-The attitude control system is identical to the one presented in~\Cref{prop:adaptive_control} with the exception of a gravity moment term and the following parameters: \(k_R = 0.4, k_\Omega = 0.7 ,c = 0.1 , \alpha = 8 \text{ and } k_\Delta = 0.05\).
-The parameters are modified to account for the differences in the hardware model of the hexrotor.
+The attitude control system is identical to the one presented in~\Cref{prop:adaptive_control} with the exception of a gravity moment term, \( M_g = r_{cg} \times m g R^T e_3\) which represents the gravitational moment due to the difference between the center of mass and the center of rotation.
+In addition, the following parameters were also modified: \(k_R = 0.4, k_\Omega = 0.7 ,c = 0.1 , \alpha = 8 \text{ and } k_\Delta = 0.05\) to account for the differences in the hardware model of the hexrotor.
 
@@
 \begin{align*}
-    \Hess(\Psi)\cdot (\delta R,\delta R)\big|_{R=R_d} = \eta^T \frac{1}{2} B \parenth{\tr{G}I -  G} \eta , 
+    \Hess(\Psi)\cdot (\delta R,\delta R)\big|_{R=R_d} = \eta \cdot \frac{1}{2} B \parenth{\tr{G}I -  G} \eta , 
 \end{align*}
@@
 \subsection{Proof of~\Cref{prop:error_dyn}}\label{proof:error_dyn}
-From the kinematics~\cref{eqn:Rdot} and noting that \( \dot{R}_d = 0 \) the time derivative of \( R_d^T R \) is given as
+From the kinematics~\cref{eqn:Rdot}, and noting that \( \dot{R}_d = 0 \) the time derivative of \( R_d^T R \) is given as
 \begin{gather*}
@@
 
-Consider the open neighborhood $D$ of $R=R_d$ defined in~\cref{proof:config_error} The proof of the upper bound of \( A(R) \) is given in~\cite{LeeITCST13}.
+Consider the open neighborhood $D$ of $R=R_d$ defined in~\Cref{prop:config_error}.
+The proof of the upper bound of \( A(R) \) is given in~\cite{LeeITCST13}.
 The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
@@
 
-Next, we show~~\cref{eqn:E_bound,eqn:F_bound} using the Frobenius norm.
+Next, we show~\cref{eqn:E_bound,eqn:F_bound} using the Frobenius norm.
 The Frobenius norm \( \norm{E}_F \) is given in~\cite{LeeITCST13} as

### 2017-01-10 manuscript.tex
Clear up neighborhood discussion

@@
 The domain \( D \) is an open neighborhood of the desired attitude \( R_d \).
-More explicitly, the set \( D \) of the metric space \( \parenth{R \in \SO, \Psi(R,R_d)} \) is an open neighborhood of \( R_d \) if there exists an \( \epsilon > 0 \) such that for any \( R \in \SO | \Psi(R,R_d) < \epsilon \), it is also true that \( R \in D \).
-We can ensure that \( D \) is an open neighborhood of \( R_d \) by choosing \( \epsilon = \min \braces{\psi, \Psi(R|r^T R^T v = \beta,R_d)}\).
 The selected domain \( D \) excludes the undesired equilibrium points of \( A(R) \) and the infeasible regions defined by the constraints \( r^T R^T v_i \), i.e.
 the desired attitude should be sufficiently far away from the constraints.
-The single equilibrium point occurs at \( R=R_d\) and results in \( e_R = 0 \) and \( \Psi = A = 0\).
+As a result, the single equilibrium point in \( D \)occurs at \( R=R_d\) and results in \( e_R = 0 \) and \( \Psi = A = 0\).
 Therefore, in \( D \) the configuration error function is quadratic and the bounds in~\cref{item:prop_psi_quadratic} are valid~\cite[Proposition 6.30]{bullo2004}.

### 2017-01-13 Response.tex
Correct some typos
Add comments from Dr. Lee

@@
     \item The quadratic property of \( \Psi \) requires the derivation of the hessian of \( \Psi \) given in~\cref{proof:config_error},
-    \item Additional detail has been included on the set \( D \) and it's properties in~\cref{proof:eR_dot_bound}.
+    \item Additional detail has been included on the set \( D \) and it's properties in~\cref{proof:config_error}.
     \item The Lyapunov function in~\cref{proof:adaptive_control} is shown to be positive definite,
@@
 
-The revised manuscript, through~\cref{prop:config_error,prop:adaptive_control}, demonstrates several properties of the error function and the error variables which are shown in the open neighborhood $D$ of the desired attitude, defined in~\cref{eq:psi_quadratic_domain}.
+The revised manuscript, through~\cref{prop:config_error,prop:adaptive_control}, demonstrates several properties of the error function and the error variables in the open neighborhood $D$ of the desired attitude, defined in~\cref{eq:psi_quadratic_domain}.
 Later in the stability proof of~\cref{prop:adaptive_control}, it is shown that the chosen Lyapunov function is positive definite in the same domain $D$, and its time-derivative is negative-semidefinite in $D$.
-As $D$ is an open neighborhood of the desired attitude, the revised manuscript completes the stability proof.
+As $D$ is an open neighborhood of the desired attitude, and it is consistently used for all of properties of the error functions and the stability analysis, the revised manuscript completes the stability proof.
 

### 2017-01-13 manuscript.tex
Fix space
Add comments from Dr. Lee

@@
 which is positive definite since \( B > 1\) and \( \sum g_i > g_i\). 
-The domain \( D \) is an open neighborhood of the desired attitude \( R_d \).
-The selected domain \( D \) excludes the undesired equilibrium points of \( A(R) \) and the infeasible regions defined by the constraints \( r^T R^T v_i \), i.e.
-the desired attitude should be sufficiently far away from the constraints.
-As a result, the single equilibrium point in \( D \)occurs at \( R=R_d\) and results in \( e_R = 0 \) and \( \Psi = A = 0\).
-Therefore, in \( D \) the configuration error function is quadratic and the bounds in~\cref{item:prop_psi_quadratic} are valid~\cite[Proposition 6.30]{bullo2004}.
+The domain \( D \) is an open neighborhood of the desired attitude \( R_d \), and it excludes the undesired equilibrium points of \( A(R) \) and the infeasible regions defined by the constraints \( r^T R^T v_i \).
+Therefore, the only critical point of the error function $\Psi$ in the domain $D$ correspond to the desired attitude $R=R_d$ with $e_R=0$ and $\Psi=0$. 
+Therefore, in \( D \) the configuration error function is quadratic and the bounds in~\cref{item:prop_psi_quadratic} are valid according to~\cite[Proposition 6.30]{bullo2004}.
 

### 2017-01-13 Response.tex
Fix some small typos

@@
     \item The quadratic property of \( \Psi \) requires the derivation of the hessian of \( \Psi \) given in~\cref{proof:config_error},
-    \item Additional detail has been included on the set \( D \) and it's properties in~\cref{proof:config_error}.
+    \item Additional detail has been included on the set \( D \) and it's properties in~\cref{proof:config_error},
     \item The Lyapunov function in~\cref{proof:adaptive_control} is shown to be positive definite,
-    \item The revised stability proof includes a modified requirement for the constant \( c \) shown in~\cref{eqn:c_bound},
+    \item The revised stability proof includes a modified requirement for the constant \( c \) shown in~\cref{eqn:c_bound}.
 \end{itemize}

### 2017-01-13 setup_repo.sh
Correct remote repo script

@@ -10,10 +10,12 @@ printf "Github: $git_repo\n"
 printf "Bitbucket: $bb_repo\n"
 printf "FDCL: $fdcl_repo\n\n"
 
+git remote remove origin
 git remote add origin $git_repo
 git remote set-url origin --push --add $bb_repo
 git remote set-url origin --push --add $git_repo
-git remote set-url origin --push --add $fdcl_repo
+
+git remote add fdcl $fdcl_repo
 
 printf "Finished! The new remotes are listed.\n"
 printf "\n"

### 2017-01-16 manuscript_new.tex
Add differences between v1.0 and v2.0

--- 2017-01-13 manuscript.tex
@@
 \end{multicols}
-\begin{figure}[t]
+\begin{figure}[h]
     \centering 
@@
 We demonstrate the ability to handle an uncertain time-varying disturbance via numerical example.
-The system is identical to the one presented in~\Cref{sec:numerical_simulation}, however we modify the external disturbance. 
+The system is identical to the one presented in~\cref{sec:numerical_simulation}, however we modify the external disturbance. 
 The external disturbance is the superposition of constant and time-varying terms as
@@
 The domain \( D \) is an open neighborhood of the desired attitude \( R_d \), and it excludes the undesired equilibrium points of \( A(R) \) and the infeasible regions defined by the constraints \( r^T R^T v_i \).
-Therefore, the only critical point of the error function $\Psi$ in the domain $D$ correspond to the desired attitude $R=R_d$ with $e_R=0$ and $\Psi=0$. 
+Therefore, the only critical point of the error function $\Psi$ in the domain $D$ corresponds to the desired attitude $R=R_d$ with $e_R=0$ and $\Psi=0$. 
 Therefore, in \( D \) the configuration error function is quadratic and the bounds in~\cref{item:prop_psi_quadratic} are valid according to~\cite[Proposition 6.30]{bullo2004}.

### 2017-01-16 v2.0_diff.tex
Add differences between v1.0 and v2.0

diff --git a/manuscript.tex b/manuscript.tex
index 0cb5340..a9773d2 100644
--- a/manuscript.tex
+++ b/manuscript.tex
@@ -1,5 +1,6 @@
-\documentclass[fleqn]{IJCAS}  % Comment this line out if you need a4paper
+\documentclass[10pt,fleqn]{IJCAS}  % Comment this line out if you need a4paper
 \usepackage{ijcas_packages}
+\allowdisplaybreaks[1]

 \newcommand{\squeezeup}{\vspace{-2.5mm}}

@@ -33,7 +34,7 @@ The effectiveness of the proposed control system is demonstrated through numeric
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 \begin{keywords}
-attitude control, asymptotic stability, special orthogonal group, constraint
+adaptive control, attitude control, constraint, obstacle, special orthogonal group
 %At least four key words or phrases in alphabetical order, separated by commas.
 \end{keywords}

@@ -116,7 +117,7 @@ Artificial potential functions are commonly used to handle kinematic constraints
 The goal is the design of attractive and repulsive terms which drive the system toward or away from a certain obstacle, respectively.
 The attractive function is designed to drive the system towards the desired state.
 Similarly, a repulsive function is constructed such that the system is directed away from the constraints. 
-The superposition of the these functions allows one to apply standard feedback control schemes for stabilization and tracking.
+The superposition of these functions allows one to apply standard feedback control schemes for stabilization and tracking.
 More specifically, artificial potential functions have previously been applied to the spacecraft attitude control problem in~\cite{lee2011b,mcinnes1994}.
 However, both of these approaches were developed using attitude parameterizations, namely Euler angles and quaternions, and as such, they are limited by the singularities of minimal representations or the ambiguity of quaternions.

@@ -173,9 +174,11 @@ More explicitly,
 \end{align*}
 for $x=[x_1,x_2,x_3]^T\in\R^{3}$. 
 The inverse of the hat map is denoted by the \textit{vee} map $\vee:\so\rightarrow\R^{3}$. 
+We use the notation \( \hat{x}\) and \( \parenth{x}^\wedge\) interchangeably.
+In particular, we use the latter form when the expression for the argument of the \textit{hat} map is long. 
 Several properties of the hat map are summarized as
 \begin{gather}
-   % \hat x y = x\times y = - y\times x = - \hat y x,\\
+   \hat x y = x\times y = - y\times x = - \hat y x, \label{eqn:cross_product}\\
     x\cdot \hat y z = y\cdot \hat z x,\quad \hat x\hat y z = (x\cdot z) y - (x\cdot y ) z\label{eqn:STP},\\
    % \hat x\hat y z = (x\cdot z) y - (x\cdot y ) z,\label{eqn:VTP}\\
    % C^TC=-C^T\hat e_3^2 C = I_2
@@ -208,7 +211,7 @@ We formulate this hard constraint as
 where we assume \( \ang{0} \leq \theta \leq \ang{90}  \) is the required minimum angular separation between \( r \) and \( R^T v \). 
 The objective is to a determine a control input \( u \) that stabilizes the system from an initial attitude \( R_0 \) to a desired attitude \( R_d \) while ensuring that~\cref{eqn:constraint} is always satisfied.
 \squeezeup
-\section{Attitude Control on $\SO$ with Inequality Constraints}
+\section{Attitude Control on $\SO$ with Inequality Constraints}\label{sec:attitude_control}

 The first step in designing a control system on a nonlinear manifold \( \Q \) is the selection of a proper configuration error function. 
 This configuration error function, \( \Psi : \Q \times \Q \to \R \), is a smooth and proper positive definite function that measures the error between the current configuration and a desired configuration. 
@@ -226,13 +229,13 @@ The proposed attitude configuration error function and several properties are su
 %We assume a desired attitude command \( ( R_d, \Omega_d = 0 ) \), the current attitude and angular velocity \( ( R, \Omega) \), and a state constraint~\cref{eqn:constraint} are given.
 Define an attitude error function \( \Psi : \SO \to \R \), an attitude error vector \( e_R \in \R^3 \), and an angular velocity error vector \( e_\Omega \in \R^3 \) as follows:
 \begin{gather}
-	\Psi(R) = A(R) B(R) , \label{eqn:psi} \\
-	e_R = e_{R_A} B(R) + A(R) e_{R_B} , \label{eqn:eR} \\
+	\Psi(R, R_d) = A(R, R_d) B(R) , \label{eqn:psi} \\
+	e_R = e_{R_A} B(R) + A(R,R_d) e_{R_B} , \label{eqn:eR} \\
 	e_\Omega = \Omega , \label{eqn:eW}
 \end{gather}
 with
 \begin{gather}
-	A(R) = \frac{1}{2} \tr{G \left( I - R_d^T R\right)} , \label{eqn:A} \\
+	A(R,R_d) = \frac{1}{2} \tr{G \left( I - R_d^T R\right)} , \label{eqn:A} \\
 	B(R) = 1 - \frac{1}{\alpha} \ln \left( \frac{\cos \theta -  r^T R^T v}{1 + \cos \theta}\right) . \label{eqn:B} \\
 	e_{R_A} = \frac{1}{2} \parenth{G R_d^T R - R^T R_d G} ^ \vee , \label{eqn:eRA} \\
 	e_{R_B} = \frac{ \left( R^T v\right)^\wedge r}{\alpha \left(r^T R^T v - \cos \theta \right)} . \label{eqn:eRB} 
@@ -242,13 +245,15 @@ Then, the following properties hold
 \begin{enumerate}[(i)]
 	\item \label{item:prop_psi_psd} \(\Psi\) is positive definite about \( R = R_d\) on $\SO$.
 	\item \label{item:prop_era}The variation of \( A(R) \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
-	\begin{align}
-		\dirDiff{A}{R} &= \eta \cdot e_{R_A} .
+	\begin{align}\label{eq:dirDiff_A}
+		\dirDiff{A}{R} &= \eta \cdot e_{R_A} ,
 	\end{align}
+	where the notation \( \dirDiff{A}{R} \) represents the directional derivative of $A$ with respect to $R$ along $\delta R$.
 	\item \label{item:prop_erb} The variation of \( B(R) \) with respect to a variation of \( \delta R = R \hat{\eta} \) for \( \eta \in \R^3 \) is given by
-	\begin{align}
-		\dirDiff{B}{R} &= \eta \cdot e_{R_{B}} .
+	\begin{align}\label{eq:dirDiff_B}
+		\dirDiff{B}{R} &= \eta \cdot e_{R_{B}}.
 	\end{align}
+%    where the notation \( \D_R A \) and \(\D_R B\) represents the derivative of \( A \) or \( B \) with respect to \( R\).
 %	\item \label{item:prop_crit}The error function \( \Psi \) is minimized when \(R = R_d\).
 	\item \label{item:prop_era_upbound}An upper bound of \( \norm{e_{R_A}} \) is given as:
 	\begin{align}
@@ -260,6 +265,15 @@ Then, the following properties hold
 		h_2 &= \min\braces{\parenth{g_1 -g_2}^2,\parenth{g_2 -g_3}^2 , \parenth{g_3 -g_1}^2} ,\\
 		h_3 &= \min\braces{\parenth{g_1 + g_2}^2, \parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2}.		
 	\end{align*}
+    \item \label{item:prop_psi_quadratic} \( \Psi \) is a locally quadratic function, which means there exist constants \( 0 < n_1 \leq n_2 \) such that
+    \begin{align}\label{eq:psi_bound}
+        n_1 \norm{e_R}^2 \leq \Psi(R) \leq n_2 \norm{e_R}^2 ,
+    \end{align}
+    on the neighborhood $D$ of the desired attitude \( R_d \)
+    \begin{align}\label{eq:psi_quadratic_domain}
+        D = \braces{R\in\SO  \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta}
+    \end{align}
+    for $0<\psi < h_1 $ and $0< \beta<\cos\theta$. 
 \end{enumerate}
 \end{prop}
 \begin{proof}
@@ -271,24 +285,27 @@ In order to visualize the attitude error function on \( \SO \), we utilize a sph
 Recall, that the spherical coordinate system represents the position of a point relative to an origin in terms of a radial distance, azimuth, and elevation.
 This coordinate system is commonly used to define locations on the Earth in terms of a latitude and longitude.
 Similarly, the positions of celestial objects are defined on the celestial sphere in terms of right ascension and declination. 
+\end{multicols}
 \begin{figure}[H]%
     \centering 
-    \subfigure[Attractive \( A(R) \) \label{fig:attract_error}]{\includegraphics[width=0.45\columnwidth]{attract_error} }~
-    \subfigure[Repulsive \( B(R) \) \label{fig:avoid_error} ]{\includegraphics[width=0.45\columnwidth]{avoid_error} }\\%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
-    \subfigure[Configuration \( \Psi \) \label{fig:combined_error}]{\includegraphics[width=0.45\columnwidth]{combined_error} }%
-    \caption{Configuration error function visualization}
+    \subfigure[Attractive \( A(R) \) \label{fig:attract_error}]{\includegraphics[width=0.33\columnwidth]{attract_error} }~
+    \subfigure[Repulsive \( B(R) \) \label{fig:avoid_error} ]{\includegraphics[width=0.33\columnwidth]{avoid_error} }~
+    \subfigure[Combined \( \Psi \) \label{fig:combined_error}]{\includegraphics[width=0.33\columnwidth]{combined_error} }%
+    \caption{Visualization of Configuration Error Functions using spherical coordinate representation}
     \label{fig:config_error} 
 \end{figure}%
+\begin{multicols}{2}
 We apply this concept and parametrize the rotation matrix \( R \in \SO \) in terms of the spherical angles \( \SI{-180}{\degree} \leq \lambda \leq \SI{180}{\degree}  \) and \( \SI{-90}{\degree} \leq \beta \leq \SI{90}{\degree} \). 
 Using the elementary Euler rotations, the rotation matrix is now defined as \( R = \exp( \lambda \hat{e}_2) \exp( \beta \hat{e}_3) \).
 We iterate over the domains of \( \lambda\) and \(\beta\) in order to rotate the body-fixed vector \( r \) throughout the two-sphere \( \S^2 \).
 Applying this method,~\cref{fig:config_error} allows us to visualize the error function on \( \SO \).
+The horizontal axes of~\cref{fig:config_error} represent the domain of the spherical angles \( \lambda \) and \( \beta \) in degrees, while the vertical axes represent the unitless magnitude of the error functions defined in~\cref{eqn:psi,eqn:A,eqn:B}.
 The attractive error function, given by~\cref{eqn:A}, has been previously used for attitude control on \(\SO\).
 The potential well of \( A(R)\) is illustrated in~\cref{fig:attract_error}, where the desired attitude lies at the minimum of \( A(R) \).

 To incorporate the state inequality constraints we apply a logarithmic barrier term.
 Barrier functions are typically used in optimal control and motion planning applications.
-A visualization of the configuration error function is presented in~\cref{fig:avoid_error} which shows that as the boundary of the constraint is neared, or \( r^T R^T v \to \cos \theta \), the barrier term increases, \( B \to \infty\).
+A visualization of the repulsive error function is presented in~\cref{fig:avoid_error} which shows that as the boundary of the constraint is neared, or \( r^T R^T v \to \cos \theta \), the barrier term increases, \( B \to \infty\).
 We use the scale factor~\(\frac{1}{1+\cos \theta} \) to ensure that \( \Psi \) remains positive definite.
 The logarithmic function is popular as it quickly decays away from the constraint boundary.
 The positive constant \( \alpha \) serves to shape the barrier function.
@@ -306,10 +323,10 @@ We present the dynamics of the configuration error function in~\Cref{prop:error_
 	The attitude error dynamics for \( \Psi, e_R, e_\Omega \) satisfy 
 	\begin{gather}
 		\diff{}{t} \parenth{\Psi} = e_R \cdot e_\Omega , \label{eqn:psi_dot}\\
-		\diff{}{t} \parenth{e_R} = \dot{e}_{R_A} B(R) + e_{R_A} \dot{B}(R) + \dot{A}(R)e_{R_B} + A \dot{e}_{R_B} , \label{eqn:eR_dot}\\
+		\diff{}{t} \parenth{e_R} = \dot{e}_{R_A} B + e_{R_A} \dot{B} + \dot{A}e_{R_B} + A \dot{e}_{R_B} , \label{eqn:eR_dot} \\
 		\diff{}{t} \parenth{e_{R_A}} = E(R, R_d) e_\Omega , \label{eqn:eRA_dot} \\
 		\diff{}{t} \parenth{e_{R_B}} = F(R) e_\Omega , \label{eqn:eRB_dot} \\
-		\diff{}{t} \parenth{A(R)} = e_{R_A} \cdot e_\Omega , \label{eqn:A_dot} \\
+    	\diff{}{t} \parenth{A(R)} = e_{R_A} \cdot e_\Omega , \label{eqn:A_dot} \\
 		\diff{}{t} \parenth{B(R)} = e_{R_B} \cdot e_\Omega , \label{eqn:B_dot} \\
 		\diff{}{t} \parenth{e_\Omega} = J^{-1} \parenth{-\Omega \times J \Omega + u + W(R, \Omega) \Delta} , \label{eqn:eW_dot}
 	\end{gather}
@@ -326,7 +343,7 @@ See~\Cref{proof:error_dyn}

 \subsection{Attitude Control without Disturbance}
 We introduce a nonlinear geometric controller for the attitude stabilization of a rigid body.
-We first assume that there is no disturbance, i.e., \( \Delta = 0 \) and present a nonlinear controller in~\Cref{prop:att_control}.
+We first assume that there is no disturbance, i.e., \( \Delta = 0 \), and present a nonlinear controller in~\Cref{prop:att_control}.
 \begin{prop}[Attitude Control]\label{prop:att_control}
 	Given a desired attitude command \( \parenth{R_d, \Omega_d = 0} \), which satisfies the constraint~\cref{eqn:constraint}, and positive constants \( k_R, k_\Omega \in \R \) we define a control input \( u \in \R^3 \) as follows
 	\begin{gather}
@@ -347,16 +364,17 @@ Aerial vehicles will similarly experience external torques due to air currents o
 An adaptive control system is introduced to asymptotically stabilize the system to a desired attitude while ensuring that state constraints are satisfied. %We first show several properties of the controlled system.

 \begin{prop}[Bound on \( \bm{\dot{e}_R} \)]\label{prop:eR_dot_bound}
-Consider a domain \( D \) about the desired attitude defined as
-\begin{align}
-	D = \braces{R \in \SO \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta}. \label{eqn:domain}
-\end{align}
-Then the following statements hold:
+Consider the neighborhood \( D \), given in~\cref{prop:config_error}, about the desired attitude, then the following statements hold:
 \begin{enumerate}[(i)]
 	\item \label{item:prop_eR_dot_bound_AB} Upper bounds of \( A(R) \) and \( B(R) \) are given by
 	\begin{gather}
-		\norm{A} < c_A  , \quad \norm{B} < c_B . \label{eqn:AB_bound}
+		\norm{A} < b_2 \norm{e_{R_A}}^2 < c_A  , \quad \norm{B} < c_B . \label{eqn:AB_bound}
 	\end{gather}
+  where the constant \( b_2\) is given by \( b_2 = \frac{h_1 h_4}{h_5 \parenth{h_1 - \psi}}\) for
+  \begin{align*}
+    h_4 &= \min\braces{g_1 + g_2, g_2 + g_3 , g_3 + g_1} ,\\
+    h_5 &= \min\braces{\parenth{g_1 + g_2}^2,\parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2} .\\
+  \end{align*}
 	\item \label{item:prop_eR_dot_bound_EF} Upper bounds of \( E(R,R_d) \) and \( F(R) \) are given by
 	\begin{gather}
 		\norm{E} \leq \frac{1}{\sqrt{2}} \tr{G}  , \label{eqn:E_bound} \\
@@ -367,6 +385,7 @@ Then the following statements hold:
 		\norm{e_{R_A}} \leq \sqrt{\frac{\psi}{b_1}}, \label{eqn:eRA_bound} \\
 		\norm{e_{R_B}} \leq \frac{\sin\theta}{\alpha \parenth{\cos \theta - \beta}}. \label{eqn:eRB_bound}
 	\end{gather}
+
 \end{enumerate}
 These results are combined to yield a maximum upper bound of the time derivative of the attitude error vector \( \dot{e}_R \) as
 \begin{gather}
@@ -392,9 +411,11 @@ Given  a desired attitude command \( (R_d, \Omega_d = 0 )\) and positive constan
 \end{align}
 If \( c \) is chosen such that
 \begin{gather}
-	0 < c < \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k-R \lambda_M H} , \label{eqn:c_bound}
+	0 < c < \min \braces{\sqrt{\frac{2 \lambda_m k_R n_1}{\lambda_M^2}},
+	%\sqrt{\frac{2 k_R n_2}{\lambda_M}}, 
+	\frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H}} , \label{eqn:c_bound}
 \end{gather}
-  the zero equilibrium of the error vectors is stable in the sense of Lyapunov. Furthermore, $e_R,e_\Omega\rightarrow 0$ as $t\rightarrow\infty$, and $\bar\Delta$ is uniformly bounded.
+  the zero equilibrium of the error vectors is stable in the sense of Lyapunov. Furthermore, $e_R,e_\Omega\rightarrow 0$ as $t\rightarrow\infty$, and $\bar\Delta$ is  bounded.
 \end{prop}
 \begin{proof}
 See~\Cref{proof:adaptive_control}
@@ -413,7 +434,18 @@ In addition, the rigorous mathematical proof guarantees stability.
 This is in contrast to many of the previous methods which offer no stability guarantees.
 The presented analysis offers provable bounds on the expected motion, which are critical for hardware implementation or mission critical applications.

-\section{Numerical Examples}
+\end{multicols}
+\begin{figure}[b]
+    \centering 
+    \subfigure[Attitude error vector \(e_R\) components \label{fig:eR_con}]{\includegraphics[width=0.3\columnwidth]{eR_con}  }~
+    \subfigure[Configuration error \( \Psi \) \label{fig:Psi_con}]{\includegraphics[width=0.3\columnwidth]{figures/Psi_con.pdf} }
+    \subfigure[Angle to each constraint \label{fig:con_angles_con}]{\includegraphics[width=0.3\columnwidth]{figures/constraint_angles_con.pdf} } 
+    \caption{Attitude stabilization without adaptive update law}
+    \label{fig:con} 
+\end{figure}
+\begin{multicols}{2}
+\section{Numerical Examples}\label{sec:numerical_simulation}
+
 We demonstrate the performance of the proposed control system via numerical simulation.
 The inertia tensor of a rigid body is given as
 \begin{gather*}
@@ -429,6 +461,15 @@ The control system parameters are chosen as
 	G = \text{diag} [0.9,1.1,1.0], \quad k_R = 0.4 , \quad	k_\Omega = 0.296 ,\\
 	c = 1.0 , \quad k_\Delta = 0.5 , \quad \alpha = 15 .
 \end{gather*}
+The diagonal matrix \( G \) serves as a weighting matrix for the relative difference between \( R \) and \( R_d \). 
+Using this term, the control designer can modify the shape of the attractive error function, given in~\cref{eqn:A}, and the resulting behavior of the closed loop system.
+Similarly, the constant \( \alpha \) is used to modify the shape of the repulsive error function, given in~\cref{eqn:B}.
+In general, this term is derived from the system design and the nature of the obstacles in the dynamic environment.
+For example, a system wishing to avoid pointing at a diffuse obstacle, such as incoming debris, may chose an appropriate value of \( \theta \), based on the best available information, and a relatively low \( \alpha \) to ensure additional safety margin near the constraint boundary. 
+Similarly, in an environment with several densely spaced obstacles, such as that presented in~\cref{fig:cad_adapt}, a much larger \( \alpha \) would enable more aggressive manuevers which pass closer to the constraint boundary without violation.
+This would increase the allowable region of operation in a highly constrained environment.
+The parameters \( k_R, k_\Omega, c, k_\Delta\) are control parameters used to modify the closed-loop behavior of the system.
+It is straightforward to chose \( k_R, k_\Omega, k_\Delta\), using a linear analysis, to satisfy desired response criteria, such as settling time or percent overshoot~\cite{nise2004}.
 A body fixed sensor is defined as \(r = [1,0,0]\), while multiple inequality constraints are defined in~\Cref{tab:constraints}.
 The simulation parameters are chosen to be similar to those found in~\cite{lee2011b}, however we increase the size of the constraint regions to create a more challenging scenario for the control system.
 \begin{table}[H]
@@ -444,41 +485,27 @@ Constraint Vector (\( v \)) & Angle (\( \theta \)) \\ \hline \hline

 The initial state is defined as \(R_0 =  \exp(\ang{225} \times \frac{\pi}{180} \hat{e}_3), \Omega_0 = 0\). 
 The desired state is \( R_d = I,\Omega_d = 0\).
-\begin{figure}[H] 
-    \centering 
-    \subfigure[Attitude error vector \(e_R\) \label{fig:eR_con}]{\includegraphics[width=0.5\columnwidth]{eR_con}  }~
-    \subfigure[Configuration error \( \Psi \) \label{fig:Psi_con}]{\includegraphics[width=0.5\columnwidth]{figures/Psi_con.pdf} }
-    \subfigure[Angle to constraints \label{fig:con_angles_con}]{\includegraphics[width=0.5\columnwidth]{figures/constraint_angles_con.pdf} }  
-    \caption{Attitude stabilization without adaptive update law}
-    \label{fig:con} 
-\end{figure}
 We show simulation results for the system stabilizing about the desired attitude with and without the adaptive update law from~\Cref{prop:adaptive_control}.
-We assume a fixed disturbance of \(\Delta = \begin{bmatrix} 0.2 & 0.2 & 0.2 \end{bmatrix}^T \), with the function \( W(R,\Omega) = I \).
+We assume a fixed disturbance of \(\Delta = \begin{bmatrix} 0.2 & 0.2 & 0.2 \end{bmatrix}^T \si{\newton\meter}\), with the function \( W(R,\Omega) = I \).
 This form is equivalent to an integral control term which penalizes deviations from the desired configuration.
 The first term of~\cref{eqn:delta_dot} has the effect of increasing the proportional gain of the control system, since the time derivative of the attitude error vector, \( \dot{e}_{R} \), is linear with respect to the angular velocity error vector \( e_\Omega\).
-\begin{figure}[H] 
-	\centering 
-    \subfigure[Configuration error \( \Psi \)\label{fig:Psi_adapt}]{\includegraphics[width=0.5\columnwidth]{Psi_adapt} }~
-    \subfigure[Angle to constraints \label{fig:con_angles}]{\includegraphics[width=0.5\columnwidth]{constraint_angles} }\\
-    \subfigure[Disturbance estimate \( \bar \Delta \)  \label{fig:delta_adapt} ]{\includegraphics[width=0.5\columnwidth]{delta_adapt}}~
-    \subfigure[Attitude trajectory \label{fig:cad_adapt}]{\includegraphics[trim=9cm 2.5cm 0 0,clip,width=0.645\columnwidth]{cad_adapt} }
-	\caption{Attitude stabilization with adaptive update law}
-	\label{fig:adapt} 
-\end{figure}

 Simulation results without the adaptive update law are shown in~\cref{fig:con}.
+\Cref{fig:eR_con} shows each component of the attitude error vector,~\cref{eqn:eR}, over the simulation time span.
+\Cref{fig:Psi_con} shows the  magnitude of the combined error function,~\cref{eqn:psi}.
 Without the update law, the system does not achieve zero steady state error. 
 \Cref{fig:Psi_con} shows that the configuration error function does not converge to zero and there exist steady state errors.
 In spite of the uncompensated disturbance, the system is able to avoid the constrained regions as shown in~\cref{fig:con_angles_con}.
-The angle to each of the constraints,  \( \arccos(r^T R^T v_i) \), is always greater than the specified angle, \( \theta_i \), in~\cref{tab:constraints}.
+The angle to each of the constraints, which is measured in degrees and given by \( \arccos(r^T R^T v_i) \), is always greater than the specified angle, \( \theta_i \), in~\Cref{tab:constraints}.

 \Cref{fig:adapt} shows the results with the addition of the adaptive update law.
+\Cref{fig:Psi_adapt,fig:con_angles} are equivalent to~\cref{fig:Psi_con,fig:con_angles_con} with the exception of the addition of the adaptive update law.
 The addition of the adaptive update law allows the system to converge to the desired attitude in the presence of constraints.
-The path of the body fixed sensor in the inertial frame, namely \( R r \), is illustrated in~\cref{fig:cad_adapt}.
-The initial attitude is represented with the green circle while the final attitude is marked with a green \(\times\).
+The path of the body fixed sensor in the inertial frame, namely \( R r \), is illustrated in~\cref{fig:cad_adapt} by the blue trajectory.
+The rendering of the spacecraft is presented in the desired, or final, orientation of the simulation.
 The inequality constraints from~\Cref{tab:constraints} are depicted as red cones, where the cone half angle is \( \theta \).
 The control system is able to asymptotically converge to zero attitude error.
-\Cref{fig:con_angles} shows that the angle \( \arccos(r^T R^T v_i) \) between the body fixed sensor and each constraint is satisfied for the entire maneuver.
+\Cref{fig:con_angles} shows that the angle, \( \arccos(r^T R^T v_i) \) and measured in degrees, between the body fixed sensor and each constraint is satisfied for the entire maneuver.
 In addition, the estimate of the disturbance converges to the the true value as shown in~\cref{fig:delta_adapt}.

 Both control system are able to automatically avoid the constrained regions. 
@@ -487,8 +514,107 @@ In spite of this challenging configuration space, the proposed control system of
 These closed-loop feedback results are computed in real time and offer a significant advantage over typical open-loop planning methods.
 These results show that the proposed geometric adaptive approach is critical to attitude stabilization in the presence of state constraints and disturbances.

-\section{Experiment on Hexrotor UAV}
+\subsection{Attitude Parameterizations}\label{ssec:attitude_parameterization}
+\end{multicols}
+\begin{figure} 
+  \centering 
+    \subfigure[Configuration error \( \Psi \)\label{fig:Psi_adapt}]{\includegraphics[width=0.4\columnwidth]{Psi_adapt} }~
+    \subfigure[Angle to each constraint \label{fig:con_angles}]{\includegraphics[width=0.4\columnwidth]{constraint_angles} }\\
+    \subfigure[Disturbance estimate \( \bar \Delta \) components \label{fig:delta_adapt} ]{\includegraphics[width=0.4\columnwidth]{Delta_adapt}}~
+    \subfigure[Attitude trajectory \label{fig:cad_adapt}]{\includegraphics[trim={10cm 0 10cm 0},clip,width=0.4\columnwidth]{cad_adapt} }
+  \caption{Attitude stabilization with adaptive update law}
+  \label{fig:adapt} 
+\end{figure}
+\begin{multicols}{2}
+% Discuss the benefits of using this geometric representation as compared to Euler angles or quaternions
+Attitude parameterizations, such as Euler angles and Quaternions, are frequently used in the aerospace and astrodynamics communities~\cite{vallado2007}.
+For example, Euler angle sequences are frequently used to describe the transformation between a variety of reference frames used to describe the position and orientation of the orbit of Earth satellites~\cite{vallado2007}.
+In addition, quaternions were used during the operation of Skylab and the NASA Space Shuttle~\cite{hughes2004}.
+However, the choice of attitude parameterization plays a critical role in control design and the resulting motion of the system.
+
+% singularities and the problems involved with using Euler angles
+Euler angle sequences are a minimum, three-parameter set of angles which describe the transformation between two reference frames.
+Using Euler angles, we can represent any general rotation as a sequence of three intermediate rotations~\cite{shuster1993}.
+By convention, there are \num{24} possible Euler angle sequences for any given rotation.
+In addition, Euler angles are a minimum representation, as only three angles, and the associated sequence, are required to describe the three angular degrees of freedom of the rigid body.
+However, there is great ambiguity in the representation of the attitude as there are many equivalent Euler angle sequences for a given attitude of the system.
+Therefore, great care must be taken in the control system design to ensure that a consistent sequence is used. 
+Furthermore, it has been shown that no minimal attitude representation can describe orientations both globally and without singularities~\cite{hughes2004,bhat2000}.
+These singularities can cause significant difficulties during control design and hardware implementation.
+
+To demonstrate the effect of the kinematic singularities inherent with Euler angles we will represent the attitude of the body fixed reference frame, \( \vecbf{b}_i \), with respect to the inertial frame, \( \vecbf{e}_i\), in terms of the \( 3-1-3\) Euler angle sequence.
+More explicitly, this corresponds to the rotation sequence \( \theta_1 \vecbf{b}_3 , \theta_2 \vecbf{b}_1, \theta_3 \vecbf{b}_3 \).
+The rotation matrix, \( R(\theta_1, \theta_2, \theta_3) \), corresponding to this sequence is 
+\begin{align}\label{eq:euler313}
+    \begin{bmatrix}
+        -s_1 c_2 s_3 + c_3 c_1 & -s_1 c_2 c_3 - s_3 c_1 & s_1s_2 \\
+        c_1 c_2 s_3 + c_3 s_1 & c_1 c_2 c_3 - s_3 s_1 & - c_1 s_2 \\
+        s_2 s_3 & s_2 c_3 & c_2
+    \end{bmatrix} ,
+\end{align}
+where \( s_i, c_i \) represent \( \sin \theta_i, \cos \theta_i \) for \( i = \braces{1,2,3}\).
+Using this representation, the kinematic differential equations for the associated Euler angles are given as
+\begin{align}\label{eq:euler313_diff}
+    \begin{bmatrix}
+        \dot{\theta}_1 \\ \dot{\theta}_2 \\ \dot{\theta}_3 
+    \end{bmatrix}
+    =
+    \begin{bmatrix}
+        \slfrac{\parenth{\Omega_1 s_3 + \Omega_2 c_3}}{s_2} \\
+        \Omega_1 c_3 - \Omega_2 s_3 \\
+        -\slfrac{\parenth{\Omega_1 s_3 + \omega_2 c_3}c_2}{s_2} + \Omega_3
+    \end{bmatrix} .
+\end{align}
+From~\cref{eq:euler313_diff}, it is immediately clear that a singularity exists when \( \sin \theta_2 = 0 \) or equivalently, \( \theta_2 = 0, \pm \pi \). 
+In the vicinity of the singularity, the angular velocities of the Euler angles will tend to approach \( \pm \infty \) and the angular velocities will experience instantaneous sign changes.
+Furthermore, all Euler angle sequences will exhibit a similar singularity at either \( \theta_2 = 0, \pm \pi \) or \( \theta_2 = \pm \frac{\pi}{2}, \pm \frac{3\pi}{2} \).
+Therefore simply switching the sequence does not alleviate the issue, but rather only moves the singularity.
+As a result, Euler angles are not appropriate for systems which experience large angular rotations, such as those demonstrated in~\cref{fig:adapt}, or control systems which rely on the angular velocities \( \theta_i \).
+% discuss the unwinding phenomenon with quaternions
+
+\end{multicols}
+\begin{figure}[h]
+    \centering 
+    \subfigure[{Configuration error \( \Psi \)} \label{fig:Psi_tv} ]{\includegraphics[width=0.3\columnwidth]{Psi_tv} }~
+    \subfigure[{Angle to constraint } \label{fig:con_angle_tv}]{\includegraphics[width=0.3\columnwidth]{figures/constraint_angle_tv.pdf} }~
+    \subfigure[{Disturbance estimate \(\bar\Delta\) components} \label{fig:Delta_tv}]{\includegraphics[width=0.3\columnwidth]{figures/delta_tv} }
+    \caption{Time-varying external disturbance simulation}
+    \label{fig:tv} 
+\end{figure}
+\begin{multicols}{2}
+\subsection{Time-varying Disturbance}\label{ssec:time_varying}
+
+The form of the uncertainty, given in~\cref{eqn:Wdot}, is commonly used in the adaptive control literature~\cite{LeeITCST13,ioannou2012}. 
+A wide variety of realistic disturbances, such as gravitational gradients or malfunctioning thrusters for spacecraft scenarios, are accurately represented via this model. 
+In addition, it is possible to represent the uncertainty of a time-varying inertia matrix as an equivalent external disturbance. 
+For example, Euler's law gives the relationship for the rate of change of angular momentum as
+\begin{align*}
+    M_{ext} = \dot{\vecbf{H}} = \dot{J} \vecbf{\Omega} + J \dot{\vecbf{\Omega}} .
+\end{align*}
+Using this, we can see that an instantaneous change in \( J \) is proportional to an external moment.
+Finally, it has been shown that this adaptive control formulation is able to handle time-varying disturbances under some mild assumptions~\cite{ioannou2012}.

+We demonstrate the ability to handle an uncertain time-varying disturbance via numerical example.
+The system is identical to the one presented in~\cref{sec:numerical_simulation}, however we modify the external disturbance. 
+The external disturbance is the superposition of constant and time-varying terms as
+\begin{align*}
+    \Delta = \begin{bmatrix} 0.2 \\ 0.2 \\0.2 \end{bmatrix} + 0.02 \begin{bmatrix} \sin 9 t \\ \cos 9 t \\ \frac{1}{2} \parenth{\sin 9t + \cos 9t}\end{bmatrix} \si{\newton\meter}.
+\end{align*}
+We define a constraint in the inertial frame as \( v = [\frac{1}{\sqrt{2}}, \frac{1}{\sqrt{2}}, 0]^T \) with \( \theta = \ang{12} \).
+The initial state is defined as \(R(0) = \exp( \frac{\pi}{2} \hat{e}_3) \), while the desired state is \(R_d =I \).
+The goal is to rotate the vehicle about the \( e_3 \) axis while avoiding the obstacle and compensating for the time-varying disturbance. 
+
+\Cref{fig:tv} demonstrates the ability for the adaptive controller, which is presented in~\Cref{prop:adaptive_control}, to handle time-varying disturbances.
+\Cref{fig:Psi_tv} shows the non-dimensional value of the configuration error function and demonstrates that the adaptive controller is able to stabilize the system to the desired attitude configuration.
+In addition,~\cref{fig:con_angle_tv} shows that the constraint is never violated as the angle between the body-fixed sensor \( r \) and the constraint \( v \) is greater than \SI{12}{\degree} over the entire attitude maneuver.
+We can see in~\cref{fig:Delta_tv} that that estimate \(\bar \Delta \) for each of the components accurately tracks the true disturbance after approximately~\SI{5}{\second}.
+
+\section{Experiment on Hexrotor UAV}\label{sec:experiment}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width = 0.75\columnwidth]{hexrotor}
+    \caption{Attitude control testbed~\label{fig:hexrotor}}
+\end{figure}
 A hexrotor unmanned aerial vehicle (UAV), as seen in~\cref{fig:hexrotor}, has been developed at the Flight Dynamics and Controls Laboratory (FDCL) at the George Washington University~\cite{kaufman2014}.
 The UAV is composed of three pairs of counter-rotating propellers. 
 Typical UAVs are composed of four or more co-planar propellers.
@@ -497,13 +623,12 @@ For example, quadrotor UAVs are unable to translate laterally without first cond
 Conversely, the propeller pairs of the hexrotor are angled relative to one another to allow for a fully actuated rigid body.
 This allows the hexrotor to impart a force in any direction and a moment about any axis.

-\begin{figure}[H]
-    \centering
-    \includegraphics[width = 0.75\columnwidth]{hexrotor}
-    \caption{Attitude control testbed~\label{fig:hexrotor}}
-\end{figure}
-Attitude information is measured by an onboard IMU and a Vicon motion capture system in the test area.
-The control input is computed onboard the hexrotor using data transmitted via WiFi in a client/server model.
+Attitude information is measured by a combination of both on and off board sensor systems.
+The VectorNav VN-100 is a rugged, miniature high-performance inertial measurement unit which provides high frequency angular velocity measurements.
+A Vicon motion capture system is installed within the test environment and used to provide high accuracy attitude measurements. 
+A series of reflective markers are placed on the hexrotor and their relative position is captured by a series of infrared optical cameras. 
+Assuming a fixed rigid body, the Vicon system is able to derive the attitude of the hexrotor and transmit this data to the processor onboard the hexrotor.
+The control input is computed on-board, using the full state measurement, and implemented at approximately \SI{100}{\hertz}.
 In order to constrain the motion, allowing us to test only the attitude dynamics, we attach the hexrotor to a spherical joint.
 Since, the center of rotation is below the center of gravity of the hexrotor there is a destabilizing gravitational moment.
 The resulting attitude dynamics are similar to an inverted pendulum model.
@@ -513,27 +638,35 @@ A sensor pointing direction is defined in the body-fixed frame of the hexrotor a
 We define an obstacle in the inertial frame as \( v = [\frac{1}{\sqrt{2}}, \frac{1}{\sqrt{2}}, 0]^T \) with \( \theta = \ang{12} \).
 An initial state is defined as \(R(0) = \exp( \frac{\pi}{2} \hat{e}_3) \), while the desired state is \(R_d =I \).
 This results in the UAV performing a \ang{90} yaw rotation about the vertical axis of the spherical joint and the constrained region is on the shortest path connecting $R_0$ and $R_d$. 
-The attitude control system is identical to the one presented in~\Cref{prop:adaptive_control} with the exception of a gravity moment term and the following parameters: \(k_R = 0.4, k_\Omega = 0.7 ,c = 0.1 , \alpha = 8 \text{ and } k_\Delta = 0.05\).
-\begin{figure}[H]
-	\centering 
-    \subfigure[{Attitude error vector \(e_R\)} \label{fig:eR_exp}]{\includegraphics[width=0.5\columnwidth]{eR_exp}  }~
-	\subfigure[{Configuration error \( \Psi \)} \label{fig:Psi_exp} ]{\includegraphics[width=0.5\columnwidth]{Psi_exp} }\\
-	\subfigure[{Control input \( u\) }\label{fig:u_exp}]{\includegraphics[width=0.5\columnwidth]{u_exp}  }~
-	\subfigure[{Attitude Trajectory } \label{fig:traj_exp}]{\includegraphics[width=0.5\columnwidth]{traj_exp} }\\
-    \subfigure[{Angle to constraint } \label{fig:con_angle_exp}]{\includegraphics[width=0.5\columnwidth]{figures/constraint_angles_exp.pdf} }
-	\caption{Constrained Attitude stabilization experiment}
-	\label{fig:exp} 
-\end{figure}
+The attitude control system is identical to the one presented in~\Cref{prop:adaptive_control} with the exception of a gravity moment term, \( M_g = r_{cg} \times m g R^T e_3\) which represents the gravitational moment due to the difference between the center of mass and the center of rotation. 
+In addition, the following parameters were also modified: \(k_R = 0.4, k_\Omega = 0.7 ,c = 0.1 , \alpha = 8 \text{ and } k_\Delta = 0.05\) to account for the differences in the hardware model of the hexrotor.
+
 The experimental results are shown in~\Cref{fig:exp}.
+\Cref{fig:eR_exp} shows the behavior of each of the components of the attitude error vector, defined by~\cref{eqn:eR}, over the experiment time span.
+\Cref{fig:Psi_exp} shows the time history of the attitude error function, defined by~\cref{eqn:psi}.
+\Cref{fig:u_exp} shows the magnitude of each component of the control input in \si{\newton\meter}, which is computed from~\cref{eqn:adaptive_control}.
+Finally,~\cref{fig:con_angle_exp} shows the angle between the body-fixed sensor and the obstacle in degrees.
 In order to maneuver the system ``close" to the constrained zone we utilize several intermediary set points on either side of the obstacle.
 From the initial attitude the hexrotor rotates to the first set point, pauses, and then continues around the obstacle to the second set point before continuing toward the desired attitude.
 As a result this creates the stepped behavior of the configuration error history as shown in~\cref{fig:Psi_exp}.

+\end{multicols}
+\begin{figure}[H]
+    \centering 
+    \subfigure[{Attitude error vector \(e_R\)} components\label{fig:eR_exp}]{\includegraphics[width=0.3\columnwidth]{eR_exp}  }~
+    \subfigure[{Configuration error \( \Psi \)} \label{fig:Psi_exp} ]{\includegraphics[width=0.3\columnwidth]{Psi_exp} }~
+    \subfigure[{Control input \( u\) } components\label{fig:u_exp}]{\includegraphics[width=0.3\columnwidth]{u_exp}  }\\
+    \subfigure[{Attitude Trajectory } \label{fig:traj_exp}]{\includegraphics[width=0.3\columnwidth]{traj_exp} }~
+    \subfigure[{Angle to constraint } \label{fig:con_angle_exp}]{\includegraphics[width=0.3\columnwidth]{figures/constraint_angles_exp.pdf} }
+    \caption{Constrained Attitude stabilization experiment}
+    \label{fig:exp} 
+\end{figure}
+\begin{multicols}{2}
 The hexrotor avoids the constrained region illustrated by the circular cone in~\cref{fig:traj_exp}, by rotating around the boundary of the constraint. 
 \Cref{fig:con_angle_exp} shows the angle, \( \arccos r^T R^T v \), between the body mounted sensor and the inertially fixed sensor.
 The experiment demonstrates that the minimum angular separation is \SI{14}{\degree} which satisfies the constraint of \( \theta = \SI{12}{\degree} \).
 This further validates that the proposed control system exhibits the desired performance in the experimental setting as well. 
-A video clip showing the attitude maneuver is available \url{https://youtu.be/dsmAbwQram4}.
+A video clip is available at \url{https://youtu.be/dsmAbwQram4}.

 \section{Conclusions}\label{sec:conclusions}
 We have developed a geometric adaptive control system which incorporates state inequality constraints on \(\SO\).
@@ -560,12 +693,16 @@ As a result, its negative logarithm is always positive and from~\cref{eqn:B}, \(
 The error function \( \Psi = A B \) is composed of two positive terms and is therefore also positive definite.

 Next, we consider~\cref{item:prop_era}.
-The variation of~\cref{eqn:A} is taken with respect to \( \delta R = R \hat \eta \) as
+The infinitesimal variation of a rotation matrix is defined as
+\begin{align*}
+    \delta R = \left. \diff{}{\epsilon} \right|_{\epsilon=0} R \exp{\epsilon \hat{\eta}} = R \hat{\eta} .
+\end{align*}
+Using this, the variation of~\cref{eqn:A} is taken with respect to \( R \) as
 \begin{align*}
 	\dirDiff{A}{R} &= \eta \cdot \frac{1}{2} \left( G R_d^T R - R^T R_d G\right)^\vee ,
 %	&= -\frac{1}{2} \tr{G R_d^T \left( R \hat{\eta}\right)} \\
 \end{align*}
-where we used~\cref{eqn:hat1}.
+where we used~\cref{eqn:hat1} to achieve the simplified form.

 A straightforward application of the chain and product rules of differentiation allows us to show~\cref{item:prop_erb} as
 \begin{align*}
@@ -580,12 +717,57 @@ where the scalar triple product~\cref{eqn:STP} was used.
 %  A(R) \geq A(R_d) \; \forall \; R \in U .
 %\end{align*}
 %Since the desired attitude, \( R_d \), must lie in the feasible set, i.e., \( r^T R^T v < \cos \theta \), the addition of the repulsive barrier function, \( B \), does not change the minimum value of \( \Psi \).
+We show~\cref{item:prop_psi_quadratic} by computing the hessian of \( \Psi \), namely \( \Hess(\Psi) \),  using the chain rule as 
+\begin{align*}
+    \Hess &(\Psi)\cdot (\delta R,\delta R)= (\mathbf{D}_R\parenth{\mathbf{D}_R A \cdot \delta R}\cdot \delta R) B\\
+    & + \parenth{\dirDiff{A}{R} }\parenth{\dirDiff{B}{R}} 
+    + \parenth{\dirDiff{B}{R} }\parenth{\dirDiff{A}{R}}\\ &+(\mathbf{D}_R\parenth{\mathbf{D}_R B \cdot \delta R}\cdot \delta R) A.
+\end{align*}
+The first order derivative of \( A(R) \) and \( B(R) \) are given by~\cref{eqn:eRA,eqn:eRB}. 
+The hessian of \( A(R) \) is computed as 
+\begin{align*}
+    \dirDiff{\parenth{\dirDiff{A}{R}}}{R} &= \eta \cdot \frac{1}{2}\parenth{G R_d^T \delta R - \delta R^T R_d G}^\vee , \\
+    &= \eta \cdot \frac{1}{2} \parenth{G R_d^T R \hat \eta + \hat \eta R^T R_d G}^\vee,\\
+    &= \eta \cdot \frac{1}{2} \bracket{\parenth{\braces{\tr{R^T R_d G} I - R^T R_d G} \eta}^\wedge}^\vee , \\
+    &= \eta \cdot \frac{1}{2} \parenth{\tr{R^T R_d G} I - R^T R_d G}\eta ,
+\end{align*}
+where we used the scalar triple product rule, from~\cref{eqn:STP}, to arrive at the final form.
+The hessian of \( B(R) \) is computed as
+\begin{align*}
+    \dirDiff{\parenth{\dirDiff{B}{R}}}{R} =& \eta \cdot \left[\frac{\parenth{\delta R^T v}^\wedge r}{\alpha\parenth{r^T R^T v - \cos \theta}} \right. \\
+    & \left. - \frac{\parenth{R^T v}^\wedge r \parenth{r^T \delta R^T v}}{\alpha \parenth{r^TR^Tv - \cos \theta}^2}   \right] .
+\end{align*}
+The term \( \parenth{\delta R^T v}^\wedge r\) is simplified as
+\begin{align*}
+    \parenth{\delta R^T v}^\wedge r &= - \hat{r} \delta R ^T v , \\
+    &= - \hat{r} \parenth{R \hat \eta}^T v , \\
+    &= \hat{r} \parenth{\hat{\eta} R^T } v , \\
+    &= - \hat{r} \parenth{R^T v}^\wedge \eta ,
+\end{align*}
+where we utilized the hat map property from~\cref{eqn:cross_product}.
+Similarly, the term \( r^T \delta R^T v \) is simplified as
+\begin{align*}
+    r^T \delta R^T v &= r^T \parenth{-\hat \eta R^T}v , \\
+    &= r^T \parenth{R^T v}^\wedge \eta .
+\end{align*}
+The hessian of \( B(R) \) then becomes
+\begin{align*}
+    \dirDiff{\parenth{\dirDiff{B}{R}}}{R} =& \eta \cdot \left[ - \frac{ \hat r \parenth{R^T v}^\wedge}{\alpha \parenth{r^T R^T v - \cos \theta}} \right. \\ 
+    & \left. - \frac{\parenth{R^T v}^\wedge r r^T \parenth{R^T v}^\wedge }{ \alpha\parenth{r^T R^T v - \cos \theta}^2}  \right] \eta .
+\end{align*}
+Using these terms, we evaluate \( \Hess{\Psi} \) at the desired attitude \( R = R_d \) as follows. Since $A=0$ and $\mathbf{D}_R A=0$ at $R=R_d$, 
+\begin{align*}
+    \Hess(\Psi)\cdot (\delta R,\delta R)\big|_{R=R_d} = \eta \cdot \frac{1}{2} B \parenth{\tr{G}I -  G} \eta , 
+\end{align*}
+which is positive definite since \( B > 1\) and \( \sum g_i > g_i\). 
+The domain \( D \) is an open neighborhood of the desired attitude \( R_d \), and it excludes the undesired equilibrium points of \( A(R) \) and the infeasible regions defined by the constraints \( r^T R^T v_i \). 
+Therefore, the only critical point of the error function $\Psi$ in the domain $D$ corresponds to the desired attitude $R=R_d$ with $e_R=0$ and $\Psi=0$. 
+Therefore, in \( D \) the configuration error function is quadratic and the bounds in~\cref{item:prop_psi_quadratic} are valid according to~\cite[Proposition 6.30]{bullo2004}.

-The desired equilibrium occurs at \( R=R_d\) and results in \( e_R = 0 \) and \( \Psi = A = 0\).
 The proof of \cref{item:prop_era_upbound} is available in~\cite{LeeITCST13}.

 \subsection{Proof of~\Cref{prop:error_dyn}}\label{proof:error_dyn}
-From the kinematics~\cref{eqn:Rdot} and noting that \( \dot{R}_d = 0 \) the time derivative of \( R_d^T R \) is given as
+From the kinematics~\cref{eqn:Rdot}, and noting that \( \dot{R}_d = 0 \) the time derivative of \( R_d^T R \) is given as
 \begin{gather*}
 	\diff{}{t} \parenth{R_d^T R} = R_d^T R \hat{e}_\Omega .
 \end{gather*}
@@ -659,11 +841,18 @@ Therefore, the inequality constraint is always satisfied given that the desired
 %	We assume that \( B > \psi \) which implies that \( A < 1 \).
 %	As \( \psi \) is increased this implies that the system is approaching the constraint and that \( A \to 0 \) in order to remain in the domain \( D \).
 %	However, since the chosen domain is assumed to exclude the constraint this situation is not possible and \( B < \psi \).
+%We choose the domain \( D \) to exclude the undesired critical points of \( A(R) \) as well as the infeasible regions defined by the state inequality constraints. 
+%Furthermore,~\cref{proof:config_error} shows that \(D \) is an open neighborhood of the desired attitude configuration, \( R_d\).
+%The proof of the upper bound of \( A(R) \) is given in~\cite{LeeITCST13}.
+
+
+Consider the open neighborhood $D$ of $R=R_d$ defined in~\Cref{prop:config_error}.
+The proof of the upper bound of \( A(R) \) is given in~\cite{LeeITCST13}.
 The selected domain ensures that the configuration error function is bounded \( \Psi < \psi \).
 This implies that that both \( A(R) \) and \( B(R) \) are bounded by constants \( c_A c_B < \psi < h_1\).
 Furthermore, since \( \norm{B} > 1 \) this ensures that \( c_A, c_B < \psi\) and shows~\cref{eqn:AB_bound}.

-Next, we show~~\cref{eqn:E_bound,eqn:F_bound} using the Frobenius norm.
+Next, we show~\cref{eqn:E_bound,eqn:F_bound} using the Frobenius norm.
 The Frobenius norm \( \norm{E}_F \) is given in~\cite{LeeITCST13} as
 \begin{gather*}
 	\norm{E}_F = \sqrt{\tr{E^T E}} = \frac{1}{2} \sqrt{\tr{G^2} + \tr{R^T R_d G}^2} .
@@ -724,22 +913,35 @@ Using~\crefrange{eqn:AB_bound}{eqn:eRB_bound} one can define \( H \) in terms of
 \subsection{Proof of~\Cref{prop:adaptive_control}}\label{proof:adaptive_control}
 Consider the Lyapunov function \( \mathcal{V} \) given by
 \begin{align*}
-	\mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi + c J e_\Omega \cdot e_R + \frac{1}{2 k_\Delta} e_\Delta \cdot e_\Delta , \label{eqn:v_adapt}
+	\mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi + c J e_\Omega \cdot e_R + \frac{1}{2 k_\Delta} e_\Delta \cdot e_\Delta , %\label{eqn:v_adapt}
 \end{align*}
-over the domain \( D \) in~\cref{eqn:domain}.
-From~\Cref{prop:eR_dot_bound}, the Lyapunov function is bounded in \( D \) by
+over the domain \( D \), defined in~\cref{prop:config_error}. 
+In this set, the properties of~\Cref{prop:config_error,prop:error_dyn} are satisfied.
+%Furthermore, the set \( D \) is an open neighborhood of the desired attitude and Lyapunov stability results are valid in this set.
+
+From~\Cref{prop:config_error}, the configuration error function is locally quadratic and it is bounded in \( D \) by~\cref{eq:psi_bound}.
+Using this, the Lyapunov function \( \mathcal{V} \) is bounded by
 \begin{align*} %\label{eqn:v_upper_bound}
-	\mathcal{V} \leq z^T W z ,
+	z^T W_1 z \leq \mathcal{V} \leq z^T W_2 z ,
 \end{align*}
-where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = [\|e_R\|,\|e_\Omega\|,\|e_\Delta\|]^T\in\R^3 \) and the matrix \(W \in \R^{3 \times 3}\) is given by
-\begin{gather*}
-	W = \begin{bmatrix}
-		k_R \psi & \frac{1}{2} c \lambda_M & 0 \\
+where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = [\|e_R\|,\|e_\Omega\|,\|e_\Delta\|]^T\in\R^3 \) and the matrices \(W_1,W_2 \in \R^{3 \times 3}\) are given by
+\begin{align*}
+	W_1 & = \begin{bmatrix}
+		k_R n_1 & -\frac{1}{2} c \lambda_M & 0 \\
+		-\frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_m & 0 \\
+		0 & 0 & \frac{1}{2 k_\Delta}
+	\end{bmatrix},\\
+	W_2 & = \begin{bmatrix}
+		k_R n_2 & \frac{1}{2} c \lambda_M & 0 \\
 		\frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_M & 0 \\
 		0 & 0 & \frac{1}{2 k_\Delta}
 	\end{bmatrix} .
-\end{gather*}
-The time derivative of \( \mathcal{V}\) with the control inputs~\cref{eqn:adaptive_control} is given by
+\end{align*}
+%\begin{gather*}
+%\frac{1}{2}\lambda_m k_R n_1 - \frac{1}{4}c^2 \lambda_M^2 >0\\
+%\frac{2\lambda_m k_R n_1}{\lambda_M^2} > c^2 \\
+%\end{gather*}
+The time derivative of \( \mathcal{V}\) with the control input defined by~\cref{eqn:adaptive_control} is given as
 \begin{align*}
 	\dot{\mathcal{V}} =& - k_\Omega e_\Omega^T e_\Omega + \parenth{e_\Omega + c e_R}^T W e_\Delta - k_R c e_R^T e_R \nonumber\\
 	&- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} , \label{eqn:vdot}
@@ -749,7 +951,7 @@ The terms linearly dependent on \( e_\Delta\) are combined with~\cref{eqn:delta_
 \begin{align*}
 	 e_\Delta^T \parenth{W^T \parenth{e_\Omega + c e_R} - \frac{1}{k_\Delta} \dot{\bar{\Delta}}} = 0 . 
 \end{align*}
-Using~\Cref{prop:eR_dot_bound} an upper bound on \( \dot{\mathcal{V}} \) is written as
+Using~\Cref{prop:eR_dot_bound}, an upper bound on \( \dot{\mathcal{V}} \) is written as
 \begin{gather*}
 	\dot{\mathcal{V}} \leq -\zeta^T M \zeta ,
 \end{gather*}
@@ -760,9 +962,17 @@ where $\zeta=[\|e_R\|,\|e_\Omega\|]\in\R^2$, and the matrix \( M \in \R^{2 \time
 		\frac{k_\Omega c}{2} & k_\Omega - c \lambda_M H
 	\end{bmatrix} .
 \end{gather*}
-If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied the matrix \( M \) is positive definite.
-This implies that $\dot{\mathcal{V}}$ is negative semidefinite and $\lim_{t\to\infty} \zeta=0$. 
-As the Lyapunov function is non-increasing $z$ is uniformly bounded. 
+%\begin{gather*}
+%k_R c (k_\Omega -c \lambda_M H) -\frac{1}{4}k_\Omega^2 c^2 < 0\\
+%k_R (k_\Omega -c \lambda_M H) -\frac{1}{4}k_\Omega^2 c < 0\\
+%4k_R k_\Omega -c(4k_R \lambda_M H +k_\Omega^2) <0
+%\end{gather*}
+
+If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied then the matrices \( W_1, W_2 \) and \( M \) are positive definite.
+This implies that $\mathcal{V}$ is positive definite and decrescent, and $\dot{\mathcal{V}}$ is negative semidefinite in the domain $D$. As such, the zero equilibrium is stable in the sense of Lyapunov, and all of the error variables are bounded. Furthermore, $\lim_{t\to\infty} \zeta=0$ according to the LaShalle-Yoshizawa theorem~\cite{khalil1996}. 
+
+%and 
+%As the Lyapunov function is non-increasing $z$ is uniformly bounded. 
 %	
 %	
 %	This implies that the Lyapunov function \( V \) is non-increasing and bounded from below.
@@ -771,30 +981,22 @@ As the Lyapunov function is non-increasing $z$ is uniformly bounded.
 %	The domain \( D \) does that include the undesired equilibria and ensures that as \( e_R \to 0 \) the attitude also converges \( R \to R_d \).
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

-%\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
-                                  % on the last page of the document manually. It shortens
-                                  % the textheight of the last page by a suitable amount.
-                                  % This command does not take effect until the next page
-                                  % so it should come on the page before the last. Make
-                                  % sure that you do not shorten the textheight too much.
-                                  
 \bibliography{BibMaster,library}
 \bibliographystyle{IEEEtran}
-
 \biography{profile}{Shankar Kulumani}
     {is a PhD Candidate in the Department of Mechanical and Aerospace Engineering at George Washington University. 
-    He received his bachelor's degree in Astronautical Engineering from the United States Air Force Academy in 2009 and his master's in Aeronautical and Astronautical Engineering from Purdue University in 2013.
+    He received his bachelor's degree in Astronautical Engineering from the US Air Force Academy in 2009 and his master's degree in Aeronautical and Astronautical Engineering from Purdue University in 2013.
     % He previously served as Deputy Space Vehicles Lead for the ORS-1 (Operationally Responsive Space ) satellite program, and as Lead Test Engineer in the Guidance, Navigation, and Control group at Air Force Research Laboratory located at Kirtland AFB, NM.
     % He is now currently a reserve air force officer where he serves as Threat Systems Engineer for the Missle and Space Intelligence Center, Defense Intelligence Agency.
     His current research interests include the application of geometric mechanics and control to aerospace systems. 
     }
-
 \biography{Lee}{Taeyoung Lee}
     {is an associate professor of Department of Mechanical and Aerospace Engineering at the George Washington University. 
     He received his doctoral degree in Aerospace Engineering and his master's degree in Mathematics at the University of Michigan in 2008. 
     His research interests include computational geometric mechanics and control of complex systems.}    
 \clearafterbiography\relax
 \clearafterbiography\relax
+
 \end{multicols}

 \end{document}

### 2017-05-04 manuscript.tex
Figure width defined in terms of textwidth

@@
-\documentclass[10pt,fleqn]{IJCAS}  % Comment this line out if you need a4paper
+\documentclass{IJCAS}  % Comment this line out if you need a4paper
 \usepackage{ijcas_packages}
@@
 %% Authors do not have to modify this section.
-% \journalvolumn{VV}
-% \journalnumber{N}
-% \journalyear{YYYY}
-% \setarticlestartpagenumber{1}
+\journalvolumn{VV}
+\journalnumber{N}
+\journalyear{YYYY}
+\setarticlestartpagenumber{1}
 %%%% End of Editorial Information
@@
 
-\runningtitle{1}{Shankar Kulumani and Taeyoung Lee}{Constrained Geometric Attitude Control on \( \SO \) }
+\runningtitle{2017}{Shankar Kulumani and Taeyoung Lee}{Constrained Geometric Attitude Control on \( \SO \) }
 
@@
 Similarly, the positions of celestial objects are defined on the celestial sphere in terms of right ascension and declination. 
+\the\columnwidth
 \end{multicols}
@@
     \centering 
-    \subfigure[Attractive \( A(R) \) \label{fig:attract_error}]{\includegraphics[width=0.33\columnwidth]{attract_error} }~
-    \subfigure[Repulsive \( B(R) \) \label{fig:avoid_error} ]{\includegraphics[width=0.33\columnwidth]{avoid_error} }~
-    \subfigure[Combined \( \Psi \) \label{fig:combined_error}]{\includegraphics[width=0.33\columnwidth]{combined_error} }%
+    \subfigure[Attractive \( A(R) \) \label{fig:attract_error}]{\includegraphics[width=0.33\textwidth]{attract_error} }~
+    \subfigure[Repulsive \( B(R) \) \label{fig:avoid_error} ]{\includegraphics[width=0.33\textwidth]{avoid_error} }~
+    \subfigure[Combined \( \Psi \) \label{fig:combined_error}]{\includegraphics[width=0.33\textwidth]{combined_error} }%
     \caption{Visualization of Configuration Error Functions using spherical coordinate representation}

### 2017-05-05 manuscript.tex
Remove the errant columnwidth
Update figures

@@
 Similarly, the positions of celestial objects are defined on the celestial sphere in terms of right ascension and declination. 
-\the\columnwidth
 \end{multicols}
@@
     \centering 
-    \subfigure[Attractive \( A(R) \) \label{fig:attract_error}]{\includegraphics[width=0.33\textwidth]{attract_error} }~
-    \subfigure[Repulsive \( B(R) \) \label{fig:avoid_error} ]{\includegraphics[width=0.33\textwidth]{avoid_error} }~
-    \subfigure[Combined \( \Psi \) \label{fig:combined_error}]{\includegraphics[width=0.33\textwidth]{combined_error} }%
+    \subfigure[Attractive \( A(R) \) \label{fig:attract_error}]{\includegraphics{figures/avoid_error.pdf}}~
+    \subfigure[Repulsive \( B(R) \) \label{fig:avoid_error} ]{\includegraphics{figures/attract_error.pdf}}~
+    \subfigure[Combined \( \Psi \) \label{fig:combined_error}]{\includegraphics{figures/combined_error.pdf}}%
     \caption{Visualization of Configuration Error Functions using spherical coordinate representation}

### 2017-05-09 manuscript.tex
Add all the pgf images

@@
     \centering 
-    \subfigure[Attractive \( A(R) \) \label{fig:attract_error}]{\includegraphics{figures/avoid_error.pdf}}~
-    \subfigure[Repulsive \( B(R) \) \label{fig:avoid_error} ]{\includegraphics{figures/attract_error.pdf}}~
+    \subfigure[Attractive \( A(R) \) \label{fig:attract_error}]{\includegraphics{figures/attract_error.pdf}}~
+    \subfigure[Repulsive \( B(R) \) \label{fig:avoid_error} ]{\includegraphics{figures/avoid_error.pdf}}~
     \subfigure[Combined \( \Psi \) \label{fig:combined_error}]{\includegraphics{figures/combined_error.pdf}}%
@@
     \centering 
-    \subfigure[Attitude error vector \(e_R\) components \label{fig:eR_con}]{\includegraphics[width=0.3\columnwidth]{eR_con}  }~
-    \subfigure[Configuration error \( \Psi \) \label{fig:Psi_con}]{\includegraphics[width=0.3\columnwidth]{figures/Psi_con.pdf} }
-    \subfigure[Angle to each constraint \label{fig:con_angles_con}]{\includegraphics[width=0.3\columnwidth]{figures/constraint_angles_con.pdf} } 
+    \subfigure[Attitude error vector \(e_R\) components \label{fig:eR_con}]{\input{pgf/eR_noadapt.pgf}}~
+    \subfigure[Configuration error \( \Psi \) \label{fig:Psi_con}]{\input{pgf/Psi_noadapt.pgf}}~
+    \subfigure[Angle to each constraint \label{fig:con_angles_con}]{\input{pgf/ang_con_noadapt.pgf}} 
     \caption{Attitude stabilization without adaptive update law}
@@
   \centering 
-    \subfigure[Configuration error \( \Psi \)\label{fig:Psi_adapt}]{\includegraphics[width=0.4\columnwidth]{Psi_adapt} }~
-    \subfigure[Angle to each constraint \label{fig:con_angles}]{\includegraphics[width=0.4\columnwidth]{constraint_angles} }\\
-    \subfigure[Disturbance estimate \( \bar \Delta \) components \label{fig:delta_adapt} ]{\includegraphics[width=0.4\columnwidth]{Delta_adapt}}~
+  \subfigure[Configuration error \( \Psi \)\label{fig:Psi_adapt}]{\input{pgf/Psi_adapt.pgf}}~
+  \subfigure[Angle to each constraint \label{fig:con_angles}]{\input{pgf/ang_con_adapt.pgf}}\\
+  \subfigure[Disturbance estimate \( \bar \Delta \) components \label{fig:delta_adapt} ]{\input{pgf/dist_adapt.pgf}}~
     \subfigure[Attitude trajectory \label{fig:cad_adapt}]{\includegraphics[trim={10cm 0 10cm 0},clip,width=0.4\columnwidth]{cad_adapt} }
@@
     \centering 
-    \subfigure[{Configuration error \( \Psi \)} \label{fig:Psi_tv} ]{\includegraphics[width=0.3\columnwidth]{Psi_tv} }~
-    \subfigure[{Angle to constraint } \label{fig:con_angle_tv}]{\includegraphics[width=0.3\columnwidth]{figures/constraint_angle_tv.pdf} }~
-    \subfigure[{Disturbance estimate \(\bar\Delta\) components} \label{fig:Delta_tv}]{\includegraphics[width=0.3\columnwidth]{figures/delta_tv} }
+    \subfigure[{Configuration error \( \Psi \)} \label{fig:Psi_tv} ]{\input{pgf/Psi_timevarying.pgf}}~
+    \subfigure[{Angle to constraint } \label{fig:con_angle_tv}]{\input{pgf/ang_con_timevarying.pgf}}~
+    \subfigure[{Disturbance estimate \(\bar\Delta\) components} \label{fig:Delta_tv}]{\input{pgf/dist_timevarying.pgf}}
     \caption{Time-varying external disturbance simulation}
@@
 
+\end{multicols}
+\begin{figure}[H]
+    \centering 
+    \subfigure[{Attitude error vector \(e_R\)} components\label{fig:eR_exp}]{\input{pgf/eR_exp.pgf}}~
+    \subfigure[{Configuration error \( \Psi \)} \label{fig:Psi_exp} ]{\input{pgf/Psi_exp.pgf}}~
+    \subfigure[{Control input \( u\) } components\label{fig:u_exp}]{\input{pgf/u_exp.pgf}}\\
+    \subfigure[{Attitude Trajectory } \label{fig:traj_exp}]{\includegraphics[width=0.3\columnwidth]{traj_exp} }~
+    \subfigure[{Angle to constraint } \label{fig:con_angle_exp}]{\input{pgf/ang_con_exp.pgf}}
+    \caption{Constrained Attitude stabilization experiment}
+    \label{fig:exp} 
+\end{figure}
+\begin{multicols}{2}
 Attitude information is measured by a combination of both on and off board sensor systems.
@@
 
-\end{multicols}
-\begin{figure}[H]
-    \centering 
-    \subfigure[{Attitude error vector \(e_R\)} components\label{fig:eR_exp}]{\includegraphics[width=0.3\columnwidth]{eR_exp}  }~
-    \subfigure[{Configuration error \( \Psi \)} \label{fig:Psi_exp} ]{\includegraphics[width=0.3\columnwidth]{Psi_exp} }~
-    \subfigure[{Control input \( u\) } components\label{fig:u_exp}]{\includegraphics[width=0.3\columnwidth]{u_exp}  }\\
-    \subfigure[{Attitude Trajectory } \label{fig:traj_exp}]{\includegraphics[width=0.3\columnwidth]{traj_exp} }~
-    \subfigure[{Angle to constraint } \label{fig:con_angle_exp}]{\includegraphics[width=0.3\columnwidth]{figures/constraint_angles_exp.pdf} }
-    \caption{Constrained Attitude stabilization experiment}
-    \label{fig:exp} 
-\end{figure}
-\begin{multicols}{2}
 The hexrotor avoids the constrained region illustrated by the circular cone in~\cref{fig:traj_exp}, by rotating around the boundary of the constraint. 

### 2017-05-09 manuscript.tex
Update error funciton visualization

@@
     \centering 
-    \subfigure[Attractive \( A(R) \) \label{fig:attract_error}]{\includegraphics{figures/attract_error.pdf}}~
-    \subfigure[Repulsive \( B(R) \) \label{fig:avoid_error} ]{\includegraphics{figures/avoid_error.pdf}}~
-    \subfigure[Combined \( \Psi \) \label{fig:combined_error}]{\includegraphics{figures/combined_error.pdf}}%
+    \subfigure[Attractive \( A(R) \) \label{fig:attract_error}]{\includegraphics[trim={8mm 0 8mm 0}, clip]{figures/attract_error.pdf}}~
+    \subfigure[Repulsive \( B(R) \) \label{fig:avoid_error} ]{\includegraphics[trim={8mm 0 8mm 0}, clip]{figures/avoid_error.pdf}}~
+    \subfigure[Combined \( \Psi \) \label{fig:combined_error}]{\includegraphics[trim={8mm 0 8mm 0}, clip]{figures/combined_error.pdf}}%
     \caption{Visualization of Configuration Error Functions using spherical coordinate representation}

### 2017-05-10 manuscript.tex
Fix some typos using vim spell

@@
 \begin{multicols}{2}
-We apply this concept and parametrize the rotation matrix \( R \in \SO \) in terms of the spherical angles \( \SI{-180}{\degree} \leq \lambda \leq \SI{180}{\degree}  \) and \( \SI{-90}{\degree} \leq \beta \leq \SI{90}{\degree} \).
+We apply this concept and parameterize the rotation matrix \( R \in \SO \) in terms of the spherical angles \( \SI{-180}{\degree} \leq \lambda \leq \SI{180}{\degree}  \) and \( \SI{-90}{\degree} \leq \beta \leq \SI{90}{\degree} \).
 Using the elementary Euler rotations, the rotation matrix is now defined as \( R = \exp( \lambda \hat{e}_2) \exp( \beta \hat{e}_3) \).
@@
 We extend the results of the previous section with the addition of a fixed but unknown disturbance \( \Delta \).
-This scenario is typical of many mechanical systems and represents unmodeled dynamics or external moments acting on the system.
+This scenario is typical of many mechanical systems and represents unmodelled dynamics or external moments acting on the system.
 For example, Earth orbiting spacecraft typically experience a torque due to a gravitational gradient.
@@
 For example, a system wishing to avoid pointing at a diffuse obstacle, such as incoming debris, may chose an appropriate value of \( \theta \), based on the best available information, and a relatively low \( \alpha \) to ensure additional safety margin near the constraint boundary.
-Similarly, in an environment with several densely spaced obstacles, such as that presented in~\cref{fig:cad_adapt}, a much larger \( \alpha \) would enable more aggressive manuevers which pass closer to the constraint boundary without violation.
+Similarly, in an environment with several densely spaced obstacles, such as that presented in~\cref{fig:cad_adapt}, a much larger \( \alpha \) would enable more aggressive maneuvers which pass closer to the constraint boundary without violation.
 This would increase the allowable region of operation in a highly constrained environment.
@@
 \Cref{fig:con_angles} shows that the angle, \( \arccos(r^T R^T v_i) \) and measured in degrees, between the body fixed sensor and each constraint is satisfied for the entire maneuver.
-In addition, the estimate of the disturbance converges to the the true value as shown in~\cref{fig:delta_adapt}.
+In addition, the estimate of the disturbance converges to the true value as shown in~\cref{fig:delta_adapt}.
 
@@
 
-\subsection{Attitude Parameterizations}\label{ssec:attitude_parameterization}
 \end{multicols}
@@
 \begin{multicols}{2}
+\subsection{Attitude Parameterizations}\label{ssec:attitude_parameterization}
 % Discuss the benefits of using this geometric representation as compared to Euler angles or quaternions
@@
 % discuss the unwinding phenomenon with quaternions
-
+\subsection{Time-varying Disturbance}\label{ssec:time_varying}
+The form of the uncertainty, given in~\cref{eqn:Wdot}, is commonly used in the adaptive control literature~\cite{LeeITCST13,ioannou2012}. 
+A wide variety of realistic disturbances, such as gravitational gradients or malfunctioning thrusters for spacecraft scenarios, are accurately represented via this model. 
+In addition, it is possible to represent the uncertainty of a time-varying inertia matrix as an equivalent external disturbance. 
+For example, Euler's law gives the relationship for the rate of change of angular momentum as
+\begin{align*}
+    M_{ext} = \dot{\vecbf{H}} = \dot{J} \vecbf{\Omega} + J \dot{\vecbf{\Omega}} .
+\end{align*}
+Using this, we can see that an instantaneous change in \( J \) is proportional to an external moment.
+Finally, it has been shown that this adaptive control formulation is able to handle time-varying disturbances under some mild assumptions~\cite{ioannou2012}.
+
+We demonstrate the ability to handle an uncertain time-varying disturbance via numerical example.
+The system is identical to the one presented in~\Cref{sec:numerical_simulation}, however we modify the external disturbance. 
+The external disturbance is the superposition of constant and time-varying terms as
+\begin{align*}
+    \Delta = \begin{bmatrix} 0.2 \\ 0.2 \\0.2 \end{bmatrix} + 0.02 \begin{bmatrix} \sin 9 t \\ \cos 9 t \\ \frac{1}{2} \parenth{\sin 9t + \cos 9t}\end{bmatrix} \si{\newton\meter}.
+\end{align*}
+We define a constraint in the inertial frame as \( v = [\frac{1}{\sqrt{2}}, \frac{1}{\sqrt{2}}, 0]^T \) with \( \theta = \ang{12} \).
+The initial state is defined as \(R(0) = \exp( \frac{\pi}{2} \hat{e}_3) \), while the desired state is \(R_d =I \).
+The goal is to rotate the vehicle about the \( e_3 \) axis while avoiding the obstacle and compensating for the time-varying disturbance.
+
+\Cref{fig:tv} demonstrates the ability for the adaptive controller, which is presented in~\Cref{prop:adaptive_control}, to handle time-varying disturbances.
+\Cref{fig:Psi_tv} shows the non-dimensional value of the configuration error function and demonstrates that the adaptive controller is able to stabilize the system to the desired attitude configuration.
+In addition,~\cref{fig:con_angle_tv} shows that the constraint is never violated as the angle between the body-fixed sensor \( r \) and the constraint \( v \) is greater than \SI{12}{\degree} over the entire attitude maneuver.
+We can see in~\cref{fig:Delta_tv} that that estimate \(\bar \Delta \) for each of the components accurately tracks the true disturbance after approximately~\SI{5}{\second}.
+
+\section{Experiment on Hexrotor UAV}\label{sec:experiment}
+\vspace{-5mm}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width = 0.50\columnwidth]{hexrotor}
+    \caption{Attitude control testbed~\label{fig:hexrotor}}
+\end{figure}
+\vspace{-3mm}
+A hexrotor unmanned aerial vehicle (UAV), as seen in~\cref{fig:hexrotor}, has been developed at the Flight Dynamics and Controls Laboratory (FDCL) at the George Washington University~\cite{kaufman2014}.
+The UAV is composed of three pairs of counter-rotating propellers. 
+Typical UAVs are composed of four or more co-planar propellers.
+As a result, these systems are underactuated and unable to impart a force along every degree of freedom.
+For example, quadrotor UAVs are unable to translate laterally without first conducting a rotation.
+Conversely, the propeller pairs of the hexrotor are angled relative to one another to allow for a fully actuated rigid body.
+This allows the hexrotor to impart a force in any direction and a moment about any axis. 
 \end{multicols}
-\begin{figure}[h]
+\begin{figure}[H]
     \centering 
@@
 \end{figure}
-\begin{multicols}{2}
-\subsection{Time-varying Disturbance}\label{ssec:time_varying}
-
-The form of the uncertainty, given in~\cref{eqn:Wdot}, is commonly used in the adaptive control literature~\cite{LeeITCST13,ioannou2012}. 
-A wide variety of realistic disturbances, such as gravitational gradients or malfunctioning thrusters for spacecraft scenarios, are accurately represented via this model. 
-In addition, it is possible to represent the uncertainty of a time-varying inertia matrix as an equivalent external disturbance. 
-For example, Euler's law gives the relationship for the rate of change of angular momentum as
-\begin{align*}
-    M_{ext} = \dot{\vecbf{H}} = \dot{J} \vecbf{\Omega} + J \dot{\vecbf{\Omega}} .
-\end{align*}
-Using this, we can see that an instantaneous change in \( J \) is proportional to an external moment.
-Finally, it has been shown that this adaptive control formulation is able to handle time-varying disturbances under some mild assumptions~\cite{ioannou2012}.
-
-We demonstrate the ability to handle an uncertain time-varying disturbance via numerical example.
-The system is identical to the one presented in~\cref{sec:numerical_simulation}, however we modify the external disturbance. 
-The external disturbance is the superposition of constant and time-varying terms as
-\begin{align*}
-    \Delta = \begin{bmatrix} 0.2 \\ 0.2 \\0.2 \end{bmatrix} + 0.02 \begin{bmatrix} \sin 9 t \\ \cos 9 t \\ \frac{1}{2} \parenth{\sin 9t + \cos 9t}\end{bmatrix} \si{\newton\meter}.
-\end{align*}
-We define a constraint in the inertial frame as \( v = [\frac{1}{\sqrt{2}}, \frac{1}{\sqrt{2}}, 0]^T \) with \( \theta = \ang{12} \).
-The initial state is defined as \(R(0) = \exp( \frac{\pi}{2} \hat{e}_3) \), while the desired state is \(R_d =I \).
-The goal is to rotate the vehicle about the \( e_3 \) axis while avoiding the obstacle and compensating for the time-varying disturbance.
-
-\Cref{fig:tv} demonstrates the ability for the adaptive controller, which is presented in~\Cref{prop:adaptive_control}, to handle time-varying disturbances.
-\Cref{fig:Psi_tv} shows the non-dimensional value of the configuration error function and demonstrates that the adaptive controller is able to stabilize the system to the desired attitude configuration.
-In addition,~\cref{fig:con_angle_tv} shows that the constraint is never violated as the angle between the body-fixed sensor \( r \) and the constraint \( v \) is greater than \SI{12}{\degree} over the entire attitude maneuver.
-We can see in~\cref{fig:Delta_tv} that that estimate \(\bar \Delta \) for each of the components accurately tracks the true disturbance after approximately~\SI{5}{\second}.
-
-\section{Experiment on Hexrotor UAV}\label{sec:experiment}
-\begin{figure}[H]
-    \centering
-    \includegraphics[width = 0.75\columnwidth]{hexrotor}
-    \caption{Attitude control testbed~\label{fig:hexrotor}}
-\end{figure}
-A hexrotor unmanned aerial vehicle (UAV), as seen in~\cref{fig:hexrotor}, has been developed at the Flight Dynamics and Controls Laboratory (FDCL) at the George Washington University~\cite{kaufman2014}.
-The UAV is composed of three pairs of counter-rotating propellers. 
-Typical UAVs are composed of four or more co-planar propellers.
-As a result, these systems are underactuated and unable to impart a force along every degree of freedom.
-For example, quadrotor UAVs are unable to translate laterally without first conducting a rotation.
-Conversely, the propeller pairs of the hexrotor are angled relative to one another to allow for a fully actuated rigid body.
-This allows the hexrotor to impart a force in any direction and a moment about any axis.
-
-\end{multicols}
-\begin{figure}[H]
+\begin{figure}[t]
     \centering 
@@
 \end{gather*}
-A straightforward substitution of~\cref{eqn:A_dot,eqn:B_dot,eqn:A,eqn:B} into this and appplying~\cref{eqn:eR} shows~\cref{eqn:psi_dot}.
+A straightforward substitution of~\cref{eqn:A_dot,eqn:B_dot,eqn:A,eqn:B} into this and applying~\cref{eqn:eR} shows~\cref{eqn:psi_dot}.
 We show~\cref{eqn:eW_dot} by rearranging~\cref{eqn:Wdot} as 
@@
 \end{gather*}
-Using the the given domain \( r^T R^T v \leq \beta \) gives the upper bound~\cref{eqn:F_bound}.
+Using the given domain \( r^T R^T v \leq \beta \) gives the upper bound~\cref{eqn:F_bound}.
 The bound on \( e_{R_A} \) is given in~\cref{eqn:psi_lower_bound} while \( e_{R_B} \) arises from the definition of the cross product \( \norm{a \times b} = \norm{a} \norm{b} \sin \theta \).
@@
 As such, the zero equilibrium is stable in the sense of Lyapunov, and all of the error variables are bounded.
-Furthermore, $\lim_{t\to\infty} \zeta=0$ according to the LaShalle-Yoshizawa theorem~\cite{khalil1996}.
+Furthermore, $\lim_{t\to\infty} \zeta=0$ according to the LaSalle-Yoshizawa theorem~\cite{khalil1996}.
 

### 2017-05-10 manuscript.tex
Fix some typos using vim spell

@@
 
+\subsection{Attitude Parameterizations}\label{ssec:attitude_parameterization}
 \end{multicols}
@@
 \begin{multicols}{2}
-\subsection{Attitude Parameterizations}\label{ssec:attitude_parameterization}
 % Discuss the benefits of using this geometric representation as compared to Euler angles or quaternions
@@
 % discuss the unwinding phenomenon with quaternions
+
+\end{multicols}
+\begin{figure}[h]
+    \centering 
+    \subfigure[{Configuration error \( \Psi \)} \label{fig:Psi_tv} ]{\input{pgf/Psi_timevarying.pgf}}~
+    \subfigure[{Angle to constraint } \label{fig:con_angle_tv}]{\input{pgf/ang_con_timevarying.pgf}}~
+    \subfigure[{Disturbance estimate \(\bar\Delta\) components} \label{fig:Delta_tv}]{\input{pgf/dist_timevarying.pgf}}
+    \caption{Time-varying external disturbance simulation}
+    \label{fig:tv} 
+\end{figure}
+\begin{multicols}{2}
 \subsection{Time-varying Disturbance}\label{ssec:time_varying}
+
 The form of the uncertainty, given in~\cref{eqn:Wdot}, is commonly used in the adaptive control literature~\cite{LeeITCST13,ioannou2012}. 
@@
 \section{Experiment on Hexrotor UAV}\label{sec:experiment}
-\vspace{-5mm}
 \begin{figure}[H]
     \centering
-    \includegraphics[width = 0.50\columnwidth]{hexrotor}
+    \includegraphics[width = 0.75\columnwidth]{hexrotor}
     \caption{Attitude control testbed~\label{fig:hexrotor}}
 \end{figure}
-\vspace{-3mm}
 A hexrotor unmanned aerial vehicle (UAV), as seen in~\cref{fig:hexrotor}, has been developed at the Flight Dynamics and Controls Laboratory (FDCL) at the George Washington University~\cite{kaufman2014}.
@@
 This allows the hexrotor to impart a force in any direction and a moment about any axis.
+
 \end{multicols}
 \begin{figure}[H]
-    \centering 
-    \subfigure[{Configuration error \( \Psi \)} \label{fig:Psi_tv} ]{\input{pgf/Psi_timevarying.pgf}}~
-    \subfigure[{Angle to constraint } \label{fig:con_angle_tv}]{\input{pgf/ang_con_timevarying.pgf}}~
-    \subfigure[{Disturbance estimate \(\bar\Delta\) components} \label{fig:Delta_tv}]{\input{pgf/dist_timevarying.pgf}}
-    \caption{Time-varying external disturbance simulation}
-    \label{fig:tv} 
-\end{figure}
-\begin{figure}[t]
     \centering 

### 2017-05-10 manuscript.tex
Incorporate suggestions from Dr. Lee
Fix some typos and define some missing terms.
Also clean up some of the presentation for awkward equations.

--- 2017-05-10 manuscript.tex
@@
 Attitude control is typically studied using a variety of attitude parameterizations, such as Euler angles or quaternions~\cite{shuster1993}.
-All attitude parameterizations fail to represent the nonlinear configuration space both globally and uniquely~\cite{chaturvedi2011a}.
+Attitude parameterizations fail to represent the nonlinear configuration space both globally and uniquely~\cite{chaturvedi2011a}.
 For example, minimal attitude representations, such as Euler angle sequences or modified Rodriguez parameters, suffer from singularities.
@@
 During implementation, the designer must carefully resolve this non-unique representation in quaternion based attitude control systems to avoid undesirable unwinding behavior~\cite{bhat2000}.
-This behavior is characterized by situations where the rigid body starts close to the desired attitude, yet the system unnecessarily rotates through a large angle even while the initial error is small.
+This behavior is characterized by situations where the rigid body starts close to the desired attitude, yet the system unnecessarily rotates through a large angle inspite of a small initial error.
 
@@
 We use the notation \( \hat{x}\) and \( \parenth{x}^\wedge\) interchangeably.
-In particular, we use the latter form when the expression for the argument of the \textit{hat} map is long. 
+In particular, we use the latter form when the expression for the argument of the \textit{hat} map is complicated. 
 Several properties of the hat map are summarized as
@@
 	\end{gather}
-	Then the zero equilibrium of the attitude error is asymptotically stable, and the inequality constraint is satisfied.
+	Then the zero equilibrium of the attitude error is asymptotically stable, and the inequality constraint is always satisfied.
 \end{prop}
@@
 \begin{gather*}
-  \hspace{-5mm}
     J = \begin{bmatrix}
-	\num{5.57e-3} & \num{6.17e-5} & \num{-2.50e-5} \\
-	\num{6.17e-5} & \num{5.57e-3} & \num{1.00e-5} \\
-	\num{-2.50e-5} & \num{1.00e-5} & \num{1.05e-2}
-	\end{bmatrix} \si{\kilo\gram\meter\squared} .
+	\num{5.5} & \num{0.06} & \num{-0.03} \\
+	\num{0.06} & \num{5.5} & \num{0.01} \\
+	\num{-0.03} & \num{0.01} & \num{0.1}
+    \end{bmatrix} \times 10^{-3}~\si{\kilo\gram\meter\squared} .
 \end{gather*} 
@@
 
-The initial state is defined as \(R_0 =  \exp(\ang{225} \times \frac{\pi}{180} \hat{e}_3), \Omega_0 = 0\). 
+The initial state is defined as \(R_0 =  \exp(\ang{225} \times \frac{\pi}{180} \hat{e}_3), \Omega_0 = 0\), with \( e_3 = \begin{bmatrix} 0 & 0 & 1 \end{bmatrix}^T \).
 The desired state is \( R_d = I,\Omega_d = 0\).
@@
 The inequality constraints from~\Cref{tab:constraints} are depicted as red cones, where the cone half angle is \( \theta \).
-The control system is able to asymptotically converge to zero attitude error.
+The control system is able to asymptotically converge to the desired attitude.
 \Cref{fig:con_angles} shows that the angle, \( \arccos(r^T R^T v_i) \) and measured in degrees, between the body fixed sensor and each constraint is satisfied for the entire maneuver.
@@
 
-To demonstrate the effect of the kinematic singularities inherent with Euler angles we will represent the attitude of the body fixed reference frame, \( \vecbf{b}_i \), with respect to the inertial frame, \( \vecbf{e}_i\), in terms of the \( 3-1-3\) Euler angle sequence.
+To demonstrate the effect of the kinematic singularities inherent with Euler angles we will represent the attitude of the body fixed reference frame, \( \vecbf{b}_i \), with respect to the inertial frame, \( \vecbf{e}_i\), in terms of the 3-1-3 Euler angle sequence.
 More explicitly, this corresponds to the rotation sequence \( \theta_1 \vecbf{b}_3 , \theta_2 \vecbf{b}_1, \theta_3 \vecbf{b}_3 \).
@@
 This results in the UAV performing a \ang{90} yaw rotation about the vertical axis of the spherical joint and the constrained region is on the shortest path connecting $R_0$ and $R_d$. 
-The attitude control system is identical to the one presented in~\Cref{prop:adaptive_control} with the exception of a gravity moment term, \( M_g = r_{cg} \times m g R^T e_3\) which represents the gravitational moment due to the difference between the center of mass and the center of rotation.
+The attitude control system is identical to the one presented in~\Cref{prop:adaptive_control} with the exception of a gravity moment term, \( M_g = r_{cg} \times m g R^T e_3\) which represents the gravitational moment due to the distance \( r_{cg} \) between the center of mass and the center of rotation.
 In addition, the following parameters were also modified: \(k_R = 0.4, k_\Omega = 0.7 ,c = 0.1 , \alpha = 8 \text{ and } k_\Delta = 0.05\) to account for the differences in the hardware model of the hexrotor.
@@
 \begin{align*}
-    \dirDiff{\parenth{\dirDiff{A}{R}}}{R} &= \eta \cdot \frac{1}{2}\parenth{G R_d^T \delta R - \delta R^T R_d G}^\vee , \\
-    &= \eta \cdot \frac{1}{2} \parenth{G R_d^T R \hat \eta + \hat \eta R^T R_d G}^\vee,\\
-    &= \eta \cdot \frac{1}{2} \bracket{\parenth{\braces{\tr{R^T R_d G} I - R^T R_d G} \eta}^\wedge}^\vee , \\
+    \dirDiff{\parenth{\dirDiff{A}{R}}}{R} &= \eta \cdot \frac{1}{2}\parenth{G R_d^T \delta R - \delta R^T R_d G}^\vee  \\
+    &= \eta \cdot \frac{1}{2} \parenth{G R_d^T R \hat \eta + \hat \eta R^T R_d G}^\vee\\
+    &= \eta \cdot \frac{1}{2} \bracket{\parenth{\braces{\tr{R^T R_d G} I - R^T R_d G} \eta}^\wedge}^\vee  \\
     &= \eta \cdot \frac{1}{2} \parenth{\tr{R^T R_d G} I - R^T R_d G}\eta ,
@@
 \begin{align*}
-    \parenth{\delta R^T v}^\wedge r &= - \hat{r} \delta R ^T v , \\
-    &= - \hat{r} \parenth{R \hat \eta}^T v , \\
-    &= \hat{r} \parenth{\hat{\eta} R^T } v , \\
+    \parenth{\delta R^T v}^\wedge r &= - \hat{r} \delta R ^T v  \\
+    &= - \hat{r} \parenth{R \hat \eta}^T v  \\
+    &= \hat{r} \parenth{\hat{\eta} R^T } v  \\
     &= - \hat{r} \parenth{R^T v}^\wedge \eta ,
@@
 \begin{align*}
-    r^T \delta R^T v &= r^T \parenth{-\hat \eta R^T}v , \\
+    r^T \delta R^T v &= r^T \parenth{-\hat \eta R^T}v  \\
     &= r^T \parenth{R^T v}^\wedge \eta .
@@
 \end{gather*}
-Using~\crefrange{eqn:AB_bound}{eqn:eRB_bound} one can define \( H \) in terms of known values.
+Using~\cref{eqn:AB_bound} to \cref{eqn:eRB_bound} one can define \( H \) in terms of known values.
 

### 2017-05-11 manuscript.tex

@@
 During implementation, the designer must carefully resolve this non-unique representation in quaternion based attitude control systems to avoid undesirable unwinding behavior~\cite{bhat2000}.
-This behavior is characterized by situations where the rigid body starts close to the desired attitude, yet the system unnecessarily rotates through a large angle inspite of a small initial error.
+This behavior is characterized by situations where the rigid body starts close to the desired attitude, yet the system unnecessarily rotates through a large angle in spite of a small initial error.
 
@@
 We define an inertial reference frame and a body-fixed frame, whose origin is at the center of mass and aligned with the principle directions of the body. 
+The standard orthonormal basis is denoted by \( e_i \) for \( i \in \braces{1, 2, 3} \).
 The configuration manifold of the attitude dynamics is the special orthogonal group:
@@
     \centering 
-    \subfigure[Attractive \( A(R) \) \label{fig:attract_error}]{\includegraphics[trim={8mm 0 8mm 0}, clip]{figures/attract_error.pdf}}~
-    \subfigure[Repulsive \( B(R) \) \label{fig:avoid_error} ]{\includegraphics[trim={8mm 0 8mm 0}, clip]{figures/avoid_error.pdf}}~
-    \subfigure[Combined \( \Psi \) \label{fig:combined_error}]{\includegraphics[trim={8mm 0 8mm 0}, clip]{figures/combined_error.pdf}}%
+    \subfigure[Attractive \( A(R) \) \label{fig:attract_error}]{\includegraphics[trim={8mm 2mm 8mm 2mm}, clip]{figures/attract_error.pdf}}~
+    \subfigure[Repulsive \( B(R) \) \label{fig:avoid_error} ]{\includegraphics[trim={8mm 2mm 8mm 2mm}, clip]{figures/avoid_error.pdf}}~
+    \subfigure[Combined \( \Psi \) \label{fig:combined_error}]{\includegraphics[trim={8mm 2mm 8mm 2mm}, clip]{figures/combined_error.pdf}}%
     \caption{Visualization of Configuration Error Functions using spherical coordinate representation}
@@
 
+\end{multicols}
+\begin{figure}[t]
+    \centering 
+    \subfigure[Attitude error vector \(e_R\) components \label{fig:eR_con}]{\input{pgf/eR_noadapt.pgf}}~
+    \subfigure[Configuration error \( \Psi \) \label{fig:Psi_con}]{\input{pgf/Psi_noadapt.pgf}}~
+    \subfigure[Angle to each constraint \label{fig:con_angles_con}]{\input{pgf/ang_con_noadapt.pgf}} 
+    \caption{Attitude stabilization without adaptive update law}
+    \label{fig:con} 
+\end{figure}
+\begin{multicols}{2}
 \subsection{Attitude Control without Disturbance}
@@
         \end{gather}
-
 \end{enumerate}
@@
 
-\end{multicols}
-\begin{figure}[b]
-    \centering 
-    \subfigure[Attitude error vector \(e_R\) components \label{fig:eR_con}]{\input{pgf/eR_noadapt.pgf}}~
-    \subfigure[Configuration error \( \Psi \) \label{fig:Psi_con}]{\input{pgf/Psi_noadapt.pgf}}~
-    \subfigure[Angle to each constraint \label{fig:con_angles_con}]{\input{pgf/ang_con_noadapt.pgf}} 
-    \caption{Attitude stabilization without adaptive update law}
-    \label{fig:con} 
-\end{figure}
-\begin{multicols}{2}
 \section{Numerical Examples}\label{sec:numerical_simulation}
@@
 The simulation parameters are chosen to be similar to those found in~\cite{lee2011b}, however we increase the size of the constraint regions to create a more challenging scenario for the control system.
+\vspace{-2.5mm}
 \begin{table}[H]
@@
 \end{table}
-
+\vspace{-2.5mm}
 The initial state is defined as \(R_0 =  \exp(\ang{225} \times \frac{\pi}{180} \hat{e}_3), \Omega_0 = 0\), with \( e_3 = \begin{bmatrix} 0 & 0 & 1 \end{bmatrix}^T \).
@@
     His research interests include computational geometric mechanics and control of complex systems.}
-\clearafterbiography\relax
-\clearafterbiography\relax
 

### 2017-11-25 manuscript.tex
Modify manuscript for arxiv  upload
Uses basic article class, fixes subcaption images and adds
a big header to cite the real journal paper

@@
-\documentclass{IJCAS}  % Comment this line out if you need a4paper
+\documentclass[10pt]{article}  % Comment this line out if you need a4paper
 \usepackage{ijcas_packages}
+\usepackage{fancyhdr}
+\usepackage{bibentry}
+\setlength{\headheight}{15.2pt}
+\pagestyle{fancyplain}
+\lhead[]{}
+\chead[]{}
+\rhead[]{}
+\fancyhf[C]{\color{red}{Please use citation: S. Kulumani and T. Lee, ``Constrained Attitude Control on \(\SO\),'' International Journal of Control, Automation, and Systems, vol. 15, no. 6, Dec. 2017}}
 \allowdisplaybreaks[1]
@@
 \newcommand{\squeezeup}{\vspace{-2.5mm}}
-
-%%%% Editorial Information
-%% Authors do not have to modify this section.
-\journalvolumn{VV}
-\journalnumber{N}
-\journalyear{YYYY}
-\setarticlestartpagenumber{1}
-%%%% End of Editorial Information
 
@@
 
+\title{\LARGE \textbf{Constrained Geometric Attitude Control on \( \SO \)} }
+\author{Shankar Kulumani* and Taeyoung Lee}%
+
 \begin{document}
-
-\title{\LARGE \textbf{Constrained Geometric Attitude Control on \( \SO \)} }
-
-\author{Shankar Kulumani* and Taeyoung Lee}%
+\maketitle
 
@@
 
-\begin{keywords}
-adaptive control, attitude control, constraint, obstacle, special orthogonal group
-%At least four key words or phrases in alphabetical order, separated by commas.
-\end{keywords}
-
-\maketitle % \maketitle command must come here after ABSTRACT and KEYWORDS environments
-
-\makeAuthorInformation{
-Manuscript received DATE; revised DATE; accepted DATE.
-
-Shankar Kulumani and Taeyoung Lee, Mechanical and Aerospace Engineering, George Washington University, Washington DC 20052 \texttt{ \{skulumani,tylee\}@gwu.edu}
-
-This research has been supported in part by NSF under the grants CMMI-1243000, CMMI-1335008, and CNS-1337722.\\
-* Corresponding author.\vskip 0.5pc
-}
-
-\runningtitle{2017}{Shankar Kulumani and Taeyoung Lee}{Constrained Geometric Attitude Control on \( \SO \) }
-
-\begin{multicols}{2}
 \section{Introduction}\label{sec:intro}
-
 Rigid body attitude control is an important problem for aerospace vehicles, ground and underwater vehicles, as well as robotic systems~\cite{hughes2004,wertz1978}.
@@
 Similarly, the positions of celestial objects are defined on the celestial sphere in terms of right ascension and declination. 
-\end{multicols}
-\begin{figure}[H]%
+\begin{figure}[htbp]%
     \centering 
-    \subfigure[Attractive \( A(R) \) \label{fig:attract_error}]{\includegraphics[trim={8mm 2mm 8mm 2mm}, clip]{figures/attract_error.pdf}}~
-    \subfigure[Repulsive \( B(R) \) \label{fig:avoid_error} ]{\includegraphics[trim={8mm 2mm 8mm 2mm}, clip]{figures/avoid_error.pdf}}~
-    \subfigure[Combined \( \Psi \) \label{fig:combined_error}]{\includegraphics[trim={8mm 2mm 8mm 2mm}, clip]{figures/combined_error.pdf}}%
+    \subcaptionbox{ Attractive \( A(R) \) \label{fig:attract_error} }{\includegraphics[trim={8mm 2mm 8mm 2mm}, clip, width=0.3\textwidth]{figures/attract_error.pdf}}~
+    \subcaptionbox{ Repulsive \( B(R) \) \label{fig:avoid_error} }{\includegraphics[trim={8mm 2mm 8mm 2mm}, clip, width=0.3\textwidth]{figures/avoid_error.pdf}}~
+    \subcaptionbox{ Combined \( \Psi \) \label{fig:combined_error} }{\includegraphics[trim={8mm 2mm 8mm 2mm}, clip, width=0.3\textwidth]{figures/combined_error.pdf}}%
     \caption{Visualization of Configuration Error Functions using spherical coordinate representation}
@@
 \end{figure}%
-\begin{multicols}{2}
 We apply this concept and parameterize the rotation matrix \( R \in \SO \) in terms of the spherical angles \( \SI{-180}{\degree} \leq \lambda \leq \SI{180}{\degree}  \) and \( \SI{-90}{\degree} \leq \beta \leq \SI{90}{\degree} \).
@@
 
-\end{multicols}
 \begin{figure}[t]
     \centering 
-    \subfigure[Attitude error vector \(e_R\) components \label{fig:eR_con}]{\input{pgf/eR_noadapt.pgf}}~
-    \subfigure[Configuration error \( \Psi \) \label{fig:Psi_con}]{\input{pgf/Psi_noadapt.pgf}}~
-    \subfigure[Angle to each constraint \label{fig:con_angles_con}]{\input{pgf/ang_con_noadapt.pgf}} 
+    \subcaptionbox{Attitude error vector \(e_R\) components \label{fig:eR_con}}{\input{pgf/eR_noadapt.pgf}}~
+    \subcaptionbox{Configuration error \( \Psi \) \label{fig:Psi_con}}{\input{pgf/Psi_noadapt.pgf}}~
+   \subcaptionbox{Angle to each constraint \label{fig:con_angles_con}}{\input{pgf/ang_con_noadapt.pgf}}~
     \caption{Attitude stabilization without adaptive update law}
@@
 \end{figure}
-\begin{multicols}{2}
 \subsection{Attitude Control without Disturbance}
@@
 \vspace{-2.5mm}
-\begin{table}[H]
+\begin{table}[htbp]
 \caption{Constraint Parameters~\label{tab:constraints}}
@@
 
-\end{multicols}
 \begin{figure} 
   \centering 
-  \subfigure[Configuration error \( \Psi \)\label{fig:Psi_adapt}]{\input{pgf/Psi_adapt.pgf}}~
-  \subfigure[Angle to each constraint \label{fig:con_angles}]{\input{pgf/ang_con_adapt.pgf}}\\
-  \subfigure[Disturbance estimate \( \bar \Delta \) components \label{fig:delta_adapt} ]{\input{pgf/dist_adapt.pgf}}~
-    \subfigure[Attitude trajectory \label{fig:cad_adapt}]{\includegraphics[trim={10cm 0 10cm 0},clip,width=0.4\columnwidth]{cad_adapt} }
+  \subcaptionbox{ Configuration error \( \Psi \)\label{fig:Psi_adapt} }{\input{pgf/Psi_adapt.pgf}}~
+  \subcaptionbox{ Angle to each constraint \label{fig:con_angles} }{\input{pgf/ang_con_adapt.pgf}}\\
+  \subcaptionbox{ Disturbance estimate \( \bar \Delta \) components \label{fig:delta_adapt} }{\input{pgf/dist_adapt.pgf}}~
+    \subcaptionbox{ Attitude trajectory \label{fig:cad_adapt} }{\includegraphics[trim={10cm 0 10cm 0},clip,width=0.4\columnwidth]{cad_adapt} }
   \caption{Attitude stabilization with adaptive update law}
@@
 \end{figure}
-\begin{multicols}{2}
 \subsection{Attitude Parameterizations}\label{ssec:attitude_parameterization}
@@
 \section{Experiment on Hexrotor UAV}\label{sec:experiment}
-\vspace{-5mm}
-\begin{figure}[H]
+
+\begin{figure}[htbp]
     \centering
@@
 This allows the hexrotor to impart a force in any direction and a moment about any axis. 
-\end{multicols}
-\begin{figure}[H]
+\begin{figure}[htbp]
     \centering 
-    \subfigure[{Configuration error \( \Psi \)} \label{fig:Psi_tv} ]{\input{pgf/Psi_timevarying.pgf}}~
-    \subfigure[{Angle to constraint } \label{fig:con_angle_tv}]{\input{pgf/ang_con_timevarying.pgf}}~
-    \subfigure[{Disturbance estimate \(\bar\Delta\) components} \label{fig:Delta_tv}]{\input{pgf/dist_timevarying.pgf}}
+    \subcaptionbox{ {Configuration error \( \Psi \)} \label{fig:Psi_tv} }{\input{pgf/Psi_timevarying.pgf}}~
+    \subcaptionbox{ {Angle to constraint } \label{fig:con_angle_tv} }{\input{pgf/ang_con_timevarying.pgf}}~
+    \subcaptionbox{ {Disturbance estimate \(\bar\Delta\) components} \label{fig:Delta_tv} }{\input{pgf/dist_timevarying.pgf}}
     \caption{Time-varying external disturbance simulation}
@@
     \centering 
-    \subfigure[{Attitude error vector \(e_R\)} components\label{fig:eR_exp}]{\input{pgf/eR_exp.pgf}}~
-    \subfigure[{Configuration error \( \Psi \)} \label{fig:Psi_exp} ]{\input{pgf/Psi_exp.pgf}}~
-    \subfigure[{Control input \( u\) } components\label{fig:u_exp}]{\input{pgf/u_exp.pgf}}\\
-    \subfigure[{Attitude Trajectory } \label{fig:traj_exp}]{\includegraphics[width=0.3\columnwidth]{traj_exp} }~
-    \subfigure[{Angle to constraint } \label{fig:con_angle_exp}]{\input{pgf/ang_con_exp.pgf}}
+    \subcaptionbox{ {Attitude error vector \(e_R\)} components\label{fig:eR_exp} }{\input{pgf/eR_exp.pgf}}~
+    \subcaptionbox{ {Configuration error \( \Psi \)} \label{fig:Psi_exp} }{\input{pgf/Psi_exp.pgf}}~
+    \subcaptionbox{ {Control input \( u\) } components\label{fig:u_exp} }{\input{pgf/u_exp.pgf}}\\
+    \subcaptionbox{ {Attitude Trajectory } \label{fig:traj_exp} }{\includegraphics[width=0.3\columnwidth]{traj_exp} }~
+    \subcaptionbox{ {Angle to constraint } \label{fig:con_angle_exp} }{\input{pgf/ang_con_exp.pgf}}
     \caption{Constrained Attitude stabilization experiment}
@@
 \end{figure}
-\begin{multicols}{2}
 Attitude information is measured by a combination of both on and off board sensor systems.
@@
 \bibliographystyle{IEEEtran}
-\biography{profile}{Shankar Kulumani}
-    {is a PhD Candidate in the Department of Mechanical and Aerospace Engineering at George Washington University. 
-    He received his bachelor's degree in Astronautical Engineering from the US Air Force Academy in 2009 and his master's degree in Aeronautical and Astronautical Engineering from Purdue University in 2013.
-    % He previously served as Deputy Space Vehicles Lead for the ORS-1 (Operationally Responsive Space ) satellite program, and as Lead Test Engineer in the Guidance, Navigation, and Control group at Air Force Research Laboratory located at Kirtland AFB, NM.
-    % He is now currently a reserve air force officer where he serves as Threat Systems Engineer for the Missle and Space Intelligence Center, Defense Intelligence Agency.
-    His current research interests include the application of geometric mechanics and control to aerospace systems. 
-    }
-\biography{Lee}{Taeyoung Lee}
-    {is an associate professor of Department of Mechanical and Aerospace Engineering at the George Washington University. 
-    He received his doctoral degree in Aerospace Engineering and his master's degree in Mathematics at the University of Michigan in 2008. 
-    His research interests include computational geometric mechanics and control of complex systems.}
-
-\end{multicols}
 
